### 2018-05-31 article_code.Rmd
added the code

---
title: "R Notebook"
output: html_notebook
---

# the project is in Dropbox/coding/cosimulation

```{r}
source("C:/Users/tl3315/Dropbox/coding/cosimulation/co_sim_condi.R")
source("C:/Users/tl3315/Dropbox/coding/cosimulation/cosim_functions.R")
```
```{r}
library(mvtnorm)
library(abind)
```

```{r}
e1<-e2<-e3<-e4<-d1<-d2<-d3<-matrix(0,nz,4)
e1[env_lat==1]=1
e2[env_lat==2]=1
e3[env_lat==3]=1
e4[env_lat==4]=1
d1[diag_lat==1]=1
d2[diag_lat==2]=1
d3[diag_lat==3]=1
e1[is.na(env_lat)]=e2[is.na(env_lat)]=e3[is.na(env_lat)]=e4[is.na(env_lat)]=NA
d1[is.na(diag_lat)]=d2[is.na(diag_lat)]=d3[is.na(diag_lat)]=NA
```
```{r}
pe1 = mean(e1,na.rm=TRUE)
pe2 = mean(e2,na.rm=TRUE)
pe3 = mean(e3,na.rm=TRUE)
pe4 = mean(e4,na.rm=TRUE)
c(pe1,pe2,pe3,pe4)
pd1=mean(d1,na.rm=TRUE)
pd2=mean(d2,na.rm=TRUE)
pd3=mean(d3,na.rm=TRUE)
c(pd1,pd2,pd3)
pd1e1=mean(d1*e1,na.rm=TRUE)/pe1
pd1e2=mean(d1*e2,na.rm=TRUE)/pe2
pd1e3=mean(d1*e3,na.rm=TRUE)/pe3
pd1e4=mean(d1*e4,na.rm=TRUE)/pe4

pd2e1=mean(d2*e1,na.rm=TRUE)/pe1
pd2e2=mean(d2*e2,na.rm=TRUE)/pe2
pd2e3=mean(d2*e3,na.rm=TRUE)/pe3
pd2e4=mean(d2*e4,na.rm=TRUE)/pe4

pd3e1=mean(d3*e1,na.rm=TRUE)/pe1
pd3e2=mean(d3*e2,na.rm=TRUE)/pe2
pd3e3=mean(d3*e3,na.rm=TRUE)/pe3
pd3e4=mean(d3*e4,na.rm=TRUE)/pe4

matrix(c(pd1e1,pd1e2,pd1e3,pd1e4,pd2e1,pd2e2,pd2e3,pd2e4,pd3e1,pd3e2,pd3e3,pd3e4),3,4,byrow=TRUE)
pe1+pe2+pe3+pe4
```

```{r}
env_lat[is.na(env_lat)]=0 # with 0, the gibbs sampler will find random values
diag_lat[is.na(diag_lat)]=0
grid<-grid_co<-array(NA,c(100,10,91))
grid[5,8,]<-env_lat[,1]
grid[25,6,]<-env_lat[,2]
grid[35,3,]<-env_lat[,3]
grid[95,7,]<-env_lat[,4]
grid_co[5,8,]<-diag_lat[,1]
grid_co[25,6,]<-diag_lat[,2]
grid_co[35,3,]<-diag_lat[,3]
grid_co[95,7,]<-diag_lat[,4]

```
ok we also want to display an image with all the logs
we are doubling the wells for a better visualization
```{r}
im<-matrix(NA,100,91)
im[5,]<-env_lat[,1]
im[4,]<-env_lat[,1]
im[25,]<-env_lat[,2]
im[24,]<-env_lat[,2]
im[35,]<-env_lat[,3]
im[34,]<-env_lat[,3]
im[95,]<-env_lat[,4]
im[94,]<-env_lat[,4]
image(x=(1:100)*9.2,y=(1:91)/10,z=im,col=c("lightgreen","dodgerblue4","darkmagenta","red"),xlab="Lateral distance (m)",ylab="Vertical distance (m)")
```
print image
```{r}
png(file="logslate.png",width=4000,height = 2500,res=300,antialias = )
image(x=(1:100)*9.2,y=(1:91)/10,z=im,col=c("lightgreen","dodgerblue4","darkmagenta","red"),xlab="Lateral distance (m)",ylab="Vertical distance (m)")
```
we also want to display the environment of depositions and the diagenesis
```{r}
im<-matrix(NA,100,91)
im[5,]<-diag_lat[,1]+4
im[4,]<-diag_lat[,1]+4
im[8,]<-env_lat[,1]
im[7,]<-env_lat[,1]
im[25,]<-diag_lat[,2]+4
im[24,]<-diag_lat[,2]+4
im[28,]<-env_lat[,2]
im[27,]<-env_lat[,2]
im[35,]<-diag_lat[,3]+4
im[34,]<-diag_lat[,3]+4
im[38,]<-env_lat[,3]
im[37,]<-env_lat[,3]
im[95,]<-diag_lat[,4]+4
im[94,]<-diag_lat[,4]+4
im[98,]<-env_lat[,4]
im[97,]<-env_lat[,4]
image(x=(1:100)*9.2,y=(1:91)/10,z=im,col=c("lightgreen","dodgerblue4","darkmagenta","red","black","grey","yellow"),xlab="Lateral distance (m)",ylab="Vertical distance (m)")
```
```{r}
png(file="logslatediag2.png",width=4000,height = 2500,res=300,antialias = )
image(x=(1:100)*9.2,y=(1:91)/10,z=im,col=c("lightgreen","dodgerblue4","darkmagenta","red","black","grey","yellow"),ylab="Vertical distance (m)",xlab = "Lateral distance (m)")
```

```{r}
grid2<-grid_co2<-array(NA,c(100,10,182))
i=1
for (j in 1:182){

    grid2[5,8,j]<-env_lat[i,1]
    grid2[25,6,j]<-env_lat[i,2]
    grid2[35,3,j]<-env_lat[i,3]
    grid2[95,7,j]<-env_lat[i,4]
    grid_co2[5,8,j]<-diag_lat[i,1]
    grid_co2[25,6,j]<-diag_lat[i,2]
    grid_co2[35,3,j]<-diag_lat[i,3]
    grid_co2[95,7,j]<-diag_lat[i,4]
    if(j%%2==0){i=i+1}
}
```

the first figure we want to have is a 3d simulation of the Latemar conditioned ! 
```{r}
rv1=0.3
rv2=1.2
rhx1=rhy1=800
rhx2=rhy2=800
b1=0
b2=5
rho=0.6
shift=0.1
rho1a<-model(shift,rv1,b1)
warning(rho>rho1a)
alpha1=(rho/rho1a)^2
alpha2=1-(rho/rho1a)^2
rv3=0.2
rv4=0.3
rhx3=rhy3=800
rhx4=rhy4=800
b3=0
b4=0
e=-0.8
f=-0.5
a14=-0.1
a24=0.1
rho1a14 = model(a14,rv1,b1)
rho2a24=model(a24,rv2,b2)

#thresholds
q1=qnorm(pe1+pe2)
Sigma1 = matrix(c(1,rho,rho,1),2,2)
q2=0
obj = Inf
for ( test in 1:100 ){
  q2test = qnorm(test/100)
  newobj =abs( pmvnorm(lower=c(-Inf,-Inf),upper=c(q1,q2test),mean=c(0,0),sigma=Sigma1) - pe1 ) 
  if (newobj < obj){
    q2 = q2test
    obj = newobj
  }
}
q3=0
obj = Inf
for ( test in 1:100 ){
  q3test = qnorm(test/100)
  newobj =abs( pmvnorm(lower=c(q1,-Inf),upper=c(Inf,q3test),mean=c(0,0),sigma=Sigma1) - pe4 ) 
  if (newobj < obj){
    q3 = q3test
    obj = newobj
  }
}
c(q1,q2,q3)
qd1e4=qnorm(pd3e4) # no correlation with the third Gaussian function
Sigmad = diag(1,3)
qd2e2=0
qd2e3=0
obje2 = Inf
obje3 = Inf
for ( test in 1:100 ){
  qd2e2test = qnorm(test/100)
  qd2e3test = qnorm(test/100)
  Sigmad[1,2]=Sigmad[2,1]=e*rho1a14
  Sigmad[1,3]=Sigmad[3,1]=e*(rho/rho1a)*model(a14-shift,rv1,b1)+f*sqrt(1-(rho/rho1a)^2)*model(a24,rv2,b2)
  Sigmad[2,3]=Sigmad[3,2]=rho
  newobje2 =abs( pmvnorm(lower=c(qd2e2test,-Inf,q2),upper=c(Inf,q1,Inf),mean=c(0,0,0),sigma=Sigmad)/pe2 - pd2e2 ) 
  newobje3 =abs( pmvnorm(lower=c(qd2e3test,q1,q3),upper=c(Inf,Inf,Inf),mean=c(0,0,0),sigma=Sigmad)/pe3 - pd2e3 )
  if (newobje2 < obje2){
    qd2e2 = qd2e2test
    obje2 = newobje2
  }
  if (newobje3 < obje3){
    qd2e3 = qd2e3test
    obje3 = newobje3
  }
}
c(qd1e4,qd2e2,qd2e3)

Y1<-sim3d(rv1,rhx1,rhy1,b1,100,0.1,91,10,100,25,10)
Y2<-sim3d(rv2,rhx2,rhy2,b2,100,0.1,91,10,100,25,10)
Y3<-sim3d(rv3,rhx3,rhy3,b3,100,0.1,91,10,100,25,10)
Y4<-sim3d(rv4,rhx4,rhy4,b4,100,0.1,91,10,100,25,10)

simwell<-gibbs_sampling3d(grid,grid_co,c(q1,q2,q3),c(qd1e4,qd2e2,qd2e3),0.1,10,25,c(rv1,rv2,rv3,rv4),c(rhx1,rhx2,rhx3,rhx4),c(rhy1,rhy2,rhy3,rhy4),c(b1,b2,b3,b4),c(rho,e*model(a14,rv1,b1),f*model(a24,rv2,b2)),c(shift,a14,a24),50)
Y1well<-simwell[,,1:91]
Y2well<-Z2well<-simwell[,,92:182]
Y3well<-simwell[,,183:273]
Y4well<-Z4well<-simwell[,,274:364]

# back transformation of the Zi into Yi at the wells
for( z in 2:90){
  Y2well[,,z]=(Z2well[,,z]-(rho/rho1a)*Y1well[,,z+1])/sqrt(1-(rho^2)/(rho1a^2))
  Y4well[,,z]=(Z4well[,,z]-Y1well[,,z-1]*e-f*Y2well[,,z+1])/sqrt(1-(e^2)-(f^2))
}

Z1c =Y1 + dual_krig_surf(Y1well-Y1,rhx1,rhy1,10,25)
Z2c<-Y2c<-Y2 +dual_krig_surf(Y2well-Y2,rhx2,rhy2,10,25)
Z3c<-Y3 +dual_krig_surf(Y3well-Y3,rhx3,rhy3,10,25)
Z4c<-Y4c<-Y4 +dual_krig_surf(Y4well-Y4,rhx4,rhy4,10,25)

for( z in 2:90){
  Z2c[,,z]=Y2c[,,z]*sqrt(1-(rho^2)/(rho1a^2))+Z1c[,,z+1]*(rho)/(rho1a)
  Z4c[,,z]=Y4c[,,z]*sqrt(1-(e^2)-(f^2))+Z1c[,,z-1]*e+f*Y2c[,,z+1]
}

faciesenv<-faciesdiag<-Z1c
faciesenv[Z1c<q1 & Z2c<q2]=1
faciesenv[Z1c<q1 & Z2c>q2]=2
faciesenv[Z1c>q1 & Z2c<q3]=4
faciesenv[Z1c>q1 & Z2c>q3]=3
faciesdiag[]=1
faciesdiag[Z1c>q1 & Z2c<q3 & Z3c<qd1e4]=3
faciesdiag[Z1c<q1 & Z2c>q2 & Z4c>qd2e2]=2
faciesdiag[Z1c>q1 & Z2c>q3 & Z4c>qd2e3]=2
col_env <- c("lightgreen","cadetblue","dodgerblue4","lightcoral")
griddata<-grid
griddata[griddata==0]=NA
W<-image(griddata[,2,],col = col_env)
W<-image(faciesenv[,2,],col = col_env)

```

```{r}
for ( z in 1:91){
  for ( y in 1:10){
    for ( x in 1:100){
      write(toString(c(faciesenv[x,y,z])),"latemarcondenv.csv",append=TRUE)
      write(toString(c(faciesdiag[x,y,z])),"latemarconddiag.csv",append=TRUE)
    }
  }
}
```
another simu with only three Gaussian functions
(verifier le gibbs sampling pour la nouvelle truncation rule)

```{r}
library(mvtnorm)
```
```{r}
source("co_sim_condi.R")
```

```{r}
par(bg="transparent")
rv1=0.3
rv2=1.2
rhx1=rhy1=800
rhx2=rhy2=800
b1=0
b2=5
rho=0.6
shift=0.1
rho1a<-model(shift,rv1,b1)
warning(rho>rho1a)
alpha1=(rho/rho1a)^2
alpha2=1-(rho/rho1a)^2
rv3=0.2
rv4=0.3
rhx3=rhy3=800
rhx4=rhy4=800
b3=0
b4=0
e=-0.8
f=-0.5
a14=-0.1
a24=0.1
rho1a14 = model(a14,rv1,b1)
rho2a24=model(a24,rv2,b2)

#thresholds
q1=qnorm(pe1+pe2)
Sigma1 = matrix(c(1,rho,rho,1),2,2)
q2=0
obj = Inf
for ( test in 1:100 ){
  q2test = qnorm(test/100)
  newobj =abs( pmvnorm(lower=c(-Inf,-Inf),upper=c(q1,q2test),mean=c(0,0),sigma=Sigma1) - pe1 ) 
  if (newobj < obj){
    q2 = q2test
    obj = newobj
  }
}
q3=0
obj = Inf
for ( test in 1:100 ){
  q3test = qnorm(test/100)
  newobj =abs( pmvnorm(lower=c(q1,-Inf),upper=c(Inf,q3test),mean=c(0,0),sigma=Sigma1) - pe4 ) 
  if (newobj < obj){
    q3 = q3test
    obj = newobj
  }
}
c(q1,q2,q3)

Sigmad = diag(1,3)
qd2e2=0
qd2e3=0
qd1e4=0
obje2 = Inf
obje3 = Inf
obje4 = Inf
for ( test in 1:100 ){
  qd2e2test = qnorm(test/100)
  qd2e3test = qnorm(test/100)
  qd1e4test = qnorm(test/100)
  Sigmad[1,2]=Sigmad[2,1]=e*rho1a14
  Sigmad[1,3]=Sigmad[3,1]=e*(rho/rho1a)*model(a14-shift,rv1,b1)+f*sqrt(1-(rho/rho1a)^2)*model(a24,rv2,b2)
  Sigmad[2,3]=Sigmad[3,2]=rho
  newobje2 =abs( pmvnorm(lower=c(qd2e2test,-Inf,q2),upper=c(Inf,q1,Inf),mean=c(0,0,0),sigma=Sigmad)/pe2 - pd2e2 ) 
  newobje3 =abs( pmvnorm(lower=c(qd2e3test,q1,q3),upper=c(Inf,Inf,Inf),mean=c(0,0,0),sigma=Sigmad)/pe3 - pd2e3 )
  newobje4 =abs( pmvnorm(lower=c(qd1e4test,q1,-Inf),upper=c(Inf,Inf,q3),mean=c(0,0,0),sigma=Sigmad)/pe4 - pd3e4 )
  if (newobje2 < obje2){
    qd2e2 = qd2e2test
    obje2 = newobje2
  }
  if (newobje3 < obje3){
    qd2e3 = qd2e3test
    obje3 = newobje3
  }
  if (newobje4 < obje4){
    qd1e4 = qd1e4test
    obje4 = newobje4
  }
}

c(qd1e4,qd2e2,qd2e3)
# here Y4 is not used
Y1<-sim3d(rv1,rhx1,rhy1,b1,100,0.05,182,10,100,25,10)
Y2<-sim3d(rv2,rhx2,rhy2,b2,100,0.05,182,10,100,25,10)
Y3<-sim3d(rv3,rhx3,rhy3,b3,100,0.05,182,10,100,25,10)
Y4<-sim3d(rv4,rhx4,rhy4,b4,100,0.05,182,10,100,25,10)
#careful to check that we put 0 to extend the gibbs sampling to where there is no data
simwell<-gibbs_sampling3d(grid2,grid_co2,c(q1,q2,q3),c(qd1e4,qd2e2,qd2e3),0.05,10,25,c(rv1,rv2,rv3,rv4),c(rhx1,rhx2,rhx3,rhx4),c(rhy1,rhy2,rhy3,rhy4),c(b1,b2,b3,b4),c(rho,e*model(a14,rv1,b1),f*model(a24,rv2,b2)),c(shift,a14,a24),50)
Y1well<-simwell[,,1:182]
Y2well<-Z2well<-simwell[,,183:364]
Y3well<-simwell[,,365:546]
Y4well<-Z4well<-simwell[,,547:728]

# back transformation of the Zi into Yi at the wells
# be VERY CAREFUL, we cannot put Y4 and Y2 in the same loop
for( z in 3:180){
  Y2well[,,z]=(Z2well[,,z]-(rho/rho1a)*Y1well[,,z+2])/sqrt(1-(rho^2)/(rho1a^2))
}
for( z in 3:180){
  Y4well[,,z]=(Z4well[,,z]-Y1well[,,z-2]*e-f*Y2well[,,z+2])/sqrt(1-(e^2)-(f^2))
}

Z1c =Y1 + dual_krig_surf(Y1well-Y1,rhx1,rhy1,10,25)
Z2c<-Y2c<-Y2 +dual_krig_surf(Y2well-Y2,rhx2,rhy2,10,25)
Z3c<-Y3 +dual_krig_surf(Y3well-Y3,rhx3,rhy3,10,25)
Z4c<-Y4c<-Y4 +dual_krig_surf(Y4well-Y4,rhx4,rhy4,10,25)

for( z in 3:180){
  Z2c[,,z]=Y2c[,,z]*sqrt(1-(rho^2)/(rho1a^2))+Z1c[,,z+2]*(rho)/(rho1a)
}
for( z in 3:180){
  Z4c[,,z]=Y4c[,,z]*sqrt(1-(e^2)-(f^2))+Z1c[,,z-2]*e+f*Y2c[,,z+2]
}

faciesenv<-faciesdiag<-Z1c
faciesenv[Z1c<q1 & Z2c<q2]=1
faciesenv[Z1c<q1 & Z2c>q2]=2
faciesenv[Z1c>q1 & Z2c<q3]=4
faciesenv[Z1c>q1 & Z2c>q3]=3
faciesdiag[]=1
faciesdiag[Z1c>q1 & Z2c<q3 & Z4c>qd1e4]=3
faciesdiag[Z1c<q1 & Z2c>q2 & Z4c>qd2e2]=2
faciesdiag[Z1c>q1 & Z2c>q3 & Z4c>qd2e3]=2
col_env <- c("lightgreen","cadetblue","dodgerblue4","lightcoral")
griddata<-grid2
griddata[griddata==0]=NA
W<-image(griddata[,8,],col = col_env)
W<-image(faciesenv[,8,],col = col_env)
W<-image(grid_co2[,8,])
W<-image(faciesdiag[,8,])
```
computing transiograms on the realization
```{r}
i1real<-i2real<-i3real<-i4real<-faciesenv
i1real[faciesenv!=1]=0
i2real[faciesenv==2]=1
i2real[faciesenv!=2]=0
i3real[faciesenv==3]=1
i3real[faciesenv!=3]=0
i4real[faciesenv==4]=1
i4real[faciesenv!=4]=0
t11real3=tr_3d_vert(i1real,i1real,60)
t12real3=tr_3d_vert(i1real,i2real,60)
t13real3=tr_3d_vert(i1real,i3real,60)
t14real3=tr_3d_vert(i1real,i4real,60)
t21real3=tr_3d_vert(i2real,i1real,60)
t22real3=tr_3d_vert(i2real,i2real,60)
t23real3=tr_3d_vert(i2real,i3real,60)
t24real3=tr_3d_vert(i2real,i4real,60)
t31real3=tr_3d_vert(i3real,i1real,60)
t32real3=tr_3d_vert(i3real,i2real,60)
t33real3=tr_3d_vert(i3real,i3real,60)
t34real3=tr_3d_vert(i3real,i4real,60)
t41real3=tr_3d_vert(i4real,i1real,60)
t42real3=tr_3d_vert(i4real,i2real,60)
t43real3=tr_3d_vert(i4real,i3real,60)
t44real3=tr_3d_vert(i4real,i4real,60)

z = (1:60)/20.
png(file="laterealtransio.png",width=2000,height = 1600,res=300)
par(mar=c(2,3,1,1),mfrow=c(4,4))
plot(z,t11real)
title(main=expression(paste('t'[e1e1],"(h)")),line=-1)
plot(z,t12real)
title(main=expression(paste('t'[e1e2],"(h)")),line=-1)
plot(z,t13real)
title(main=expression(paste('t'[e1e3],"(h)")),line=-1)
plot(z,t14real)
title(main=expression(paste('t'[e1e4],"(h)")),line=-1)
plot(z,t21real)
title(main=expression(paste('t'[e2e1],"(h)")),line=-1)
plot(z,t22real)
title(main=expression(paste('t'[e2e2],"(h)")),line=-1)
plot(z,t23real)
title(main=expression(paste('t'[e2e3],"(h)")),line=-1)
plot(z,t24real)
title(main=expression(paste('t'[e2e4],"(h)")),line=-1)
plot(z,t31real)
title(main=expression(paste('t'[e3e1],"(h)")),line=-1)
plot(z,t32real)
title(main=expression(paste('t'[e3e2],"(h)")),line=-1)
plot(z,t33real)
title(main=expression(paste('t'[e3e3],"(h)")),line=-1)
plot(z,t34real)
title(main=expression(paste('t'[e3e4],"(h)")),line=-1)
plot(z,t41real)
title(main=expression(paste('t'[e4e1],"(h)")),line=-1)
plot(z,t42real)
title(main=expression(paste('t'[e4e2],"(h)")),line=-1)
plot(z,t43real)
title(main=expression(paste('t'[e4e3],"(h)")),line=-1)
plot(z,t44real)
title(main=expression(paste('t'[e4e4],"(h)")),line=-1)
```
average
```{r}
t11reals=(t11real+t11real2+t11real3)/3
t12reals=(t12real+t12real2+t12real3)/3
t13reals=(t13real+t13real2+t13real3)/3
t14reals=(t14real+t14real2+t14real3)/3
t21reals=(t21real+t21real2+t21real3)/3
t22reals=(t22real+t22real2+t22real3)/3
t23reals=(t23real+t23real2+t23real3)/3
t24reals=(t24real+t24real2+t24real3)/3
t31reals=(t31real+t31real2+t31real3)/3
t32reals=(t32real+t32real2+t32real3)/3
t33reals=(t33real+t33real2+t33real3)/3
t34reals=(t34real+t34real2+t34real3)/3
t41reals=(t41real+t41real2+t41real3)/3
t42reals=(t42real+t42real2+t42real3)/3
t43reals=(t43real+t43real2+t43real3)/3
t44reals=(t44real+t44real2+t44real3)/3
```
and also with the diagenetic facies
```{r}
d1real<-d2real<-d3real<-faciesdiag
d1real[faciesdiag!=1]=0
d2real[faciesdiag==2]=1
d2real[faciesdiag!=2]=0
d3real[faciesdiag==3]=1
d3real[faciesdiag!=3]=0
td3e1real3=tr_3d_vert(d3real,i1real,60)
td3e2real3=tr_3d_vert(d3real,i2real,60)
td3e3real3=tr_3d_vert(d3real,i3real,60)
td3e4real3=tr_3d_vert(d3real,i4real,60)
td2e1real3=tr_3d_vert(d2real,i1real,60)
td2e2real3=tr_3d_vert(d2real,i2real,60)
td2e3real3=tr_3d_vert(d2real,i3real,60)
td2e4real3=tr_3d_vert(d2real,i4real,60)
td3d3real3=tr_3d_vert(d3real,d3real,60)
td2d3real3=tr_3d_vert(d2real,d3real,60)
td3d2real3=tr_3d_vert(d3real,d2real,60)
td2d2real3=tr_3d_vert(d2real,d2real,60)

```

```{r}
for ( z in 1:182){
  for ( y in 1:10){
    for ( x in 1:100){
      write(toString(c(faciesenv[x,y,z])),"latemarcondenvres6.csv",append=TRUE)
      write(toString(c(faciesdiag[x,y,z])),"latemarconddiagres.csv",append=TRUE)
    }
  }
}
```
we can also combine the environment and the diagenesis in a single model
```{r}
combined<-faciesenv
combined[faciesdiag==2]=5
combined[faciesdiag==3]=6
for ( z in 1:182){
  for ( y in 1:10){
    for ( x in 1:100){
      write(toString(c(combined[x,y,z])),"latemarcombined4.csv",append=TRUE)
    }
  }
}
```

we also want to enter the data ! 
```{r}
griddata<-grid
griddata[griddata==0]=NA
gridcodata<-grid_co
gridcodata[gridcodata==0]=NA

for ( z in 1:91){
  for ( y in 1:10){
    for ( x in 1:100){
      write(toString(c(griddata[x,y,z])),"dataenv.csv",append=TRUE)
      write(toString(c(gridcodata[x,y,z])),"datadiag.csv",append=TRUE)
    }
  }
}
```
data with all facies
```{r}
griddata<-grid
griddata[griddata==0]=NA
gridcodata<-grid_co
gridcodata[gridcodata==0]=NA
combineddata<-griddata
combineddata[gridcodata==2]=5
combineddata[gridcodata==3]=6
for ( z in 1:91){
  for ( y in 1:10){
    for ( x in 1:100){
      write(toString(c(combineddata[x,y,z])),"latemarcombineddata.csv",append=TRUE)
    }
  }
}
```
let s compute the embedded transitions of one realization
```{r}
i1real<-i2real<-i3real<-i4real<-faciesenv
i1real[faciesenv!=1]=0
i2real[faciesenv==2]=1
i2real[faciesenv!=2]=0
i3real[faciesenv==3]=1
i3real[faciesenv!=3]=0
i4real[faciesenv==4]=1
i4real[faciesenv!=4]=0
r12=embedded3d(i1real,i2real)
r13=embedded3d(i1real,i3real)
r14=embedded3d(i1real,i4real)
r21=embedded3d(i2real,i1real)
r23=embedded3d(i2real,i3real)
r24=embedded3d(i2real,i4real)
r31=embedded3d(i3real,i1real)
r32=embedded3d(i3real,i2real)
r34=embedded3d(i3real,i4real)
r41=embedded3d(i4real,i1real)
r42=embedded3d(i4real,i2real)
r43=embedded3d(i4real,i3real)
matrix(c(0,r12,r13,r14,r21,0,r23,r24,r31,r32,0,r34,r41,r42,r43,0),4,4,byrow=TRUE)
```
```{r}
real7<-matrix(c(0,r12,r13,r14,r21,0,r23,r24,r31,r32,0,r34,r41,r42,r43,0),4,4,byrow=TRUE)
```
```{r}
(real1+real2+real3+real4+real5+real6)/6
```

and the data
```{r}
r12d=embedded2d(e1,e2)
r13d=embedded2d(e1,e3)
r14d=embedded2d(e1,e4)
s1=r12d+r13d+r14d
r21d=embedded2d(e2,e1)
r23d=embedded2d(e2,e3)
r24d=embedded2d(e2,e4)
s2=r21d+r23d+r24d
r31d=embedded2d(e3,e1)
r32d=embedded2d(e3,e2)
r34d=embedded2d(e3,e4)
s3=r31d+r32d+r34d
r41d=embedded2d(e4,e1)
r42d=embedded2d(e4,e2)
r43d=embedded2d(e4,e3)
s4=r41d+r42d+r43d
matrix(c(0,r12d/s1,r13d/s1,r14d/s1,r21d/s2,0,r23d/s2,r24d/s2,r31d/s3,r32d/s3,0,r34d/s3,r41d/s4,r42d/s4,r43d/s4,0),4,4,byrow=TRUE)
```

ok it is also necessary to compute the transiograms on the final model
```{r}
real1<-real2<-real3<-real4<-faciesenv
real1[faciesenv!=1]=0
real2[faciesenv==2]=1
real2[faciesenv!=2]=0
real3[faciesenv==3]=1
real3[faciesenv!=3]=0
real4[faciesenv==4]=1
real4[faciesenv!=4]=0
t11real<-tr_3d_vert(real1,real1,50)
t12real<-tr_3d_vert(real1,real2,50)
t13real<-tr_3d_vert(real1,real3,50)
t14real<-tr_3d_vert(real1,real4,50)
t21real<-tr_3d_vert(real2,real1,50)
t22real<-tr_3d_vert(real2,real2,50)
t23real<-tr_3d_vert(real2,real3,50)
t24real<-tr_3d_vert(real2,real4,50)
t31real<-tr_3d_vert(real3,real1,50)
t32real<-tr_3d_vert(real3,real2,50)
t33real<-tr_3d_vert(real3,real3,50)
t34real<-tr_3d_vert(real3,real4,50)
t41real<-tr_3d_vert(real4,real1,50)
t42real<-tr_3d_vert(real4,real2,50)
t43real<-tr_3d_vert(real4,real3,50)
t44real<-tr_3d_vert(real4,real4,50)
par(mfrow=c(4,4))
plot(50,t11real)
plot(length(t44real),t12real)
plot(length(t44real),t13real)
plot(length(t44real),t14real)
plot(length(t44real),t21real)
plot(length(t44real),t22real)
plot(length(t44real),t23real)
plot(length(t44real),t24real)
plot(length(t44real),t31real)
plot(length(t44real),t32real)
plot(length(t44real),t33real)
plot(length(t44real),t34real)
plot(length(t44real),t41real)
plot(length(t44real),t42real)
plot(length(t44real),t43real)
plot(length(t44real),t44real)
```

ok now that we have looked at the case study of the Latemar, 
we also want to create synthetic examples with a simpler parameter space. 
So we have only two Gaussian functions with two truncation rules, so it is like two TGS!

```{r}
model<-function(h,range,b){return(exp(-abs(h/range)^2)*cos(b*h) )}
```
```{r}
library(mvtnorm)
```

```{r}

# set of parameters 
pe1=0.5
pe2=1-pe1
pe1d1=0.0
pe2d1=0.3
rv1=0.3
rv2=1
rhx1=40
rhx2=10
b1=0
b2=0
a=0.9
shift=0.1
rho1a<-model(shift,rv1,b1)

#thresholds
q1=qnorm(pe1) # threshold for environment of deposition

q2e1=q2e2=0 # two thresholds for diagenetic facies 
Sigma = matrix(c(1,a*rho1a,a*rho1a,1),2,2)
obj1=obj2=Inf
for ( test in 1:100 ){
  q2e1test = qnorm(test/100)
  q2e2test = qnorm(test/100)
  newobj1 =abs( pmvnorm(lower=c(-Inf,-Inf),upper=c(q1,q2e1test),mean=c(0,0),sigma=Sigma)/pe1 - pe1d1) 
  newobj2 =abs( pmvnorm(lower=c(q1,-Inf),upper=c(Inf,q2e2test),mean=c(0,0),sigma=Sigma)/pe2 - pe2d1)
  if (newobj1 < obj1){
    q2e1= q2e1test
    obj1 = newobj1
  }
  if (newobj2 < obj2){
    q2e2= q2e2test
    obj2 = newobj2
  }
}

#transiograms
te1d1=te2d1=te1d2=te2d2=rep(0,300)
te1d1opp=te2d1opp=te1d2opp=te2d2opp=rep(0,300)
Sigma = diag(1,3)
Sigma[3,2]=Sigma[2,3]=a*rho1a
Sigmaopp = Sigma

for (i in 1:300){
    d = i/100.
    Sigma[1,2]=Sigma[2,1]= model(d,rv1,b1)
    Sigma[1,3]=Sigma[3,1]=a*model(d+shift,rv1,b1)

    Sigmaopp[1,2]=Sigmaopp[2,1]= model(-d,rv1,b1)
    Sigmaopp[1,3]=Sigmaopp[3,1]=a*model(-d+shift,rv1,b1)

    te1d1[i]=(pmvnorm(lower=c(-Inf,-Inf,-Inf),upper=c(q1,q1,q2e1),mean=c(0,0,0),sigma=Sigma) + pmvnorm(lower=c(-Inf,q1,-Inf),upper=c(q1,Inf,q2e2),mean=c(0,0,0),sigma=Sigma))/ pe1
    te2d1[i]=(pmvnorm(lower=c(q1,-Inf,-Inf),upper=c(Inf,q1,q2e1),mean=c(0,0,0),sigma=Sigma) + pmvnorm(lower=c(q1,q1,-Inf),upper=c(Inf,Inf,q2e2),mean=c(0,0,0),sigma=Sigma))/ pe2
    te1d2[i]=(pmvnorm(lower=c(-Inf,-Inf,q2e1),upper=c(q1,q1,Inf),mean=c(0,0,0),sigma=Sigma) + pmvnorm(lower=c(-Inf,q1,q2e2),upper=c(q1,Inf,Inf),mean=c(0,0,0),sigma=Sigma))/ pe1
    te2d2[i]=(pmvnorm(lower=c(q1,-Inf,q2e1),upper=c(Inf,q1,Inf),mean=c(0,0,0),sigma=Sigma) + pmvnorm(lower=c(q1,q1,q2e2),upper=c(Inf,Inf,Inf),mean=c(0,0,0),sigma=Sigma))/ pe2

    te1d1opp[i]=(pmvnorm(lower=c(-Inf,-Inf,-Inf),upper=c(q1,q1,q2e1),mean=c(0,0,0),sigma=Sigmaopp) + pmvnorm(lower=c(-Inf,q1,-Inf),upper=c(q1,Inf,q2e2),mean=c(0,0,0),sigma=Sigma))/ pe1
    te2d1opp[i]=(pmvnorm(lower=c(q1,-Inf,-Inf),upper=c(Inf,q1,q2e1),mean=c(0,0,0),sigma=Sigmaopp) + pmvnorm(lower=c(q1,q1,-Inf),upper=c(Inf,Inf,q2e2),mean=c(0,0,0),sigma=Sigma))/ pe2
    te1d2opp[i]=(pmvnorm(lower=c(-Inf,-Inf,q2e1),upper=c(q1,q1,Inf),mean=c(0,0,0),sigma=Sigmaopp) + pmvnorm(lower=c(-Inf,q1,q2e2),upper=c(q1,Inf,Inf),mean=c(0,0,0),sigma=Sigma))/ pe1
    te2d2opp[i]=(pmvnorm(lower=c(q1,-Inf,q2e1),upper=c(Inf,q1,Inf),mean=c(0,0,0),sigma=Sigmaopp) + pmvnorm(lower=c(q1,q1,q2e2),upper=c(Inf,Inf,Inf),mean=c(0,0,0),sigma=Sigma))/ pe2
}

z = (1:300)/100.
par(mfrow=c(2,2))
plot(z,te1d1,ylim=c(0.,1),type="l")
plot(z,te1d2,ylim=c(0.,1),type="l")
plot(z,te2d1,ylim=c(0.,1),type="l")
plot(z,te2d2,ylim=c(0.,1.2),type="l")
plot(z,te1d1opp,ylim=c(0.,1),type="l")
plot(z,te1d2opp,ylim=c(0.,1),type="l")
plot(z,te2d1opp,ylim=c(0.,1),type="l")
plot(z,te2d2opp,ylim=c(0.,1.2),type="l")
```

lets do the simulation
```{r}
Y1<-sim2d(rv1,rhx1,b1,100,0.1,91,2,100)
Z2<-Y2<-sim2d(rv2,rhx2,b2,100,0.1,91,2,100)

for( z in 2:90){
  Z2[,z]=Y2[,z]*sqrt(1-(a^2))+Y1[,z-1]*a
}

faciesenv<-faciesdiag<-Y1
faciesenv[Y1<q1]=1
faciesenv[Y1>q1 ]=2
both<-faciesenv
faciesdiag[]=2
faciesdiag[Y1<q1 & Z2<q2e1 ]=1
faciesdiag[Y1>q1 & Z2<q2e2 ]=1
both[faciesdiag==1]=3
image(faciesenv,col=c("white","grey"))
#image(faciesdiag)
image(both,col=c("white","grey","red"))
```

okay now that we hae studied some transiograms, the aim is to generate beautiful images with more facies

```{r}

pe1=0.4
pe2=0.4
pe3=0.2
pe1d1=0.3
pe2d1=0.3
pe3d1=0.3
rv1=0.3
rv2=0.3
rhx1=60
rhx2=60
b1=0
b2=0
a=0.8
shift=0.1
rho1a<-model(shift,rv1,b1)

q1a=qnorm(pe1) # threshold for environment of deposition
q1b=qnorm(pe1+pe2)

q2e1=q2e2=q2e3=0 # two thresholds for diagenetic facies 
Sigma = matrix(c(1,a*rho1a,a*rho1a,1),2,2)
obj1=obj2=obj3=Inf
for ( test in 1:100 ){
  q2e1test = qnorm(test/100)
  q2e2test = qnorm(test/100)
  q2e3test = qnorm(test/100)
  newobj1 =abs( pmvnorm(lower=c(-Inf,-Inf),upper=c(q1a,q2e1test),mean=c(0,0),sigma=Sigma)/pe1 - pe1d1) 
  newobj2 =abs( pmvnorm(lower=c(q1a,-Inf),upper=c(q1b,q2e2test),mean=c(0,0),sigma=Sigma)/pe2 - pe2d1)
  newobj3 =abs( pmvnorm(lower=c(q1b,-Inf),upper=c(Inf,q2e3test),mean=c(0,0),sigma=Sigma)/pe3 - pe3d1)
  if (newobj1 < obj1){
    q2e1= q2e1test
    obj1 = newobj1
  }
  if (newobj2 < obj2){
    q2e2= q2e2test
    obj2 = newobj2
  }
  if (newobj3 < obj3){
    q2e3= q2e3test
    obj3 = newobj3
  }
}

Y1<-sim2d(rv1,rhx1,b1,100,0.05,91,1,100)
Z2<-Y2<-sim2d(rv2,rhx2,b2,100,0.05,91,1,100)

for( z in 2:90){
  Z2[,z]=Y2[,z]*sqrt(1-(a^2))+Y1[,z-1]*a
}

faciesenv<-faciesdiag<-Y1
faciesenv[Y1<q1a]=1
faciesenv[Y1>q1a & Y1<q1b ]=2
faciesenv[Y1>q1b ]=3
combined<-faciesenv
faciesdiag[]=2
faciesdiag[Y1<q1a & Z2<q2e1 ]=1
faciesdiag[Y1>q1a & Y1<q1b & Z2<q2e2 ]=1
faciesdiag[Y1>q1b & Z2<q2e3 ]=1
combined[faciesenv==1 & faciesdiag==1]=4
combined[faciesenv==2 & faciesdiag==1]=5
combined[faciesenv==3 & faciesdiag==1]=6
image(faciesenv,col=c("ivory1","ivory3","ivory4"))
image(combined,col=c("ivory1","ivory3","ivory4","gold","darkorange","firebrick"))
```
same facies here but with vertical anisotropy for some so that it looks like fracture related diagenesis
```{r}
pe1=0.4
pe2=0.4
pe3=0.2
pe1d1=0.3
pe2d1=0.3
pe3d1=0.3
rv1=0.3
rv2=10
rhx1=60
rhx2=5
b1=0
b2=0
a=0.8
shift=0.1
rho1a<-model(shift,rv1,b1)

q1a=qnorm(pe1) # threshold for environment of deposition
q1b=qnorm(pe1+pe2)

q2e1=q2e2=q2e3=0 # two thresholds for diagenetic facies 
Sigma = matrix(c(1,a*rho1a,a*rho1a,1),2,2)
obj1=obj2=obj3=Inf
for ( test in 1:100 ){
  q2e1test = qnorm(test/100)
  q2e2test = qnorm(test/100)
  q2e3test = qnorm(test/100)
  newobj1 =abs( pmvnorm(lower=c(-Inf,-Inf),upper=c(q1a,q2e1test),mean=c(0,0),sigma=Sigma)/pe1 - pe1d1) 
  newobj2 =abs( pmvnorm(lower=c(q1a,-Inf),upper=c(q1b,q2e2test),mean=c(0,0),sigma=Sigma)/pe2 - pe2d1)
  newobj3 =abs( pmvnorm(lower=c(q1b,-Inf),upper=c(Inf,q2e3test),mean=c(0,0),sigma=Sigma)/pe3 - pe3d1)
  if (newobj1 < obj1){
    q2e1= q2e1test
    obj1 = newobj1
  }
  if (newobj2 < obj2){
    q2e2= q2e2test
    obj2 = newobj2
  }
  if (newobj3 < obj3){
    q2e3= q2e3test
    obj3 = newobj3
  }
}

Y1<-sim2d(rv1,rhx1,b1,100,0.05,91,1,100)
Z2<-Y2<-sim2d(rv2,rhx2,b2,100,0.05,91,1,100)

for( z in 2:90){
  Z2[,z]=Y2[,z]*sqrt(1-(a^2))+Y1[,z-1]*a
}

faciesenv<-faciesdiag<-Y1
faciesenv[Y1<q1a]=1
faciesenv[Y1>q1a & Y1<q1b ]=2
faciesenv[Y1>q1b ]=3
combined<-faciesenv
faciesdiag[]=2
faciesdiag[Y1<q1a & Z2<q2e1 ]=1
faciesdiag[Y1>q1a & Y1<q1b & Z2<q2e2 ]=1
faciesdiag[Y1>q1b & Z2<q2e3 ]=1
combined[faciesenv==1 & faciesdiag==1]=4
combined[faciesenv==2 & faciesdiag==1]=5
combined[faciesenv==3 & faciesdiag==1]=6
image(faciesenv,col=c("ivory1","ivory3","ivory4"))
image(combined,col=c("ivory1","ivory3","ivory4","gold","darkorange","firebrick"))
```

in three dimensions
```{r}
Z1<-sim3d(r1v,r1l,r1l,0,100,0.1,50,5,50,5,50)
Z2<-sim3d(r2v,r2l,r2l,0,100,0.1,50,5,50,5,50)
Y2<-Z2
for( z in 2:50){
  Z2[,,z]=Y2[,,z]*sqrt(1-(a^2))+Z1[,,z-1]*a
}
faciesenv<-faciesdiag<-Z1
faciesenv[Z1<q1a]=1
faciesenv[Z1>q1a & Z1<q1b ]=2
faciesenv[Z1>q1b ]=3
combined<-faciesenv
faciesdiag[]=2
faciesdiag[Z1<q1a & Z2<q2e1 ]=1
faciesdiag[Z1>q1a & Z1<q1b & Z2<q2e2 ]=1
faciesdiag[Z1>q1b & Z2<q2e3 ]=1
combined[faciesenv==1 & faciesdiag==1]=4
combined[faciesenv==2 & faciesdiag==1]=5
combined[faciesenv==3 & faciesdiag==1]=6

for ( z in 1:50){
  for ( y in 1:50){
    for ( x in 1:50){
      write(toString(c(combined[x,y,z])),"fracturecombined.csv",append=TRUE)
    }
  }
}
```

okay, we are going to change slighlty the simulation. 
We now do a pgs simulation for the environment of depositions so that we can have cyclicity. 
And the diagenesis happens only in two of the facies intertidal and supratidal. 
It might be better to visualize it like this.

```{r}
pe1=0.34
pe2=0.33
pe3=0.34
pe1d1=0.
pe2d1=0.3
pe3d1=0.4
rv1=0.2
rv2=0.2
rv3=0.2
rhx1=60
rhx2=60
rhx3=200
b1=0
b2=0
b3=0
a=0.99
b=0.99
shift=0.1
shiftb=-0.1
rho1a<-model(shift,rv1,b1)
rho1b<-model(shiftb,rv1,b1)

q1=qnorm(pe1) # subtidal facies defined by one Gaussian function

# for intertidal and supratidal, second Gaussian function
Sigma2 = matrix(c(1,a*rho1a,a*rho1a,1),2,2)
q2=0 
obj = Inf
for ( test in 1:100 ){
  q2test = qnorm(test/100)
  newobj =abs( pmvnorm(lower=c(q1,-Inf),upper=c(Inf,q2test),mean=c(0,0),sigma=Sigma2) - pe3 ) 
  if (newobj < obj){
    q2 = q2test
    obj = newobj
  }
}

q3e1=-Inf
q3e2=q3e3=0 # two thresholds for diagenetic facies 
Sigma3 = diag(1,3)
Sigma3[1,2]=Sigma3[2,1]=a*rho1a
Sigma3[1,3]=Sigma3[3,1]=b*rho1b
Sigma3[2,3]=Sigma3[3,2]=a*b*model(shift-shiftb,rv1,b1)

obj1=obj2=obj3=Inf
for ( test in 1:1000 ){
  q3e2test = qnorm(test/1000)
  q3e3test = qnorm(test/1000)
  newobj2 =abs( pmvnorm(lower=c(q1,q2,-Inf),upper=c(Inf,Inf,q3e2test),mean=c(0,0,0),sigma=Sigma3)/pe2 - pe2d1)
  newobj3 =abs( pmvnorm(lower=c(q1,-Inf,-Inf),upper=c(Inf,q2,q3e3test),mean=c(0,0,0),sigma=Sigma3)/pe3 - pe3d1)
  if (newobj2 < obj2){
    q3e2= q3e2test
    obj2 = newobj2
  }
  if (newobj3 < obj3){
    q3e3= q3e3test
    obj3 = newobj3
  }
}

# Te2de2 as if there is only one facies field, which means that I will have a matrix slightly bigger.
# Z1(x)>q1 Z2(x)>q2 Z1(x+h)>q1 Z2(x+h)>q2 Z3(x+h)<q3e2 Z3(x)>q3e2
# Which means we have a 6*6 matrix
# 
# Cov[Z3(x),Z1(x)]=cov[bZ1(x+beta),Z1(x)]
# Cov[Z3(x),Z2(x)]=cov[bZ1(x+beta),aZ1(x+alpha)]
# 
# Cov[Z2(x),Z2(x+h)]=Cov[aZ1(x+alpha)+sqrt(1-a)Y2(x), aZ1(x+h+alpha)+sqrt(1-a)Y2(x+h)]

# #transiograms
te1de2=te2de2=te3de2=te1de3=te2de3=te3de3=rep(0,300)
te1de2opp=te2de2opp=te3de2opp=te1de3opp=te2de3opp=te3de3opp=rep(0,300)
Sigma = diag(1,6)
Sigmaopp = diag(1,6)
Sigma[1,2]=Sigma[2,1]=Sigma[3,4]=Sigma[4,3]=a*rho1a
Sigma[3,5]=Sigma[5,3]=Sigma[1,6]=Sigma[6,1]=b*rho1b
Sigma[4,5]=Sigma[5,4]=Sigma[2,6]=Sigma[6,2]=a*b*model(shiftb-shift,rv1,b1)

Sigmaopp = Sigma
for (i in 1:300){
    d = i/100.
    Sigma[1,3]=Sigma[3,1]= model(d,rv1,b1)
    Sigma[1,4]=Sigma[4,1]=a*model(d+shift,rv1,b1)
    Sigma[1,5]=Sigma[5,1]=b*model(d+shiftb,rv1,b1)
    Sigma[2,3]=Sigma[3,2]=a*model(d-shift,rv1,b1)
    Sigma[2,4]=Sigma[4,2]= (a^2)*model(d,rv1,b1)+sqrt(1-a^2)*model(d,rv2,b2)
    Sigma[2,5]=Sigma[5,2]=a*b*model(d+shiftb-shift,rv1,b1)

    Sigma[3,6]=Sigma[6,3]=b*model(d-shiftb,rv1,b1)
    Sigma[4,6]=Sigma[6,4]=a*b*model(d+shift-shiftb,rv1,b1)
    Sigma[5,6]=Sigma[6,5]=(b^2)*model(d,rv1,b1)+sqrt(1-b^2)*model(d,rv3,b3)

    Sigmaopp[1,3]=Sigmaopp[3,1]= model(-d,rv1,b1)
    Sigmaopp[1,4]=Sigmaopp[4,1]=a*model(-d+shift,rv1,b1)
    Sigmaopp[1,5]=Sigmaopp[5,1]=b*model(-d+shiftb,rv1,b1)
    Sigmaopp[2,3]=Sigmaopp[3,2]=a*model(-d-shift,rv1,b1)
    Sigmaopp[2,4]=Sigmaopp[4,2]= (a^2)*model(-d,rv1,b1)+sqrt(1-a^2)*model(-d,rv2,b2)
    Sigmaopp[2,5]=Sigmaopp[5,2]=a*b*model(-d+shiftb-shift,rv1,b1)

    Sigmaopp[3,6]=Sigmaopp[6,3]=b*model(-d-shiftb,rv1,b1)
    Sigmaopp[4,6]=Sigmaopp[6,4]=a*b*model(-d+shift-shiftb,rv1,b1)
    Sigmaopp[5,6]=Sigmaopp[6,5]=(b^2)*model(-d,rv1,b1)+sqrt(1-b^2)*model(-d,rv3,b3)

    te1de2[i]=pmvnorm(lower=c(-Inf,-Inf,q1,q2,-Inf,-Inf),upper=c(q1,Inf,Inf,Inf,q3e2,Inf),mean=c(0,0,0,0,0,0),sigma=Sigma)/ pe1
    te2de2[i]=pmvnorm(lower=c(q1,q2,q1,q2,-Inf,q3e2),upper=c(Inf,Inf,Inf,Inf,q3e2,Inf),mean=c(0,0,0,0,0,0),sigma=Sigma)/ pe2
    te3de2[i]=pmvnorm(lower=c(q1,-Inf,q1,q2,-Inf,q3e3),upper=c(Inf,q2,Inf,Inf,q3e2,Inf),mean=c(0,0,0,0,0,0),sigma=Sigma)/ pe3

    te1de3[i]=pmvnorm(lower=c(-Inf,-Inf,q1,-Inf,-Inf,-Inf),upper=c(q1,Inf,Inf,q2,q3e3,Inf),mean=c(0,0,0,0,0,0),sigma=Sigma)/ pe1
    te2de3[i]=pmvnorm(lower=c(q1,q2,q1,-Inf,-Inf,q3e2),upper=c(Inf,Inf,Inf,q2,q3e3,Inf),mean=c(0,0,0,0,0,0),sigma=Sigma)/ pe2
    te3de3[i]=pmvnorm(lower=c(q1,-Inf,q1,-Inf,-Inf,q3e3),upper=c(Inf,q2,Inf,q2,q3e3,Inf),mean=c(0,0,0,0,0,0),sigma=Sigma)/ pe3

    te1de2opp[i]=pmvnorm(lower=c(-Inf,-Inf,q1,q2,-Inf,-Inf),upper=c(q1,Inf,Inf,Inf,q3e2,Inf),mean=c(0,0,0,0,0,0),sigma=Sigmaopp)/ pe1
    te2de2opp[i]=pmvnorm(lower=c(q1,q2,q1,q2,-Inf,q3e2),upper=c(Inf,Inf,Inf,Inf,q3e2,Inf),mean=c(0,0,0,0,0,0),sigma=Sigmaopp)/ pe2
    te3de2opp[i]=pmvnorm(lower=c(q1,-Inf,q1,q2,-Inf,q3e3),upper=c(Inf,q2,Inf,Inf,q3e2,Inf),mean=c(0,0,0,0,0,0),sigma=Sigmaopp)/ pe3

    te1de3opp[i]=pmvnorm(lower=c(-Inf,-Inf,q1,-Inf,-Inf,-Inf),upper=c(q1,Inf,Inf,q2,q3e3,Inf),mean=c(0,0,0,0,0,0),sigma=Sigmaopp)/ pe1
    te2de3opp[i]=pmvnorm(lower=c(q1,q2,q1,-Inf,-Inf,q3e2),upper=c(Inf,Inf,Inf,q2,q3e3,Inf),mean=c(0,0,0,0,0,0),sigma=Sigmaopp)/ pe2
    te3de3opp[i]=pmvnorm(lower=c(q1,-Inf,q1,-Inf,-Inf,q3e3),upper=c(Inf,q2,Inf,q2,q3e3,Inf),mean=c(0,0,0,0,0,0),sigma=Sigmaopp)/ pe3

    # te1d1opp[i]=(pmvnorm(lower=c(-Inf,-Inf,-Inf),upper=c(q1,q1,q2e1),mean=c(0,0,0),sigma=Sigmaopp) + pmvnorm(lower=c(-Inf,q1,-Inf),upper=c(q1,Inf,q2e2),mean=c(0,0,0),sigma=Sigma))/ pe1
    # te2d1opp[i]=(pmvnorm(lower=c(q1,-Inf,-Inf),upper=c(Inf,q1,q2e1),mean=c(0,0,0),sigma=Sigmaopp) + pmvnorm(lower=c(q1,q1,-Inf),upper=c(Inf,Inf,q2e2),mean=c(0,0,0),sigma=Sigma))/ pe2
    # te1d2opp[i]=(pmvnorm(lower=c(-Inf,-Inf,q2e1),upper=c(q1,q1,Inf),mean=c(0,0,0),sigma=Sigmaopp) + pmvnorm(lower=c(-Inf,q1,q2e2),upper=c(q1,Inf,Inf),mean=c(0,0,0),sigma=Sigma))/ pe1
    # te2d2opp[i]=(pmvnorm(lower=c(q1,-Inf,q2e1),upper=c(Inf,q1,Inf),mean=c(0,0,0),sigma=Sigmaopp) + pmvnorm(lower=c(q1,q1,q2e2),upper=c(Inf,Inf,Inf),mean=c(0,0,0),sigma=Sigma))/ pe2
}
z = (1:300)/100.
par(mfrow=c(2,3))
plot(z,te1de2,ylim=c(0.,1),type="l")
plot(z,te2de2,ylim=c(0.,1),type="l")
plot(z,te3de2,ylim=c(0.,1),type="l")
plot(z,te1de3,ylim=c(0.,1),type="l")
plot(z,te2de3,ylim=c(0.,1),type="l")
plot(z,te3de3,ylim=c(0.,1),type="l")

z = (1:300)/100.
par(mfrow=c(2,3))
plot(z,te1de2opp,ylim=c(0.,1),type="l")
plot(z,te2de2opp,ylim=c(0.,1),type="l")
plot(z,te3de2opp,ylim=c(0.,1),type="l")
plot(z,te1de3opp,ylim=c(0.,1),type="l")
plot(z,te2de3opp,ylim=c(0.,1),type="l")
plot(z,te3de3opp,ylim=c(0.,1),type="l")

#simulation
Y1<-sim2d(rv1,rhx1,b1,100,0.025,182,0.5,200)
Z2<-Y2<-sim2d(rv2,rhx2,b2,100,0.025,182,0.5,200)
Z3<-Y3<-sim2d(rv3,rhx3,b3,100,0.025,182,0.5,200)
for( z in 5:178){
  Z2[,z]=Y2[,z]*sqrt(1-(a^2))+Y1[,z+4]*a
}
for( z in 5:178){
  Z3[,z]=Y3[,z]*sqrt(1-(b^2))+Y1[,z-4]*b
}
faciesenv<-faciesdiag<-Y1
faciesenv[Y1<q1]=1
faciesenv[Y1>q1 & Z2<q2 ]=3
faciesenv[Y1>q1 & Z2>q2  ]=2
combined<-faciesenv
faciesdiag[]=2
faciesdiag[Y1>q1 & Z2<q2 & Z3<q3e3 ]=1
faciesdiag[Y1>q1 & Z2>q2 & Z3<q3e2 ]=1
combined[faciesenv==2 & faciesdiag==1]=4
combined[faciesenv==3 & faciesdiag==1]=5
par(mfrow=c(1,1))
image(faciesenv,col=c("ivory1","ivory3","ivory4"))
image(combined,col=c("ivory1","ivory3","ivory4","gold","firebrick"),axes = FALSE)
#image(combined,col=c("ivory1","ivory3","ivory4","gold"),axes = FALSE)
#image(combined,col=c("ivory1","ivory3","ivory4","firebrick"),axes = FALSE)
```
Okay, we can do this simulation in three dimensions
```{r}
Y1<-sim3d(rv1,rhx1,rhx1,b1,100,0.025,182,0.5,200,5,10)
Z2<-Y2<-sim3d(rv2,rhx2,rhx2,b2,100,0.025,182,0.5,200,5,10)
Z3<-Y3<-sim3d(rv3,rhx3,rhx3,b3,100,0.025,182,0.5,200,5,10)
for( z in 5:178){
  Z2[,,z]=Y2[,,z]*sqrt(1-(a^2))+Y1[,,z+4]*a
}
for( z in 5:178){
  Z3[,,z]=Y3[,,z]*sqrt(1-(b^2))+Y1[,,z-4]*b
}

```

```{r}
faciesenv<-faciesdiag<-Y1
faciesenv[Y1<q1]=1
faciesenv[Y1>q1 & Z2<q2 ]=3
faciesenv[Y1>q1 & Z2>q2  ]=2
faciesenv[faciesenv==3 & Z3<q3e3]=4
faciesenv[faciesenv==2 & Z3<q3e2]=5
for ( z in 1:182){
  for ( y in 1:10){
    for ( x in 1:200){
      write(toString(c(faciesenv[x,y,z])),"fracturecombined.csv",append=TRUE)
    }
  }
}
```

here with vertical fractures dolomitized 
```{r}
pe1=0.34
pe2=0.33
pe3=0.34
pe1d1=0.
pe2d1=0.2
pe3d1=0.4
rv1=0.2
rv2=0.2
rv3=5
rhx1=60
rhx2=60
rhx3=5
b1=0
b2=0
b3=0
a=0.99
b=0.8
shift=0.1
shiftb=0.
rho1a<-model(shift,rv1,b1)
rho1b<-model(shiftb,rv1,b1)

q1=qnorm(pe1) # subtidal facies defined by one Gaussian function

# for intertidal and supratidal, second Gaussian function
Sigma2 = matrix(c(1,a*rho1a,a*rho1a,1),2,2)
q2=0 
obj = Inf
for ( test in 1:100 ){
  q2test = qnorm(test/100)
  newobj =abs( pmvnorm(lower=c(q1,-Inf),upper=c(Inf,q2test),mean=c(0,0),sigma=Sigma2) - pe3 ) 
  if (newobj < obj){
    q2 = q2test
    obj = newobj
  }
}

q3e1=-Inf
q3e2=q3e3=0 # two thresholds for diagenetic facies 
Sigma3 = diag(1,3)
Sigma3[1,2]=Sigma3[2,1]=a*rho1a
Sigma3[1,3]=Sigma3[3,1]=b*rho1b
Sigma3[2,3]=Sigma3[3,2]=a*b*model(shift-shiftb,rv1,b1)

obj1=obj2=obj3=Inf
for ( test in 1:1000 ){
  q3e2test = qnorm(test/1000)
  q3e3test = qnorm(test/1000)
  newobj2 =abs( pmvnorm(lower=c(q1,q2,-Inf),upper=c(Inf,Inf,q3e2test),mean=c(0,0,0),sigma=Sigma3)/pe2 - pe2d1)
  newobj3 =abs( pmvnorm(lower=c(q1,-Inf,-Inf),upper=c(Inf,q2,q3e3test),mean=c(0,0,0),sigma=Sigma3)/pe3 - pe3d1)
  if (newobj2 < obj2){
    q3e2= q3e2test
    obj2 = newobj2
  }
  if (newobj3 < obj3){
    q3e3= q3e3test
    obj3 = newobj3
  }
}

Y1<-sim2d(rv1,rhx1,b1,100,0.025,182,0.5,200)
Z2<-Y2<-sim2d(rv2,rhx2,b2,100,0.025,182,0.5,200)
Z3<-Y3<-sim2d(rv3,rhx3,b3,100,0.025,182,0.5,200)
for( z in 4:178){
  Z2[,z]=Y2[,z]*sqrt(1-(a^2))+Y1[,z+4]*a
}
for( z in 4:178){
  Z3[,z]=Y3[,z]*sqrt(1-(b^2))+Y1[,z]*b
}
faciesenv<-faciesdiag<-Y1
faciesenv[Y1<q1]=1
faciesenv[Y1>q1 & Z2<q2 ]=3
faciesenv[Y1>q1 & Z2>q2  ]=2
combined<-faciesenv
faciesdiag[]=2
faciesdiag[Y1>q1 & Z2<q2 & Z3<q3e3 ]=1
faciesdiag[Y1>q1 & Z2>q2 & Z3<q3e2 ]=1
combined[faciesenv==2 & faciesdiag==1]=4
combined[faciesenv==3 & faciesdiag==1]=5
image(faciesenv,col=c("ivory1","ivory3","ivory4"))
image(combined,col=c("ivory1","ivory3","ivory4","gold","firebrick"),axes = FALSE)
```
in three dimensions
```{r}
Y1<-sim3d(rv1,rhx1,rhx1,b1,100,0.025,182,0.5,200,5,10)
Z2<-Y2<-sim3d(rv2,rhx2,rhx2,b2,100,0.025,182,0.5,200,5,10)
Z3<-Y3<-sim3d(rv3,rhx3,rhx3,b3,100,0.025,182,0.5,200,5,10)
for( z in 4:178){
  Z2[,,z]=Y2[,,z]*sqrt(1-(a^2))+Y1[,,z+1]*a
}
for( z in 4:178){
  Z3[,,z]=Y3[,,z]*sqrt(1-(b^2))+Y1[,,z]*b
}

```

```{r}
faciesenv<-faciesdiag<-Y1
faciesenv[Y1<q1]=1
faciesenv[Y1>q1 & Z2<q2 ]=3
faciesenv[Y1>q1 & Z2>q2  ]=2
faciesenv[faciesenv==3 & Z3<q3e3]=4
faciesenv[faciesenv==2 & Z3<q3e2]=5
for ( z in 1:182){
  for ( y in 1:10){
    for ( x in 1:200){
      write(toString(c(faciesenv[x,y,z])),"fracturecombined.csv",append=TRUE)
    }
  }
}
```

new simulation with four facies with the first two Gaussian functions
The fourth facies is marine cementation during transgression phase. This facies is the last of the cycle.
The diagenesic facies is dolomite and just happen in the supratidal environment.

```{r}
pe1=0.2
pe2=0.2
pe3=0.2
pe4=0.2
pe3d1=0.4
rv1=0.2
rv2=0.2
rv3=0.2
rhx1=60
rhx2=60
rhx3=60
b1=0
b2=0
b3=0
a=0.99
b=0.
shift=0.1
shiftb=0.
rho1a<-model(shift,rv1,b1)
rho1b<-model(shiftb,rv1,b1)

q1=qnorm(pe1+pe2) # subtidal facies defined by one Gaussian function

# for intertidal and supratidal, second Gaussian function
Sigma2 = matrix(c(1,a*rho1a,a*rho1a,1),2,2)
q2=0
q3=0
obj=obj2 = Inf
for ( test in 1:100 ){
  q2test = qnorm(test/100)
  q3test = qnorm(test/100)
  newobj =abs( pmvnorm(lower=c(-Inf,-Inf),upper=c(q1,q2test),mean=c(0,0),sigma=Sigma2) - pe1 ) 
  newobj2 =abs( pmvnorm(lower=c(q1,-Inf),upper=c(Inf,q3test),mean=c(0,0),sigma=Sigma2) - pe4 )
  if (newobj < obj){
    q2 = q2test
    obj = newobj
  }
  if (newobj2 < obj2){
    q3 = q3test
    obj2 = newobj2
  }
}

q3e3=-Inf
Sigma3 = diag(1,3)
Sigma3[1,2]=Sigma3[2,1]=a*rho1a
Sigma3[1,3]=Sigma3[3,1]=b*rho1b
Sigma3[2,3]=Sigma3[3,2]=a*b*model(shift-shiftb,rv1,b1)

obj3=Inf
for ( test in 1:1000 ){
  q3e3test = qnorm(test/1000)
  newobj3 =abs( pmvnorm(lower=c(q1,q2,-Inf),upper=c(Inf,Inf,q3e3test),mean=c(0,0,0),sigma=Sigma3)/pe3 - pe3d1)

  if (newobj3 < obj3){
    q3e3= q3e3test
    obj3 = newobj3
  }
}

#simulation
Y1<-sim2d(rv1,rhx1,b1,100,0.025,182,0.5,200)
Z2<-Y2<-sim2d(rv2,rhx2,b2,100,0.025,182,0.5,200)
Z3<-Y3<-sim2d(rv3,rhx3,b3,100,0.025,182,0.5,200)
for( z in 4:178){
  Z2[,z]=Y2[,z]*sqrt(1-(a^2))+Y1[,z+4]*a
}
for( z in 4:178){
  Z3[,z]=Y3[,z]*sqrt(1-(b^2))+Y1[,z]*b
}
faciesenv<-faciesdiag<-Y1
faciesenv[Y1<q1 & Z2<q2]=1
faciesenv[Y1<q1 & Z2>q2]=2
faciesenv[Y1>q1 & Z2>q3]=3
faciesenv[Y1>q1 & Z2<q3]=4

combined<-faciesenv
combined[faciesenv==3 & Z3<q3e3]=5
image(faciesenv,col=c("ivory1","ivory3","ivory4"))
image(combined,col=c("ivory1","ivory3","ivory4","cyan3","firebrick"),axes = FALSE)
```

### 2018-05-31 cosim_expo.Rmd
added the code

---
title: "R Notebook"
output: html_notebook
---

we have seen that the conditioning was difficult with a Gaussian covariance. 
Therefore, we perform the same method that precedently, with exponential covariances. 
We have proved that the covariance matrix was more stable, and could be inverted safely. 
We may still use a Gaussian covariance in the lateral direction, it is more stable because less data in this direction.

```{r}
source("cosim_functions.R")
```
```{r}
library(mvtnorm)
```

```{r}
model<-function(h,range,b){return(exp(-abs(h/range))*cos(b*h) )}
model_lat<-function(h,range){return(exp(-(h/range)^2) )}
```

```{r}
rv1=0.3
rhx1=50
b1=0
Z3<-sim2dexp(rv3,rhx3,b3,100,0.1,91,1,100)
image(Z3,col = heat.colors(100))
```

```{r}
rv1=0.3
rv2=0.5
rhx1=100
rhx2=100
b1=0
b2=0
rho=0.6
shift=0.1
rho1a<-model(shift,rv1,b1)

alpha1=(rho/rho1a)^2
alpha2=1-(rho/rho1a)^2
rv3=0.2
rv4=0.3
rhx3=100
rhx4=100
b3=0
b4=0
rho34=0.
c=0.
e=0.65
a13=-0.
a14=-0.1
rho1a14 = model(a14,rv1,b1)
```

thresholds of diagenetic facies, depend on the parameters

```{r}
qd1e4=qnorm(pd3e4)

# now the threshold with the fourth Gaussian function, that does depend on the first
sigma1=diag(1,3)
sigma1[1,2]=sigma1[2,1]=e*model(a14,rv1,b1)
sigma1[1,3]=sigma1[3,1]=e*(rho/rho1a)*model(a14-shift,rv1,b1)
sigma1[2,3]=sigma1[3,2]=rho

qd2e2=0
obj = Inf
for ( test in 1:100 ){
  qd2e2test = qnorm(test/100)
  newobj =abs( pmvnorm(lower=c(qd2e2test,-Inf,q2),upper=c(Inf,q1,Inf),mean=c(0,0,0),sigma=sigma1)/pe2 - pd2e2 ) 
  if (newobj < obj){
    qd2e2 = qd2e2test
    obj = newobj
  }
}

qd2e3=0
obj = Inf
for ( test in 1:100 ){
  qd2e3test = qnorm(test/100)
  newobj =abs( pmvnorm(lower=c(qd2e3test,q1,q3),upper=c(Inf,Inf,Inf),mean=c(0,0,0),sigma=sigma1)/pe3 - pd2e3 ) 
  if (newobj < obj){
    qd2e3 = qd2e3test
    obj = newobj
  }
}

print(c(qd1e4,qd2e2,qd2e3))
```

simu

```{r}
Z1<-sim2dexp(rv1,rhx1,b1,100,0.05,182,0.5,200)
Y2<-sim2dexp(rv2,rhx2,b2,100,0.05,182,0.5,200)
Z2=Y2
for ( z in 1:180){
  Z2[,z]=Y2[,z]*sqrt(1-(rho^2)/(rho1a^2))+Z1[,z+2]*(rho)/(rho1a)
}
Z3<-sim2dexp(rv3,rhx3,b3,100,0.05,182,0.5,200)
Y4<-sim2dexp(rv4,rhx4,b4,100,0.05,182,0.5,200)
Z4=Y4
for ( z in 2:182){
  Z4[,z]=Y4[,z]*sqrt(1-e^2)+Z1[,z-1]*e
}

faciesenv<-faciesdiag<-Z1
faciesenv[Z1<q1 & Z2<q2]=1
faciesenv[Z1<q1 & Z2>q2]=2
faciesenv[Z1>q1 & Z2<q3]=4
faciesenv[Z1>q1 & Z2>q3]=3
faciesdiag[]=1
faciesdiag[Z1>q1 & Z2<q3 & Z3<qd1e4]=3
faciesdiag[Z1<q1 & Z2>q2 & Z4>qd2e2]=2
faciesdiag[Z1>q1 & Z2>q3 & Z4>qd2e3]=2
col_env <- c("lightgreen","cadetblue","dodgerblue4","lightcoral")
col_diag<-dcolors <- c("black","grey","yellow")
image(faciesenv,col = col_env)
image(faciesdiag,col = col_diag)
bin<-bin2<-faciesenv
#bin[]<-rbinom(91*100, 1, 0.5)
bin[]=bin2[]=0
bin[seq(2,182*200,by=2)]=1
facies=faciesenv
facies[faciesdiag==2 & bin ==1 ] = 5
facies[faciesdiag==3]=5

col_combine <- c("lightgreen","cadetblue","dodgerblue4","lightcoral","yellow")
W<-image(facies,col = col_combine)
```

we need to look again at the experimental transiogram, to do an accurate fitting with the exponential covariance.
transiograms of environment of depositions

```{r}
rv1=0.6
rv2=0.7
rhx1=50
rhx2=50
b1=5
b2=0
rho=0.7
shift=0.1
rho1a<-model(shift,rv1,b1)

alpha1=(rho/rho1a)^2
alpha2=1-(rho/rho1a)^2
rv3=0.4
rv4=0.3
rhx3=50
rhx4=50
b3=0
b4=0
rho34=0.
c=0.
e=0.65
a13=-0.
a14=-0.1
rho1a14 = model(a14,rv1,b1)

z = (1:300)/100.
t11_model=t12_model=t13_model=t21_model=t22_model=t23_model=t31_model=t32_model=t33_model=rep(0,300)
Sigma = diag(1,4)
for (i in 1:300){
    d = i/100.
    Sigma[1,2]=Sigma[2,1]= Sigma[3,4]=Sigma[4,3]=rho
    Sigma[1,3]=Sigma[3,1]=model(d,rv1,b1)
    Sigma[1,4]=Sigma[4,1]=(rho/rho1a)*model(abs(d+shift),rv1,b1)
    Sigma[2,3]=Sigma[3,2]=(rho/rho1a)*model(abs(d-shift),rv1,b1)
    Sigma[2,4]=Sigma[4,2]=alpha1*model(d,rv1,b1)+alpha2*model(d,rv2,b2)
    t11_model[i]=pmvnorm(lower=c(-Inf,-Inf,-Inf,-Inf),upper=c(q1,q2,q1,q2),mean=c(0,0,0,0),sigma=Sigma)/ pe1 
    t12_model[i]=pmvnorm(lower=c(-Inf,-Inf,-Inf,q2),upper=c(q1,q2,q1,Inf),mean=c(0,0,0,0),sigma=Sigma)/ pe1 
    t13_model[i]=pmvnorm(lower=c(-Inf,-Inf,q1,q3),upper=c(q1,q2,Inf,Inf),mean=c(0,0,0,0),sigma=Sigma)/ pe1 
    t21_model[i]=pmvnorm(lower=c(-Inf,q2,-Inf,-Inf),upper=c(q1,Inf,q1,q2),mean=c(0,0,0,0),sigma=Sigma)/ pe2
    t22_model[i]=pmvnorm(lower=c(-Inf,q2,-Inf,q2),upper=c(q1,Inf,q1,Inf),mean=c(0,0,0,0),sigma=Sigma)/ pe2
    t23_model[i]=pmvnorm(lower=c(-Inf,q2,q1,q3),upper=c(q1,Inf,Inf,Inf),mean=c(0,0,0,0),sigma=Sigma)/ pe2
    t31_model[i]=pmvnorm(lower=c(q1,q3,-Inf,-Inf),upper=c(Inf,Inf,q1,q2),mean=c(0,0,0,0),sigma=Sigma)/ pe3
    t32_model[i]=pmvnorm(lower=c(q1,q3,-Inf,q2),upper=c(Inf,Inf,q1,Inf),mean=c(0,0,0,0),sigma=Sigma)/ pe3
    t33_model[i]=pmvnorm(lower=c(q1,q3,q1,q3),upper=c(Inf,Inf,Inf,Inf),mean=c(0,0,0,0),sigma=Sigma)/ pe3
}
par(mfrow=c(3,3))
t11<-tr_2d_vert(e1,e1,30,nz,0.1)
lines(z,t11_model)
t12<-tr_2d_vert(e1,e2,30,nz,0.1)
lines(z,t12_model)
t13<-tr_2d_vert(e1,e3,30,nz,0.1)
lines(z,t13_model)
t21<-tr_2d_vert(e2,e1,30,nz,0.1)
lines(z,t21_model)
t22<-tr_2d_vert(e2,e2,30,nz,0.1)
lines(z,t22_model)
t23<-tr_2d_vert(e2,e3,30,nz,0.1)
lines(z,t23_model)
t31<-tr_2d_vert(e3,e1,30,nz,0.1)
lines(z,t31_model)
t32<-tr_2d_vert(e3,e2,30,nz,0.1)
lines(z,t32_model)
t33<-tr_2d_vert(e3,e3,30,nz,0.1)
lines(z,t33_model)
```

now the diagenetic transiograms

```{r}

rv3=0.2
rv4=0.6
qd1=qnorm(pd3)
Sigma1 = matrix(c(1,rho34,rho34,1),2,2)
qd2=0
obj = Inf
for ( test in 1:100 ){
  q2test = qnorm(test/100)
  newobj =abs( pmvnorm(lower=c(qd1,q2test),upper=c(Inf,Inf),mean=c(0,0),sigma=Sigma1) - pd2 ) 
  if (newobj < obj){
    qd2 = q2test
    obj = newobj
  }
}

c(qd1,qd2)

#transiograms

z = (1:300)/100.
t33d_model=t32d_model=t23d_model=t22d_model=rep(0,300)
Sigma = diag(1,4)
for (i in 1:300){
    d = i/100.
    Sigma[1,2]=Sigma[2,1]= Sigma[3,4]=Sigma[4,3]=rho34
    Sigma[1,3]=Sigma[3,1]=model(d,rv3,b3)
    Sigma[1,4]=Sigma[4,1]=Sigma[2,3]=Sigma[3,2]=rho34*model(d,rv3,b3)
    Sigma[2,4]=Sigma[4,2]=(rho34^2)*model(d,rv3,b3)+(1-rho34^2)*model(d,rv4,b4)

    t22d_model[i]=pmvnorm(lower=c(qd1,qd2,qd1,qd2),upper=c(Inf,Inf,Inf,Inf),mean=c(0,0,0,0),sigma=Sigma)/ pd2
    t23d_model[i]=pmvnorm(lower=c(qd1,qd2,-Inf,-Inf),upper=c(Inf,Inf,qd1,Inf),mean=c(0,0,0,0),sigma=Sigma)/ pd2
    t32d_model[i]=pmvnorm(lower=c(-Inf,-Inf,qd1,qd2),upper=c(qd1,Inf,Inf,Inf),mean=c(0,0,0,0),sigma=Sigma)/ pd3
    t33d_model[i]=pmvnorm(lower=c(-Inf,-Inf,-Inf,-Inf),upper=c(qd1,Inf,qd1,Inf),mean=c(0,0,0,0),sigma=Sigma)/ pd3
}
par(mfrow=c(2,2))
t22d<-tr_2d_vert(d2,d2,30,nz,0.1)
lines(z,t22d_model)
t23d<-tr_2d_vert(d2,d3,30,nz,0.1)
lines(z,t23d_model)
t32d<-tr_2d_vert(d3,d2,30,nz,0.1)
lines(z,t32d_model)
t33d<-tr_2d_vert(d3,d3,30,nz,0.1)
lines(z,t33d_model)
```

conditioning

```{r}
source("co_sim_condi.R")
```

```{r}
rv1=0.6
rv2=0.7
rhx1=40
rhx2=40
#b1=5
b1=0
b2=0
rho=0.7
shift=0.1
rho1a<-model(shift,rv1,b1)

alpha1=(rho/rho1a)^2
alpha2=1-(rho/rho1a)^2
rv3=0.2
rv4=0.6
rhx3=40
rhx4=40
b3=0
b4=0
rho34=0.
c=0.
e=0.65
a13=-0.
a14=-0.1
rho1a14 = model(a14,rv1,b1)

Z1<-sim2dexp(rv1,rhx1,b1,100,0.1,91,1,100)
Y2<-sim2dexp(rv2,rhx2,b2,100,0.1,91,1,100)
Z2=Y2
for ( z in 1:90){
  Z2[,z]=Y2[,z]*sqrt(1-(rho^2)/(rho1a^2))+Z1[,z+1]*(rho)/(rho1a)
}
Z3<-sim2dexp(rv3,rhx3,b3,100,0.1,91,1,100)
Y4<-sim2dexp(rv4,rhx4,b4,100,0.1,91,1,100)
Z4=Y4
for ( z in 2:91){
  Z4[,z]=Y4[,z]*sqrt(1-e^2)+Z1[,z-1]*e
}
grid<-grid_co<-array(NA,c(100,91))
grid[3,]<-env_lat[,1]
grid[20,]<-env_lat[,2]
grid[55,]<-env_lat[,3]
grid[80,]<-env_lat[,4]
grid_co[3,]<-diag_lat[,1]
grid_co[20,]<-diag_lat[,2]
grid_co[55,]<-diag_lat[,3]
grid_co[80,]<-diag_lat[,4]

simwell<-coco_gibbs_sampling(grid,grid_co,c(q1,q2,q3),c(qd1e4,qd2e2,qd2e3),0.1,1,c(rv1,rv2,rv3,rv4),c(rhx1,rhx2,rhx3,rhx4),c(b1,b2,b3,b4),c(rho,e*model(a14,rv1,b1)),c(shift,a14),30)
Z1well<-simwell[,1:91]
Z2well<-simwell[,92:182]
Z3well<-simwell[,183:273]
Z4well<-simwell[,274:364]
E<-coco_dual_krig(Z1well-Z1,Z2well-Z2,Z3well-Z3,Z4well-Z4,0.1,1,c(rv1,rv2,rv3,rv4),c(rhx1,rhx2,rhx3,rhx4),c(b1,b2,b3,b4),c(rho,e*model(a14,rv1,b1)),c(shift,a14))
Z1c=Z1 + E[,1:91]
Z2c<-Z2 +E[,92:182]
Z3c<-Z3 +E[,183:273]
Z4c<-Z4 +E[,274:364]

faciesenv<-faciesdiag<-Z1c
faciesenv[Z1c<q1 & Z2c<q2]=1
faciesenv[Z1c<q1 & Z2c>q2]=2
faciesenv[Z1c>q1 & Z2c<q3]=4
faciesenv[Z1c>q1 & Z2c>q3]=3
faciesdiag[]=1
faciesdiag[Z1c>q1 & Z2c<q3 & Z3c<qd1e4]=3
faciesdiag[Z1c<q1 & Z2c>q2 & Z4c>qd2e2]=2
faciesdiag[Z1c>q1 & Z2c>q3 & Z4c>qd2e3]=2
col_env <- c("lightgreen","cadetblue","dodgerblue4","lightcoral")
W<-image(faciesenv,col = col_env)
bin<-bin2<-faciesenv
#bin[]<-rbinom(91*100, 1, 0.5)
bin[]=bin2[]=0
bin[seq(2,91*100,by=2)]=1
facies=faciesenv
facies[faciesdiag==2 & bin ==1 ] = 5
facies[faciesdiag==3]=5

col_combine <- c("lightgreen","cadetblue","dodgerblue4","lightcoral","yellow")
W<-image(facies,col = col_combine)
image(Z2c)
image(Z2)
```

### 2018-05-31 fitting.Rmd
added the code

---
title: "R Notebook"
output: html_notebook
---
we are trying here to fit all the transiogram of the co-simulation !

```{r}
library(mvtnorm)
```
```{r}
source("cosim_functions.R")
```

```{r}
model<-function(h,range,b){return(exp(-abs(h/range)^2)*cos(b*h) )}
```
```{r}
c(pe1,pe2,pe3,pe4)
```

conditional proportions
```{r}

pd1e1=mean(d1*e1,na.rm=TRUE)/pe1
pd1e2=mean(d1*e2,na.rm=TRUE)/pe2
pd1e3=mean(d1*e3,na.rm=TRUE)/pe3
pd1e4=mean(d1*e4,na.rm=TRUE)/pe4

pd2e1=mean(d2*e1,na.rm=TRUE)/pe1
pd2e2=mean(d2*e2,na.rm=TRUE)/pe2
pd2e3=mean(d2*e3,na.rm=TRUE)/pe3
pd2e4=mean(d2*e4,na.rm=TRUE)/pe4

pd3e1=mean(d3*e1,na.rm=TRUE)/pe1
pd3e2=mean(d3*e2,na.rm=TRUE)/pe2
pd3e3=mean(d3*e3,na.rm=TRUE)/pe3
pd3e4=mean(d3*e4,na.rm=TRUE)/pe4

matrix(c(pd1e1,pd1e2,pd1e3,pd1e4,pd2e1,pd2e2,pd2e3,pd2e4,pd3e1,pd3e2,pd3e3,pd3e4),3,4,byrow=TRUE)

```

```{r}
# rv1=0.3
# rv2=1.2
# rhx1=40
# rhx2=40
# b1=0
# b2=5
# rho=0.6
# shift=0.1
# rho1a<-model(shift,rv1,b1)
# warning(rho>rho1a)
# alpha1=(rho/rho1a)^2
# alpha2=1-(rho/rho1a)^2
# rv3=0.2
# rv4=0.3
# rhx3=40
# rhx4=40
# b3=0
# b4=0
# rho34=-0.6
# c=0.
# e=0.65
# a13=-0.
# a14=-0.1
# rho1a14 = model(a14,rv1,b1)

rv1=0.3
rv2=1.2
rhx1=40
rhx2=40
b1=0
b2=5
rho=0.6
shift=0.1
rho1a<-model(shift,rv1,b1)
warning(rho>rho1a)
alpha1=(rho/rho1a)^2
alpha2=1-(rho/rho1a)^2
rv3=0.2
rv4=0.3
rhx3=40
rhx4=40
b3=0
b4=0
e=-0.8
f=-0.5

a14=-0.1
a24=0.1
rho1a14 = model(a14,rv1,b1)
rho2a24=model(a24,rv2,b2)

#thresholds
q1=qnorm(pe1+pe2)
Sigma1 = matrix(c(1,rho,rho,1),2,2)
q2=0
obj = Inf
for ( test in 1:100 ){
  q2test = qnorm(test/100)
  newobj =abs( pmvnorm(lower=c(-Inf,-Inf),upper=c(q1,q2test),mean=c(0,0),sigma=Sigma1) - pe1 ) 
  if (newobj < obj){
    q2 = q2test
    obj = newobj
  }
}
q3=0
obj = Inf
for ( test in 1:100 ){
  q3test = qnorm(test/100)
  newobj =abs( pmvnorm(lower=c(q1,-Inf),upper=c(Inf,q3test),mean=c(0,0),sigma=Sigma1) - pe4 ) 
  if (newobj < obj){
    q3 = q3test
    obj = newobj
  }
}

c(q1,q2,q3)

qd1e4=qnorm(pd3e4) # no correlation with the third Gaussian function
Sigmad = diag(1,3)
qd2e2=0
qd2e3=0
obje2 = Inf
obje3 = Inf
for ( test in 1:100 ){
  qd2e2test = qnorm(test/100)
  qd2e3test = qnorm(test/100)
  Sigmad[1,2]=Sigmad[2,1]=e*rho1a14
  Sigmad[1,3]=Sigmad[3,1]=e*rho1a14*rho
  Sigmad[2,3]=Sigmad[3,2]=rho
  newobje2 =abs( pmvnorm(lower=c(qd2e2test,-Inf,q2),upper=c(Inf,q1,Inf),mean=c(0,0,0),sigma=Sigmad)/pe2 - pd2e2 ) 
  newobje3 =abs( pmvnorm(lower=c(qd2e2test,q1,q3),upper=c(Inf,Inf,Inf),mean=c(0,0,0),sigma=Sigmad)/pe3 - pd2e3 )
  if (newobje2 < obje2){
    qd2e2 = qd2e2test
    obje2 = newobje2
  }
  if (newobje3 < obje3){
    qd2e3 = qd2e3test
    obje3 = newobje3
  }
}

c(qd1e4,qd2e2,qd2e3)

#transiograms
z = (1:300)/100.
t11_model=t12_model=t13_model=t14_model=t21_model=t22_model=t23_model=t24_model=t31_model=t32_model=t33_model=t34_model=t41_model=t42_model=t43_model=t44_model=rep(0,300)
Sigma = diag(1,4)
for (i in 1:300){
    d = i/100.
    Sigma[1,2]=Sigma[2,1]= Sigma[3,4]=Sigma[4,3]=rho
    Sigma[1,3]=Sigma[3,1]=model(d,rv1,b1)
    Sigma[1,4]=Sigma[4,1]=(rho/rho1a)*model(abs(d+shift),rv1,b1)
    Sigma[2,3]=Sigma[3,2]=(rho/rho1a)*model(abs(d-shift),rv1,b1)
    Sigma[2,4]=Sigma[4,2]=alpha1*model(d,rv1,b1)+alpha2*model(d,rv2,b2)
    t11_model[i]=pmvnorm(lower=c(-Inf,-Inf,-Inf,-Inf),upper=c(q1,q2,q1,q2),mean=c(0,0,0,0),sigma=Sigma)/ pe1 
    t12_model[i]=pmvnorm(lower=c(-Inf,-Inf,-Inf,q2),upper=c(q1,q2,q1,Inf),mean=c(0,0,0,0),sigma=Sigma)/ pe1 
    t13_model[i]=pmvnorm(lower=c(-Inf,-Inf,q1,q3),upper=c(q1,q2,Inf,Inf),mean=c(0,0,0,0),sigma=Sigma)/ pe1 
    t14_model[i]=pmvnorm(lower=c(-Inf,-Inf,q1,-Inf),upper=c(q1,q2,Inf,q3),mean=c(0,0,0,0),sigma=Sigma)/ pe1
    t21_model[i]=pmvnorm(lower=c(-Inf,q2,-Inf,-Inf),upper=c(q1,Inf,q1,q2),mean=c(0,0,0,0),sigma=Sigma)/ pe2
    t22_model[i]=pmvnorm(lower=c(-Inf,q2,-Inf,q2),upper=c(q1,Inf,q1,Inf),mean=c(0,0,0,0),sigma=Sigma)/ pe2
    t23_model[i]=pmvnorm(lower=c(-Inf,q2,q1,q3),upper=c(q1,Inf,Inf,Inf),mean=c(0,0,0,0),sigma=Sigma)/ pe2
    t24_model[i]=pmvnorm(lower=c(-Inf,q2,q1,-Inf),upper=c(q1,Inf,Inf,q3),mean=c(0,0,0,0),sigma=Sigma)/ pe2
    t31_model[i]=pmvnorm(lower=c(q1,q3,-Inf,-Inf),upper=c(Inf,Inf,q1,q2),mean=c(0,0,0,0),sigma=Sigma)/ pe3
    t32_model[i]=pmvnorm(lower=c(q1,q3,-Inf,q2),upper=c(Inf,Inf,q1,Inf),mean=c(0,0,0,0),sigma=Sigma)/ pe3
    t33_model[i]=pmvnorm(lower=c(q1,q3,q1,q3),upper=c(Inf,Inf,Inf,Inf),mean=c(0,0,0,0),sigma=Sigma)/ pe3
    t34_model[i]=pmvnorm(lower=c(q1,q3,q1,-Inf),upper=c(Inf,Inf,Inf,q3),mean=c(0,0,0,0),sigma=Sigma)/ pe3
    t41_model[i]=pmvnorm(lower=c(q1,-Inf,-Inf,-Inf),upper=c(Inf,q3,q1,q2),mean=c(0,0,0,0),sigma=Sigma)/ pe4
    t42_model[i]=pmvnorm(lower=c(q1,-Inf,-Inf,q2),upper=c(Inf,q3,q1,Inf),mean=c(0,0,0,0),sigma=Sigma)/ pe4
    t43_model[i]=pmvnorm(lower=c(q1,-Inf,q1,q3),upper=c(Inf,q3,Inf,Inf),mean=c(0,0,0,0),sigma=Sigma)/ pe4
    t44_model[i]=pmvnorm(lower=c(q1,-Inf,q1,-Inf),upper=c(Inf,q3,Inf,q3),mean=c(0,0,0,0),sigma=Sigma)/ pe4
}
par(mfrow=c(4,4))
t11<-tr_2d_vert(e1,e1,30,nz,0.1)
lines(z,t11_model)
t12<-tr_2d_vert(e1,e2,30,nz,0.1)
lines(z,t12_model)
t13<-tr_2d_vert(e1,e3,30,nz,0.1)
lines(z,t13_model)
t14<-tr_2d_vert(e1,e4,30,nz,0.1)
lines(z,t14_model)
t21<-tr_2d_vert(e2,e1,30,nz,0.1)
lines(z,t21_model)
t22<-tr_2d_vert(e2,e2,30,nz,0.1)
lines(z,t22_model)
t23<-tr_2d_vert(e2,e3,30,nz,0.1)
lines(z,t23_model)
t24<-tr_2d_vert(e2,e4,30,nz,0.1)
lines(z,t24_model)
t31<-tr_2d_vert(e3,e1,30,nz,0.1)
lines(z,t31_model)
t32<-tr_2d_vert(e3,e2,30,nz,0.1)
lines(z,t32_model)
t33<-tr_2d_vert(e3,e3,30,nz,0.1)
lines(z,t33_model)
t34<-tr_2d_vert(e3,e4,30,nz,0.1)
lines(z,t34_model)
t41<-tr_2d_vert(e4,e1,30,nz,0.1)
lines(z,t41_model)
t42<-tr_2d_vert(e4,e2,30,nz,0.1)
lines(z,t42_model)
t43<-tr_2d_vert(e4,e3,30,nz,0.1)
lines(z,t43_model)
t44<-tr_2d_vert(e4,e4,30,nz,0.1)
lines(z,t44_model)

t33d_model=t32d_model=t23d_model=t22d_model=rep(0,300)
Sigma = diag(1,4)
for (i in 1:300){
    d = i/100.
    Sigma[1,2]=Sigma[2,1]= Sigma[3,4]=Sigma[4,3]=rho34
    Sigma[1,3]=Sigma[3,1]=model(d,rv3,b3)
    Sigma[1,4]=Sigma[4,1]=Sigma[2,3]=Sigma[3,2]=rho34*model(d,rv3,b3)
    Sigma[2,4]=Sigma[4,2]=(rho34^2)*model(d,rv3,b3)+(1-rho34^2)*model(d,rv4,b4)

    t22d_model[i]=pmvnorm(lower=c(qd1,qd2,qd1,qd2),upper=c(Inf,Inf,Inf,Inf),mean=c(0,0,0,0),sigma=Sigma)/ pd2
    t23d_model[i]=pmvnorm(lower=c(qd1,qd2,-Inf,-Inf),upper=c(Inf,Inf,qd1,Inf),mean=c(0,0,0,0),sigma=Sigma)/ pd2
    t32d_model[i]=pmvnorm(lower=c(-Inf,-Inf,qd1,qd2),upper=c(qd1,Inf,Inf,Inf),mean=c(0,0,0,0),sigma=Sigma)/ pd3
    t33d_model[i]=pmvnorm(lower=c(-Inf,-Inf,-Inf,-Inf),upper=c(qd1,Inf,qd1,Inf),mean=c(0,0,0,0),sigma=Sigma)/ pd3
}
par(mfrow=c(2,2))
t22d<-tr_2d_vert(d2,d2,30,nz,0.1)
lines(z,t22d_model)
t23d<-tr_2d_vert(d2,d3,30,nz,0.1)
lines(z,t23d_model)
t32d<-tr_2d_vert(d3,d2,30,nz,0.1)
lines(z,t32d_model)
t33d<-tr_2d_vert(d3,d3,30,nz,0.1)
lines(z,t33d_model)

td1e1_model=td1e2_model=td1e3_model=td1e4_model=td2e1_model=td2e2_model=td2e3_model=td2e4_model=rep(0,300)
te1d1_model=te2d1_model=te3d1_model=te4d1_model=te1d2_model=te2d2_model=te3d2_model=te4d2_model=rep(0,300)
Sigma = diag(1,4)
for (i in 1:300){
    d = i/100.
    Sigma[1,2]=Sigma[2,1]=rho34
    Sigma[1,3]=Sigma[3,1]=c*model(-d-a13,rv1,b1)
    Sigma[1,4]=Sigma[4,1]=c*(rho/rho1a)*model(a13+d-shift,rv1,b1)
    Sigma[2,3]=Sigma[3,2]=e*model(a14+d,rv1,b1)
    Sigma[2,4]=Sigma[4,2]=e*(rho/rho1a)*model(a14+d-shift,rv1,b1)
    Sigma[3,4]=Sigma[4,3]=rho

    td1e1_model[i]=pmvnorm(lower=c(qd1,-Inf,-Inf,-Inf),upper=c(Inf,qd2,q1,q2),mean=c(0,0,0,0),sigma=Sigma)/ pd1
    td1e2_model[i]=pmvnorm(lower=c(qd1,-Inf,-Inf,q2),upper=c(Inf,qd2,q1,Inf),mean=c(0,0,0,0),sigma=Sigma)/ pd1
    td1e3_model[i]=pmvnorm(lower=c(qd1,-Inf,q1,q3),upper=c(Inf,qd2,Inf,Inf),mean=c(0,0,0,0),sigma=Sigma)/ pd1
    td1e4_model[i]=pmvnorm(lower=c(qd1,-Inf,q1,-Inf),upper=c(Inf,qd2,Inf,q3),mean=c(0,0,0,0),sigma=Sigma)/ pd1

    td2e1_model[i]=pmvnorm(lower=c(qd1,qd2,-Inf,-Inf),upper=c(Inf,Inf,q1,q2),mean=c(0,0,0,0),sigma=Sigma)/ pd2
    td2e2_model[i]=pmvnorm(lower=c(qd1,qd2,-Inf,q2),upper=c(Inf,Inf,q1,Inf),mean=c(0,0,0,0),sigma=Sigma)/ pd2
    td2e3_model[i]=pmvnorm(lower=c(qd1,qd2,q1,q3),upper=c(Inf,Inf,Inf,Inf),mean=c(0,0,0,0),sigma=Sigma)/ pd2
    td2e4_model[i]=pmvnorm(lower=c(qd1,qd2,q1,-Inf),upper=c(Inf,Inf,Inf,q3),mean=c(0,0,0,0),sigma=Sigma)/ pd2

    te1d1_model[i]=pmvnorm(lower=c(qd1,-Inf,-Inf,-Inf),upper=c(Inf,qd2,q1,q2),mean=c(0,0,0,0),sigma=Sigma)/ pe1
    te2d1_model[i]=pmvnorm(lower=c(qd1,-Inf,-Inf,q2),upper=c(Inf,qd2,q1,Inf),mean=c(0,0,0,0),sigma=Sigma)/ pe2
    te3d1_model[i]=pmvnorm(lower=c(qd1,-Inf,q1,q3),upper=c(Inf,qd2,Inf,Inf),mean=c(0,0,0,0),sigma=Sigma)/ pe3
    te4d1_model[i]=pmvnorm(lower=c(qd1,-Inf,q1,-Inf),upper=c(Inf,qd2,Inf,q3),mean=c(0,0,0,0),sigma=Sigma)/ pe4

    te1d2_model[i]=pmvnorm(lower=c(qd1,qd2,-Inf,-Inf),upper=c(Inf,Inf,q1,q2),mean=c(0,0,0,0),sigma=Sigma)/ pe1
    te2d2_model[i]=pmvnorm(lower=c(qd1,qd2,-Inf,q2),upper=c(Inf,Inf,q1,Inf),mean=c(0,0,0,0),sigma=Sigma)/ pe2
    te3d2_model[i]=pmvnorm(lower=c(qd1,qd2,q1,q3),upper=c(Inf,Inf,Inf,Inf),mean=c(0,0,0,0),sigma=Sigma)/ pe3
    te4d2_model[i]=pmvnorm(lower=c(qd1,qd2,q1,-Inf),upper=c(Inf,Inf,Inf,q3),mean=c(0,0,0,0),sigma=Sigma)/ pe4
}

par(mfrow=c(2,4))
tr_2d_vert(d1,e1,30,nz,0.1)
lines(z,td1e1_model)
tr_2d_vert(d1,e2,30,nz,0.1)
lines(z,td1e2_model)
tr_2d_vert(d1,e3,30,nz,0.1)
lines(z,td1e3_model)
tr_2d_vert(d1,e4,30,nz,0.1)
lines(z,td1e4_model)
tr_2d_vert(d2,e1,30,nz,0.1)
lines(z,td2e1_model)
tr_2d_vert(d2,e2,30,nz,0.1)
lines(z,td2e2_model)
tr_2d_vert(d2,e3,30,nz,0.1)
lines(z,td2e3_model)
tr_2d_vert(d2,e4,30,nz,0.1)
lines(z,td2e4_model)

par(mfrow=c(4,2))
tr_2d_vert(e1,d1,30,nz,0.1)
lines(z,te1d1_model)
tr_2d_vert(e2,d1,30,nz,0.1)
lines(z,te2d1_model)
tr_2d_vert(e3,d1,30,nz,0.1)
lines(z,te3d1_model)
tr_2d_vert(e4,d1,30,nz,0.1)
lines(z,te4d1_model)
tr_2d_vert(e1,d2,30,nz,0.1)
lines(z,te1d2_model)
tr_2d_vert(e2,d2,30,nz,0.1)
lines(z,te2d2_model)
tr_2d_vert(e3,d2,30,nz,0.1)
lines(z,te3d2_model)
tr_2d_vert(e4,d2,30,nz,0.1)
lines(z,te4d2_model)

```
beautiful picture for transiograms

```{r}
png(file="latemartransiotest.png",width=2000,height = 1600,res=300)
par(mar=c(2,3,1,1),mfrow=c(4,4))
t11<-tr_2d_vert(e1,e1,30,nz,0.1)
lines(z,t11_model)
title(main=expression(paste('t'[e1e1],"(h)")),line=-1)
t12<-tr_2d_vert(e1,e2,30,nz,0.1)
lines(z,t12_model)
title(main=expression(paste('t'[e1e2],"(h)")),line=-1)
t13<-tr_2d_vert(e1,e3,30,nz,0.1)
lines(z,t13_model)
title(main=expression(paste('t'[e1e3],"(h)")),line=-1)
t14<-tr_2d_vert(e1,e4,30,nz,0.1)
lines(z,t14_model)
title(main=expression(paste('t'[e1e4],"(h)")),line=-1)
t21<-tr_2d_vert(e2,e1,30,nz,0.1)
lines(z,t21_model)
title(main=expression(paste('t'[e2e1],"(h)")),line=-1)
t22<-tr_2d_vert(e2,e2,30,nz,0.1)
lines(z,t22_model)
title(main=expression(paste('t'[e2e2],"(h)")),line=-1)
t23<-tr_2d_vert(e2,e3,30,nz,0.1)
lines(z,t23_model)
title(main=expression(paste('t'[e2e3],"(h)")),line=-1)
t24<-tr_2d_vert(e2,e4,30,nz,0.1)
lines(z,t24_model)
title(main=expression(paste('t'[e2e4],"(h)")),line=-1)
t31<-tr_2d_vert(e3,e1,30,nz,0.1)
lines(z,t31_model)
title(main=expression(paste('t'[e3e1],"(h)")),line=-1)
t32<-tr_2d_vert(e3,e2,30,nz,0.1)
lines(z,t32_model)
title(main=expression(paste('t'[e3e2],"(h)")),line=-1)
t33<-tr_2d_vert(e3,e3,30,nz,0.1)
lines(z,t33_model)
title(main=expression(paste('t'[e3e3],"(h)")),line=-1)
t34<-tr_2d_vert(e3,e4,30,nz,0.1)
lines(z,t34_model)
title(main=expression(paste('t'[e3e4],"(h)")),line=-1)
t41<-tr_2d_vert(e4,e1,30,nz,0.1)
lines(z,t41_model)
title(main=expression(paste('t'[e4e1],"(h)")),line=-1)
t42<-tr_2d_vert(e4,e2,30,nz,0.1)
lines(z,t42_model)
title(main=expression(paste('t'[e4e2],"(h)")),line=-1)
t43<-tr_2d_vert(e4,e3,30,nz,0.1)
lines(z,t43_model)
title(main=expression(paste('t'[e4e3],"(h)")),line=-1)
t44<-tr_2d_vert(e4,e4,30,nz,0.1)
lines(z,t44_model)
title(main=expression(paste('t'[e4e4],"(h)")),line=-1)
```
we are showing here a figure with the transiograms on the realization
```{r}
z = (1:300)/100.
z2= (1:60)/20
png(file="latemartransiototal.png",width=2000,height = 1600,res=300)
par(mar=c(2,3,1,1),mfrow=c(4,4))
t11<-tr_2d_vert(e1,e1,30,nz,0.1)
lines(z,t11_model)
lines(z2,t11real,lwd=0.6)
lines(z2,t11real2,lwd=0.6)
lines(z2,t11real3,lwd=0.6)
title(main=expression(paste('t'[e1e1],"(h)")),line=-1)
t12<-tr_2d_vert(e1,e2,30,nz,0.1)
lines(z,t12_model)
lines(z2,t12real,lwd=0.5)
lines(z2,t12real2,lwd=0.5)
lines(z2,t12real3,lwd=0.5)
title(main=expression(paste('t'[e1e2],"(h)")),line=-1)
t13<-tr_2d_vert(e1,e3,30,nz,0.1)
lines(z,t13_model)
lines(z2,t13real,lwd=0.5)
lines(z2,t13real2,lwd=0.5)
lines(z2,t13real3,lwd=0.5)
title(main=expression(paste('t'[e1e3],"(h)")),line=-1)
t14<-tr_2d_vert(e1,e4,30,nz,0.1)
lines(z,t14_model)
lines(z2,t14real,lwd=0.5)
lines(z2,t14real2,lwd=0.5)
lines(z2,t14real3,lwd=0.5)
title(main=expression(paste('t'[e1e4],"(h)")),line=-1)
t21<-tr_2d_vert(e2,e1,30,nz,0.1)
lines(z,t21_model)
lines(z2,t21real,lwd=0.5)
lines(z2,t21real2,lwd=0.5)
lines(z2,t21real3,lwd=0.5)
title(main=expression(paste('t'[e2e1],"(h)")),line=-1)
t22<-tr_2d_vert(e2,e2,30,nz,0.1)
lines(z,t22_model)
lines(z2,t22real,lwd=0.5)
lines(z2,t22real2,lwd=0.5)
lines(z2,t22real3,lwd=0.5)
title(main=expression(paste('t'[e2e2],"(h)")),line=-1)
t23<-tr_2d_vert(e2,e3,30,nz,0.1)
lines(z,t23_model)
lines(z2,t23real,lwd=0.5)
lines(z2,t23real2,lwd=0.5)
lines(z2,t23real3,lwd=0.5)
title(main=expression(paste('t'[e2e3],"(h)")),line=-1)
t24<-tr_2d_vert(e2,e4,30,nz,0.1)
lines(z,t24_model)
lines(z2,t24real,lwd=0.5)
lines(z2,t24real2,lwd=0.5)
lines(z2,t24real3,lwd=0.5)
title(main=expression(paste('t'[e2e4],"(h)")),line=-1)
t31<-tr_2d_vert(e3,e1,30,nz,0.1)
lines(z,t31_model)
lines(z2,t31real,lwd=0.5)
lines(z2,t31real2,lwd=0.5)
lines(z2,t31real3,lwd=0.5)
title(main=expression(paste('t'[e3e1],"(h)")),line=-1)
t32<-tr_2d_vert(e3,e2,30,nz,0.1)
lines(z,t32_model)
lines(z2,t32real,lwd=0.5)
lines(z2,t32real2,lwd=0.5)
lines(z2,t32real3,lwd=0.5)
title(main=expression(paste('t'[e3e2],"(h)")),line=-1)
t33<-tr_2d_vert(e3,e3,30,nz,0.1)
lines(z,t33_model)
lines(z2,t33real,lwd=0.5)
lines(z2,t33real2,lwd=0.5)
lines(z2,t33real3,lwd=0.5)
title(main=expression(paste('t'[e3e3],"(h)")),line=-1)
t34<-tr_2d_vert(e3,e4,30,nz,0.1)
lines(z,t34_model)
lines(z2,t34real,lwd=0.5)
lines(z2,t34real2,lwd=0.5)
lines(z2,t34real3,lwd=0.5)
title(main=expression(paste('t'[e3e4],"(h)")),line=-1)
t41<-tr_2d_vert(e4,e1,30,nz,0.1)
lines(z,t41_model)
lines(z2,t41real,lwd=0.5)
lines(z2,t41real2,lwd=0.5)
lines(z2,t41real3,lwd=0.5)
title(main=expression(paste('t'[e4e1],"(h)")),line=-1)
t42<-tr_2d_vert(e4,e2,30,nz,0.1)
lines(z,t42_model)
lines(z2,t42real,lwd=0.5)
lines(z2,t42real2,lwd=0.5)
lines(z2,t42real3,lwd=0.5)
title(main=expression(paste('t'[e4e2],"(h)")),line=-1)
t43<-tr_2d_vert(e4,e3,30,nz,0.1)
lines(z,t43_model)
lines(z2,t43real,lwd=0.5)
lines(z2,t43real2,lwd=0.5)
lines(z2,t43real3,lwd=0.5)
title(main=expression(paste('t'[e4e3],"(h)")),line=-1)
t44<-tr_2d_vert(e4,e4,30,nz,0.1)
lines(z,t44_model)
lines(z2,t44real,lwd=0.5)
lines(z2,t44real2,lwd=0.5)
lines(z2,t44real3,lwd=0.5)
title(main=expression(paste('t'[e4e4],"(h)")),line=-1)
```

lets try to fit the embedded transiograms
```{r}
rv1=0.4
rv2=1.2
rhx1=40
rhx2=40
b1=0
b2=5
rho=0.8
shift=0.1
rho1a<-model(shift,rv1,b1)
warning(rho>rho1a)
alpha1=(rho/rho1a)^2
alpha2=1-(rho/rho1a)^2
rv3=0.2
rv4=0.3
rhx3=40
rhx4=40
b3=0
b4=0
e=-0.8
f=-0.5

a14=-0.1
a24=0.1
rho1a14 = model(a14,rv1,b1)
rho2a24=model(a24,rv2,b2)

#thresholds
q1=qnorm(pe1+pe2)
Sigma1 = matrix(c(1,rho,rho,1),2,2)
q2=0
obj = Inf
for ( test in 1:100 ){
  q2test = qnorm(test/100)
  newobj =abs( pmvnorm(lower=c(-Inf,-Inf),upper=c(q1,q2test),mean=c(0,0),sigma=Sigma1) - pe1 ) 
  if (newobj < obj){
    q2 = q2test
    obj = newobj
  }
}
q3=0
obj = Inf
for ( test in 1:100 ){
  q3test = qnorm(test/100)
  newobj =abs( pmvnorm(lower=c(q1,-Inf),upper=c(Inf,q3test),mean=c(0,0),sigma=Sigma1) - pe4 ) 
  if (newobj < obj){
    q3 = q3test
    obj = newobj
  }
}
d = 1/5.
    Sigma[1,2]=Sigma[2,1]= Sigma[3,4]=Sigma[4,3]=rho
    Sigma[1,3]=Sigma[3,1]=model(d,rv1,b1)
    Sigma[1,4]=Sigma[4,1]=(rho/rho1a)*model(abs(d+shift),rv1,b1)
    Sigma[2,3]=Sigma[3,2]=(rho/rho1a)*model(abs(d-shift),rv1,b1)
    Sigma[2,4]=Sigma[4,2]=alpha1*model(d,rv1,b1)+alpha2*model(d,rv2,b2)
    r11_model=1-pmvnorm(lower=c(-Inf,-Inf,-Inf,-Inf),upper=c(q1,q2,q1,q2),mean=c(0,0,0,0),sigma=Sigma)/ pe1 
    r12_model=pmvnorm(lower=c(-Inf,-Inf,-Inf,q2),upper=c(q1,q2,q1,Inf),mean=c(0,0,0,0),sigma=Sigma)/ pe1 
    r13_model=pmvnorm(lower=c(-Inf,-Inf,q1,q3),upper=c(q1,q2,Inf,Inf),mean=c(0,0,0,0),sigma=Sigma)/ pe1 
    r14_model=pmvnorm(lower=c(-Inf,-Inf,q1,-Inf),upper=c(q1,q2,Inf,q3),mean=c(0,0,0,0),sigma=Sigma)/ pe1
    r21_model=pmvnorm(lower=c(-Inf,q2,-Inf,-Inf),upper=c(q1,Inf,q1,q2),mean=c(0,0,0,0),sigma=Sigma)/ pe2
    r22_model=1-pmvnorm(lower=c(-Inf,q2,-Inf,q2),upper=c(q1,Inf,q1,Inf),mean=c(0,0,0,0),sigma=Sigma)/ pe2
    r23_model=pmvnorm(lower=c(-Inf,q2,q1,q3),upper=c(q1,Inf,Inf,Inf),mean=c(0,0,0,0),sigma=Sigma)/ pe2
    r24_model=pmvnorm(lower=c(-Inf,q2,q1,-Inf),upper=c(q1,Inf,Inf,q3),mean=c(0,0,0,0),sigma=Sigma)/ pe2
    r31_model=pmvnorm(lower=c(q1,q3,-Inf,-Inf),upper=c(Inf,Inf,q1,q2),mean=c(0,0,0,0),sigma=Sigma)/ pe3
    r32_model=pmvnorm(lower=c(q1,q3,-Inf,q2),upper=c(Inf,Inf,q1,Inf),mean=c(0,0,0,0),sigma=Sigma)/ pe3
    r33_model=1-pmvnorm(lower=c(q1,q3,q1,q3),upper=c(Inf,Inf,Inf,Inf),mean=c(0,0,0,0),sigma=Sigma)/ pe3
    r34_model=pmvnorm(lower=c(q1,q3,q1,-Inf),upper=c(Inf,Inf,Inf,q3),mean=c(0,0,0,0),sigma=Sigma)/ pe3
    r41_model=pmvnorm(lower=c(q1,-Inf,-Inf,-Inf),upper=c(Inf,q3,q1,q2),mean=c(0,0,0,0),sigma=Sigma)/ pe4
    r42_model=pmvnorm(lower=c(q1,-Inf,-Inf,q2),upper=c(Inf,q3,q1,Inf),mean=c(0,0,0,0),sigma=Sigma)/ pe4
    r43_model=pmvnorm(lower=c(q1,-Inf,q1,q3),upper=c(Inf,q3,Inf,Inf),mean=c(0,0,0,0),sigma=Sigma)/ pe4
    r44_model=1-pmvnorm(lower=c(q1,-Inf,q1,-Inf),upper=c(Inf,q3,Inf,q3),mean=c(0,0,0,0),sigma=Sigma)/ pe4
    matrix(c(0,r12_model/r11_model,r13_model/r11_model,r14_model/r11_model,r21_model/r22_model,0,r23_model/r22_model,r24_model/r22_model,r31_model/r33_model,r32_model/r33_model,0,r34_model/r33_model,r41_model/r44_model,r42_model/r44_model,r43_model/r44_model,0),4,4,byrow=TRUE)
```

trying td2e1, td2e2, td2e3 and td2e4

```{r}
rv1=0.3
rv2=0.5
rhx1=40
rhx2=40
b1=0
b2=0
rho=0.6
shift=0.1
rho1a<-model(shift,rv1,b1)
warning(rho>rho1a)
alpha1=(rho/rho1a)^2
alpha2=1-(rho/rho1a)^2
rv3=0.2
rv4=0.3
rhx3=40
rhx4=40
b3=0
b4=0
e=0.8

a14=0.1
rho1a14 = model(a14,rv1,b1)
#thresholds
q1=qnorm(pe1+pe2)
Sigma1 = matrix(c(1,rho,rho,1),2,2)
q2=0
obj = Inf
for ( test in 1:100 ){
  q2test = qnorm(test/100)
  newobj =abs( pmvnorm(lower=c(-Inf,-Inf),upper=c(q1,q2test),mean=c(0,0),sigma=Sigma1) - pe1 ) 
  if (newobj < obj){
    q2 = q2test
    obj = newobj
  }
}
q3=0
obj = Inf
for ( test in 1:100 ){
  q3test = qnorm(test/100)
  newobj =abs( pmvnorm(lower=c(q1,-Inf),upper=c(Inf,q3test),mean=c(0,0),sigma=Sigma1) - pe4 ) 
  if (newobj < obj){
    q3 = q3test
    obj = newobj
  }
}

c(q1,q2,q3)

qd1e4=qnorm(pd3e4) # no correlation with the third Gaussian function
Sigmad = diag(1,3)
qd2e2=0
qd2e3=0
obje2 = Inf
obje3 = Inf
for ( test in 1:100 ){
  qd2e2test = qnorm(test/100)
  qd2e3test = qnorm(test/100)
  Sigmad[1,2]=Sigmad[2,1]=e*rho1a14
  Sigmad[1,3]=Sigmad[3,1]=e*(rho/rho1a)*model(a14-shift,rv1,b1)
  Sigmad[2,3]=Sigmad[3,2]=rho
  newobje2 =abs( pmvnorm(lower=c(qd2e2test,-Inf,q2),upper=c(Inf,q1,Inf),mean=c(0,0,0),sigma=Sigmad)/pe2 - pd2e2 ) 
  newobje3 =abs( pmvnorm(lower=c(qd2e2test,q1,q3),upper=c(Inf,Inf,Inf),mean=c(0,0,0),sigma=Sigmad)/pe3 - pd2e3 )
  if (newobje2 < obje2){
    qd2e2 = qd2e2test
    obje2 = newobje2
  }
  if (newobje3 < obje3){
    qd2e3 = qd2e3test
    obje3 = newobje3
  }
}

c(qd1e4,qd2e2,qd2e3)

td2e1_model=td2e2_model=td2e3_model=td2e4_model=rep(0,300)

Sigma = diag(1,5)
for (i in 1:300){
    d = i/100.
    Sigma[1,2]=Sigma[2,1]=Sigma[4,5]=Sigma[5,4]=rho
    Sigma[1,3]=Sigma[3,1]=e*rho1a14
    Sigma[1,4]=Sigma[4,1]=model(d,rv1,b1)
    Sigma[1,5]=Sigma[5,1]=rho*model(d+shift,rv1,b1)/rho1a
    Sigma[2,3]=Sigma[3,2]=e*rho*model(shift-a14,rv1,b1)/rho1a
    Sigma[2,4]=Sigma[4,2]=rho*model(shift-d,rv1,b1)/rho1a
    Sigma[2,5]=Sigma[5,2]=(1-(rho/rho1a)^2)*model(d,rv2,b2)+(rho^2)*model(d,rv1,b1)/(rho1a^2)
    Sigma[3,4]=Sigma[4,3]=e*model(d-a14,rv1,b1)
    Sigma[3,5]=Sigma[5,3]=e*rho*model(d+shift-a14,rv1,b1)/rho1a

    td2e1_model[i]=pmvnorm(lower=c(-Inf,q2,qd2e2,-Inf,-Inf),upper=c(q1,Inf,Inf,q1,q2),mean=c(0,0,0,0,0),sigma=Sigma)/ pd2
    td2e1_model[i]=td2e1_model[i]+pmvnorm(lower=c(q1,q3,qd2e3,-Inf,-Inf),upper=c(Inf,Inf,Inf,q1,q2),mean=c(0,0,0,0,0),sigma=Sigma)/ pd2
    if(td2e1_model[i]==0){td2e1_model[i]=NA}

    td2e2_model[i]=pmvnorm(lower=c(-Inf,q2,qd2e2,-Inf,q2),upper=c(q1,Inf,Inf,q1,Inf),mean=c(0,0,0,0,0),sigma=Sigma)/ pd2
    td2e2_model[i]=td2e2_model[i]+pmvnorm(lower=c(q1,q3,qd2e3,-Inf,q2),upper=c(Inf,Inf,Inf,q1,Inf),mean=c(0,0,0,0,0),sigma=Sigma)/ pd2
    if(td2e2_model[i]==0){td2e2_model[i]=NA}

    td2e3_model[i]=pmvnorm(lower=c(-Inf,q2,qd2e2,q1,q3),upper=c(q1,Inf,Inf,Inf,Inf),mean=c(0,0,0,0,0),sigma=Sigma)/ pd2
    td2e3_model[i]=td2e3_model[i]+pmvnorm(lower=c(q1,q3,qd2e3,q1,q3),upper=c(Inf,Inf,Inf,Inf,Inf),mean=c(0,0,0,0,0),sigma=Sigma)/ pd2
    if(td2e3_model[i]==0){td2e3_model[i]=NA}

    td2e4_model[i]=pmvnorm(lower=c(-Inf,q2,qd2e2,q1,-Inf),upper=c(q1,Inf,Inf,Inf,q3),mean=c(0,0,0,0,0),sigma=Sigma)/ pd2
    td2e4_model[i]=td2e4_model[i]+pmvnorm(lower=c(q1,q3,qd2e3,q1,-Inf),upper=c(Inf,Inf,Inf,Inf,q3),mean=c(0,0,0,0,0),sigma=Sigma)/ pd2
    if(td2e4_model[i]==0){td2e4_model[i]=NA}
}
z = (1:300)/100.
tr_2d_vert(d2,e1,30,nz,0.1)
lines(z,td2e1_model)
tr_2d_vert(d2,e2,30,nz,0.1)
lines(z,td2e2_model)
tr_2d_vert(d2,e3,30,nz,0.1)
lines(z,td2e3_model)
tr_2d_vert(d2,e4,30,nz,0.1)
lines(z,td2e4_model)

```

ok we develop now a more complex model to see if we are able to capture better the co-transiograms of 50dol. 
We add for this a correlation between the second gaussian function and the fourth which slightly complexify the correlation matrix, but not that much.

```{r}
rv1=0.3
rv2=1.2
rhx1=40
rhx2=40
b1=0
b2=5
rho=0.6
shift=0.1
rho1a<-model(shift,rv1,b1)
warning(rho>rho1a)
alpha1=(rho/rho1a)^2
alpha2=1-(rho/rho1a)^2
rv3=0.2
rv4=0.3
rhx3=40
rhx4=40
b3=0
b4=0
e=-0.8
f=-0.5

a14=-0.1
a24=0.1
rho1a14 = model(a14,rv1,b1)
rho2a24=model(a24,rv2,b2)
#thresholds
q1=qnorm(pe1+pe2)
Sigma1 = matrix(c(1,rho,rho,1),2,2)
q2=0
obj = Inf
for ( test in 1:100 ){
  q2test = qnorm(test/100)
  newobj =abs( pmvnorm(lower=c(-Inf,-Inf),upper=c(q1,q2test),mean=c(0,0),sigma=Sigma1) - pe1 ) 
  if (newobj < obj){
    q2 = q2test
    obj = newobj
  }
}
q3=0
obj = Inf
for ( test in 1:100 ){
  q3test = qnorm(test/100)
  newobj =abs( pmvnorm(lower=c(q1,-Inf),upper=c(Inf,q3test),mean=c(0,0),sigma=Sigma1) - pe4 ) 
  if (newobj < obj){
    q3 = q3test
    obj = newobj
  }
}

c(q1,q2,q3)

Sigmad = diag(1,3)
qd2e2=0
qd2e3=0
qd1e4=0
obje2 = Inf
obje3 = Inf
obje4 = Inf
for ( test in 1:100 ){
  qd2e2test = qnorm(test/100)
  qd2e3test = qnorm(test/100)
  qd1e4test = qnorm(test/100)
  Sigmad[1,2]=Sigmad[2,1]=e*rho1a14
  Sigmad[1,3]=Sigmad[3,1]=e*(rho/rho1a)*model(a14-shift,rv1,b1)+f*sqrt(1-(rho/rho1a)^2)*model(a24,rv2,b2)
  Sigmad[2,3]=Sigmad[3,2]=rho
  newobje2 =abs( pmvnorm(lower=c(qd2e2test,-Inf,q2),upper=c(Inf,q1,Inf),mean=c(0,0,0),sigma=Sigmad)/pe2 - pd2e2 ) 
  newobje3 =abs( pmvnorm(lower=c(qd2e3test,q1,q3),upper=c(Inf,Inf,Inf),mean=c(0,0,0),sigma=Sigmad)/pe3 - pd2e3 )
  newobje4 =abs( pmvnorm(lower=c(qd1e4test,q1,-Inf),upper=c(Inf,Inf,q3),mean=c(0,0,0),sigma=Sigmad)/pe4 - pd3e4 )
  if (newobje2 < obje2){
    qd2e2 = qd2e2test
    obje2 = newobje2
  }
  if (newobje3 < obje3){
    qd2e3 = qd2e3test
    obje3 = newobje3
  }
  if (newobje4 < obje4){
    qd1e4 = qd1e4test
    obje4 = newobje4
  }
}

c(qd1e4,qd2e2,qd2e3)

td2e1_model=td2e2_model=td2e3_model=td2e4_model=rep(0,300)
td3e1_model=td3e2_model=td3e3_model=td3e4_model=rep(0,300)

Sigma = diag(1,5)
for (i in 1:300){
    d = i/100.
    Sigma[1,2]=Sigma[2,1]=Sigma[4,5]=Sigma[5,4]=rho
    Sigma[1,3]=Sigma[3,1]=e*rho1a14
    Sigma[1,4]=Sigma[4,1]=model(d,rv1,b1)
    Sigma[1,5]=Sigma[5,1]=rho*model(d+shift,rv1,b1)/rho1a
    Sigma[2,3]=Sigma[3,2]=(e*rho*model(shift-a14,rv1,b1)/rho1a)+f*sqrt(1-(rho/rho1a)^2)*model(a24,rv2,b2)
    Sigma[2,4]=Sigma[4,2]=rho*model(shift-d,rv1,b1)/rho1a
    Sigma[2,5]=Sigma[5,2]=(1-(rho/rho1a)^2)*model(d,rv2,b2)+(rho^2)*model(d,rv1,b1)/(rho1a^2)
    Sigma[3,4]=Sigma[4,3]=e*model(d-a14,rv1,b1)
    Sigma[3,5]=Sigma[5,3]=(e*rho*model(d+shift-a14,rv1,b1)/rho1a)+f*sqrt(1-(rho/rho1a)^2)*model(d-a24,rv2,b2)

    td2e1_model[i]=pmvnorm(lower=c(-Inf,q2,qd2e2,-Inf,-Inf),upper=c(q1,Inf,Inf,q1,q2),mean=c(0,0,0,0,0),sigma=Sigma)/ pd2
    td2e1_model[i]=td2e1_model[i]+pmvnorm(lower=c(q1,q3,qd2e3,-Inf,-Inf),upper=c(Inf,Inf,Inf,q1,q2),mean=c(0,0,0,0,0),sigma=Sigma)/ pd2
    if(td2e1_model[i]==0){td2e1_model[i]=NA}

    td2e2_model[i]=pmvnorm(lower=c(-Inf,q2,qd2e2,-Inf,q2),upper=c(q1,Inf,Inf,q1,Inf),mean=c(0,0,0,0,0),sigma=Sigma)/ pd2
    td2e2_model[i]=td2e2_model[i]+pmvnorm(lower=c(q1,q3,qd2e3,-Inf,q2),upper=c(Inf,Inf,Inf,q1,Inf),mean=c(0,0,0,0,0),sigma=Sigma)/ pd2
    if(td2e2_model[i]==0){td2e2_model[i]=NA}

    td2e3_model[i]=pmvnorm(lower=c(-Inf,q2,qd2e2,q1,q3),upper=c(q1,Inf,Inf,Inf,Inf),mean=c(0,0,0,0,0),sigma=Sigma)/ pd2
    td2e3_model[i]=td2e3_model[i]+pmvnorm(lower=c(q1,q3,qd2e3,q1,q3),upper=c(Inf,Inf,Inf,Inf,Inf),mean=c(0,0,0,0,0),sigma=Sigma)/ pd2
    if(td2e3_model[i]==0){td2e3_model[i]=NA}

    td2e4_model[i]=pmvnorm(lower=c(-Inf,q2,qd2e2,q1,-Inf),upper=c(q1,Inf,Inf,Inf,q3),mean=c(0,0,0,0,0),sigma=Sigma)/ pd2
    td2e4_model[i]=td2e4_model[i]+pmvnorm(lower=c(q1,q3,qd2e3,q1,-Inf),upper=c(Inf,Inf,Inf,Inf,q3),mean=c(0,0,0,0,0),sigma=Sigma)/ pd2
    if(td2e4_model[i]==0){td2e4_model[i]=NA}

    td3e1_model[i]=pmvnorm(lower=c(q1,-Inf,qd1e4,-Inf,-Inf),upper=c(Inf,q3,Inf,q1,q2),mean=c(0,0,0,0,0),sigma=Sigma)/ pd3
    if(td3e1_model[i]==0){td3e1_model[i]=NA}
    td3e2_model[i]=pmvnorm(lower=c(q1,-Inf,qd1e4,-Inf,q2),upper=c(Inf,q3,Inf,q1,Inf),mean=c(0,0,0,0,0),sigma=Sigma)/ pd3
    if(td3e2_model[i]==0){td3e2_model[i]=NA}
    td3e3_model[i]=pmvnorm(lower=c(q1,-Inf,qd1e4,q1,q3),upper=c(Inf,q3,Inf,Inf,Inf),mean=c(0,0,0,0,0),sigma=Sigma)/ pd3
    if(td3e3_model[i]==0){td3e3_model[i]=NA}
    td3e4_model[i]=pmvnorm(lower=c(q1,-Inf,qd1e4,q1,-Inf),upper=c(Inf,q3,Inf,Inf,q3),mean=c(0,0,0,0,0),sigma=Sigma)/ pd3
    if(td3e4_model[i]==0){td3e4_model[i]=NA}
}

z = (1:300)/100.
par(mfrow=c(2,4))
tr_2d_vert(d3,e1,30,nz,0.1)
lines(z,td3e1_model)
tr_2d_vert(d3,e2,30,nz,0.1)
lines(z,td3e2_model)
tr_2d_vert(d3,e3,30,nz,0.1)
lines(z,td3e3_model)
tr_2d_vert(d3,e4,30,nz,0.1)
lines(z,td3e4_model)
tr_2d_vert(d2,e1,30,nz,0.1)
lines(z,td2e1_model)
tr_2d_vert(d2,e2,30,nz,0.1)
lines(z,td2e2_model)
tr_2d_vert(d2,e3,30,nz,0.1)
lines(z,td2e3_model)
tr_2d_vert(d2,e4,30,nz,0.1)
lines(z,td2e4_model)
```

nice figure
```{r}
z = (1:300)/100.
z2= (1:60)/20
png(file="latemarcotransiototal.png",width=3000,height = 1200,res=300)
par(mar=c(2,3,1,1),mfrow=c(2,4))
tr_2d_vert(d3,e1,30,nz,0.1)
lines(z,td3e1_model)
lines(z2,td3e1real,lwd=0.5)
lines(z2,td3e1real2,lwd=0.5)
lines(z2,td3e1real3,lwd=0.5)
title(main=expression(paste('t'[d1e1],"(h)")),line=-1,cex.main=2)
tr_2d_vert(d3,e2,30,nz,0.1)
lines(z,td3e2_model)
lines(z2,td3e2real,lwd=0.5)
lines(z2,td3e2real2,lwd=0.5)
lines(z2,td3e2real3,lwd=0.5)
title(main=expression(paste('t'[d1e2],"(h)")),cex.main=2)
tr_2d_vert(d3,e3,30,nz,0.1)
lines(z,td3e3_model)
lines(z2,td3e3real,lwd=0.5)
lines(z2,td3e3real2,lwd=0.5)
lines(z2,td3e3real3,lwd=0.5)
title(main=expression(paste('t'[d1e3],"(h)")),line=-1,cex.main=2)
tr_2d_vert(d3,e4,30,nz,0.1)
lines(z,td3e4_model)
lines(z2,td3e4real,lwd=0.5)
lines(z2,td3e4real2,lwd=0.5)
lines(z2,td3e4real3,lwd=0.5)
title(main=expression(paste('t'[d1e4],"(h)")),line=-1,cex.main=2)
tr_2d_vert(d2,e1,30,nz,0.1)
lines(z,td2e1_model)
lines(z2,td2e1real,lwd=0.5)
lines(z2,td2e1real2,lwd=0.5)
lines(z2,td2e1real3,lwd=0.5)
title(main=expression(paste('t'[d2e1],"(h)")),line=-1,cex.main=2)
tr_2d_vert(d2,e2,30,nz,0.1)
lines(z,td2e2_model)
lines(z2,td2e2real,lwd=0.5)
lines(z2,td2e2real2,lwd=0.5)
lines(z2,td2e2real3,lwd=0.5)
title(main=expression(paste('t'[d2e2],"(h)")),line=-1,cex.main=2)
tr_2d_vert(d2,e3,30,nz,0.1)
lines(z,td2e3_model)
lines(z2,td2e3real,lwd=0.5)
lines(z2,td2e3real2,lwd=0.5)
lines(z2,td2e3real3,lwd=0.5)
title(main=expression(paste('t'[d2e3],"(h)")),line=-1,cex.main=2)
tr_2d_vert(d2,e4,30,nz,0.1)
title(main=expression(paste('t'[d2e4],"(h)")),line=-1,cex.main=2)
lines(z,td2e4_model)
lines(z2,td2e4real,lwd=0.5)
lines(z2,td2e4real2,lwd=0.5)
lines(z2,td2e4real3,lwd=0.5)
```

we need now to look at the auto transiograms of the diagenetic facies 
we use the preceding covariance matrix and add one order
```{r}
Sigmad = diag(1,3)
qd2e2=0
qd2e3=0
qd1e4=0
obje2 = Inf
obje3 = Inf
obje4 = Inf
for ( test in 1:100 ){
  qd2e2test = qnorm(test/100)
  qd2e3test = qnorm(test/100)
  qd1e4test = qnorm(test/100)
  Sigmad[1,2]=Sigmad[2,1]=e*rho1a14
  Sigmad[1,3]=Sigmad[3,1]=e*(rho/rho1a)*model(a14-shift,rv1,b1)+f*sqrt(1-(rho/rho1a)^2)*model(a24,rv2,b2)
  Sigmad[2,3]=Sigmad[3,2]=rho
  newobje2 =abs( pmvnorm(lower=c(qd2e2test,-Inf,q2),upper=c(Inf,q1,Inf),mean=c(0,0,0),sigma=Sigmad)/pe2 - pd2e2 ) 
  newobje3 =abs( pmvnorm(lower=c(qd2e3test,q1,q3),upper=c(Inf,Inf,Inf),mean=c(0,0,0),sigma=Sigmad)/pe3 - pd2e3 )
  newobje4 =abs( pmvnorm(lower=c(qd1e4test,q1,-Inf),upper=c(Inf,Inf,q3),mean=c(0,0,0),sigma=Sigmad)/pe4 - pd3e4 )
  if (newobje2 < obje2){
    qd2e2 = qd2e2test
    obje2 = newobje2
  }
  if (newobje3 < obje3){
    qd2e3 = qd2e3test
    obje3 = newobje3
  }
  if (newobje4 < obje4){
    qd1e4 = qd1e4test
    obje4 = newobje4
  }
}

td2d2_model=td2d3_model=td3d2_model=td3d3_model=rep(0,300)
Sigma = diag(1,6)
for (i in 1:300){
    d = i/100.
    Sigma[1,2]=Sigma[2,1]=Sigma[4,5]=Sigma[5,4]=rho
    Sigma[1,3]=Sigma[3,1]=Sigma[6,4]=Sigma[4,6]=e*rho1a14
    Sigma[1,4]=Sigma[4,1]=model(d,rv1,b1)
    Sigma[1,5]=Sigma[5,1]=rho*model(d+shift,rv1,b1)/rho1a
    Sigma[2,3]=Sigma[3,2]=Sigma[5,6]=Sigma[6,5]=(e*rho*model(shift-a14,rv1,b1)/rho1a)+f*sqrt(1-(rho/rho1a)^2)*model(a24,rv2,b2)
    Sigma[2,4]=Sigma[4,2]=rho*model(shift-d,rv1,b1)/rho1a
    Sigma[2,5]=Sigma[5,2]=(1-(rho/rho1a)^2)*model(d,rv2,b2)+(rho^2)*model(d,rv1,b1)/(rho1a^2)
    Sigma[3,4]=Sigma[4,3]=e*model(d-a14,rv1,b1)
    Sigma[3,5]=Sigma[5,3]=(e*rho*model(d+shift-a14,rv1,b1)/rho1a)+f*sqrt(1-(rho/rho1a)^2)*model(d-a24,rv2,b2)
    Sigma[3,6]=Sigma[6,3]=(e^2)*model(d,rv1,b1)+(f^2)*model(d,rv2,b2)+(1-(e^2)-(f^2))*model(d,rv3,b3)
    Sigma[1,6]=Sigma[6,1]=e*model(d+a14,rv1,b1)
    Sigma[2,6]=Sigma[6,2]=(rho/rho1a)*e*model(d+a14-shift,rv1,b1)+f*sqrt(1-(rho/rho1a)^2)*model(d+a24,rv2,b2)

    td3d3_model[i]=pmvnorm(lower=c(q1,-Inf,qd1e4,q1,-Inf,qd1e4),upper=c(Inf,q3,Inf,Inf,q3,Inf),mean=c(0,0,0,0,0,0),sigma=Sigma)/ pd3
    if(td3d3_model[i]==0){td3d3_model[i]=NA}

    td2d2_model[i]=pmvnorm(lower=c(-Inf,q2,qd2e2,q1,q3,qd2e2),upper=c(q1,Inf,Inf,Inf,Inf,Inf),mean=c(0,0,0,0,0,0),sigma=Sigma)/ pd2
    td2d2_model[i]=td2d2_model[i]+pmvnorm(lower=c(q1,q3,qd2e3,q1,q3,qd2e2),upper=c(Inf,Inf,Inf,Inf,Inf,Inf),mean=c(0,0,0,0,0,0),sigma=Sigma)/ pd2
    td2d2_model[i]=td2d2_model[i]+pmvnorm(lower=c(q1,q3,qd2e3,-Inf,q2,qd2e2),upper=c(Inf,Inf,Inf,q1,Inf,Inf),mean=c(0,0,0,0,0,0),sigma=Sigma)/ pd2
    td2d2_model[i]=td2d2_model[i]+pmvnorm(lower=c(-Inf,q2,qd2e3,-Inf,q2,qd2e2),upper=c(q1,Inf,Inf,q1,Inf,Inf),mean=c(0,0,0,0,0,0),sigma=Sigma)/ pd2
    if(td2d2_model[i]==0){td2d2_model[i]=NA}

    td2d3_model[i]=pmvnorm(lower=c(-Inf,q2,qd2e2,q1,-Inf,qd1e4),upper=c(q1,Inf,Inf,Inf,q3,Inf),mean=c(0,0,0,0,0,0),sigma=Sigma)/ pd2
    td2d3_model[i]=td2d3_model[i]+pmvnorm(lower=c(q1,q3,qd2e2,q1,-Inf,qd1e4),upper=c(Inf,Inf,Inf,Inf,q3,Inf),mean=c(0,0,0,0,0,0),sigma=Sigma)/ pd2
    if(td2d3_model[i]==0){td2d3_model[i]=NA}

  td3d2_model[i]=pmvnorm(lower=c(q1,-Inf,qd1e4,-Inf,q2,qd2e2),upper=c(Inf,q3,Inf,q1,Inf,Inf),mean=c(0,0,0,0,0,0),sigma=Sigma)/ pd3
    td3d2_model[i]=td3d2_model[i]+pmvnorm(lower=c(q1,-Inf,qd1e4,q1,q3,qd2e2),upper=c(Inf,q3,Inf,Inf,Inf,Inf),mean=c(0,0,0,0,0,0),sigma=Sigma)/ pd3
    if(td3d2_model[i]==0){td3d2_model[i]=NA}
}

z = (1:300)/100.
par(mfrow=c(2,2))
tr_2d_vert(d3,d3,30,nz,0.1)
lines(z,td3d3_model)
tr_2d_vert(d3,d2,30,nz,0.1)
lines(z,td3d2_model)
tr_2d_vert(d2,d3,30,nz,0.1)
lines(z,td2d3_model)
tr_2d_vert(d2,d2,30,nz,0.1)
lines(z,td2d2_model)
```

```{r}
z = (1:300)/100.
z2= (1:60)/20
png(file="latemardiagtransiototal.png",width=3000,height = 2000,res=300)
par(mar=c(2,3,1,1),mfrow=c(2,2))
tr_2d_vert(d3,d3,30,nz,0.1)
lines(z,td3d3_model)
lines(z2,td3d3real,lwd=0.5)
lines(z2,td3d3real2,lwd=0.5)
lines(z2,td3d3real3,lwd=0.5)
title(main=expression(paste('t'[d1d1],"(h)")),line=-1,cex.main=2)
tr_2d_vert(d3,d2,30,nz,0.1)
lines(z,td3d2_model)
lines(z2,td3d2real,lwd=0.5)
lines(z2,td3d2real2,lwd=0.5)
lines(z2,td3d2real3,lwd=0.5)
title(main=expression(paste('t'[d1d2],"(h)")),line=-1,cex.main=2)
tr_2d_vert(d2,d3,30,nz,0.1)
lines(z,td2d3_model)
lines(z2,td2d3real,lwd=0.5)
lines(z2,td2d3real2,lwd=0.5)
lines(z2,td2d3real3,lwd=0.5)
title(main=expression(paste('t'[d2d1],"(h)")),line=-1,cex.main=2)
tr_2d_vert(d2,d2,30,nz,0.1)
lines(z,td2d2_model)
lines(z2,td2d2real,lwd=0.5)
lines(z2,td2d2real2,lwd=0.5)
lines(z2,td2d2real3,lwd=0.5)
title(main=expression(paste('t'[d2d2],"(h)")),line=-1,cex.main=2)
# 
# tr_2d_vert(d3,e1,30,nz,0.1)
# lines(z,td3e1_model)
# title(main=expression(paste('t'[d1e1],"(h)")),line=-1,cex.main=2)
# tr_2d_vert(d3,e2,30,nz,0.1)
# lines(z,td3e2_model)
# title(main=expression(paste('t'[d1e2],"(h)")),cex.main=2)
# tr_2d_vert(d3,e3,30,nz,0.1)
# lines(z,td3e3_model)
# title(main=expression(paste('t'[d1e3],"(h)")),line=-1,cex.main=2)
# tr_2d_vert(d3,e4,30,nz,0.1)
# lines(z,td3e4_model)
# title(main=expression(paste('t'[d1e4],"(h)")),line=-1,cex.main=2)
# tr_2d_vert(d2,e1,30,nz,0.1)
# lines(z,td2e1_model)
# title(main=expression(paste('t'[d2e1],"(h)")),line=-1,cex.main=2)
# tr_2d_vert(d2,e2,30,nz,0.1)
# lines(z,td2e2_model)
# title(main=expression(paste('t'[d2e2],"(h)")),line=-1,cex.main=2)
# tr_2d_vert(d2,e3,30,nz,0.1)
# lines(z,td2e3_model)
# title(main=expression(paste('t'[d2e3],"(h)")),line=-1,cex.main=2)
# tr_2d_vert(d2,e4,30,nz,0.1)
# title(main=expression(paste('t'[d2e4],"(h)")),line=-1,cex.main=2)
# lines(z,td2e4_model)
```

### 2018-05-31 main_cosim.Rmd
added the code

---
title: "R Notebook"
output: html_notebook
---

```{r}
library(mvtnorm)
```

getting the data
```{r}
env_lat<-data.matrix(read.table("depo_latemar.txt"))
diag_lat<-data.matrix(read.table("diag_latemar.txt"))
nz=nrow(env_lat)
nz
```

transforming into indicators
```{r}
e1<-e2<-e3<-e4<-d1<-d2<-d3<-matrix(0,nz,4)
e1[env_lat==1]=1
e2[env_lat==2]=1
e3[env_lat==3]=1
e4[env_lat==4]=1
d1[diag_lat==1]=1
d2[diag_lat==2]=1
d3[diag_lat==3]=1
e1[is.na(env_lat)]=e2[is.na(env_lat)]=e3[is.na(env_lat)]=e4[is.na(env_lat)]=NA
d1[is.na(diag_lat)]=d2[is.na(diag_lat)]=d3[is.na(diag_lat)]=NA
```

```{r}
source("cosim_functions.R")
```

computing transiograms between different facies
the environment of depositions
```{r, fig.height=6, fig.width=8}
par(mfrow=c(4,4))
tr_2d_vert(e1,e1,30,nz,0.1)
tr_2d_vert(e1,e2,30,nz,0.1)
tr_2d_vert(e1,e3,30,nz,0.1)
tr_2d_vert(e1,e4,30,nz,0.1)
tr_2d_vert(e2,e1,30,nz,0.1)
tr_2d_vert(e2,e2,30,nz,0.1)
tr_2d_vert(e2,e3,30,nz,0.1)
tr_2d_vert(e2,e4,30,nz,0.1)
tr_2d_vert(e3,e1,30,nz,0.1)
tr_2d_vert(e3,e2,30,nz,0.1)
tr_2d_vert(e3,e3,30,nz,0.1)
tr_2d_vert(e3,e4,30,nz,0.1)
tr_2d_vert(e4,e1,30,nz,0.1)
tr_2d_vert(e4,e2,30,nz,0.1)
tr_2d_vert(e4,e3,30,nz,0.1)
tr_2d_vert(e4,e4,30,nz,0.1)

```
```{r}
par(mfrow=c(3,3))
tr_2d_vert(e1,e1,30,nz,0.1)
tr_2d_vert(e1,e2,30,nz,0.1)
tr_2d_vert(e1,e3,30,nz,0.1)
tr_2d_vert(e2,e1,30,nz,0.1)
tr_2d_vert(e2,e2,30,nz,0.1)
tr_2d_vert(e2,e3,30,nz,0.1)
tr_2d_vert(e3,e1,30,nz,0.1)
tr_2d_vert(e3,e2,30,nz,0.1)
tr_2d_vert(e3,e3,30,nz,0.1)
```

the diagenetic facies
```{r, fig.height=8, fig.width=8}
par(mfrow=c(3,3))
tr_2d_vert(d1,d1,30,nz,0.1)
tr_2d_vert(d1,d2,30,nz,0.1)
tr_2d_vert(d1,d3,30,nz,0.1)
tr_2d_vert(d2,d1,30,nz,0.1)
tr_2d_vert(d2,d2,30,nz,0.1)
tr_2d_vert(d2,d3,30,nz,0.1)
tr_2d_vert(d3,d1,30,nz,0.1)
tr_2d_vert(d3,d2,30,nz,0.1)
tr_2d_vert(d3,d3,30,nz,0.1)
```

cross-correlations between depositional and diagenetic facies
```{r, fig.height=8, fig.width=8}
par(mfrow=c(4,3))
tr_2d_vert(e1,d1,30,nz,0.1)
tr_2d_vert(e1,d2,30,nz,0.1)
tr_2d_vert(e1,d3,30,nz,0.1)
tr_2d_vert(e2,d1,30,nz,0.1)
tr_2d_vert(e2,d2,30,nz,0.1)
tr_2d_vert(e2,d3,30,nz,0.1)
tr_2d_vert(e3,d1,30,nz,0.1)
tr_2d_vert(e3,d2,30,nz,0.1)
tr_2d_vert(e3,d3,30,nz,0.1)
tr_2d_vert(e4,d1,30,nz,0.1)
tr_2d_vert(e4,d2,30,nz,0.1)
tr_2d_vert(e4,d3,30,nz,0.1)
```

```{r, fig.height=8, fig.width=8}
par(mfrow=c(3,4))
tr_2d_vert(d1,e1,30,nz,0.1)
tr_2d_vert(d1,e2,30,nz,0.1)
tr_2d_vert(d1,e3,30,nz,0.1)
tr_2d_vert(d1,e4,30,nz,0.1)
tr_2d_vert(d2,e1,30,nz,0.1)
tr_2d_vert(d2,e2,30,nz,0.1)
tr_2d_vert(d2,e3,30,nz,0.1)
tr_2d_vert(d2,e4,30,nz,0.1)
tr_2d_vert(d3,e1,30,nz,0.1)
tr_2d_vert(d3,e2,30,nz,0.1)
tr_2d_vert(d3,e3,30,nz,0.1)
tr_2d_vert(d3,e4,30,nz,0.1)
```

ok now we can try to fit a model to these transiograms
first the environment of depositions
we get their proportions

```{r}
pe1 = mean(e1,na.rm=TRUE)
pe2 = mean(e2,na.rm=TRUE)
pe3 = mean(e3,na.rm=TRUE)
pe4 = mean(e4,na.rm=TRUE)
c(pe1,pe2,pe3,pe4)
```

```{r}
library(mvtnorm)
```

model used for the covariances
```{r}
model1<-function(h,range,b){return(exp(-(h/range)^2)*cos(b*h))}
```
fitting 
```{r}
rv1=0.3
rv2=0.5
rhx1=40
rhx2=40
b1=0
b2=0
rho=0.8
shift=0.1
rho1a<-model1(shift,rv1,b1)
alpha1=(rho/rho1a)^2
alpha2=1-(rho/rho1a)^2
#thresholds
q1=qnorm(pe1+pe2)
Sigma1 = matrix(c(1,rho,rho,1),2,2)
q2=0
obj = Inf
for ( test in 1:100 ){
  q2test = qnorm(test/100)
  newobj =abs( pmvnorm(lower=c(-Inf,-Inf),upper=c(q1,q2test),mean=c(0,0),sigma=Sigma1) - pe1 ) 
  if (newobj < obj){
    q2 = q2test
    obj = newobj
  }
}
q3=0
obj = Inf
for ( test in 1:100 ){
  q3test = qnorm(test/100)
  newobj =abs( pmvnorm(lower=c(q1,-Inf),upper=c(Inf,q3test),mean=c(0,0),sigma=Sigma1) - pe4 ) 
  if (newobj < obj){
    q3 = q3test
    obj = newobj
  }
}

c(q1,q2,q3)

#transiograms
z = (1:300)/100.
t11_model=t12_model=t13_model=t21_model=t22_model=t23_model=t31_model=t32_model=t33_model=rep(0,300)
Sigma = diag(1,4)
for (i in 1:300){
    d = i/100.
    Sigma[1,2]=Sigma[2,1]= Sigma[3,4]=Sigma[4,3]=rho
    Sigma[1,3]=Sigma[3,1]=model1(d,rv1,b1)
    Sigma[1,4]=Sigma[4,1]=(rho/rho1a)*model1(abs(d+shift),rv1,b1)
    Sigma[2,3]=Sigma[3,2]=(rho/rho1a)*model1(abs(d-shift),rv1,b1)
    Sigma[2,4]=Sigma[4,2]=alpha1*model1(d,rv1,b1)+alpha2*model1(d,rv2,b2)
    t11_model[i]=pmvnorm(lower=c(-Inf,-Inf,-Inf,-Inf),upper=c(q1,q2,q1,q2),mean=c(0,0,0,0),sigma=Sigma)/ pe1 
    t12_model[i]=pmvnorm(lower=c(-Inf,-Inf,-Inf,q2),upper=c(q1,q2,q1,Inf),mean=c(0,0,0,0),sigma=Sigma)/ pe1 
    t13_model[i]=pmvnorm(lower=c(-Inf,-Inf,q1,q3),upper=c(q1,q2,Inf,Inf),mean=c(0,0,0,0),sigma=Sigma)/ pe1 
    t21_model[i]=pmvnorm(lower=c(-Inf,q2,-Inf,-Inf),upper=c(q1,Inf,q1,q2),mean=c(0,0,0,0),sigma=Sigma)/ pe2
    t22_model[i]=pmvnorm(lower=c(-Inf,q2,-Inf,q2),upper=c(q1,Inf,q1,Inf),mean=c(0,0,0,0),sigma=Sigma)/ pe2
    t23_model[i]=pmvnorm(lower=c(-Inf,q2,q1,q3),upper=c(q1,Inf,Inf,Inf),mean=c(0,0,0,0),sigma=Sigma)/ pe2
    t31_model[i]=pmvnorm(lower=c(q1,q3,-Inf,-Inf),upper=c(Inf,Inf,q1,q2),mean=c(0,0,0,0),sigma=Sigma)/ pe3
    t32_model[i]=pmvnorm(lower=c(q1,q3,-Inf,q2),upper=c(Inf,Inf,q1,Inf),mean=c(0,0,0,0),sigma=Sigma)/ pe3
    t33_model[i]=pmvnorm(lower=c(q1,q3,q1,q3),upper=c(Inf,Inf,Inf,Inf),mean=c(0,0,0,0),sigma=Sigma)/ pe3
}
par(mfrow=c(3,3))
t11<-tr_2d_vert(e1,e1,30,nz,0.1)
lines(z,t11_model)
t12<-tr_2d_vert(e1,e2,30,nz,0.1)
lines(z,t12_model)
t13<-tr_2d_vert(e1,e3,30,nz,0.1)
lines(z,t13_model)
t21<-tr_2d_vert(e2,e1,30,nz,0.1)
lines(z,t21_model)
t22<-tr_2d_vert(e2,e2,30,nz,0.1)
lines(z,t22_model)
t23<-tr_2d_vert(e2,e3,30,nz,0.1)
lines(z,t23_model)
t31<-tr_2d_vert(e3,e1,30,nz,0.1)
lines(z,t31_model)
t32<-tr_2d_vert(e3,e2,30,nz,0.1)
lines(z,t32_model)
t33<-tr_2d_vert(e3,e3,30,nz,0.1)
lines(z,t33_model)
```

ok now we can look at the diagenetic facies
their proportions

```{r}
pd1=mean(d1,na.rm=TRUE)
pd2=mean(d2,na.rm=TRUE)
pd3=mean(d3,na.rm=TRUE)
c(pd1,pd2,pd3)
```
now the transiograms
```{r}
rv3=0.2
rv4=0.3
rhx3=40
rhx4=40
b3=0
b4=0
rho34=0.

#thresholds
qd1=qnorm(pd3)
Sigma1 = matrix(c(1,rho34,rho34,1),2,2)
qd2=0
obj = Inf
for ( test in 1:100 ){
  q2test = qnorm(test/100)
  newobj =abs( pmvnorm(lower=c(qd1,q2test),upper=c(Inf,Inf),mean=c(0,0),sigma=Sigma1) - pd2 ) 
  if (newobj < obj){
    qd2 = q2test
    obj = newobj
  }
}

c(qd1,qd2)

#transiograms

z = (1:300)/100.
t33d_model=t32d_model=t23d_model=t22d_model=rep(0,300)
Sigma = diag(1,4)
for (i in 1:300){
    d = i/100.
    Sigma[1,2]=Sigma[2,1]= Sigma[3,4]=Sigma[4,3]=rho34
    Sigma[1,3]=Sigma[3,1]=model1(d,rv3,b3)
    Sigma[1,4]=Sigma[4,1]=Sigma[2,3]=Sigma[3,2]=rho34*model1(d,rv3,b3)
    Sigma[2,4]=Sigma[4,2]=(rho34^2)*model1(d,rv3,b3)+(1-rho34^2)*model1(d,rv4,b4)

    t22d_model[i]=pmvnorm(lower=c(qd1,qd2,qd1,qd2),upper=c(Inf,Inf,Inf,Inf),mean=c(0,0,0,0),sigma=Sigma)/ pd2
    t23d_model[i]=pmvnorm(lower=c(qd1,qd2,-Inf,-Inf),upper=c(Inf,Inf,qd1,Inf),mean=c(0,0,0,0),sigma=Sigma)/ pd2
    t32d_model[i]=pmvnorm(lower=c(-Inf,-Inf,qd1,qd2),upper=c(qd1,Inf,Inf,Inf),mean=c(0,0,0,0),sigma=Sigma)/ pd3
    t33d_model[i]=pmvnorm(lower=c(-Inf,-Inf,-Inf,-Inf),upper=c(qd1,Inf,qd1,Inf),mean=c(0,0,0,0),sigma=Sigma)/ pd3
}
par(mfrow=c(2,2))
t22d<-tr_2d_vert(d2,d2,30,nz,0.1)
lines(z,t22d_model)
t23d<-tr_2d_vert(d2,d3,30,nz,0.1)
lines(z,t23d_model)
t32d<-tr_2d_vert(d3,d2,30,nz,0.1)
lines(z,t32d_model)
t33d<-tr_2d_vert(d3,d3,30,nz,0.1)
lines(z,t33d_model)
```

Let's now do a more complex case study, where the four Gaussian functions are correlated. 
Z1 =Y1
Z2 = a Y1(x+a12) + b Y2(x)
Z3 = c Y1(x+a13) + d Y3(x)
Z4 = e Y1(x+a14) + f Y4(x)
```{r}
rv1=0.3
rv2=0.5
rhx1=40
rhx2=40
b1=0
b2=0
rho=0.8
shift=0.1
rho1a<-model(shift,rv1,b1)

alpha1=(rho/rho1a)^2
alpha2=1-(rho/rho1a)^2
rv3=0.2
rv4=0.3
rhx3=40
rhx4=40
b3=0
b4=0
rho34=0.
c=0.
e=0.65
a13=-0.
a14=-0.1
rho1a14 = model1(a14,rv1,b1)
#thresholds of environment of depositions, do not depend on diagenesis functions
q1=qnorm(pe1+pe2)
Sigma1 = matrix(c(1,rho,rho,1),2,2)
q2=0
obj = Inf
for ( test in 1:100 ){
  q2test = qnorm(test/100)
  newobj =abs( pmvnorm(lower=c(-Inf,-Inf),upper=c(q1,q2test),mean=c(0,0),sigma=Sigma1) - pe1 ) 
  if (newobj < obj){
    q2 = q2test
    obj = newobj
  }
}
q3=0
obj = Inf
for ( test in 1:100 ){
  q3test = qnorm(test/100)
  newobj =abs( pmvnorm(lower=c(q1,-Inf),upper=c(Inf,q3test),mean=c(0,0),sigma=Sigma1) - pe4 ) 
  if (newobj < obj){
    q3 = q3test
    obj = newobj
  }
}

# thresholds of diagenesis
qd1=qnorm(pd3)
Sigma1 = matrix(c(1,rho34,rho34,1),2,2)
qd2=0
obj = Inf
for ( test in 1:100 ){
  q2test = qnorm(test/100)
  newobj =abs( pmvnorm(lower=c(qd1,q2test),upper=c(Inf,Inf),mean=c(0,0),sigma=Sigma1) - pd2 ) 
  if (newobj < obj){
    qd2 = q2test
    obj = newobj
  }
}

c(qd1,qd2)

#now we can look at the transition probabilities between half dolomite and subaerial exposure
z = (1:300)/100.
td2e4_model=rep(0,300)
Sigma = diag(1,4)
for (i in 1:300){
    d = i/100.
    Sigma[1,2]=Sigma[2,1]=rho34
    Sigma[1,3]=Sigma[3,1]=c*model1(d-a13,rv1,b1)
    Sigma[1,4]=Sigma[4,1]=c*(rho/rho1a)*model1(a13-d-shift,rv1,b1)
    Sigma[2,3]=Sigma[3,2]=e*model1(a14-d,rv1,b1)
    Sigma[2,4]=Sigma[4,2]=e*(rho/rho1a)*model1(a14-d-shift,rv1,b1)
    Sigma[3,4]=Sigma[4,3]=rho

    td2e4_model[i]=pmvnorm(lower=c(qd1,qd2,q1,-Inf),upper=c(Inf,Inf,Inf,q3),mean=c(0,0,0,0),sigma=Sigma)/ pd2
}

tr_2d_vert(d2,e4,30,nz,0.1)
lines(z,td2e4_model)
```
looking at different cases
```{r}
e=0.0
a14=-0.
z = (1:300)/100.
td2e4_model=rep(0,300)
Sigma = diag(1,4)
for (i in 1:300){
    d = i/100.
    Sigma[1,2]=Sigma[2,1]=rho34
    Sigma[1,3]=Sigma[3,1]=c*model1(d-a13,rv1,b1)
    Sigma[1,4]=Sigma[4,1]=c*(rho/rho1a)*model1(a13-d-shift,rv1,b1)
    Sigma[2,3]=Sigma[3,2]=e*model1(a14-d,rv1,b1)
    Sigma[2,4]=Sigma[4,2]=e*(rho/rho1a)*model1(a14-d-shift,rv1,b1)
    Sigma[3,4]=Sigma[4,3]=rho

    td2e4_model[i]=pmvnorm(lower=c(qd1,qd2,q1,-Inf),upper=c(Inf,Inf,Inf,q3),mean=c(0,0,0,0),sigma=Sigma)/ pd2
}

tr_2d_vert(d2,e4,30,nz,0.1)
lines(z,td2e4_model)

e=0.7
a14=-0.

td2e4_model=rep(0,300)
Sigma = diag(1,4)
for (i in 1:300){
    d = i/100.
    Sigma[1,2]=Sigma[2,1]=rho34
    Sigma[1,3]=Sigma[3,1]=c*model1(d-a13,rv1,b1)
    Sigma[1,4]=Sigma[4,1]=c*(rho/rho1a)*model1(a13-d-shift,rv1,b1)
    Sigma[2,3]=Sigma[3,2]=e*model1(a14-d,rv1,b1)
    Sigma[2,4]=Sigma[4,2]=e*(rho/rho1a)*model1(a14-d-shift,rv1,b1)
    Sigma[3,4]=Sigma[4,3]=rho

    td2e4_model[i]=pmvnorm(lower=c(qd1,qd2,q1,-Inf),upper=c(Inf,Inf,Inf,q3),mean=c(0,0,0,0),sigma=Sigma)/ pd2
}
tr_2d_vert(d2,e4,30,nz,0.1)
lines(z,td2e4_model)

e=0.7
a14=-0.1
td2e4_model=rep(0,300)
Sigma = diag(1,4)
for (i in 1:300){
    d = i/100.
    Sigma[1,2]=Sigma[2,1]=rho34
    Sigma[1,3]=Sigma[3,1]=c*model1(d-a13,rv1,b1)
    Sigma[1,4]=Sigma[4,1]=c*(rho/rho1a)*model1(a13-d-shift,rv1,b1)
    Sigma[2,3]=Sigma[3,2]=e*model1(a14-d,rv1,b1)
    Sigma[2,4]=Sigma[4,2]=e*(rho/rho1a)*model1(a14-d-shift,rv1,b1)
    Sigma[3,4]=Sigma[4,3]=rho

    td2e4_model[i]=pmvnorm(lower=c(qd1,qd2,q1,-Inf),upper=c(Inf,Inf,Inf,q3),mean=c(0,0,0,0),sigma=Sigma)/ pd2
}
tr_2d_vert(d2,e4,30,nz,0.1)
lines(z,td2e4_model) 
```
```{r}
rv1=0.3
rv2=0.5
rhx1=40
rhx2=40
b1=20
b2=0
rho=0.8
shift=0.1
rho1a<-model1(shift,rv1,b1)

alpha1=(rho/rho1a)^2
alpha2=1-(rho/rho1a)^2
rv3=0.2
rv4=0.3
rhx3=40
rhx4=40
b3=0
b4=0
rho34=0.
c=-0.
e=-0.65
a13=0.
a14=-0.1
rho1a14 = model1(a14,rv1,b1)
#thresholds of environment of depositions, do not depend on diagenesis functions
q1=qnorm(pe1+pe2)
Sigma1 = matrix(c(1,rho,rho,1),2,2)
q2=0
obj = Inf
for ( test in 1:100 ){
  q2test = qnorm(test/100)
  newobj =abs( pmvnorm(lower=c(-Inf,-Inf),upper=c(q1,q2test),mean=c(0,0),sigma=Sigma1) - pe1 ) 
  if (newobj < obj){
    q2 = q2test
    obj = newobj
  }
}
q3=0
obj = Inf
for ( test in 1:100 ){
  q3test = qnorm(test/100)
  newobj =abs( pmvnorm(lower=c(q1,-Inf),upper=c(Inf,q3test),mean=c(0,0),sigma=Sigma1) - pe4 ) 
  if (newobj < obj){
    q3 = q3test
    obj = newobj
  }
}

# thresholds of diagenesis
qd1=qnorm(pd3)
Sigma1 = matrix(c(1,rho34,rho34,1),2,2)
qd2=0
obj = Inf
for ( test in 1:100 ){
  q2test = qnorm(test/100)
  newobj =abs( pmvnorm(lower=c(qd1,q2test),upper=c(Inf,Inf),mean=c(0,0),sigma=Sigma1) - pd2 ) 
  if (newobj < obj){
    qd2 = q2test
    obj = newobj
  }
}

c(qd1,qd2)

#now we can look at the transition probabilities between half dolomite and subaerial exposure
z = (1:300)/100.
td2e2_model=rep(0,300)
Sigma = diag(1,4)
for (i in 1:300){
    d = i/100.
    Sigma[1,2]=Sigma[2,1]=rho34
    Sigma[1,3]=Sigma[3,1]=c*model1(d-a13,rv1,b1)
    Sigma[1,4]=Sigma[4,1]=c*(rho/rho1a)*model1(a13-d-shift,rv1,b1)
    Sigma[2,3]=Sigma[3,2]=e*model1(a14-d,rv1,b1)
    Sigma[2,4]=Sigma[4,2]=e*(rho/rho1a)*model1(a14-d-shift,rv1,b1)
    Sigma[3,4]=Sigma[4,3]=rho

    td2e2_model[i]=pmvnorm(lower=c(qd1,qd2,-Inf,q2),upper=c(Inf,Inf,q1,Inf),mean=c(0,0,0,0),sigma=Sigma)/ pd2
}

tr_2d_vert(d2,e2,30,nz,0.1)
lines(z,td2e2_model)
```

The proportions of diagenetic facies conditional to the environment of depositions
this will be useful for the simulation
```{r}
pd1e1=mean(d1*e1,na.rm=TRUE)/pe1
pd1e2=mean(d1*e2,na.rm=TRUE)/pe2
pd1e3=mean(d1*e3,na.rm=TRUE)/pe3
pd1e4=mean(d1*e4,na.rm=TRUE)/pe4

pd2e1=mean(d2*e1,na.rm=TRUE)/pe1
pd2e2=mean(d2*e2,na.rm=TRUE)/pe2
pd2e3=mean(d2*e3,na.rm=TRUE)/pe3
pd2e4=mean(d2*e4,na.rm=TRUE)/pe4

pd3e1=mean(d3*e1,na.rm=TRUE)/pe1
pd3e2=mean(d3*e2,na.rm=TRUE)/pe2
pd3e3=mean(d3*e3,na.rm=TRUE)/pe3
pd3e4=mean(d3*e4,na.rm=TRUE)/pe4

matrix(c(pd1e1,pd1e2,pd1e3,pd1e4,pd2e1,pd2e2,pd2e3,pd2e4,pd3e1,pd3e2,pd3e3,pd3e4),3,4,byrow=TRUE)

```

all these proportions should result in thresholds for the different facies (there are 3 thresholds to compute)
```{r}
qd1e4=qnorm(pd3e4)
qd2e2=qnorm(pd1e2) # i am not sure this is true if there is a correlation between fourth and first Gaussian function
qd2e3=qnorm(pd1e3)
```
now we can perform the simulation

```{r}
#gaussian simulation
rhx3=80
rhx4=80
rhx1=80
rhx2=80
Z1<-sim2d(rv1,rhx1,b1,100,0.05,182,0.5,200)
Y2<-sim2d(rv2,rhx2,b2,100,0.05,182,0.5,200)
Z2=Y2
for ( z in 1:180){
  Z2[,z]=Y2[,z]*sqrt(1-(rho^2)/(rho1a^2))+Z1[,z+2]*(rho)/(rho1a)
}
Z3<-sim2d(rv3,rhx3,b3,100,0.05,182,0.5,200)
Z4<-sim2d(rv4,rhx4,b4,100,0.05,182,0.5,200)

# truncation
faciesenv<-faciesdiag<-Z1
faciesenv[Z1<q1 & Z2<q2]=1
faciesenv[Z1<q1 & Z2>q2]=2
faciesenv[Z1>q1 & Z2<q3]=4
faciesenv[Z1>q1 & Z2>q3]=3
faciesdiag[]=1
faciesdiag[Z1>q1 & Z2<q3 & Z3<qd1e4]=3
faciesdiag[Z1<q1 & Z2>q2 & Z4>qd2e2]=2
faciesdiag[Z1>q1 & Z2>q3 & Z4>qd2e3]=2
col_env <- c("lightgreen","cadetblue","dodgerblue4","lightcoral")
col_diag<-dcolors <- c("black","grey","yellow")
image(faciesenv,col = col_env)
image(faciesdiag,col = col_diag)
```

now we would like to do a view with both facies fields on the same image
```{r}
bin<-bin2<-faciesenv
#bin[]<-rbinom(91*100, 1, 0.5)
bin[]=bin2[]=0
bin[seq(2,182*200,by=2)]=1
facies=faciesenv
facies[faciesdiag==2 & bin ==1 ] = 5
facies[faciesdiag==3]=5

col_combine <- c("lightgreen","cadetblue","dodgerblue4","lightcoral","yellow")
W<-image(facies,col = col_combine)
```

now we want to perform a simulation with correlation between Z1 and Z4 and shift
so that the facies 50 dol is below the subaerial exposure facies

first we need to re-compute the thresholds

```{r}
rv1=0.3
rv2=0.5
rhx1=40
rhx2=40
b1=0
b2=0
rho=0.8
shift=0.1
rho1a<-model1(shift,rv1,b1)

alpha1=(rho/rho1a)^2
alpha2=1-(rho/rho1a)^2
rv3=0.2
rv4=0.3
rhx3=40
rhx4=40
b3=0
b4=0
rho34=0.
c=0.
e=0.65
a13=-0.
a14=-0.1
rho1a14 = model1(a14,rv1,b1)

# this one does not change because no correlation of the third gaussian function
qd1e4=qnorm(pd3e4)

# now the threshold with the fourth Gaussian function, that does depend on the first
sigma1=diag(1,3)
sigma1[1,2]=sigma1[2,1]=e*model1(a14,rv1,b1)
sigma1[1,3]=sigma1[3,1]=e*(rho/rho1a)*model1(a14-shift,rv1,b1)
sigma1[2,3]=sigma1[3,2]=rho

qd2e2=0
obj = Inf
for ( test in 1:100 ){
  qd2e2test = qnorm(test/100)
  newobj =abs( pmvnorm(lower=c(qd2e2test,-Inf,q2),upper=c(Inf,q1,Inf),mean=c(0,0,0),sigma=sigma1)/pe2 - pd2e2 ) 
  if (newobj < obj){
    qd2e2 = qd2e2test
    obj = newobj
  }
}

qd2e3=0
obj = Inf
for ( test in 1:100 ){
  qd2e3test = qnorm(test/100)
  newobj =abs( pmvnorm(lower=c(qd2e3test,q1,q3),upper=c(Inf,Inf,Inf),mean=c(0,0,0),sigma=sigma1)/pe3 - pd2e3 ) 
  if (newobj < obj){
    qd2e3 = qd2e3test
    obj = newobj
  }
}

print(c(qd1e4,qd2e2,qd2e3))
```

Okay, we may now perform the simulation

```{r}
Z1<-sim2d(rv1,rhx1,b1,100,0.05,182,0.5,200)
Y2<-sim2d(rv2,rhx2,b2,100,0.05,182,0.5,200)
Z2=Y2
for ( z in 1:180){
  Z2[,z]=Y2[,z]*sqrt(1-(rho^2)/(rho1a^2))+Z1[,z+2]*(rho)/(rho1a)
}
Z3<-sim2d(rv3,rhx3,b3,100,0.05,182,0.5,200)
Y4<-sim2d(rv4,rhx4,b4,100,0.05,182,0.5,200)
for ( z in 2:182){
  Z4[,z]=Y4[,z]*sqrt(1-e^2)+Z1[,z-1]*e
}

# truncation
faciesenv<-faciesdiag<-Z1
faciesenv[Z1<q1 & Z2<q2]=1
faciesenv[Z1<q1 & Z2>q2]=2
faciesenv[Z1>q1 & Z2<q3]=4
faciesenv[Z1>q1 & Z2>q3]=3
faciesdiag[]=1
faciesdiag[Z1>q1 & Z2<q3 & Z3<qd1e4]=3
faciesdiag[Z1<q1 & Z2>q2 & Z4>qd2e2]=2
faciesdiag[Z1>q1 & Z2>q3 & Z4>qd2e3]=2
col_env <- c("lightgreen","cadetblue","dodgerblue4","lightcoral")
col_diag<-dcolors <- c("black","grey","yellow")
image(faciesenv,col = col_env)
image(faciesdiag,col = col_diag)

```
```{r}
bin<-bin2<-faciesenv
#bin[]<-rbinom(91*100, 1, 0.5)
bin[]=bin2[]=0
bin[seq(2,182*200,by=2)]=1
facies=faciesenv
facies[faciesdiag==2 & bin ==1 ] = 5
facies[faciesdiag==3]=5

col_combine <- c("lightgreen","cadetblue","dodgerblue4","lightcoral","yellow")
W<-image(facies,col = col_combine)
```

```{r}
for ( z in 1:181){
  Z4[,z]=Y4[,z]*sqrt(1-e^2)+Z1[,z+1]*e
}

faciesenv<-faciesdiag<-Z1
faciesenv[Z1<q1 & Z2<q2]=1
faciesenv[Z1<q1 & Z2>q2]=2
faciesenv[Z1>q1 & Z2<q3]=4
faciesenv[Z1>q1 & Z2>q3]=3
faciesdiag[]=1
faciesdiag[Z1>q1 & Z2<q3 & Z3<qd1e4]=3
faciesdiag[Z1<q1 & Z2>q2 & Z4>qd2e2]=2
faciesdiag[Z1>q1 & Z2>q3 & Z4>qd2e3]=2
col_env <- c("lightgreen","cadetblue","dodgerblue4","lightcoral")
col_diag<-dcolors <- c("black","grey","yellow")
image(faciesenv,col = col_env)
image(faciesdiag,col = col_diag)
bin<-bin2<-faciesenv
#bin[]<-rbinom(91*100, 1, 0.5)
bin[]=bin2[]=0
bin[seq(2,182*200,by=2)]=1
facies=faciesenv
facies[faciesdiag==2 & bin ==1 ] = 5
facies[faciesdiag==3]=5

col_combine <- c("lightgreen","cadetblue","dodgerblue4","lightcoral","yellow")
W<-image(facies,col = col_combine)
```

I would like to try the conditioning now for the co-simulation

```{r}
source("co_sim_condi.R")
```

```{r}
grid<-grid_co<-array(NA,c(100,91))
grid[5,]<-env_lat[,1]
grid[25,]<-env_lat[,2]
grid[35,]<-env_lat[,3]
grid[95,]<-env_lat[,4]
grid_co[5,]<-diag_lat[,1]
grid_co[25,]<-diag_lat[,2]
grid_co[35,]<-diag_lat[,3]
grid_co[95,]<-diag_lat[,4]
image(grid)
image(grid_co)
simwell<-coco_gibbs_sampling(grid,grid_co,c(q1,q2,q3),c(qd1e4,qd2e2,qd2e3),0.1,1,c(rv1,rv2,rv3,rv4),c(rhx1,rhx2,rhx3,rhx4),c(b1,b2,b3,b4),c(rho,e*model1(a14,rv1,b1)),c(shift,a14),5)
Z1<-simwell[,1:91]
Z2<-simwell[,92:182]
Z3<-simwell[,183:273]
Z4<-simwell[,274:364]
image(Z1)
faciesenv<-faciesdiag<-Z1
faciesenv[Z1<q1 & Z2<q2]=1
faciesenv[Z1<q1 & Z2>q2]=2
faciesenv[Z1>q1 & Z2<q3]=4
faciesenv[Z1>q1 & Z2>q3]=3
faciesdiag[]=NA
faciesdiag[3,]=faciesdiag[20,]=faciesdiag[55,]=faciesdiag[80,]=1
faciesdiag[Z1>q1 & Z2<q3 & Z3<qd1e4]=3
faciesdiag[Z1<q1 & Z2>q2 & Z4>qd2e2]=2
faciesdiag[Z1>q1 & Z2>q3 & Z4>qd2e3]=2
col_env <- c("lightgreen","cadetblue","dodgerblue4","lightcoral")
col_diag<-dcolors <- c("black","grey","yellow")
image(grid,col = col_env)
image(faciesenv,col = col_env)
image(faciesdiag,col = col_diag)
image(grid_co,col = col_diag)
```

```{r}
source("co_sim_condi.R")
```

totalsimu
```{r}
rv1=0.3
rv2=0.5
rhx1=50
rhx2=50
b1=0
b2=0
rho=0.8
shift=0.1
rho1a<-model1(shift,rv1,b1)

alpha1=(rho/rho1a)^2
alpha2=1-(rho/rho1a)^2
rv3=0.2
rv4=0.3
rhx3=50
rhx4=50
b3=0
b4=0
rho34=0.
c=0.
e=0.65
a13=-0.
a14=-0.1
rho1a14 = model1(a14,rv1,b1)

Z1<-sim2d(rv1,rhx1,b1,100,0.1,91,1,100)
Y2<-sim2d(rv2,rhx2,b2,100,0.1,91,1,100)
Z2=Y2
for ( z in 1:90){
  Z2[,z]=Y2[,z]*sqrt(1-(rho^2)/(rho1a^2))+Z1[,z+1]*(rho)/(rho1a)
}
Z3<-sim2d(rv3,rhx3,b3,100,0.1,91,1,100)
Y4<-sim2d(rv4,rhx4,b4,100,0.1,91,1,100)
for ( z in 2:91){
  Z4[,z]=Y4[,z]*sqrt(1-e^2)+Z1[,z-1]*e
}
#grid<-grid_co<-array(NA,c(100,91))
#grid[3,]<-env_lat[,1]
#grid_co[3,]<-diag_lat[,1]

simwell<-coco_gibbs_sampling(grid,grid_co,c(q1,q2,q3),c(qd1e4,qd2e2,qd2e3),0.1,1,c(rv1,rv2,rv3,rv4),c(rhx1,rhx2,rhx3,rhx4),c(b1,b2,b3,b4),c(rho,e*model1(a14,rv1,b1)),c(shift,a14),10)
Z1well<-simwell[,1:91]
Z2well<-simwell[,92:182]
Z3well<-simwell[,183:273]
Z4well<-simwell[,274:364]
```

now the kriging
```{r}
#rv1=rv2=rv3=rv4 = 0.1
#rhx1=rhx2=rhx3=rhx4=1
#b1=b2=b3=b4=0
#rho=e=0.0
#shift=a14=0.0
E<-coco_dual_krig(Z1well-Z1,Z2well-Z2,Z3well-Z3,Z4well-Z4,0.1,1,c(rv1,rv2,rv3,rv4),c(rhx1,rhx2,rhx3,rhx4),c(b1,b2,b3,b4),c(rho,e*model1(a14,rv1,b1)),c(shift,a14))
Z1c=Z1 + E[,1:91]
Z2c<-Z2 +E[,92:182]
Z3c<-Z3 +E[,183:273]
Z4c<-Z4 +E[,274:364]

faciesenv<-faciesdiag<-Z1c
faciesenv[Z1c<q1 & Z2c<q2]=1
faciesenv[Z1c<q1 & Z2c>q2]=2
faciesenv[Z1c>q1 & Z2c<q3]=4
faciesenv[Z1c>q1 & Z2c>q3]=3
faciesdiag[]=1
faciesdiag[Z1c>q1 & Z2c<q3 & Z3c<qd1e4]=3
faciesdiag[Z1c<q1 & Z2c>q2 & Z4c>qd2e2]=2
faciesdiag[Z1c>q1 & Z2c>q3 & Z4c>qd2e3]=2
col_env <- c("lightgreen","cadetblue","dodgerblue4","lightcoral")
W<-image(faciesenv,col = col_env)
bin<-bin2<-faciesenv
#bin[]<-rbinom(91*100, 1, 0.5)
bin[]=bin2[]=0
bin[seq(2,91*100,by=2)]=1
facies=faciesenv
facies[faciesdiag==2 & bin ==1 ] = 5
facies[faciesdiag==3]=5

col_combine <- c("lightgreen","cadetblue","dodgerblue4","lightcoral","yellow")
W<-image(facies,col = col_combine)
image(Z1c)
```

trying simulation with noise
```{r}
source("co_sim_condi.R")
```

```{r}
model<-function(h,range,b){return(exp(-abs(h/range))*cos(b*h) )}
model_lat<-function(h,range){return(exp(-(h/range)^2) )}
```
```{r}
rv1=0.3
rv2=1.2
rhx1=40
rhx2=40
b1=0
b2=5
rho=0.6
shift=0.1
rho1a<-model(shift,rv1,b1)
warning(rho>rho1a)
alpha1=(rho/rho1a)^2
alpha2=1-(rho/rho1a)^2
rv3=0.2
rv4=0.3
rhx3=40
rhx4=40
b3=0
b4=0
e=-0.8
f=-0.5

a14=-0.1
a24=0.1
rho1a14 = model(a14,rv1,b1)
rho2a24=model(a24,rv2,b2)

q1=qnorm(pe1+pe2)
Sigma1 = matrix(c(1,rho,rho,1),2,2)
q2=0
obj = Inf
for ( test in 1:100 ){
  q2test = qnorm(test/100)
  newobj =abs( pmvnorm(lower=c(-Inf,-Inf),upper=c(q1,q2test),mean=c(0,0),sigma=Sigma1) - pe1 ) 
  if (newobj < obj){
    q2 = q2test
    obj = newobj
  }
}
q3=0
obj = Inf
for ( test in 1:100 ){
  q3test = qnorm(test/100)
  newobj =abs( pmvnorm(lower=c(q1,-Inf),upper=c(Inf,q3test),mean=c(0,0),sigma=Sigma1) - pe4 ) 
  if (newobj < obj){
    q3 = q3test
    obj = newobj
  }
}

c(q1,q2,q3)

qd1e4=qnorm(pd3e4) # no correlation with the third Gaussian function
Sigmad = diag(1,3)
qd2e2=0
qd2e3=0
obje2 = Inf
obje3 = Inf
for ( test in 1:100 ){
  qd2e2test = qnorm(test/100)
  qd2e3test = qnorm(test/100)
  Sigmad[1,2]=Sigmad[2,1]=e*rho1a14
  Sigmad[1,3]=Sigmad[3,1]=e*(rho/rho1a)*model(a14-shift,rv1,b1)+f*sqrt(1-(rho/rho1a)^2)*model(a24,rv2,b2)
  Sigmad[2,3]=Sigmad[3,2]=rho
  newobje2 =abs( pmvnorm(lower=c(qd2e2test,-Inf,q2),upper=c(Inf,q1,Inf),mean=c(0,0,0),sigma=Sigmad)/pe2 - pd2e2 ) 
  newobje3 =abs( pmvnorm(lower=c(qd2e3test,q1,q3),upper=c(Inf,Inf,Inf),mean=c(0,0,0),sigma=Sigmad)/pe3 - pd2e3 )
  if (newobje2 < obje2){
    qd2e2 = qd2e2test
    obje2 = newobje2
  }
  if (newobje3 < obje3){
    qd2e3 = qd2e3test
    obje3 = newobje3
  }
}

c(qd1e4,qd2e2,qd2e3)

Z1<-sim2dexp(rv1,rhx1,b1,100,0.1,91,1,100)
Y2<-sim2dexp(rv2,rhx2,b2,100,0.1,91,1,100)
Z2=Y2
for ( z in 1:90){
  Z2[,z]=Y2[,z]*sqrt(1-(rho^2)/(rho1a^2))+Z1[,z+1]*(rho)/(rho1a)
}
Z3<-sim2dexp(rv3,rhx3,b3,100,0.1,91,1,100)
Y4<-sim2dexp(rv4,rhx4,b4,100,0.1,91,1,100)
Z4=Y4
for ( z in 2:90){
  Z4[,z]=Y4[,z]*sqrt(1-(e^2)-(f^2))+Z1[,z-1]*e+f*Y2[,z+1]
}
#grid<-grid_co<-array(NA,c(100,91))
#grid[3,]<-env_lat[,1]
#grid_co[3,]<-diag_lat[,1]

simwell<-coco_gibbs_sampling(grid,grid_co,c(q1,q2,q3),c(qd1e4,qd2e2,qd2e3),0.1,1,c(rv1,rv2,rv3,rv4),c(rhx1,rhx2,rhx3,rhx4),c(b1,b2,b3,b4),c(rho,e*model(a14,rv1,b1),f*model(a24,rv2,b2)),c(shift,a14,a24),50)
Z1well<-simwell[,1:91]
Z2well<-simwell[,92:182]
Z3well<-simwell[,183:273]
Z4well<-simwell[,274:364]

E<-coco_dual_krig(Z1well-Z1,Z2well-Z2,Z3well-Z3,Z4well-Z4,0.1,1,c(rv1,rv2,rv3,rv4),c(rhx1,rhx2,rhx3,rhx4),c(b1,b2,b3,b4),c(rho,e*model(a14,rv1,b1),f*model(a24,rv2,b2)),c(shift,a14,a24))
Z1c=Z1 + E[,1:91]
Z2c<-Z2 +E[,92:182]
Z3c<-Z3 +E[,183:273]
Z4c<-Z4 +E[,274:364]

faciesenv<-faciesdiag<-Z1c
faciesenv[Z1c<q1 & Z2c<q2]=1
faciesenv[Z1c<q1 & Z2c>q2]=2
faciesenv[Z1c>q1 & Z2c<q3]=4
faciesenv[Z1c>q1 & Z2c>q3]=3
faciesdiag[]=1
faciesdiag[Z1c>q1 & Z2c<q3 & Z3c<qd1e4]=3
faciesdiag[Z1c<q1 & Z2c>q2 & Z4c>qd2e2]=2
faciesdiag[Z1c>q1 & Z2c>q3 & Z4c>qd2e3]=2
col_env <- c("lightgreen","cadetblue","dodgerblue4","lightcoral")
W<-image(faciesenv,col = col_env)
bin<-bin2<-faciesenv
#bin[]<-rbinom(91*100, 1, 0.5)
bin[]=bin2[]=0
bin[seq(2,91*100,by=2)]=1
facies=faciesenv
facies[faciesdiag==2 & bin ==1 ] = 5
facies[faciesdiag==3]=5

col_combine <- c("lightgreen","cadetblue","dodgerblue4","lightcoral","yellow")
W<-image(facies,col = col_combine)
```

ok we have seen that the co-kriging creates a singular matrix. 
Therefore, for the kriging step we back transform the Zi on the wells in Yi and we perform the kriging on the Yi. Finally, the Yi realization is transformed into Zi. 
The advantage of that method is that because we use the Yi, they are separable. 
Therefore there is no kriging on the vertical direction and a Gaussian cosine can therefore be used!

```{r}
source("co_sim_condi.R")
```
```{r}
library(mvtnorm)
```

```{r}
model<-function(h,range,b){return(exp(-abs(h/range)^2)*cos(b*h) )}
model_lat<-function(h,range){return(exp(-(h/range)^2) )}
```

```{r}
env_lat[is.na(env_lat)]=0 # with 0, the gibbs sampler will find random values
diag_lat[is.na(diag_lat)]=0
grid<-grid_co<-array(NA,c(100,91))
grid[5,]<-env_lat[,1]
grid[25,]<-env_lat[,2]
grid[35,]<-env_lat[,3]
grid[95,]<-env_lat[,4]
grid_co[5,]<-diag_lat[,1]
grid_co[25,]<-diag_lat[,2]
grid_co[35,]<-diag_lat[,3]
grid_co[95,]<-diag_lat[,4]

```

```{r}
#parameters
rv1=0.3
rv2=1.2
rhx1=40
rhx2=40
b1=0
b2=5
rho=0.6
shift=0.1
rho1a<-model(shift,rv1,b1)
warning(rho>rho1a)
alpha1=(rho/rho1a)^2
alpha2=1-(rho/rho1a)^2
rv3=0.2
rv4=0.3
rhx3=40
rhx4=40
b3=0
b4=0
e=-0.8
f=-0.5
a14=-0.1
a24=0.1
rho1a14 = model(a14,rv1,b1)
rho2a24=model(a24,rv2,b2)

#thresholds
q1=qnorm(pe1+pe2)
Sigma1 = matrix(c(1,rho,rho,1),2,2)
q2=0
obj = Inf
for ( test in 1:100 ){
  q2test = qnorm(test/100)
  newobj =abs( pmvnorm(lower=c(-Inf,-Inf),upper=c(q1,q2test),mean=c(0,0),sigma=Sigma1) - pe1 ) 
  if (newobj < obj){
    q2 = q2test
    obj = newobj
  }
}
q3=0
obj = Inf
for ( test in 1:100 ){
  q3test = qnorm(test/100)
  newobj =abs( pmvnorm(lower=c(q1,-Inf),upper=c(Inf,q3test),mean=c(0,0),sigma=Sigma1) - pe4 ) 
  if (newobj < obj){
    q3 = q3test
    obj = newobj
  }
}
c(q1,q2,q3)
qd1e4=qnorm(pd3e4) # no correlation with the third Gaussian function
Sigmad = diag(1,3)
qd2e2=0
qd2e3=0
obje2 = Inf
obje3 = Inf
for ( test in 1:100 ){
  qd2e2test = qnorm(test/100)
  qd2e3test = qnorm(test/100)
  Sigmad[1,2]=Sigmad[2,1]=e*rho1a14
  Sigmad[1,3]=Sigmad[3,1]=e*(rho/rho1a)*model(a14-shift,rv1,b1)+f*sqrt(1-(rho/rho1a)^2)*model(a24,rv2,b2)
  Sigmad[2,3]=Sigmad[3,2]=rho
  newobje2 =abs( pmvnorm(lower=c(qd2e2test,-Inf,q2),upper=c(Inf,q1,Inf),mean=c(0,0,0),sigma=Sigmad)/pe2 - pd2e2 ) 
  newobje3 =abs( pmvnorm(lower=c(qd2e3test,q1,q3),upper=c(Inf,Inf,Inf),mean=c(0,0,0),sigma=Sigmad)/pe3 - pd2e3 )
  if (newobje2 < obje2){
    qd2e2 = qd2e2test
    obje2 = newobje2
  }
  if (newobje3 < obje3){
    qd2e3 = qd2e3test
    obje3 = newobje3
  }
}
c(qd1e4,qd2e2,qd2e3)

#unconditioned Yi
Y1<-sim2d(rv1,rhx1,b1,100,0.1,91,1,100)
Y2<-sim2d(rv2,rhx2,b2,100,0.1,91,1,100)
Y3<-sim2d(rv3,rhx3,b3,100,0.1,91,1,100)
Y4<-sim2d(rv4,rhx4,b4,100,0.1,91,1,100)

#conditioned Zi at the wells
simwell<-coco_gibbs_sampling(grid,grid_co,c(q1,q2,q3),c(qd1e4,qd2e2,qd2e3),0.1,1,c(rv1,rv2,rv3,rv4),c(rhx1,rhx2,rhx3,rhx4),c(b1,b2,b3,b4),c(rho,e*model(a14,rv1,b1),f*model(a24,rv2,b2)),c(shift,a14,a24),50)
Y1well<-simwell[,1:91]
Y2well<-Z2well<-simwell[,92:182]
Y3well<-simwell[,183:273]
Y4well<-Z4well<-simwell[,274:364]

# back transformation of the Zi into Yi at the wells
for( z in 2:90){
  Y2well[,z]=(Z2well[,z]-(rho/rho1a)*Y1well[,z+1])/sqrt(1-(rho^2)/(rho1a^2))
  Y4well[,z]=(Z4well[,z]-Y1well[,z-1]*e-f*Y2well[,z+1])/sqrt(1-(e^2)-(f^2))
}

# kriging on the Yi
Z1c =Y1 + dual_krig_line(Y1well-Y1,rhx1,1)
Z2c<-Y2c<-Y2 +dual_krig_line(Y2well-Y2,rhx2,1)
Z3c<-Y3 +dual_krig_line(Y3well-Y3,rhx3,1)
Z4c<-Y4c<-Y4 +dual_krig_line(Y4well-Y4,rhx4,1)

# transforming the conditioned realization Yi into Zi
for( z in 2:90){
  Z2c[,z]=Y2c[,z]*sqrt(1-(rho^2)/(rho1a^2))+Z1c[,z+1]*(rho)/(rho1a)
  Z4c[,z]=Y4c[,z]*sqrt(1-(e^2)-(f^2))+Z1c[,z-1]*e+f*Y2c[,z+1]
}

# transforming the Zi into facies 
faciesenv<-faciesdiag<-Z1c
faciesenv[Z1c<q1 & Z2c<q2]=1
faciesenv[Z1c<q1 & Z2c>q2]=2
faciesenv[Z1c>q1 & Z2c<q3]=4
faciesenv[Z1c>q1 & Z2c>q3]=3
faciesdiag[]=1
faciesdiag[Z1c>q1 & Z2c<q3 & Z3c<qd1e4]=3
faciesdiag[Z1c<q1 & Z2c>q2 & Z4c>qd2e2]=2
faciesdiag[Z1c>q1 & Z2c>q3 & Z4c>qd2e3]=2
col_env <- c("lightgreen","cadetblue","dodgerblue4","lightcoral")
griddata<-grid
griddata[griddata==0]=NA
W<-image(griddata,col = col_env)
W<-image(faciesenv,col = col_env)
bin<-bin2<-faciesenv
#bin[]<-rbinom(91*100, 1, 0.5)
bin[]=bin2[]=0
bin[seq(2,91*100,by=2)]=1
facies=faciesenv
facies[faciesdiag==2 & bin ==1 ] = 5
facies[faciesdiag==3]=5

col_combine <- c("lightgreen","cadetblue","dodgerblue4","lightcoral","yellow")
W<-image(facies,col = col_combine)
```

### 2018-05-31 simu3d.Rmd
added the code

---
title: "R Notebook"
output: html_notebook
---
```{r}
source("functions.R")
```

```{r}
library(mvtnorm)
```

Creation of the grid

```{r}
env_lat<-data.matrix(read.table("depo_latemar.txt"))
grid<-array(NA,c(100,10,91))
grid[5,2,]<-env_lat[,1]
grid[25,5,]<-env_lat[,2]
grid[35,8,]<-env_lat[,3]
grid[95,3,]<-env_lat[,4]

```
```{r}
e1<-e2<-e3<-e4<-matrix(0,91,4)
e1[env_lat==1]=1
e2[env_lat==2]=1
e3[env_lat==3]=1
e4[env_lat==4]=1
pe1 = mean(e1,na.rm=TRUE)
pe2 = mean(e2,na.rm=TRUE)
pe3 = mean(e3,na.rm=TRUE)
pe4 = mean(e4,na.rm=TRUE)
c(pe1,pe2,pe3,pe4)
```

```{r}
q1=qnorm(pe1+pe2)
Sigma1 = matrix(c(1,rho,rho,1),2,2)
q2=0
obj = Inf
for ( test in 1:100 ){
  q2test = qnorm(test/100)
  newobj =abs( pmvnorm(lower=c(-Inf,-Inf),upper=c(q1,q2test),mean=c(0,0),sigma=Sigma1) - pe1 ) 
  if (newobj < obj){
    q2 = q2test
    obj = newobj
  }
}
q3=0
obj = Inf
for ( test in 1:100 ){
  q3test = qnorm(test/100)
  newobj =abs( pmvnorm(lower=c(q1,-Inf),upper=c(Inf,q3test),mean=c(0,0),sigma=Sigma1) - pe4 ) 
  if (newobj < obj){
    q3 = q3test
    obj = newobj
  }
}
c(q1,q2,q3)
```

```{r}
q1=qnorm(pe1+pe2)
Sigma1 = matrix(c(1,rho,rho,1),2,2)
q2=0
obj = Inf
for ( test in 1:100 ){
  q2test = qnorm(test/100)
  newobj =abs( pmvnorm(lower=c(-Inf,-Inf),upper=c(q1,q2test),mean=c(0,0),sigma=Sigma1) - pe1 ) 
  if (newobj < obj){
    q2 = q2test
    obj = newobj
  }
}
q3=0
obj = Inf
for ( test in 1:100 ){
  q3test = qnorm(test/100)
  newobj =abs( pmvnorm(lower=c(q1,-Inf),upper=c(Inf,q3test),mean=c(0,0),sigma=Sigma1) - pe4 ) 
  if (newobj < obj){
    q3 = q3test
    obj = newobj
  }
}

```

```{r}
model<-function(h,range,b){return(exp(-(h/range)^2)*cos(b*h))}
```

```{r}
rho=0.8
shift=0.1
rho1a=model(shift,0.3,0)
Z1<-sim3d(0.3,100,0,100,0.1,91,5,100,10,10)
Z2<-sim3d(1.2,100,5,100,0.1,91,5,100,10,10)
for ( z in 1:90){
  Z2[,,z]=Z2[,,z]*sqrt(1-(rho^2)/(rho1a^2))+Z1[,,z+1]*(rho)/(rho1a)
}
```

```{r}
faciesenv<-Z1
faciesenv[Z1<q1 & Z2<q2]=1
faciesenv[Z1<q1 & Z2>q2]=2
faciesenv[Z1>q1 & Z2<q3]=4
faciesenv[Z1>q1 & Z2>q3]=3
```

```{r}
for ( z in 1:91){
  for ( y in 1:10){
    for ( x in 1:100){
      write(toString(c(faciesenv[x,y,z])),"latemaruncondrythm.csv",append=TRUE)
    }
  }
}
```

we want now to compare the experimental transiograms to the one simulated
```{r}
csime1<-csime2<-csime3<-csime4<-array(0,c(100,10,91))
csime1[faciesenv==1]=1
csime2[faciesenv==2]=1
csime3[faciesenv==3]=1
csime4[faciesenv==4]=1
```

```{r}
par(mfrow=c(3,3))
nz=91
z = (1:30)/10.
t11<-tr_2d_vert(e1,e1,30,nz,0.1)
t11sim<-tr_3d_vert(sime1,sime1,30,nz,0.1)
bt11sim<-tr_3d_vert(bsime1,bsime1,30,nz,0.1)
ct11sim<-tr_3d_vert(csime1,csime1,30,nz,0.1)
lines(z,t11sim)
lines(z,bt11sim)
lines(z,ct11sim)
t12<-tr_2d_vert(e1,e2,30,nz,0.1)
t12sim<-tr_3d_vert(sime1,sime2,30,nz,0.1)
bt12sim<-tr_3d_vert(bsime1,bsime2,30,nz,0.1)
ct12sim<-tr_3d_vert(csime1,csime2,30,nz,0.1)
lines(z,t12sim)
lines(z,bt12sim)
lines(z,ct12sim)
t13<-tr_2d_vert(e1,e3,30,nz,0.1)
t13sim<-tr_3d_vert(sime1,sime3,30,nz,0.1)
bt13sim<-tr_3d_vert(bsime1,bsime3,30,nz,0.1)
ct13sim<-tr_3d_vert(csime1,csime3,30,nz,0.1)
lines(z,t13sim)
lines(z,bt13sim)
lines(z,ct13sim)
t21<-tr_2d_vert(e2,e1,30,nz,0.1)
t21sim<-tr_3d_vert(sime2,sime1,30,nz,0.1)
bt21sim<-tr_3d_vert(bsime2,bsime1,30,nz,0.1)
ct21sim<-tr_3d_vert(csime2,csime1,30,nz,0.1)
lines(z,t21sim)
lines(z,bt21sim)
lines(z,ct21sim)
t22<-tr_2d_vert(e2,e2,30,nz,0.1)
t22sim<-tr_3d_vert(sime2,sime2,30,nz,0.1)
bt22sim<-tr_3d_vert(bsime2,bsime2,30,nz,0.1)
ct22sim<-tr_3d_vert(csime2,csime2,30,nz,0.1)
lines(z,t22sim)
lines(z,bt22sim)
lines(z,ct22sim)
t23<-tr_2d_vert(e2,e3,30,nz,0.1)
t23sim<-tr_3d_vert(sime2,sime3,30,nz,0.1)
bt23sim<-tr_3d_vert(bsime2,bsime3,30,nz,0.1)
ct23sim<-tr_3d_vert(csime2,csime3,30,nz,0.1)
lines(z,t23sim)
lines(z,bt23sim)
lines(z,ct23sim)
t31<-tr_2d_vert(e3,e1,30,nz,0.1)
t31sim<-tr_3d_vert(sime3,sime1,30,nz,0.1)
bt31sim<-tr_3d_vert(bsime3,bsime1,30,nz,0.1)
ct31sim<-tr_3d_vert(csime3,csime1,30,nz,0.1)
lines(z,t31sim)
lines(z,bt31sim)
lines(z,ct31sim)
t32<-tr_2d_vert(e3,e2,30,nz,0.1)
t32sim<-tr_3d_vert(sime3,sime2,30,nz,0.1)
bt32sim<-tr_3d_vert(bsime3,bsime2,30,nz,0.1)
ct32sim<-tr_3d_vert(csime3,csime2,30,nz,0.1)
lines(z,t32sim)
lines(z,bt32sim)
lines(z,ct32sim)
t33<-tr_2d_vert(e3,e3,30,nz,0.1)
t33sim<-tr_3d_vert(sime3,sime3,30,nz,0.1)
bt33sim<-tr_3d_vert(bsime3,bsime3,30,nz,0.1)
ct33sim<-tr_3d_vert(csime3,csime3,30,nz,0.1)
lines(z,t33sim)
lines(z,bt33sim)
lines(z,ct33sim)
```

### 2018-05-31 co_sim_condi.R
simulation tools

@@ -1,0 +1,593 @@
+# conditioning for four Gaussian functions
+# the covariance matrix is going to be very big
+# probably not inversible, so that we will probably need to use exponential covariances
+
+negrnorm<-function(q,mean,sd){
+  a=rnorm(1,mean,sd)
+  while(a>q){
+    a=rnorm(1,mean,sd)
+  }
+  return(a)
+}
+
+posrnorm<-function(q,mean,sd){
+  a=rnorm(1,mean,sd)
+  while(a<q){
+    a=rnorm(1,mean,sd)
+  }
+  return(a)
+}
+
+truncnorm<-function(qmin,qmax,mean,sd){
+  a=rnorm(1,mean,sd)
+  while(a<qmin | a >qmax){
+    a=rnorm(1,mean,sd)
+  }
+  return(a)
+}
+
+coco_cov_data<-function(data_loc,data_loc_co,dz,dhx,rv,rhx,b,rho,shift){
+  # the matrix is going to be non symmetric but positive definit
+  # we are here coding the general case where n can be different from n_co
+  n=nrow(data_loc)
+  n_co=nrow(data_loc_co)
+  dist_hx <- dist_v<- matrix(0,n,n)
+  for ( i in 1:(n-1)){
+    for (j in (i+1):n ){
+      dist_v[i,j]=-(data_loc[i,2]-data_loc[j,2])*dz
+      dist_v[j,i]=-dist_v[i,j]
+      dist_hx[i,j]=dist_hx[j,i]=abs(data_loc[i,1]-data_loc[j,1])*dhx
+    }
+  }
+  dist_hx_co <- dist_v_co<- matrix(0,n,n_co)
+  co_dist_hx <- co_dist_hy <- co_dist_v<- matrix(0,n_co,n)
+  for ( i in 1:n){
+    for (j in 1:n_co ){
+      dist_v_co[i,j]=-(data_loc[i,2]-data_loc_co[j,2])*dz
+      co_dist_v[j,i]=-dist_v_co[i,j]
+      dist_hx_co[i,j]=co_dist_hx[j,i]=abs(data_loc[i,1]-data_loc_co[j,1])*dhx
+    }
+  }
+  co_dist_hx_co  <- co_dist_v_co<- matrix(0,n_co,n_co)
+  for ( i in 1:(n_co-1)){
+    for (j in (i+1):n_co ){
[…]

### 2018-05-31 cosim_functions.R

@@ -1,0 +1,155 @@
+
+# basic function to plot a transiogram
+tr_2d_vert<-function(datai,dataj,size,ncell,dz){
+  cov<-numeric(size)
+  for (l in 1:size){
+    npair = nrow(datai)-l
+    t =0
+    for ( pair in 1:npair){
+      for ( y in 1:ncol(datai)){
+        if(is.na(datai[pair,y])== FALSE & is.na(dataj[pair+l,y]) == FALSE){
+          cov[l] = cov[l]+ datai[pair,y]*dataj[pair+l-1,y]
+          t = t+1
+        }
+      }
+    }
+    cov[l]=cov[l]/t
+  }
+  cov = cov /mean(datai,na.rm = TRUE)# we are measuring a correlation
+  dist = (0:(size-1))/(ncell*dz)
+  plot(dist,cov,type = "p",col="black",pch=21,bg="grey",cex=2,ylim=c(0.,1),ylab = "", xlab = "", axes = FALSE)
+  axis(1,at = seq(0,3,0.5),cex.axis=1.5)
+  axis(2,cex.axis=1.5)
+  #mtext("Distance", side = 1, line = 2.5, cex = 1.)
+  #mtext("Transiogram", side = 2, line = 2.5, cex = 1.,las = 0)
+  return(cov)
+}
+
+embedded3d<-function(datai,dataj){
+  # we assume there is no NA 
+  ndim=dim(datai)
+  embed=0
+  Tii=0
+  n=ndim[3]-1
+  prop=mean(datai[,,-182]) # the last line is not counted
+  for ( z in 1:n){
+    Tii=Tii+mean(datai[,,z]*datai[,,z+1])/n
+    embed=embed+mean(datai[,,z]*dataj[,,z+1])/n
+  }
+  Tii=(1-Tii/prop)
+  embed=embed/prop
+  return(embed/Tii) 
+}
+
+embedded2d<-function(datai,dataj){
+  
+  embed=0
+  Tii=0
+  n=nrow(datai)-1
+  prop=mean(datai[-(n+1),],na.rm=TRUE) # the last line is not counted
+  count=0
+  for ( z in 1:n){
+    for (x in 1:ncol(dataj)){
[…]

### 2018-09-13 article_code.Rmd
comment

@@
 
+loading the functions, replace with the location of your files
 ```{r}

### 2018-09-13 article_code.Rmd
title
Comments

--- 2018-05-31 article_code.Rmd
@@
 ---
-
-# the project is in Dropbox/coding/cosimulation
-
+# Simulation of the Latemar Carbonate platform
+
+loading the functions, replace with the location of your files
 ```{r}
@@
 ```
+Two libraries used that you first need to install with R
+mvtnorm compute integral over Gaussian densities
 ```{r}

### 2018-09-13 article_code.Rmd
space

@@
 Two libraries used that you first need to install with R
+
 mvtnorm compute integral over Gaussian densities

### 2018-09-13 article_code.Rmd
re arranging

@@
 ```
-
-```{r}
+Getting the facies logs and transforming them into indicator variables
+```{r}
+env_lat<-data.matrix(read.table("depo_latemar.txt"))
+diag_lat<-data.matrix(read.table("diag_latemar.txt"))
+nz=nrow(env_lat)
 e1<-e2<-e3<-e4<-d1<-d2<-d3<-matrix(0,nz,4)
@@
 ```
+Computing proportions of the different facies in the logs
+
 ```{r}
@@
 ```
+Building the grids for the Earth models
+
+Because there are two fields: depositional and diagenetic, there are two grids
 
@@
 ```
-ok we also want to display an image with all the logs
-we are doubling the wells for a better visualization
-```{r}
+displaying an image with all the logs
+```{r}
+# we are doubling the logs for a better visualization
 im<-matrix(NA,100,91)
@@
 ```
-we also want to display the environment of depositions and the diagenesis
+Another image the environment of depositions and the diagenesis logs
 ```{r}
@@
 ```
+print image
 ```{r}
@@
 (verifier le gibbs sampling pour la nouvelle truncation rule)
-
-```{r}
-library(mvtnorm)
-```
-```{r}
-source("co_sim_condi.R")
-```
 

### 2018-09-17 main.Rmd
deletion
deleted synthetic examples not used in the paper

--- 2018-09-13 article_code.Rmd
@@
 ```{r}
-source("C:/Users/tl3315/Dropbox/coding/cosimulation/co_sim_condi.R")
-source("C:/Users/tl3315/Dropbox/coding/cosimulation/cosim_functions.R")
+source("C:/Users/tl3315/Desktop/GitHub/AsymBiPGS/co_sim_condi.R")
+source("C:/Users/tl3315/Desktop/GitHub/AsymBiPGS/cosim_functions.R")
 ```
@@
 ```
+increasing the details of the section
 
@@
 the first figure we want to have is a 3d simulation of the Latemar conditioned !
-```{r}
-rv1=0.3
-rv2=1.2
-rhx1=rhy1=800
-rhx2=rhy2=800
-b1=0
-b2=5
-rho=0.6
-shift=0.1
-rho1a<-model(shift,rv1,b1)
-warning(rho>rho1a)
-alpha1=(rho/rho1a)^2
-alpha2=1-(rho/rho1a)^2
-rv3=0.2
-rv4=0.3
-rhx3=rhy3=800
-rhx4=rhy4=800
-b3=0
-b4=0
-e=-0.8
-f=-0.5
-a14=-0.1
-a24=0.1
-rho1a14 = model(a14,rv1,b1)
-rho2a24=model(a24,rv2,b2)
 
-#thresholds
-q1=qnorm(pe1+pe2)
-Sigma1 = matrix(c(1,rho,rho,1),2,2)
-q2=0
-obj = Inf
-for ( test in 1:100 ){
-  q2test = qnorm(test/100)
-  newobj =abs( pmvnorm(lower=c(-Inf,-Inf),upper=c(q1,q2test),mean=c(0,0),sigma=Sigma1) - pe1 ) 
-  if (newobj < obj){
-    q2 = q2test
-    obj = newobj
-  }
-}
-q3=0
-obj = Inf
-for ( test in 1:100 ){
-  q3test = qnorm(test/100)
-  newobj =abs( pmvnorm(lower=c(q1,-Inf),upper=c(Inf,q3test),mean=c(0,0),sigma=Sigma1) - pe4 ) 
-  if (newobj < obj){
-    q3 = q3test
-    obj = newobj
-  }
-}
-c(q1,q2,q3)
-qd1e4=qnorm(pd3e4) # no correlation with the third Gaussian function
-Sigmad = diag(1,3)
-qd2e2=0
-qd2e3=0
-obje2 = Inf
-obje3 = Inf
-for ( test in 1:100 ){
-  qd2e2test = qnorm(test/100)
-  qd2e3test = qnorm(test/100)
-  Sigmad[1,2]=Sigmad[2,1]=e*rho1a14
-  Sigmad[1,3]=Sigmad[3,1]=e*(rho/rho1a)*model(a14-shift,rv1,b1)+f*sqrt(1-(rho/rho1a)^2)*model(a24,rv2,b2)
-  Sigmad[2,3]=Sigmad[3,2]=rho
-  newobje2 =abs( pmvnorm(lower=c(qd2e2test,-Inf,q2),upper=c(Inf,q1,Inf),mean=c(0,0,0),sigma=Sigmad)/pe2 - pd2e2 ) 
-  newobje3 =abs( pmvnorm(lower=c(qd2e3test,q1,q3),upper=c(Inf,Inf,Inf),mean=c(0,0,0),sigma=Sigmad)/pe3 - pd2e3 )
-  if (newobje2 < obje2){
-    qd2e2 = qd2e2test
-    obje2 = newobje2
-  }
-  if (newobje3 < obje3){
-    qd2e3 = qd2e3test
-    obje3 = newobje3
-  }
-}
-c(qd1e4,qd2e2,qd2e3)
-
-Y1<-sim3d(rv1,rhx1,rhy1,b1,100,0.1,91,10,100,25,10)
-Y2<-sim3d(rv2,rhx2,rhy2,b2,100,0.1,91,10,100,25,10)
-Y3<-sim3d(rv3,rhx3,rhy3,b3,100,0.1,91,10,100,25,10)
-Y4<-sim3d(rv4,rhx4,rhy4,b4,100,0.1,91,10,100,25,10)
-
-simwell<-gibbs_sampling3d(grid,grid_co,c(q1,q2,q3),c(qd1e4,qd2e2,qd2e3),0.1,10,25,c(rv1,rv2,rv3,rv4),c(rhx1,rhx2,rhx3,rhx4),c(rhy1,rhy2,rhy3,rhy4),c(b1,b2,b3,b4),c(rho,e*model(a14,rv1,b1),f*model(a24,rv2,b2)),c(shift,a14,a24),50)
-Y1well<-simwell[,,1:91]
-Y2well<-Z2well<-simwell[,,92:182]
-Y3well<-simwell[,,183:273]
-Y4well<-Z4well<-simwell[,,274:364]
-
-# back transformation of the Zi into Yi at the wells
-for( z in 2:90){
-  Y2well[,,z]=(Z2well[,,z]-(rho/rho1a)*Y1well[,,z+1])/sqrt(1-(rho^2)/(rho1a^2))
-  Y4well[,,z]=(Z4well[,,z]-Y1well[,,z-1]*e-f*Y2well[,,z+1])/sqrt(1-(e^2)-(f^2))
-}
-
-Z1c =Y1 + dual_krig_surf(Y1well-Y1,rhx1,rhy1,10,25)
-Z2c<-Y2c<-Y2 +dual_krig_surf(Y2well-Y2,rhx2,rhy2,10,25)
-Z3c<-Y3 +dual_krig_surf(Y3well-Y3,rhx3,rhy3,10,25)
-Z4c<-Y4c<-Y4 +dual_krig_surf(Y4well-Y4,rhx4,rhy4,10,25)
-
-for( z in 2:90){
-  Z2c[,,z]=Y2c[,,z]*sqrt(1-(rho^2)/(rho1a^2))+Z1c[,,z+1]*(rho)/(rho1a)
-  Z4c[,,z]=Y4c[,,z]*sqrt(1-(e^2)-(f^2))+Z1c[,,z-1]*e+f*Y2c[,,z+1]
-}
-
-faciesenv<-faciesdiag<-Z1c
-faciesenv[Z1c<q1 & Z2c<q2]=1
-faciesenv[Z1c<q1 & Z2c>q2]=2
-faciesenv[Z1c>q1 & Z2c<q3]=4
-faciesenv[Z1c>q1 & Z2c>q3]=3
-faciesdiag[]=1
-faciesdiag[Z1c>q1 & Z2c<q3 & Z3c<qd1e4]=3
-faciesdiag[Z1c<q1 & Z2c>q2 & Z4c>qd2e2]=2
-faciesdiag[Z1c>q1 & Z2c>q3 & Z4c>qd2e3]=2
-col_env <- c("lightgreen","cadetblue","dodgerblue4","lightcoral")
-griddata<-grid
-griddata[griddata==0]=NA
-W<-image(griddata[,2,],col = col_env)
-W<-image(faciesenv[,2,],col = col_env)
-
-```
-
-```{r}
-for ( z in 1:91){
-  for ( y in 1:10){
-    for ( x in 1:100){
-      write(toString(c(faciesenv[x,y,z])),"latemarcondenv.csv",append=TRUE)
-      write(toString(c(faciesdiag[x,y,z])),"latemarconddiag.csv",append=TRUE)
-    }
-  }
-}
-```
 another simu with only three Gaussian functions
@@
 ```
-
-ok now that we have looked at the case study of the Latemar, 
-we also want to create synthetic examples with a simpler parameter space. 
-So we have only two Gaussian functions with two truncation rules, so it is like two TGS!
-
-```{r}
-model<-function(h,range,b){return(exp(-abs(h/range)^2)*cos(b*h) )}
-```
-```{r}
-library(mvtnorm)
-```
-
-```{r}
-
-# set of parameters 
-pe1=0.5
-pe2=1-pe1
-pe1d1=0.0
-pe2d1=0.3
-rv1=0.3
-rv2=1
-rhx1=40
-rhx2=10
-b1=0
-b2=0
-a=0.9
-shift=0.1
-rho1a<-model(shift,rv1,b1)
-
-#thresholds
-q1=qnorm(pe1) # threshold for environment of deposition
-
-q2e1=q2e2=0 # two thresholds for diagenetic facies 
-Sigma = matrix(c(1,a*rho1a,a*rho1a,1),2,2)
-obj1=obj2=Inf
-for ( test in 1:100 ){
-  q2e1test = qnorm(test/100)
-  q2e2test = qnorm(test/100)
-  newobj1 =abs( pmvnorm(lower=c(-Inf,-Inf),upper=c(q1,q2e1test),mean=c(0,0),sigma=Sigma)/pe1 - pe1d1) 
-  newobj2 =abs( pmvnorm(lower=c(q1,-Inf),upper=c(Inf,q2e2test),mean=c(0,0),sigma=Sigma)/pe2 - pe2d1)
-  if (newobj1 < obj1){
-    q2e1= q2e1test
-    obj1 = newobj1
-  }
-  if (newobj2 < obj2){
-    q2e2= q2e2test
-    obj2 = newobj2
-  }
-}
-
-#transiograms
-te1d1=te2d1=te1d2=te2d2=rep(0,300)
-te1d1opp=te2d1opp=te1d2opp=te2d2opp=rep(0,300)
-Sigma = diag(1,3)
-Sigma[3,2]=Sigma[2,3]=a*rho1a
-Sigmaopp = Sigma
-
-for (i in 1:300){
-    d = i/100.
-    Sigma[1,2]=Sigma[2,1]= model(d,rv1,b1)
-    Sigma[1,3]=Sigma[3,1]=a*model(d+shift,rv1,b1)
-
-    Sigmaopp[1,2]=Sigmaopp[2,1]= model(-d,rv1,b1)
-    Sigmaopp[1,3]=Sigmaopp[3,1]=a*model(-d+shift,rv1,b1)
-
-    te1d1[i]=(pmvnorm(lower=c(-Inf,-Inf,-Inf),upper=c(q1,q1,q2e1),mean=c(0,0,0),sigma=Sigma) + pmvnorm(lower=c(-Inf,q1,-Inf),upper=c(q1,Inf,q2e2),mean=c(0,0,0),sigma=Sigma))/ pe1
-    te2d1[i]=(pmvnorm(lower=c(q1,-Inf,-Inf),upper=c(Inf,q1,q2e1),mean=c(0,0,0),sigma=Sigma) + pmvnorm(lower=c(q1,q1,-Inf),upper=c(Inf,Inf,q2e2),mean=c(0,0,0),sigma=Sigma))/ pe2
-    te1d2[i]=(pmvnorm(lower=c(-Inf,-Inf,q2e1),upper=c(q1,q1,Inf),mean=c(0,0,0),sigma=Sigma) + pmvnorm(lower=c(-Inf,q1,q2e2),upper=c(q1,Inf,Inf),mean=c(0,0,0),sigma=Sigma))/ pe1
-    te2d2[i]=(pmvnorm(lower=c(q1,-Inf,q2e1),upper=c(Inf,q1,Inf),mean=c(0,0,0),sigma=Sigma) + pmvnorm(lower=c(q1,q1,q2e2),upper=c(Inf,Inf,Inf),mean=c(0,0,0),sigma=Sigma))/ pe2
-
-    te1d1opp[i]=(pmvnorm(lower=c(-Inf,-Inf,-Inf),upper=c(q1,q1,q2e1),mean=c(0,0,0),sigma=Sigmaopp) + pmvnorm(lower=c(-Inf,q1,-Inf),upper=c(q1,Inf,q2e2),mean=c(0,0,0),sigma=Sigma))/ pe1
-    te2d1opp[i]=(pmvnorm(lower=c(q1,-Inf,-Inf),upper=c(Inf,q1,q2e1),mean=c(0,0,0),sigma=Sigmaopp) + pmvnorm(lower=c(q1,q1,-Inf),upper=c(Inf,Inf,q2e2),mean=c(0,0,0),sigma=Sigma))/ pe2
-    te1d2opp[i]=(pmvnorm(lower=c(-Inf,-Inf,q2e1),upper=c(q1,q1,Inf),mean=c(0,0,0),sigma=Sigmaopp) + pmvnorm(lower=c(-Inf,q1,q2e2),upper=c(q1,Inf,Inf),mean=c(0,0,0),sigma=Sigma))/ pe1
-    te2d2opp[i]=(pmvnorm(lower=c(q1,-Inf,q2e1),upper=c(Inf,q1,Inf),mean=c(0,0,0),sigma=Sigmaopp) + pmvnorm(lower=c(q1,q1,q2e2),upper=c(Inf,Inf,Inf),mean=c(0,0,0),sigma=Sigma))/ pe2
-}
-
-z = (1:300)/100.
-par(mfrow=c(2,2))
-plot(z,te1d1,ylim=c(0.,1),type="l")
-plot(z,te1d2,ylim=c(0.,1),type="l")
-plot(z,te2d1,ylim=c(0.,1),type="l")
-plot(z,te2d2,ylim=c(0.,1.2),type="l")
-plot(z,te1d1opp,ylim=c(0.,1),type="l")
-plot(z,te1d2opp,ylim=c(0.,1),type="l")
-plot(z,te2d1opp,ylim=c(0.,1),type="l")
-plot(z,te2d2opp,ylim=c(0.,1.2),type="l")
-```
-
-lets do the simulation
-```{r}
-Y1<-sim2d(rv1,rhx1,b1,100,0.1,91,2,100)
-Z2<-Y2<-sim2d(rv2,rhx2,b2,100,0.1,91,2,100)
-
-for( z in 2:90){
-  Z2[,z]=Y2[,z]*sqrt(1-(a^2))+Y1[,z-1]*a
-}
-
-faciesenv<-faciesdiag<-Y1
-faciesenv[Y1<q1]=1
-faciesenv[Y1>q1 ]=2
-both<-faciesenv
-faciesdiag[]=2
-faciesdiag[Y1<q1 & Z2<q2e1 ]=1
-faciesdiag[Y1>q1 & Z2<q2e2 ]=1
-both[faciesdiag==1]=3
-image(faciesenv,col=c("white","grey"))
-#image(faciesdiag)
-image(both,col=c("white","grey","red"))
-```
-
-okay now that we hae studied some transiograms, the aim is to generate beautiful images with more facies
-
-```{r}
-
-pe1=0.4
-pe2=0.4
-pe3=0.2
-pe1d1=0.3
-pe2d1=0.3
-pe3d1=0.3
-rv1=0.3
-rv2=0.3
-rhx1=60
-rhx2=60
-b1=0
-b2=0
-a=0.8
-shift=0.1
-rho1a<-model(shift,rv1,b1)
-
-q1a=qnorm(pe1) # threshold for environment of deposition
-q1b=qnorm(pe1+pe2)
-
-q2e1=q2e2=q2e3=0 # two thresholds for diagenetic facies 
-Sigma = matrix(c(1,a*rho1a,a*rho1a,1),2,2)
-obj1=obj2=obj3=Inf
-for ( test in 1:100 ){
-  q2e1test = qnorm(test/100)
-  q2e2test = qnorm(test/100)
-  q2e3test = qnorm(test/100)
-  newobj1 =abs( pmvnorm(lower=c(-Inf,-Inf),upper=c(q1a,q2e1test),mean=c(0,0),sigma=Sigma)/pe1 - pe1d1) 
-  newobj2 =abs( pmvnorm(lower=c(q1a,-Inf),upper=c(q1b,q2e2test),mean=c(0,0),sigma=Sigma)/pe2 - pe2d1)
-  newobj3 =abs( pmvnorm(lower=c(q1b,-Inf),upper=c(Inf,q2e3test),mean=c(0,0),sigma=Sigma)/pe3 - pe3d1)
-  if (newobj1 < obj1){
-    q2e1= q2e1test
-    obj1 = newobj1
-  }
-  if (newobj2 < obj2){
-    q2e2= q2e2test
-    obj2 = newobj2
-  }
-  if (newobj3 < obj3){
-    q2e3= q2e3test
-    obj3 = newobj3
-  }
-}
-
-Y1<-sim2d(rv1,rhx1,b1,100,0.05,91,1,100)
-Z2<-Y2<-sim2d(rv2,rhx2,b2,100,0.05,91,1,100)
-
-for( z in 2:90){
-  Z2[,z]=Y2[,z]*sqrt(1-(a^2))+Y1[,z-1]*a
-}
-
-faciesenv<-faciesdiag<-Y1
-faciesenv[Y1<q1a]=1
-faciesenv[Y1>q1a & Y1<q1b ]=2
-faciesenv[Y1>q1b ]=3
-combined<-faciesenv
-faciesdiag[]=2
-faciesdiag[Y1<q1a & Z2<q2e1 ]=1
-faciesdiag[Y1>q1a & Y1<q1b & Z2<q2e2 ]=1
-faciesdiag[Y1>q1b & Z2<q2e3 ]=1
-combined[faciesenv==1 & faciesdiag==1]=4
-combined[faciesenv==2 & faciesdiag==1]=5
-combined[faciesenv==3 & faciesdiag==1]=6
-image(faciesenv,col=c("ivory1","ivory3","ivory4"))
-image(combined,col=c("ivory1","ivory3","ivory4","gold","darkorange","firebrick"))
-```
-same facies here but with vertical anisotropy for some so that it looks like fracture related diagenesis
-```{r}
-pe1=0.4
-pe2=0.4
-pe3=0.2
-pe1d1=0.3
-pe2d1=0.3
-pe3d1=0.3
-rv1=0.3
-rv2=10
-rhx1=60
-rhx2=5
-b1=0
-b2=0
-a=0.8
-shift=0.1
-rho1a<-model(shift,rv1,b1)
-
-q1a=qnorm(pe1) # threshold for environment of deposition
-q1b=qnorm(pe1+pe2)
-
-q2e1=q2e2=q2e3=0 # two thresholds for diagenetic facies 
-Sigma = matrix(c(1,a*rho1a,a*rho1a,1),2,2)
-obj1=obj2=obj3=Inf
-for ( test in 1:100 ){
-  q2e1test = qnorm(test/100)
-  q2e2test = qnorm(test/100)
-  q2e3test = qnorm(test/100)
-  newobj1 =abs( pmvnorm(lower=c(-Inf,-Inf),upper=c(q1a,q2e1test),mean=c(0,0),sigma=Sigma)/pe1 - pe1d1) 
-  newobj2 =abs( pmvnorm(lower=c(q1a,-Inf),upper=c(q1b,q2e2test),mean=c(0,0),sigma=Sigma)/pe2 - pe2d1)
-  newobj3 =abs( pmvnorm(lower=c(q1b,-Inf),upper=c(Inf,q2e3test),mean=c(0,0),sigma=Sigma)/pe3 - pe3d1)
-  if (newobj1 < obj1){
-    q2e1= q2e1test
-    obj1 = newobj1
-  }
-  if (newobj2 < obj2){
-    q2e2= q2e2test
-    obj2 = newobj2
-  }
-  if (newobj3 < obj3){
-    q2e3= q2e3test
-    obj3 = newobj3
-  }
-}
-
-Y1<-sim2d(rv1,rhx1,b1,100,0.05,91,1,100)
-Z2<-Y2<-sim2d(rv2,rhx2,b2,100,0.05,91,1,100)
-
-for( z in 2:90){
-  Z2[,z]=Y2[,z]*sqrt(1-(a^2))+Y1[,z-1]*a
-}
-
-faciesenv<-faciesdiag<-Y1
-faciesenv[Y1<q1a]=1
-faciesenv[Y1>q1a & Y1<q1b ]=2
-faciesenv[Y1>q1b ]=3
-combined<-faciesenv
-faciesdiag[]=2
-faciesdiag[Y1<q1a & Z2<q2e1 ]=1
-faciesdiag[Y1>q1a & Y1<q1b & Z2<q2e2 ]=1
-faciesdiag[Y1>q1b & Z2<q2e3 ]=1
-combined[faciesenv==1 & faciesdiag==1]=4
-combined[faciesenv==2 & faciesdiag==1]=5
-combined[faciesenv==3 & faciesdiag==1]=6
-image(faciesenv,col=c("ivory1","ivory3","ivory4"))
-image(combined,col=c("ivory1","ivory3","ivory4","gold","darkorange","firebrick"))
-```
-
-in three dimensions
-```{r}
-Z1<-sim3d(r1v,r1l,r1l,0,100,0.1,50,5,50,5,50)
-Z2<-sim3d(r2v,r2l,r2l,0,100,0.1,50,5,50,5,50)
-Y2<-Z2
-for( z in 2:50){
-  Z2[,,z]=Y2[,,z]*sqrt(1-(a^2))+Z1[,,z-1]*a
-}
-faciesenv<-faciesdiag<-Z1
-faciesenv[Z1<q1a]=1
-faciesenv[Z1>q1a & Z1<q1b ]=2
-faciesenv[Z1>q1b ]=3
-combined<-faciesenv
-faciesdiag[]=2
-faciesdiag[Z1<q1a & Z2<q2e1 ]=1
-faciesdiag[Z1>q1a & Z1<q1b & Z2<q2e2 ]=1
-faciesdiag[Z1>q1b & Z2<q2e3 ]=1
-combined[faciesenv==1 & faciesdiag==1]=4
-combined[faciesenv==2 & faciesdiag==1]=5
-combined[faciesenv==3 & faciesdiag==1]=6
-
-for ( z in 1:50){
-  for ( y in 1:50){
-    for ( x in 1:50){
-      write(toString(c(combined[x,y,z])),"fracturecombined.csv",append=TRUE)
-    }
-  }
-}
-```
-
-okay, we are going to change slighlty the simulation. 
-We now do a pgs simulation for the environment of depositions so that we can have cyclicity. 
-And the diagenesis happens only in two of the facies intertidal and supratidal. 
-It might be better to visualize it like this.
-
-```{r}
-pe1=0.34
-pe2=0.33
-pe3=0.34
-pe1d1=0.
-pe2d1=0.3
-pe3d1=0.4
-rv1=0.2
-rv2=0.2
-rv3=0.2
-rhx1=60
-rhx2=60
-rhx3=200
-b1=0
-b2=0
-b3=0
-a=0.99
-b=0.99
-shift=0.1
-shiftb=-0.1
-rho1a<-model(shift,rv1,b1)
-rho1b<-model(shiftb,rv1,b1)
-
-q1=qnorm(pe1) # subtidal facies defined by one Gaussian function
-
-# for intertidal and supratidal, second Gaussian function
-Sigma2 = matrix(c(1,a*rho1a,a*rho1a,1),2,2)
-q2=0 
-obj = Inf
-for ( test in 1:100 ){
-  q2test = qnorm(test/100)
-  newobj =abs( pmvnorm(lower=c(q1,-Inf),upper=c(Inf,q2test),mean=c(0,0),sigma=Sigma2) - pe3 ) 
-  if (newobj < obj){
-    q2 = q2test
-    obj = newobj
-  }
-}
-
-q3e1=-Inf
-q3e2=q3e3=0 # two thresholds for diagenetic facies 
-Sigma3 = diag(1,3)
-Sigma3[1,2]=Sigma3[2,1]=a*rho1a
-Sigma3[1,3]=Sigma3[3,1]=b*rho1b
-Sigma3[2,3]=Sigma3[3,2]=a*b*model(shift-shiftb,rv1,b1)
-
-obj1=obj2=obj3=Inf
-for ( test in 1:1000 ){
-  q3e2test = qnorm(test/1000)
-  q3e3test = qnorm(test/1000)
-  newobj2 =abs( pmvnorm(lower=c(q1,q2,-Inf),upper=c(Inf,Inf,q3e2test),mean=c(0,0,0),sigma=Sigma3)/pe2 - pe2d1)
-  newobj3 =abs( pmvnorm(lower=c(q1,-Inf,-Inf),upper=c(Inf,q2,q3e3test),mean=c(0,0,0),sigma=Sigma3)/pe3 - pe3d1)
-  if (newobj2 < obj2){
-    q3e2= q3e2test
-    obj2 = newobj2
-  }
-  if (newobj3 < obj3){
-    q3e3= q3e3test
-    obj3 = newobj3
-  }
-}
-
-# Te2de2 as if there is only one facies field, which means that I will have a matrix slightly bigger.
-# Z1(x)>q1 Z2(x)>q2 Z1(x+h)>q1 Z2(x+h)>q2 Z3(x+h)<q3e2 Z3(x)>q3e2
-# Which means we have a 6*6 matrix
-# 
-# Cov[Z3(x),Z1(x)]=cov[bZ1(x+beta),Z1(x)]
-# Cov[Z3(x),Z2(x)]=cov[bZ1(x+beta),aZ1(x+alpha)]
-# 
-# Cov[Z2(x),Z2(x+h)]=Cov[aZ1(x+alpha)+sqrt(1-a)Y2(x), aZ1(x+h+alpha)+sqrt(1-a)Y2(x+h)]
-
-# #transiograms
-te1de2=te2de2=te3de2=te1de3=te2de3=te3de3=rep(0,300)
-te1de2opp=te2de2opp=te3de2opp=te1de3opp=te2de3opp=te3de3opp=rep(0,300)
-Sigma = diag(1,6)
-Sigmaopp = diag(1,6)
-Sigma[1,2]=Sigma[2,1]=Sigma[3,4]=Sigma[4,3]=a*rho1a
-Sigma[3,5]=Sigma[5,3]=Sigma[1,6]=Sigma[6,1]=b*rho1b
-Sigma[4,5]=Sigma[5,4]=Sigma[2,6]=Sigma[6,2]=a*b*model(shiftb-shift,rv1,b1)
-
-Sigmaopp = Sigma
-for (i in 1:300){
-    d = i/100.
-    Sigma[1,3]=Sigma[3,1]= model(d,rv1,b1)
-    Sigma[1,4]=Sigma[4,1]=a*model(d+shift,rv1,b1)
-    Sigma[1,5]=Sigma[5,1]=b*model(d+shiftb,rv1,b1)
-    Sigma[2,3]=Sigma[3,2]=a*model(d-shift,rv1,b1)
-    Sigma[2,4]=Sigma[4,2]= (a^2)*model(d,rv1,b1)+sqrt(1-a^2)*model(d,rv2,b2)
-    Sigma[2,5]=Sigma[5,2]=a*b*model(d+shiftb-shift,rv1,b1)
-
-    Sigma[3,6]=Sigma[6,3]=b*model(d-shiftb,rv1,b1)
-    Sigma[4,6]=Sigma[6,4]=a*b*model(d+shift-shiftb,rv1,b1)
-    Sigma[5,6]=Sigma[6,5]=(b^2)*model(d,rv1,b1)+sqrt(1-b^2)*model(d,rv3,b3)
-
-    Sigmaopp[1,3]=Sigmaopp[3,1]= model(-d,rv1,b1)
-    Sigmaopp[1,4]=Sigmaopp[4,1]=a*model(-d+shift,rv1,b1)
-    Sigmaopp[1,5]=Sigmaopp[5,1]=b*model(-d+shiftb,rv1,b1)
-    Sigmaopp[2,3]=Sigmaopp[3,2]=a*model(-d-shift,rv1,b1)
-    Sigmaopp[2,4]=Sigmaopp[4,2]= (a^2)*model(-d,rv1,b1)+sqrt(1-a^2)*model(-d,rv2,b2)
-    Sigmaopp[2,5]=Sigmaopp[5,2]=a*b*model(-d+shiftb-shift,rv1,b1)
-
-    Sigmaopp[3,6]=Sigmaopp[6,3]=b*model(-d-shiftb,rv1,b1)
-    Sigmaopp[4,6]=Sigmaopp[6,4]=a*b*model(-d+shift-shiftb,rv1,b1)
-    Sigmaopp[5,6]=Sigmaopp[6,5]=(b^2)*model(-d,rv1,b1)+sqrt(1-b^2)*model(-d,rv3,b3)
-
-    te1de2[i]=pmvnorm(lower=c(-Inf,-Inf,q1,q2,-Inf,-Inf),upper=c(q1,Inf,Inf,Inf,q3e2,Inf),mean=c(0,0,0,0,0,0),sigma=Sigma)/ pe1
-    te2de2[i]=pmvnorm(lower=c(q1,q2,q1,q2,-Inf,q3e2),upper=c(Inf,Inf,Inf,Inf,q3e2,Inf),mean=c(0,0,0,0,0,0),sigma=Sigma)/ pe2
-    te3de2[i]=pmvnorm(lower=c(q1,-Inf,q1,q2,-Inf,q3e3),upper=c(Inf,q2,Inf,Inf,q3e2,Inf),mean=c(0,0,0,0,0,0),sigma=Sigma)/ pe3
-
-    te1de3[i]=pmvnorm(lower=c(-Inf,-Inf,q1,-Inf,-Inf,-Inf),upper=c(q1,Inf,Inf,q2,q3e3,Inf),mean=c(0,0,0,0,0,0),sigma=Sigma)/ pe1
-    te2de3[i]=pmvnorm(lower=c(q1,q2,q1,-Inf,-Inf,q3e2),upper=c(Inf,Inf,Inf,q2,q3e3,Inf),mean=c(0,0,0,0,0,0),sigma=Sigma)/ pe2
-    te3de3[i]=pmvnorm(lower=c(q1,-Inf,q1,-Inf,-Inf,q3e3),upper=c(Inf,q2,Inf,q2,q3e3,Inf),mean=c(0,0,0,0,0,0),sigma=Sigma)/ pe3
-
-    te1de2opp[i]=pmvnorm(lower=c(-Inf,-Inf,q1,q2,-Inf,-Inf),upper=c(q1,Inf,Inf,Inf,q3e2,Inf),mean=c(0,0,0,0,0,0),sigma=Sigmaopp)/ pe1
-    te2de2opp[i]=pmvnorm(lower=c(q1,q2,q1,q2,-Inf,q3e2),upper=c(Inf,Inf,Inf,Inf,q3e2,Inf),mean=c(0,0,0,0,0,0),sigma=Sigmaopp)/ pe2
-    te3de2opp[i]=pmvnorm(lower=c(q1,-Inf,q1,q2,-Inf,q3e3),upper=c(Inf,q2,Inf,Inf,q3e2,Inf),mean=c(0,0,0,0,0,0),sigma=Sigmaopp)/ pe3
-
-    te1de3opp[i]=pmvnorm(lower=c(-Inf,-Inf,q1,-Inf,-Inf,-Inf),upper=c(q1,Inf,Inf,q2,q3e3,Inf),mean=c(0,0,0,0,0,0),sigma=Sigmaopp)/ pe1
-    te2de3opp[i]=pmvnorm(lower=c(q1,q2,q1,-Inf,-Inf,q3e2),upper=c(Inf,Inf,Inf,q2,q3e3,Inf),mean=c(0,0,0,0,0,0),sigma=Sigmaopp)/ pe2
-    te3de3opp[i]=pmvnorm(lower=c(q1,-Inf,q1,-Inf,-Inf,q3e3),upper=c(Inf,q2,Inf,q2,q3e3,Inf),mean=c(0,0,0,0,0,0),sigma=Sigmaopp)/ pe3
-
-    # te1d1opp[i]=(pmvnorm(lower=c(-Inf,-Inf,-Inf),upper=c(q1,q1,q2e1),mean=c(0,0,0),sigma=Sigmaopp) + pmvnorm(lower=c(-Inf,q1,-Inf),upper=c(q1,Inf,q2e2),mean=c(0,0,0),sigma=Sigma))/ pe1
-    # te2d1opp[i]=(pmvnorm(lower=c(q1,-Inf,-Inf),upper=c(Inf,q1,q2e1),mean=c(0,0,0),sigma=Sigmaopp) + pmvnorm(lower=c(q1,q1,-Inf),upper=c(Inf,Inf,q2e2),mean=c(0,0,0),sigma=Sigma))/ pe2
-    # te1d2opp[i]=(pmvnorm(lower=c(-Inf,-Inf,q2e1),upper=c(q1,q1,Inf),mean=c(0,0,0),sigma=Sigmaopp) + pmvnorm(lower=c(-Inf,q1,q2e2),upper=c(q1,Inf,Inf),mean=c(0,0,0),sigma=Sigma))/ pe1
-    # te2d2opp[i]=(pmvnorm(lower=c(q1,-Inf,q2e1),upper=c(Inf,q1,Inf),mean=c(0,0,0),sigma=Sigmaopp) + pmvnorm(lower=c(q1,q1,q2e2),upper=c(Inf,Inf,Inf),mean=c(0,0,0),sigma=Sigma))/ pe2
-}
-z = (1:300)/100.
-par(mfrow=c(2,3))
-plot(z,te1de2,ylim=c(0.,1),type="l")
-plot(z,te2de2,ylim=c(0.,1),type="l")
-plot(z,te3de2,ylim=c(0.,1),type="l")
-plot(z,te1de3,ylim=c(0.,1),type="l")
-plot(z,te2de3,ylim=c(0.,1),type="l")
-plot(z,te3de3,ylim=c(0.,1),type="l")
-
-z = (1:300)/100.
-par(mfrow=c(2,3))
-plot(z,te1de2opp,ylim=c(0.,1),type="l")
-plot(z,te2de2opp,ylim=c(0.,1),type="l")
-plot(z,te3de2opp,ylim=c(0.,1),type="l")
-plot(z,te1de3opp,ylim=c(0.,1),type="l")
-plot(z,te2de3opp,ylim=c(0.,1),type="l")
-plot(z,te3de3opp,ylim=c(0.,1),type="l")
-
-#simulation
-Y1<-sim2d(rv1,rhx1,b1,100,0.025,182,0.5,200)
-Z2<-Y2<-sim2d(rv2,rhx2,b2,100,0.025,182,0.5,200)
-Z3<-Y3<-sim2d(rv3,rhx3,b3,100,0.025,182,0.5,200)
-for( z in 5:178){
-  Z2[,z]=Y2[,z]*sqrt(1-(a^2))+Y1[,z+4]*a
-}
-for( z in 5:178){
-  Z3[,z]=Y3[,z]*sqrt(1-(b^2))+Y1[,z-4]*b
-}
-faciesenv<-faciesdiag<-Y1
-faciesenv[Y1<q1]=1
-faciesenv[Y1>q1 & Z2<q2 ]=3
-faciesenv[Y1>q1 & Z2>q2  ]=2
-combined<-faciesenv
-faciesdiag[]=2
-faciesdiag[Y1>q1 & Z2<q2 & Z3<q3e3 ]=1
-faciesdiag[Y1>q1 & Z2>q2 & Z3<q3e2 ]=1
-combined[faciesenv==2 & faciesdiag==1]=4
-combined[faciesenv==3 & faciesdiag==1]=5
-par(mfrow=c(1,1))
-image(faciesenv,col=c("ivory1","ivory3","ivory4"))
-image(combined,col=c("ivory1","ivory3","ivory4","gold","firebrick"),axes = FALSE)
-#image(combined,col=c("ivory1","ivory3","ivory4","gold"),axes = FALSE)
-#image(combined,col=c("ivory1","ivory3","ivory4","firebrick"),axes = FALSE)
-```
-Okay, we can do this simulation in three dimensions
-```{r}
-Y1<-sim3d(rv1,rhx1,rhx1,b1,100,0.025,182,0.5,200,5,10)
-Z2<-Y2<-sim3d(rv2,rhx2,rhx2,b2,100,0.025,182,0.5,200,5,10)
-Z3<-Y3<-sim3d(rv3,rhx3,rhx3,b3,100,0.025,182,0.5,200,5,10)
-for( z in 5:178){
-  Z2[,,z]=Y2[,,z]*sqrt(1-(a^2))+Y1[,,z+4]*a
-}
-for( z in 5:178){
-  Z3[,,z]=Y3[,,z]*sqrt(1-(b^2))+Y1[,,z-4]*b
-}
-
-```
-
-```{r}
-faciesenv<-faciesdiag<-Y1
-faciesenv[Y1<q1]=1
-faciesenv[Y1>q1 & Z2<q2 ]=3
-faciesenv[Y1>q1 & Z2>q2  ]=2
-faciesenv[faciesenv==3 & Z3<q3e3]=4
-faciesenv[faciesenv==2 & Z3<q3e2]=5
-for ( z in 1:182){
-  for ( y in 1:10){
-    for ( x in 1:200){
-      write(toString(c(faciesenv[x,y,z])),"fracturecombined.csv",append=TRUE)
-    }
-  }
-}
-```
-
-here with vertical fractures dolomitized 
-```{r}
-pe1=0.34
-pe2=0.33
-pe3=0.34
-pe1d1=0.
-pe2d1=0.2
-pe3d1=0.4
-rv1=0.2
-rv2=0.2
-rv3=5
-rhx1=60
-rhx2=60
-rhx3=5
-b1=0
-b2=0
-b3=0
-a=0.99
-b=0.8
-shift=0.1
-shiftb=0.
-rho1a<-model(shift,rv1,b1)
-rho1b<-model(shiftb,rv1,b1)
-
-q1=qnorm(pe1) # subtidal facies defined by one Gaussian function
-
-# for intertidal and supratidal, second Gaussian function
-Sigma2 = matrix(c(1,a*rho1a,a*rho1a,1),2,2)
-q2=0 
-obj = Inf
-for ( test in 1:100 ){
-  q2test = qnorm(test/100)
-  newobj =abs( pmvnorm(lower=c(q1,-Inf),upper=c(Inf,q2test),mean=c(0,0),sigma=Sigma2) - pe3 ) 
-  if (newobj < obj){
-    q2 = q2test
-    obj = newobj
-  }
-}
-
-q3e1=-Inf
-q3e2=q3e3=0 # two thresholds for diagenetic facies 
-Sigma3 = diag(1,3)
-Sigma3[1,2]=Sigma3[2,1]=a*rho1a
-Sigma3[1,3]=Sigma3[3,1]=b*rho1b
-Sigma3[2,3]=Sigma3[3,2]=a*b*model(shift-shiftb,rv1,b1)
-
-obj1=obj2=obj3=Inf
-for ( test in 1:1000 ){
-  q3e2test = qnorm(test/1000)
-  q3e3test = qnorm(test/1000)
-  newobj2 =abs( pmvnorm(lower=c(q1,q2,-Inf),upper=c(Inf,Inf,q3e2test),mean=c(0,0,0),sigma=Sigma3)/pe2 - pe2d1)
-  newobj3 =abs( pmvnorm(lower=c(q1,-Inf,-Inf),upper=c(Inf,q2,q3e3test),mean=c(0,0,0),sigma=Sigma3)/pe3 - pe3d1)
-  if (newobj2 < obj2){
-    q3e2= q3e2test
-    obj2 = newobj2
-  }
-  if (newobj3 < obj3){
-    q3e3= q3e3test
-    obj3 = newobj3
-  }
-}
-
-Y1<-sim2d(rv1,rhx1,b1,100,0.025,182,0.5,200)
-Z2<-Y2<-sim2d(rv2,rhx2,b2,100,0.025,182,0.5,200)
-Z3<-Y3<-sim2d(rv3,rhx3,b3,100,0.025,182,0.5,200)
-for( z in 4:178){
-  Z2[,z]=Y2[,z]*sqrt(1-(a^2))+Y1[,z+4]*a
-}
-for( z in 4:178){
-  Z3[,z]=Y3[,z]*sqrt(1-(b^2))+Y1[,z]*b
-}
-faciesenv<-faciesdiag<-Y1
-faciesenv[Y1<q1]=1
-faciesenv[Y1>q1 & Z2<q2 ]=3
-faciesenv[Y1>q1 & Z2>q2  ]=2
-combined<-faciesenv
-faciesdiag[]=2
-faciesdiag[Y1>q1 & Z2<q2 & Z3<q3e3 ]=1
-faciesdiag[Y1>q1 & Z2>q2 & Z3<q3e2 ]=1
-combined[faciesenv==2 & faciesdiag==1]=4
-combined[faciesenv==3 & faciesdiag==1]=5
-image(faciesenv,col=c("ivory1","ivory3","ivory4"))
-image(combined,col=c("ivory1","ivory3","ivory4","gold","firebrick"),axes = FALSE)
-```
-in three dimensions
-```{r}
-Y1<-sim3d(rv1,rhx1,rhx1,b1,100,0.025,182,0.5,200,5,10)
-Z2<-Y2<-sim3d(rv2,rhx2,rhx2,b2,100,0.025,182,0.5,200,5,10)
-Z3<-Y3<-sim3d(rv3,rhx3,rhx3,b3,100,0.025,182,0.5,200,5,10)
-for( z in 4:178){
-  Z2[,,z]=Y2[,,z]*sqrt(1-(a^2))+Y1[,,z+1]*a
-}
-for( z in 4:178){
-  Z3[,,z]=Y3[,,z]*sqrt(1-(b^2))+Y1[,,z]*b
-}
-
-```
-
-```{r}
-faciesenv<-faciesdiag<-Y1
-faciesenv[Y1<q1]=1
-faciesenv[Y1>q1 & Z2<q2 ]=3
-faciesenv[Y1>q1 & Z2>q2  ]=2
-faciesenv[faciesenv==3 & Z3<q3e3]=4
-faciesenv[faciesenv==2 & Z3<q3e2]=5
-for ( z in 1:182){
-  for ( y in 1:10){
-    for ( x in 1:200){
-      write(toString(c(faciesenv[x,y,z])),"fracturecombined.csv",append=TRUE)
-    }
-  }
-}
-```
-
-new simulation with four facies with the first two Gaussian functions
-The fourth facies is marine cementation during transgression phase. This facies is the last of the cycle.
-The diagenesic facies is dolomite and just happen in the supratidal environment.
-
-```{r}
-pe1=0.2
-pe2=0.2
-pe3=0.2
-pe4=0.2
-pe3d1=0.4
-rv1=0.2
-rv2=0.2
-rv3=0.2
-rhx1=60
-rhx2=60
-rhx3=60
-b1=0
-b2=0
-b3=0
-a=0.99
-b=0.
-shift=0.1
-shiftb=0.
-rho1a<-model(shift,rv1,b1)
-rho1b<-model(shiftb,rv1,b1)
-
-q1=qnorm(pe1+pe2) # subtidal facies defined by one Gaussian function
-
-# for intertidal and supratidal, second Gaussian function
-Sigma2 = matrix(c(1,a*rho1a,a*rho1a,1),2,2)
-q2=0
-q3=0
-obj=obj2 = Inf
-for ( test in 1:100 ){
-  q2test = qnorm(test/100)
-  q3test = qnorm(test/100)
-  newobj =abs( pmvnorm(lower=c(-Inf,-Inf),upper=c(q1,q2test),mean=c(0,0),sigma=Sigma2) - pe1 ) 
-  newobj2 =abs( pmvnorm(lower=c(q1,-Inf),upper=c(Inf,q3test),mean=c(0,0),sigma=Sigma2) - pe4 )
-  if (newobj < obj){
-    q2 = q2test
-    obj = newobj
-  }
-  if (newobj2 < obj2){
-    q3 = q3test
-    obj2 = newobj2
-  }
-}
-
-q3e3=-Inf
-Sigma3 = diag(1,3)
-Sigma3[1,2]=Sigma3[2,1]=a*rho1a
-Sigma3[1,3]=Sigma3[3,1]=b*rho1b
-Sigma3[2,3]=Sigma3[3,2]=a*b*model(shift-shiftb,rv1,b1)
-
-obj3=Inf
-for ( test in 1:1000 ){
-  q3e3test = qnorm(test/1000)
-  newobj3 =abs( pmvnorm(lower=c(q1,q2,-Inf),upper=c(Inf,Inf,q3e3test),mean=c(0,0,0),sigma=Sigma3)/pe3 - pe3d1)
-
-  if (newobj3 < obj3){
-    q3e3= q3e3test
-    obj3 = newobj3
-  }
-}
-
-#simulation
-Y1<-sim2d(rv1,rhx1,b1,100,0.025,182,0.5,200)
-Z2<-Y2<-sim2d(rv2,rhx2,b2,100,0.025,182,0.5,200)
-Z3<-Y3<-sim2d(rv3,rhx3,b3,100,0.025,182,0.5,200)
-for( z in 4:178){
-  Z2[,z]=Y2[,z]*sqrt(1-(a^2))+Y1[,z+4]*a
-}
-for( z in 4:178){
-  Z3[,z]=Y3[,z]*sqrt(1-(b^2))+Y1[,z]*b
-}
-faciesenv<-faciesdiag<-Y1
-faciesenv[Y1<q1 & Z2<q2]=1
-faciesenv[Y1<q1 & Z2>q2]=2
-faciesenv[Y1>q1 & Z2>q3]=3
-faciesenv[Y1>q1 & Z2<q3]=4
-
-combined<-faciesenv
-combined[faciesenv==3 & Z3<q3e3]=5
-image(faciesenv,col=c("ivory1","ivory3","ivory4"))
-image(combined,col=c("ivory1","ivory3","ivory4","cyan3","firebrick"),axes = FALSE)
-```

### 2018-09-17 cosim_functions.R
added function
covariance model for gaussian random function

@@ -1,4 +1,9 @@
 
+
+# Covariance function used for the Gaussian random function
+model<-function(h,range,b){return(exp(-abs(h/range)^2)*cos(b*h) )}
+model_lat<-function(h,range){return(exp(-(h/range)^2) )}
+
 # basic function to plot a transiogram
 tr_2d_vert<-function(datai,dataj,size,ncell,dz){
   cov<-numeric(size)

### 2018-09-17 main.Rmd
commentary
Explanation on the technic

@@
 ```
-increasing the details of the section
+Increasing the details of the section
 
@@
 
-the first figure we want to have is a 3d simulation of the Latemar conditioned !
-
-another simu with only three Gaussian functions
-(verifier le gibbs sampling pour la nouvelle truncation rule)
+3 dimensional simulation of the Latemar conditionned to the logs
 
 ```{r}
+# Parameters of the simulation defined according to the experimental transiograms
+# this is done in the file fitting.rmd
 par(bg="transparent")
@@
 c(qd1e4,qd2e2,qd2e3)
-# here Y4 is not used
+
+# The Gibbs sampling is designed for 4 Gaussian functions, 
+# But here we will use only three as defined by the truncation rule
+# Therefore Y3 is here not meaningful 
 Y1<-sim3d(rv1,rhx1,rhy1,b1,100,0.05,182,10,100,25,10)
@@
 Y4<-sim3d(rv4,rhx4,rhy4,b4,100,0.05,182,10,100,25,10)
-#careful to check that we put 0 to extend the gibbs sampling to where there is no data
+
 simwell<-gibbs_sampling3d(grid2,grid_co2,c(q1,q2,q3),c(qd1e4,qd2e2,qd2e3),0.05,10,25,c(rv1,rv2,rv3,rv4),c(rhx1,rhx2,rhx3,rhx4),c(rhy1,rhy2,rhy3,rhy4),c(b1,b2,b3,b4),c(rho,e*model(a14,rv1,b1),f*model(a24,rv2,b2)),c(shift,a14,a24),50)
@@
 
+# 4 separate krigings on the independant Gaussian random functions
+# so that they are conditioned 
 Z1c =Y1 + dual_krig_surf(Y1well-Y1,rhx1,rhy1,10,25)
@@
 
+# Transform in the correlated Gaussian random functions
+# according to the shifted linear model of coregionalization
 for( z in 3:180){
@@
 
+# Truncation of the Gaussian random functions into facies
+# according to the truncation rule
 faciesenv<-faciesdiag<-Z1c
@@
 ```
-average
+Computing the average over three realizations
 ```{r}
@@
 ```
-and also with the diagenetic facies
+and also transigorams with the diagenetic facies
 ```{r}
@@
 
+Creating a text file for exporting the realizations
 ```{r}
@@
 ```
-we can also combine the environment and the diagenesis in a single model
+Environments and diagenesis are also combined in a single model
 ```{r}
@@
 
-we also want to enter the data ! 
+Exporting the data in three dimensions
 ```{r}
@@
 
-ok it is also necessary to compute the transiograms on the final model
+we also compute the transiograms on the final model
 ```{r}

### 2018-09-17 main.Rmd
cleaned and simplify
simulate only three Gaussian random function instead of four
Have to check how to visualize data logs

@@
 rv2=1.2
-rhx1=rhy1=800
-rhx2=rhy2=800
 b1=0
@@
 alpha2=1-(rho/rho1a)^2
-rv3=0.2
-rv4=0.3
-rhx3=rhy3=800
-rhx4=rhy4=800
-b3=0
-b4=0
+rv3=rv4=0.2
+b3=b4=0
 e=-0.8
@@
 
-#thresholds
+# The lateral ranges are defined by checking the lateral extension of the facies on the realizations
+rhx1=rhy1=800
+rhx2=rhy2=800
+rhx3=rhy3=800
+rhx4=rhy4=800
+
+# thresholds of environment of deposition
 q1=qnorm(pe1+pe2)
@@
 
+# thresholds for diagenesis
 Sigmad = diag(1,3)
@@
 Y2<-sim3d(rv2,rhx2,rhy2,b2,100,0.05,182,10,100,25,10)
-Y3<-sim3d(rv3,rhx3,rhy3,b3,100,0.05,182,10,100,25,10)
-Y4<-sim3d(rv4,rhx4,rhy4,b4,100,0.05,182,10,100,25,10)
+Y4=Y3<-sim3d(rv3,rhx3,rhy3,b3,100,0.05,182,10,100,25,10)
 
+# Unconditional simulation at log location with Gibbs Sampling
 simwell<-gibbs_sampling3d(grid2,grid_co2,c(q1,q2,q3),c(qd1e4,qd2e2,qd2e3),0.05,10,25,c(rv1,rv2,rv3,rv4),c(rhx1,rhx2,rhx3,rhx4),c(rhy1,rhy2,rhy3,rhy4),c(b1,b2,b3,b4),c(rho,e*model(a14,rv1,b1),f*model(a24,rv2,b2)),c(shift,a14,a24),50)
@@
 ```
-let s compute the embedded transitions of one realization
+computing the embedded transitions of one realization
 ```{r}

### 2018-09-17 fitting_latemar.Rmd
rename
just the latemar here

--- 2018-05-31 fitting.Rmd
@@
 ---
-we are trying here to fit all the transiogram of the co-simulation !
+Fitting the transiograms of the Latemar
 
@@
 
-```{r}
-model<-function(h,range,b){return(exp(-abs(h/range)^2)*cos(b*h) )}
-```
+Proportions of the depositional facies
 ```{r}
@@
 
-conditional proportions
+conditional proportions of the diagenetic facies
 ```{r}
@@
 
+Fitting environments of deposition
 ```{r}
-# rv1=0.3
-# rv2=1.2
-# rhx1=40
-# rhx2=40
-# b1=0
-# b2=5
-# rho=0.6
-# shift=0.1
-# rho1a<-model(shift,rv1,b1)
-# warning(rho>rho1a)
-# alpha1=(rho/rho1a)^2
-# alpha2=1-(rho/rho1a)^2
-# rv3=0.2
-# rv4=0.3
-# rhx3=40
-# rhx4=40
-# b3=0
-# b4=0
-# rho34=-0.6
-# c=0.
-# e=0.65
-# a13=-0.
-# a14=-0.1
-# rho1a14 = model(a14,rv1,b1)
 
@@
 rv2=1.2
-rhx1=40
-rhx2=40
 b1=0
 b2=5
-rho=0.6
-shift=0.1
+rho=0.6 # correlation between Z1 and Z2
+shift=0.1 # Shift between Z1 and Z2
 rho1a<-model(shift,rv1,b1)
-warning(rho>rho1a)
+warning(rho>rho1a) # limit for the correlation between Z1 and Z2
 alpha1=(rho/rho1a)^2
 alpha2=1-(rho/rho1a)^2
-rv3=0.2
-rv4=0.3
-rhx3=40
-rhx4=40
-b3=0
-b4=0
-e=-0.8
-f=-0.5
 
-a14=-0.1
-a24=0.1
-rho1a14 = model(a14,rv1,b1)
-rho2a24=model(a24,rv2,b2)
-
-#thresholds
+# the thresholds are computed according to the truncation rule
+# These are for the environment of deposition
 q1=qnorm(pe1+pe2)
@@
 c(q1,q2,q3)
-
-qd1e4=qnorm(pd3e4) # no correlation with the third Gaussian function
-Sigmad = diag(1,3)
-qd2e2=0
-qd2e3=0
-obje2 = Inf
-obje3 = Inf
-for ( test in 1:100 ){
-  qd2e2test = qnorm(test/100)
-  qd2e3test = qnorm(test/100)
-  Sigmad[1,2]=Sigmad[2,1]=e*rho1a14
-  Sigmad[1,3]=Sigmad[3,1]=e*rho1a14*rho
-  Sigmad[2,3]=Sigmad[3,2]=rho
-  newobje2 =abs( pmvnorm(lower=c(qd2e2test,-Inf,q2),upper=c(Inf,q1,Inf),mean=c(0,0,0),sigma=Sigmad)/pe2 - pd2e2 ) 
-  newobje3 =abs( pmvnorm(lower=c(qd2e2test,q1,q3),upper=c(Inf,Inf,Inf),mean=c(0,0,0),sigma=Sigmad)/pe3 - pd2e3 )
-  if (newobje2 < obje2){
-    qd2e2 = qd2e2test
-    obje2 = newobje2
-  }
-  if (newobje3 < obje3){
-    qd2e3 = qd2e3test
-    obje3 = newobje3
-  }
-}
-
-c(qd1e4,qd2e2,qd2e3)
 
@@
 
-t33d_model=t32d_model=t23d_model=t22d_model=rep(0,300)
-Sigma = diag(1,4)
-for (i in 1:300){
-    d = i/100.
-    Sigma[1,2]=Sigma[2,1]= Sigma[3,4]=Sigma[4,3]=rho34
-    Sigma[1,3]=Sigma[3,1]=model(d,rv3,b3)
-    Sigma[1,4]=Sigma[4,1]=Sigma[2,3]=Sigma[3,2]=rho34*model(d,rv3,b3)
-    Sigma[2,4]=Sigma[4,2]=(rho34^2)*model(d,rv3,b3)+(1-rho34^2)*model(d,rv4,b4)
-
-    t22d_model[i]=pmvnorm(lower=c(qd1,qd2,qd1,qd2),upper=c(Inf,Inf,Inf,Inf),mean=c(0,0,0,0),sigma=Sigma)/ pd2
-    t23d_model[i]=pmvnorm(lower=c(qd1,qd2,-Inf,-Inf),upper=c(Inf,Inf,qd1,Inf),mean=c(0,0,0,0),sigma=Sigma)/ pd2
-    t32d_model[i]=pmvnorm(lower=c(-Inf,-Inf,qd1,qd2),upper=c(qd1,Inf,Inf,Inf),mean=c(0,0,0,0),sigma=Sigma)/ pd3
-    t33d_model[i]=pmvnorm(lower=c(-Inf,-Inf,-Inf,-Inf),upper=c(qd1,Inf,qd1,Inf),mean=c(0,0,0,0),sigma=Sigma)/ pd3
-}
-par(mfrow=c(2,2))
-t22d<-tr_2d_vert(d2,d2,30,nz,0.1)
-lines(z,t22d_model)
-t23d<-tr_2d_vert(d2,d3,30,nz,0.1)
-lines(z,t23d_model)
-t32d<-tr_2d_vert(d3,d2,30,nz,0.1)
-lines(z,t32d_model)
-t33d<-tr_2d_vert(d3,d3,30,nz,0.1)
-lines(z,t33d_model)
-
-td1e1_model=td1e2_model=td1e3_model=td1e4_model=td2e1_model=td2e2_model=td2e3_model=td2e4_model=rep(0,300)
-te1d1_model=te2d1_model=te3d1_model=te4d1_model=te1d2_model=te2d2_model=te3d2_model=te4d2_model=rep(0,300)
-Sigma = diag(1,4)
-for (i in 1:300){
-    d = i/100.
-    Sigma[1,2]=Sigma[2,1]=rho34
-    Sigma[1,3]=Sigma[3,1]=c*model(-d-a13,rv1,b1)
-    Sigma[1,4]=Sigma[4,1]=c*(rho/rho1a)*model(a13+d-shift,rv1,b1)
-    Sigma[2,3]=Sigma[3,2]=e*model(a14+d,rv1,b1)
-    Sigma[2,4]=Sigma[4,2]=e*(rho/rho1a)*model(a14+d-shift,rv1,b1)
-    Sigma[3,4]=Sigma[4,3]=rho
-
-    td1e1_model[i]=pmvnorm(lower=c(qd1,-Inf,-Inf,-Inf),upper=c(Inf,qd2,q1,q2),mean=c(0,0,0,0),sigma=Sigma)/ pd1
-    td1e2_model[i]=pmvnorm(lower=c(qd1,-Inf,-Inf,q2),upper=c(Inf,qd2,q1,Inf),mean=c(0,0,0,0),sigma=Sigma)/ pd1
-    td1e3_model[i]=pmvnorm(lower=c(qd1,-Inf,q1,q3),upper=c(Inf,qd2,Inf,Inf),mean=c(0,0,0,0),sigma=Sigma)/ pd1
-    td1e4_model[i]=pmvnorm(lower=c(qd1,-Inf,q1,-Inf),upper=c(Inf,qd2,Inf,q3),mean=c(0,0,0,0),sigma=Sigma)/ pd1
-
-    td2e1_model[i]=pmvnorm(lower=c(qd1,qd2,-Inf,-Inf),upper=c(Inf,Inf,q1,q2),mean=c(0,0,0,0),sigma=Sigma)/ pd2
-    td2e2_model[i]=pmvnorm(lower=c(qd1,qd2,-Inf,q2),upper=c(Inf,Inf,q1,Inf),mean=c(0,0,0,0),sigma=Sigma)/ pd2
-    td2e3_model[i]=pmvnorm(lower=c(qd1,qd2,q1,q3),upper=c(Inf,Inf,Inf,Inf),mean=c(0,0,0,0),sigma=Sigma)/ pd2
-    td2e4_model[i]=pmvnorm(lower=c(qd1,qd2,q1,-Inf),upper=c(Inf,Inf,Inf,q3),mean=c(0,0,0,0),sigma=Sigma)/ pd2
-
-    te1d1_model[i]=pmvnorm(lower=c(qd1,-Inf,-Inf,-Inf),upper=c(Inf,qd2,q1,q2),mean=c(0,0,0,0),sigma=Sigma)/ pe1
-    te2d1_model[i]=pmvnorm(lower=c(qd1,-Inf,-Inf,q2),upper=c(Inf,qd2,q1,Inf),mean=c(0,0,0,0),sigma=Sigma)/ pe2
-    te3d1_model[i]=pmvnorm(lower=c(qd1,-Inf,q1,q3),upper=c(Inf,qd2,Inf,Inf),mean=c(0,0,0,0),sigma=Sigma)/ pe3
-    te4d1_model[i]=pmvnorm(lower=c(qd1,-Inf,q1,-Inf),upper=c(Inf,qd2,Inf,q3),mean=c(0,0,0,0),sigma=Sigma)/ pe4
-
-    te1d2_model[i]=pmvnorm(lower=c(qd1,qd2,-Inf,-Inf),upper=c(Inf,Inf,q1,q2),mean=c(0,0,0,0),sigma=Sigma)/ pe1
-    te2d2_model[i]=pmvnorm(lower=c(qd1,qd2,-Inf,q2),upper=c(Inf,Inf,q1,Inf),mean=c(0,0,0,0),sigma=Sigma)/ pe2
-    te3d2_model[i]=pmvnorm(lower=c(qd1,qd2,q1,q3),upper=c(Inf,Inf,Inf,Inf),mean=c(0,0,0,0),sigma=Sigma)/ pe3
-    te4d2_model[i]=pmvnorm(lower=c(qd1,qd2,q1,-Inf),upper=c(Inf,Inf,Inf,q3),mean=c(0,0,0,0),sigma=Sigma)/ pe4
-}
-
-par(mfrow=c(2,4))
-tr_2d_vert(d1,e1,30,nz,0.1)
-lines(z,td1e1_model)
-tr_2d_vert(d1,e2,30,nz,0.1)
-lines(z,td1e2_model)
-tr_2d_vert(d1,e3,30,nz,0.1)
-lines(z,td1e3_model)
-tr_2d_vert(d1,e4,30,nz,0.1)
-lines(z,td1e4_model)
-tr_2d_vert(d2,e1,30,nz,0.1)
-lines(z,td2e1_model)
-tr_2d_vert(d2,e2,30,nz,0.1)
-lines(z,td2e2_model)
-tr_2d_vert(d2,e3,30,nz,0.1)
-lines(z,td2e3_model)
-tr_2d_vert(d2,e4,30,nz,0.1)
-lines(z,td2e4_model)
-
-par(mfrow=c(4,2))
-tr_2d_vert(e1,d1,30,nz,0.1)
-lines(z,te1d1_model)
-tr_2d_vert(e2,d1,30,nz,0.1)
-lines(z,te2d1_model)
-tr_2d_vert(e3,d1,30,nz,0.1)
-lines(z,te3d1_model)
-tr_2d_vert(e4,d1,30,nz,0.1)
-lines(z,te4d1_model)
-tr_2d_vert(e1,d2,30,nz,0.1)
-lines(z,te1d2_model)
-tr_2d_vert(e2,d2,30,nz,0.1)
-lines(z,te2d2_model)
-tr_2d_vert(e3,d2,30,nz,0.1)
-lines(z,te3d2_model)
-tr_2d_vert(e4,d2,30,nz,0.1)
-lines(z,te4d2_model)
-
 ```
-beautiful picture for transiograms
+paper figure for transiograms of environment of depositions
 
@@
 ```
-we are showing here a figure with the transiograms on the realization
+
+We can find the embedded transiograms between environment of deposition
 ```{r}
-z = (1:300)/100.
-z2= (1:60)/20
-png(file="latemartransiototal.png",width=2000,height = 1600,res=300)
-par(mar=c(2,3,1,1),mfrow=c(4,4))
-t11<-tr_2d_vert(e1,e1,30,nz,0.1)
-lines(z,t11_model)
-lines(z2,t11real,lwd=0.6)
-lines(z2,t11real2,lwd=0.6)
-lines(z2,t11real3,lwd=0.6)
-title(main=expression(paste('t'[e1e1],"(h)")),line=-1)
-t12<-tr_2d_vert(e1,e2,30,nz,0.1)
-lines(z,t12_model)
-lines(z2,t12real,lwd=0.5)
-lines(z2,t12real2,lwd=0.5)
-lines(z2,t12real3,lwd=0.5)
-title(main=expression(paste('t'[e1e2],"(h)")),line=-1)
-t13<-tr_2d_vert(e1,e3,30,nz,0.1)
-lines(z,t13_model)
-lines(z2,t13real,lwd=0.5)
-lines(z2,t13real2,lwd=0.5)
-lines(z2,t13real3,lwd=0.5)
-title(main=expression(paste('t'[e1e3],"(h)")),line=-1)
-t14<-tr_2d_vert(e1,e4,30,nz,0.1)
-lines(z,t14_model)
-lines(z2,t14real,lwd=0.5)
-lines(z2,t14real2,lwd=0.5)
-lines(z2,t14real3,lwd=0.5)
-title(main=expression(paste('t'[e1e4],"(h)")),line=-1)
-t21<-tr_2d_vert(e2,e1,30,nz,0.1)
-lines(z,t21_model)
-lines(z2,t21real,lwd=0.5)
-lines(z2,t21real2,lwd=0.5)
-lines(z2,t21real3,lwd=0.5)
-title(main=expression(paste('t'[e2e1],"(h)")),line=-1)
-t22<-tr_2d_vert(e2,e2,30,nz,0.1)
-lines(z,t22_model)
-lines(z2,t22real,lwd=0.5)
-lines(z2,t22real2,lwd=0.5)
-lines(z2,t22real3,lwd=0.5)
-title(main=expression(paste('t'[e2e2],"(h)")),line=-1)
-t23<-tr_2d_vert(e2,e3,30,nz,0.1)
-lines(z,t23_model)
-lines(z2,t23real,lwd=0.5)
-lines(z2,t23real2,lwd=0.5)
-lines(z2,t23real3,lwd=0.5)
-title(main=expression(paste('t'[e2e3],"(h)")),line=-1)
-t24<-tr_2d_vert(e2,e4,30,nz,0.1)
-lines(z,t24_model)
-lines(z2,t24real,lwd=0.5)
-lines(z2,t24real2,lwd=0.5)
-lines(z2,t24real3,lwd=0.5)
-title(main=expression(paste('t'[e2e4],"(h)")),line=-1)
-t31<-tr_2d_vert(e3,e1,30,nz,0.1)
-lines(z,t31_model)
-lines(z2,t31real,lwd=0.5)
-lines(z2,t31real2,lwd=0.5)
-lines(z2,t31real3,lwd=0.5)
-title(main=expression(paste('t'[e3e1],"(h)")),line=-1)
-t32<-tr_2d_vert(e3,e2,30,nz,0.1)
-lines(z,t32_model)
-lines(z2,t32real,lwd=0.5)
-lines(z2,t32real2,lwd=0.5)
-lines(z2,t32real3,lwd=0.5)
-title(main=expression(paste('t'[e3e2],"(h)")),line=-1)
-t33<-tr_2d_vert(e3,e3,30,nz,0.1)
-lines(z,t33_model)
-lines(z2,t33real,lwd=0.5)
-lines(z2,t33real2,lwd=0.5)
-lines(z2,t33real3,lwd=0.5)
-title(main=expression(paste('t'[e3e3],"(h)")),line=-1)
-t34<-tr_2d_vert(e3,e4,30,nz,0.1)
-lines(z,t34_model)
-lines(z2,t34real,lwd=0.5)
-lines(z2,t34real2,lwd=0.5)
-lines(z2,t34real3,lwd=0.5)
-title(main=expression(paste('t'[e3e4],"(h)")),line=-1)
-t41<-tr_2d_vert(e4,e1,30,nz,0.1)
-lines(z,t41_model)
-lines(z2,t41real,lwd=0.5)
-lines(z2,t41real2,lwd=0.5)
-lines(z2,t41real3,lwd=0.5)
-title(main=expression(paste('t'[e4e1],"(h)")),line=-1)
-t42<-tr_2d_vert(e4,e2,30,nz,0.1)
-lines(z,t42_model)
-lines(z2,t42real,lwd=0.5)
-lines(z2,t42real2,lwd=0.5)
-lines(z2,t42real3,lwd=0.5)
-title(main=expression(paste('t'[e4e2],"(h)")),line=-1)
-t43<-tr_2d_vert(e4,e3,30,nz,0.1)
-lines(z,t43_model)
-lines(z2,t43real,lwd=0.5)
-lines(z2,t43real2,lwd=0.5)
-lines(z2,t43real3,lwd=0.5)
-title(main=expression(paste('t'[e4e3],"(h)")),line=-1)
-t44<-tr_2d_vert(e4,e4,30,nz,0.1)
-lines(z,t44_model)
-lines(z2,t44real,lwd=0.5)
-lines(z2,t44real2,lwd=0.5)
-lines(z2,t44real3,lwd=0.5)
-title(main=expression(paste('t'[e4e4],"(h)")),line=-1)
-```
-
-lets try to fit the embedded transiograms
-```{r}
-rv1=0.4
-rv2=1.2
-rhx1=40
-rhx2=40
-b1=0
-b2=5
-rho=0.8
-shift=0.1
-rho1a<-model(shift,rv1,b1)
-warning(rho>rho1a)
-alpha1=(rho/rho1a)^2
-alpha2=1-(rho/rho1a)^2
-rv3=0.2
-rv4=0.3
-rhx3=40
-rhx4=40
-b3=0
-b4=0
-e=-0.8
-f=-0.5
-
-a14=-0.1
-a24=0.1
-rho1a14 = model(a14,rv1,b1)
-rho2a24=model(a24,rv2,b2)
-
-#thresholds
-q1=qnorm(pe1+pe2)
-Sigma1 = matrix(c(1,rho,rho,1),2,2)
-q2=0
-obj = Inf
-for ( test in 1:100 ){
-  q2test = qnorm(test/100)
-  newobj =abs( pmvnorm(lower=c(-Inf,-Inf),upper=c(q1,q2test),mean=c(0,0),sigma=Sigma1) - pe1 ) 
-  if (newobj < obj){
-    q2 = q2test
-    obj = newobj
-  }
-}
-q3=0
-obj = Inf
-for ( test in 1:100 ){
-  q3test = qnorm(test/100)
-  newobj =abs( pmvnorm(lower=c(q1,-Inf),upper=c(Inf,q3test),mean=c(0,0),sigma=Sigma1) - pe4 ) 
-  if (newobj < obj){
-    q3 = q3test
-    obj = newobj
-  }
-}
 d = 1/5.
@@
 
-trying td2e1, td2e2, td2e3 and td2e4
+Fitting the cross-transiograms between partial dolomite and environment of depositions
 
 ```{r}
-rv1=0.3
-rv2=0.5
-rhx1=40
-rhx2=40
-b1=0
-b2=0
-rho=0.6
-shift=0.1
-rho1a<-model(shift,rv1,b1)
-warning(rho>rho1a)
-alpha1=(rho/rho1a)^2
-alpha2=1-(rho/rho1a)^2
-rv3=0.2
-rv4=0.3
-rhx3=40
-rhx4=40
-b3=0
-b4=0
-e=0.8
+# correlations
+e=-0.8 # between the first and third Gaussian random function
+f=-0.5 # between the second and third Gaussian random function
 
-a14=0.1
-rho1a14 = model(a14,rv1,b1)
-#thresholds
-q1=qnorm(pe1+pe2)
-Sigma1 = matrix(c(1,rho,rho,1),2,2)
-q2=0
-obj = Inf
-for ( test in 1:100 ){
-  q2test = qnorm(test/100)
-  newobj =abs( pmvnorm(lower=c(-Inf,-Inf),upper=c(q1,q2test),mean=c(0,0),sigma=Sigma1) - pe1 ) 
-  if (newobj < obj){
-    q2 = q2test
-    obj = newobj
-  }
-}
-q3=0
-obj = Inf
-for ( test in 1:100 ){
-  q3test = qnorm(test/100)
-  newobj =abs( pmvnorm(lower=c(q1,-Inf),upper=c(Inf,q3test),mean=c(0,0),sigma=Sigma1) - pe4 ) 
-  if (newobj < obj){
-    q3 = q3test
-    obj = newobj
-  }
-}
-
-c(q1,q2,q3)
-
-qd1e4=qnorm(pd3e4) # no correlation with the third Gaussian function
-Sigmad = diag(1,3)
-qd2e2=0
-qd2e3=0
-obje2 = Inf
-obje3 = Inf
-for ( test in 1:100 ){
-  qd2e2test = qnorm(test/100)
-  qd2e3test = qnorm(test/100)
-  Sigmad[1,2]=Sigmad[2,1]=e*rho1a14
-  Sigmad[1,3]=Sigmad[3,1]=e*(rho/rho1a)*model(a14-shift,rv1,b1)
-  Sigmad[2,3]=Sigmad[3,2]=rho
-  newobje2 =abs( pmvnorm(lower=c(qd2e2test,-Inf,q2),upper=c(Inf,q1,Inf),mean=c(0,0,0),sigma=Sigmad)/pe2 - pd2e2 ) 
-  newobje3 =abs( pmvnorm(lower=c(qd2e2test,q1,q3),upper=c(Inf,Inf,Inf),mean=c(0,0,0),sigma=Sigmad)/pe3 - pd2e3 )
-  if (newobje2 < obje2){
-    qd2e2 = qd2e2test
-    obje2 = newobje2
-  }
-  if (newobje3 < obje3){
-    qd2e3 = qd2e3test
-    obje3 = newobje3
-  }
-}
-
-c(qd1e4,qd2e2,qd2e3)
-
-td2e1_model=td2e2_model=td2e3_model=td2e4_model=rep(0,300)
-
-Sigma = diag(1,5)
-for (i in 1:300){
-    d = i/100.
-    Sigma[1,2]=Sigma[2,1]=Sigma[4,5]=Sigma[5,4]=rho
-    Sigma[1,3]=Sigma[3,1]=e*rho1a14
-    Sigma[1,4]=Sigma[4,1]=model(d,rv1,b1)
-    Sigma[1,5]=Sigma[5,1]=rho*model(d+shift,rv1,b1)/rho1a
-    Sigma[2,3]=Sigma[3,2]=e*rho*model(shift-a14,rv1,b1)/rho1a
-    Sigma[2,4]=Sigma[4,2]=rho*model(shift-d,rv1,b1)/rho1a
-    Sigma[2,5]=Sigma[5,2]=(1-(rho/rho1a)^2)*model(d,rv2,b2)+(rho^2)*model(d,rv1,b1)/(rho1a^2)
-    Sigma[3,4]=Sigma[4,3]=e*model(d-a14,rv1,b1)
-    Sigma[3,5]=Sigma[5,3]=e*rho*model(d+shift-a14,rv1,b1)/rho1a
-
-    td2e1_model[i]=pmvnorm(lower=c(-Inf,q2,qd2e2,-Inf,-Inf),upper=c(q1,Inf,Inf,q1,q2),mean=c(0,0,0,0,0),sigma=Sigma)/ pd2
-    td2e1_model[i]=td2e1_model[i]+pmvnorm(lower=c(q1,q3,qd2e3,-Inf,-Inf),upper=c(Inf,Inf,Inf,q1,q2),mean=c(0,0,0,0,0),sigma=Sigma)/ pd2
-    if(td2e1_model[i]==0){td2e1_model[i]=NA}
-
-    td2e2_model[i]=pmvnorm(lower=c(-Inf,q2,qd2e2,-Inf,q2),upper=c(q1,Inf,Inf,q1,Inf),mean=c(0,0,0,0,0),sigma=Sigma)/ pd2
-    td2e2_model[i]=td2e2_model[i]+pmvnorm(lower=c(q1,q3,qd2e3,-Inf,q2),upper=c(Inf,Inf,Inf,q1,Inf),mean=c(0,0,0,0,0),sigma=Sigma)/ pd2
-    if(td2e2_model[i]==0){td2e2_model[i]=NA}
-
-    td2e3_model[i]=pmvnorm(lower=c(-Inf,q2,qd2e2,q1,q3),upper=c(q1,Inf,Inf,Inf,Inf),mean=c(0,0,0,0,0),sigma=Sigma)/ pd2
-    td2e3_model[i]=td2e3_model[i]+pmvnorm(lower=c(q1,q3,qd2e3,q1,q3),upper=c(Inf,Inf,Inf,Inf,Inf),mean=c(0,0,0,0,0),sigma=Sigma)/ pd2
-    if(td2e3_model[i]==0){td2e3_model[i]=NA}
-
-    td2e4_model[i]=pmvnorm(lower=c(-Inf,q2,qd2e2,q1,-Inf),upper=c(q1,Inf,Inf,Inf,q3),mean=c(0,0,0,0,0),sigma=Sigma)/ pd2
-    td2e4_model[i]=td2e4_model[i]+pmvnorm(lower=c(q1,q3,qd2e3,q1,-Inf),upper=c(Inf,Inf,Inf,Inf,q3),mean=c(0,0,0,0,0),sigma=Sigma)/ pd2
-    if(td2e4_model[i]==0){td2e4_model[i]=NA}
-}
-z = (1:300)/100.
-tr_2d_vert(d2,e1,30,nz,0.1)
-lines(z,td2e1_model)
-tr_2d_vert(d2,e2,30,nz,0.1)
-lines(z,td2e2_model)
-tr_2d_vert(d2,e3,30,nz,0.1)
-lines(z,td2e3_model)
-tr_2d_vert(d2,e4,30,nz,0.1)
-lines(z,td2e4_model)
-
-```
-
-ok we develop now a more complex model to see if we are able to capture better the co-transiograms of 50dol. 
-We add for this a correlation between the second gaussian function and the fourth which slightly complexify the correlation matrix, but not that much.
-
-```{r}
-rv1=0.3
-rv2=1.2
-rhx1=40
-rhx2=40
-b1=0
-b2=5
-rho=0.6
-shift=0.1
-rho1a<-model(shift,rv1,b1)
-warning(rho>rho1a)
-alpha1=(rho/rho1a)^2
-alpha2=1-(rho/rho1a)^2
-rv3=0.2
-rv4=0.3
-rhx3=40
-rhx4=40
-b3=0
-b4=0
-e=-0.8
-f=-0.5
-
+# shifts 
 a14=-0.1
@@
 rho2a24=model(a24,rv2,b2)
-#thresholds
-q1=qnorm(pe1+pe2)
-Sigma1 = matrix(c(1,rho,rho,1),2,2)
-q2=0
-obj = Inf
-for ( test in 1:100 ){
-  q2test = qnorm(test/100)
-  newobj =abs( pmvnorm(lower=c(-Inf,-Inf),upper=c(q1,q2test),mean=c(0,0),sigma=Sigma1) - pe1 ) 
-  if (newobj < obj){
-    q2 = q2test
-    obj = newobj
-  }
-}
-q3=0
-obj = Inf
-for ( test in 1:100 ){
-  q3test = qnorm(test/100)
-  newobj =abs( pmvnorm(lower=c(q1,-Inf),upper=c(Inf,q3test),mean=c(0,0),sigma=Sigma1) - pe4 ) 
-  if (newobj < obj){
-    q3 = q3test
-    obj = newobj
-  }
-}
 
-c(q1,q2,q3)
-
+# Thresholds of the third Gaussian random function
 Sigmad = diag(1,3)
@@
 }
-
 c(qd1e4,qd2e2,qd2e3)
 
+# cross-transiograms
 td2e1_model=td2e2_model=td2e3_model=td2e4_model=rep(0,300)
 td3e1_model=td3e2_model=td3e3_model=td3e4_model=rep(0,300)
-
 Sigma = diag(1,5)
@@
 
-nice figure
+paper figure
 ```{r}
@@
 lines(z,td3e1_model)
-lines(z2,td3e1real,lwd=0.5)
-lines(z2,td3e1real2,lwd=0.5)
-lines(z2,td3e1real3,lwd=0.5)
+#lines(z2,td3e1real,lwd=0.5)
+#lines(z2,td3e1real2,lwd=0.5)
+#lines(z2,td3e1real3,lwd=0.5)
 title(main=expression(paste('t'[d1e1],"(h)")),line=-1,cex.main=2)
@@
 lines(z,td3e2_model)
-lines(z2,td3e2real,lwd=0.5)
-lines(z2,td3e2real2,lwd=0.5)
-lines(z2,td3e2real3,lwd=0.5)
+#lines(z2,td3e2real,lwd=0.5)
+#lines(z2,td3e2real2,lwd=0.5)
+#lines(z2,td3e2real3,lwd=0.5)
 title(main=expression(paste('t'[d1e2],"(h)")),cex.main=2)
@@
 lines(z,td3e3_model)
-lines(z2,td3e3real,lwd=0.5)
-lines(z2,td3e3real2,lwd=0.5)
-lines(z2,td3e3real3,lwd=0.5)
+#lines(z2,td3e3real,lwd=0.5)
+#lines(z2,td3e3real2,lwd=0.5)
+#lines(z2,td3e3real3,lwd=0.5)
 title(main=expression(paste('t'[d1e3],"(h)")),line=-1,cex.main=2)
@@
 lines(z,td3e4_model)
-lines(z2,td3e4real,lwd=0.5)
-lines(z2,td3e4real2,lwd=0.5)
-lines(z2,td3e4real3,lwd=0.5)
+#lines(z2,td3e4real,lwd=0.5)
+#lines(z2,td3e4real2,lwd=0.5)
+#lines(z2,td3e4real3,lwd=0.5)
 title(main=expression(paste('t'[d1e4],"(h)")),line=-1,cex.main=2)
@@
 lines(z,td2e1_model)
-lines(z2,td2e1real,lwd=0.5)
-lines(z2,td2e1real2,lwd=0.5)
-lines(z2,td2e1real3,lwd=0.5)
+#lines(z2,td2e1real,lwd=0.5)
+#lines(z2,td2e1real2,lwd=0.5)
+#lines(z2,td2e1real3,lwd=0.5)
 title(main=expression(paste('t'[d2e1],"(h)")),line=-1,cex.main=2)
@@
 lines(z,td2e2_model)
-lines(z2,td2e2real,lwd=0.5)
-lines(z2,td2e2real2,lwd=0.5)
-lines(z2,td2e2real3,lwd=0.5)
+#lines(z2,td2e2real,lwd=0.5)
+#lines(z2,td2e2real2,lwd=0.5)
+#lines(z2,td2e2real3,lwd=0.5)
 title(main=expression(paste('t'[d2e2],"(h)")),line=-1,cex.main=2)
@@
 lines(z,td2e3_model)
-lines(z2,td2e3real,lwd=0.5)
-lines(z2,td2e3real2,lwd=0.5)
-lines(z2,td2e3real3,lwd=0.5)
+#lines(z2,td2e3real,lwd=0.5)
+#lines(z2,td2e3real2,lwd=0.5)
+#lines(z2,td2e3real3,lwd=0.5)
 title(main=expression(paste('t'[d2e3],"(h)")),line=-1,cex.main=2)
@@
 lines(z,td2e4_model)
-lines(z2,td2e4real,lwd=0.5)
-lines(z2,td2e4real2,lwd=0.5)
-lines(z2,td2e4real3,lwd=0.5)
+#lines(z2,td2e4real,lwd=0.5)
+#lines(z2,td2e4real2,lwd=0.5)
+#lines(z2,td2e4real3,lwd=0.5)
 ```
 
-we need now to look at the auto transiograms of the diagenetic facies 
-we use the preceding covariance matrix and add one order
+Fitting auto transiograms of the diagenetic facies
+
 ```{r}
+# Parameters
+rv3=0.2
+rv4=0.3
+b3=0
+b4=0
+
+# Transiograms
 Sigmad = diag(1,3)
@@
 lines(z,td3d3_model)
-lines(z2,td3d3real,lwd=0.5)
-lines(z2,td3d3real2,lwd=0.5)
-lines(z2,td3d3real3,lwd=0.5)
+#lines(z2,td3d3real,lwd=0.5)
+#lines(z2,td3d3real2,lwd=0.5)
+#lines(z2,td3d3real3,lwd=0.5)
 title(main=expression(paste('t'[d1d1],"(h)")),line=-1,cex.main=2)
@@
 lines(z,td3d2_model)
-lines(z2,td3d2real,lwd=0.5)
-lines(z2,td3d2real2,lwd=0.5)
-lines(z2,td3d2real3,lwd=0.5)
+#lines(z2,td3d2real,lwd=0.5)
+#lines(z2,td3d2real2,lwd=0.5)
+#lines(z2,td3d2real3,lwd=0.5)
 title(main=expression(paste('t'[d1d2],"(h)")),line=-1,cex.main=2)
@@
 lines(z,td2d3_model)
-lines(z2,td2d3real,lwd=0.5)
-lines(z2,td2d3real2,lwd=0.5)
-lines(z2,td2d3real3,lwd=0.5)
+#lines(z2,td2d3real,lwd=0.5)
+#lines(z2,td2d3real2,lwd=0.5)
+#lines(z2,td2d3real3,lwd=0.5)
 title(main=expression(paste('t'[d2d1],"(h)")),line=-1,cex.main=2)
@@
 lines(z,td2d2_model)
-lines(z2,td2d2real,lwd=0.5)
-lines(z2,td2d2real2,lwd=0.5)
-lines(z2,td2d2real3,lwd=0.5)
+#lines(z2,td2d2real,lwd=0.5)
+#lines(z2,td2d2real2,lwd=0.5)
+#lines(z2,td2d2real3,lwd=0.5)
 title(main=expression(paste('t'[d2d2],"(h)")),line=-1,cex.main=2)
-# 
-# tr_2d_vert(d3,e1,30,nz,0.1)
-# lines(z,td3e1_model)
-# title(main=expression(paste('t'[d1e1],"(h)")),line=-1,cex.main=2)
-# tr_2d_vert(d3,e2,30,nz,0.1)
-# lines(z,td3e2_model)
-# title(main=expression(paste('t'[d1e2],"(h)")),cex.main=2)
-# tr_2d_vert(d3,e3,30,nz,0.1)
-# lines(z,td3e3_model)
-# title(main=expression(paste('t'[d1e3],"(h)")),line=-1,cex.main=2)
-# tr_2d_vert(d3,e4,30,nz,0.1)
-# lines(z,td3e4_model)
-# title(main=expression(paste('t'[d1e4],"(h)")),line=-1,cex.main=2)
-# tr_2d_vert(d2,e1,30,nz,0.1)
-# lines(z,td2e1_model)
-# title(main=expression(paste('t'[d2e1],"(h)")),line=-1,cex.main=2)
-# tr_2d_vert(d2,e2,30,nz,0.1)
-# lines(z,td2e2_model)
-# title(main=expression(paste('t'[d2e2],"(h)")),line=-1,cex.main=2)
-# tr_2d_vert(d2,e3,30,nz,0.1)
-# lines(z,td2e3_model)
-# title(main=expression(paste('t'[d2e3],"(h)")),line=-1,cex.main=2)
-# tr_2d_vert(d2,e4,30,nz,0.1)
-# title(main=expression(paste('t'[d2e4],"(h)")),line=-1,cex.main=2)
-# lines(z,td2e4_model)
+
 ```

### 2018-09-17 main_bookcliff.Rmd
importing book cliffs
data main and functions

---
title: "R Notebook"
output: html_notebook
---
facies1=distal lower shoreface heteroliths & offshore mudstones
facies2=proximal lower shoreface sandstones
facies3=foreshore & upper shoreface sandstones

This case study is not stationary so we are importing functions
redefined in a non stationary case
```{r}
source("nonstation_functions.R")
```
```{r}
library(mvtnorm)
```

```{r}
i1=i2=i3=env_lat<-data.matrix(read.table("envclastic.txt"))
i1[env_lat!=1]=0
i2[env_lat==2]=1
i2[env_lat!=2]=0
i3[env_lat==3]=1
i3[env_lat!=3]=0
p1=mean(i1,na.rm=TRUE)
p2=mean(i2,na.rm=TRUE)
p3=mean(i3,na.rm=TRUE)
c(p1,p2,p3)
image(t(env_lat),col=c("blue","green","red"))
```

```{r}
par(mfrow=c(3,3))
t11exp=tr_2d_vert(i1,i1,200,566,56.6)
t12exp=tr_2d_vert(i1,i2,200,566,56.6)
t13exp=tr_2d_vert(i1,i3,200,566,56.6)
t21exp=tr_2d_vert(i2,i1,200,566,56.6)
t22exp=tr_2d_vert(i2,i2,200,566,56.6)
t23exp=tr_2d_vert(i2,i3,200,566,56.6)
t31exp=tr_2d_vert(i3,i1,200,566,56.6)
t32exp=tr_2d_vert(i3,i2,200,566,56.6)
t33exp=tr_2d_vert(i3,i3,200,566,56.6)
```

okay, if we want to fit these transiograms, we need to implement non stationarity
therefore, we need to compute the proportion on each horizontal 
```{r}
prop1=prop2=prop3=numeric(nrow(env_lat))
for (i in 1:nrow(env_lat)){
  prop1[i]=mean(i1[i,],na.rm=TRUE)
  prop2[i]=mean(i2[i,],na.rm=TRUE)
  prop3[i]=mean(i3[i,],na.rm=TRUE)
}
plot(1:nrow(i1),prop1,type = "l")
plot(1:nrow(i1),prop2,type = "l")
plot(1:nrow(i1),prop3,type = "l")
```
ok we are trying to smooth the curves with moving average
```{r}
f50=rep(1/50,50)
prop1filter<-filter(prop1,f50,sides=2)
prop1filter[542:566]=prop1[542:566]
prop1filter[1:24]=prop1[1:24]
plot(1:nrow(i1),prop1filter,type = "l")
#prop2filter<-filter(prop2,f50,sides=2)
#prop2filter[542:566]=prop2[542:566]
#prop2filter[1:24]=prop2[1:24]
#plot(1:nrow(i1),prop2filter,type = "l")
prop3filter<-filter(prop3,f50,sides=2)
prop3filter[542:566]=prop3[542:566]
prop3filter[1:24]=prop3[1:24]
plot(1:nrow(i1),prop3filter,type = "l")
prop2filter=1-prop1filter-prop3filter
plot(1:nrow(i1),prop2filter,type = "l")
#prop1filter+prop2filter+prop3filter
```
we want to plot an image with those curves
```{r}
png(file="PCvert.png",width=2000,height = 800,res=300,antialias = )
par(mar=c(0,0,0,0))
n=nrow(i1)
plot(1:n,prop2filter+prop3filter,type="l",axes=FALSE,ann=FALSE)
lines(1:n,prop3filter)
lines(1:n,rep(1,n))
lines(1:n,rep(0,n))
```

ok now we need to compute the theoretical transiograms with the accurate proportions
this is not good because the global proportions also depend on the horizontal PC
```{r}
rv1=5
rv2=5
b1=0
b2=0
rho=0
n=nrow(i1)
# ok so the thresolds depends on the z, we have a vector
q1=q2=numeric(n)
Sigma1 = matrix(c(1,rho,rho,1),2,2)
for (z in 1:n){
  q1[z]=qnorm(prop1filter[z])
  obj=Inf
  for(test in 1:100){
    q2test = qnorm(test/100)
    newobj =abs( pmvnorm(lower=c(q1[z],q2test),upper=c(Inf,Inf),mean=c(0,0),sigma=Sigma1) - prop2filter[z] ) 
    if (newobj < obj){
    q2[z] = q2test
    obj = newobj
    }
  }
}
```
```{r}
model<-function(h,range,b){return(exp(-abs(h/range)^2)*cos(b*h) )}
```

transiograms now only with vertical proportion curves
```{r}
x = (1:200)/10.
t11_model=t12_model=t13_model=t21_model=t22_model=t23_model=t31_model=t32_model=t33_model=rep(0,200)
Sigma = diag(1,4)
for (i in 1:200){
    t1=t2=t3=0
    d = i/100.
    Sigma[1,2]=Sigma[2,1]= Sigma[3,4]=Sigma[4,3]=rho
    Sigma[1,3]=Sigma[3,1]=model(d,rv1,b1)
    Sigma[1,4]=Sigma[4,1]=(rho)*model(abs(d),rv1,b1)
    Sigma[2,3]=Sigma[3,2]=(rho)*model(abs(d),rv1,b1)
    Sigma[2,4]=Sigma[4,2]=(rho^2)*model(d,rv1,b1)+(1-(rho^2))*model(d,rv2,b2)
    for (z in 1:(n-i)){
      if (prop1filter[z]!=0){
        t11_model[i]=t11_model[i]+pmvnorm(lower=c(-Inf,-Inf,-Inf,-Inf),upper=c(q1[z],Inf,q1[z+i],Inf),mean=c(0,0,0,0),sigma=Sigma)/ prop1filter[z]
        t12_model[i]=t12_model[i]+pmvnorm(lower=c(-Inf,-Inf,q1[z+i],q2[z+i]),upper=c(q1[z],Inf,Inf,Inf),mean=c(0,0,0,0),sigma=Sigma)/ prop1filter[z]  
        t13_model[i]=t13_model[i]+pmvnorm(lower=c(-Inf,-Inf,q1[z+i],-Inf),upper=c(q1[z],Inf,Inf,q2[z+i]),mean=c(0,0,0,0),sigma=Sigma)/ prop1filter[z]
        t1= t1+1
      }

      if(prop2filter[z]!=0){
        t21_model[i]=t21_model[i]+pmvnorm(lower=c(q1[z],q2[z],-Inf,-Inf),upper=c(Inf,Inf,q1[z+i],Inf),mean=c(0,0,0,0),sigma=Sigma)/ prop2filter[z]
        t22_model[i]=t22_model[i]+pmvnorm(lower=c(q1[z],q2[z],q1[z+i],q2[z+i]),upper=c(Inf,Inf,Inf,Inf),mean=c(0,0,0,0),sigma=Sigma)/ prop2filter[z]
        t23_model[i]=t23_model[i]+pmvnorm(lower=c(q1[z],q2[z],q1[z+i],-Inf),upper=c(Inf,Inf,Inf,q2[z+i]),mean=c(0,0,0,0),sigma=Sigma)/ prop2filter[z]
        t2=t2+1
      }

      if(prop3filter[z]!=0){
        t31_model[i]=t31_model[i]+pmvnorm(lower=c(q1[z],-Inf,-Inf,-Inf),upper=c(Inf,q2[z],q1[z+i],Inf),mean=c(0,0,0,0),sigma=Sigma)/ prop3filter[z]
        t32_model[i]=t32_model[i]+pmvnorm(lower=c(q1[z],-Inf,q1[z+i],q2[z+i]),upper=c(Inf,q2[z],Inf,Inf),mean=c(0,0,0,0),sigma=Sigma)/ prop3filter[z]
        t33_model[i]=t33_model[i]+pmvnorm(lower=c(q1[z],-Inf,q1[z+i],-Inf),upper=c(Inf,q2[z],Inf,q2[z+i]),mean=c(0,0,0,0),sigma=Sigma)/ prop3filter[z]
        t3=t3+1
      }

    }
    t11_model[i]=t11_model[i]/t1
    t12_model[i]=t12_model[i]/t1
    t13_model[i]=t13_model[i]/t1
    t21_model[i]=t21_model[i]/t2
    t22_model[i]=t22_model[i]/t2
    t23_model[i]=t23_model[i]/t2
    t31_model[i]=t31_model[i]/t3
    t32_model[i]=t32_model[i]/t3
    t33_model[i]=t33_model[i]/t3

}

par(mfrow=c(3,3))
plot(x,t11exp,type="l",ylim=c(0,1))
lines(x,t11_model,lwd=2)
plot(x,t12exp,type="l",ylim=c(0,1))
lines(x,t12_model,lwd=2)
plot(x,t13exp,type="l",ylim=c(0,1))
lines(x,t13_model,lwd=2)
plot(x,t21exp,type="l",ylim=c(0,1))
lines(x,t21_model,lwd=2)
plot(x,t22exp,type="l",ylim=c(0,1))
lines(x,t22_model,lwd=2)
plot(x,t23exp,type="l",ylim=c(0,1))
lines(x,t23_model,lwd=2)
plot(x,t31exp,type="l",ylim=c(0,1))
lines(x,t31_model,lwd=2)
plot(x,t32exp,type="l",ylim=c(0,1))
lines(x,t32_model,lwd=2)
plot(x,t33exp,type="l",ylim=c(0,1))
lines(x,t33_model,lwd=2)
```

The transiograms are still not perfect, we need to also put a lateral non stationarity

okay, if we want to fit these transiograms, we need to implement non stationarity
therefore, we need to compute the proportion on each horizontal 
```{r}
prop1lat=prop2lat=prop3lat=numeric(ncol(env_lat))
for (i in 1:ncol(env_lat)){
  prop1lat[i]=mean(i1[,i],na.rm=TRUE)
  prop2lat[i]=mean(i2[,i],na.rm=TRUE)
  prop3lat[i]=mean(i3[,i],na.rm=TRUE)
}
plot(1:ncol(i1),prop1lat,type = "p")
plot(1:ncol(i1),prop2lat,type = "p")
plot(1:ncol(i1),prop3lat,type = "p")
```
now doing a good figure
```{r}
png(file="PChor.png",width=2000,height = 800,res=300,antialias = )
par(mar=c(0,0,0,0))
n=ncol(i1)
plot(1:n,prop2lat+prop3lat,type="p",axes=FALSE,ann=FALSE,ylim=c(0,1))
lines(1:n,prop3lat,type="p")
lines(1:n,rep(1,n))
lines(1:n,rep(0,n))
```

we are now doing the mean of the lateral and vertical proportion curves
```{r}
prop1mat=prop2mat=prop3mat=matrix(0,nrow=nrow(env_lat),ncol=ncol(env_lat))
for ( i in 1:nrow(env_lat)){
  for (j in 1:ncol(env_lat)){
    prop1mat[i,j]=(prop1filter[i]+prop1lat[j])/2
    prop2mat[i,j]=(prop2filter[i]+prop2lat[j])/2
    #prop3mat[i,j]=(prop3filter[i]+prop3lat[j])/2
  }
}
prop3mat=1-prop2mat-prop1mat
prop3mat[prop3mat<0]=0
image(prop1mat)
image(prop2mat)
image(prop3mat)
```
thresholds this one need to be the same that on the whole grid

```{r}
#this one is not precise enough
n=nrow(i1)
m=ncol(i1)
q1=q2=matrix(0,n,m)
Sigma1 = matrix(c(1,rho,rho,1),2,2)
for (z in 1:n){
  for(x in 1:m){
    q1[z,x]=qnorm(prop1mat[z,x])
    obj=Inf
    for(test in 1:10){
      q2test = qnorm(test/10)
      newobj =abs( pmvnorm(lower=c(q1[z,x],q2test),upper=c(Inf,Inf),mean=c(0,0),sigma=Sigma1) - prop2mat[z,x] ) 
      if (newobj < obj){
      q2[z,x] = q2test
      obj = newobj
      }
    }
  }
}
```
we implement an analytic way to compute the thresholds
```{r}
n=nrow(i1)
m=ncol(i1)
q1=q2=matrix(0,n,m)
for (z in 1:n){
  for(x in 1:m){
      q1[z,x]=qnorm(prop1mat[z,x])
      if (prop3mat[z,x]!=0) {
      q2[z,x]=qnorm(1-(prop2mat[z,x]/(1-prop1mat[z,x])))
      }
      else{q2[z,x]=-Inf}
  }
}
```

the transios now with vertical and horizontal proportion curves
```{r}
rv1=0.5
rv2=0.5
b1=0
b2=0
rho=0
n=nrow(i1)
m=ncol(i1)
d = (1:200)/10.
t11_model=t12_model=t13_model=t21_model=t22_model=t23_model=t31_model=t32_model=t33_model=rep(0,200)
Sigma = diag(1,4)
for (i in 1:200){
    t1=t2=t3=0
    d = i/100.
    Sigma[1,2]=Sigma[2,1]= Sigma[3,4]=Sigma[4,3]=rho
    Sigma[1,3]=Sigma[3,1]=model(d,rv1,b1)
    Sigma[1,4]=Sigma[4,1]=(rho)*model(abs(d),rv1,b1)
    Sigma[2,3]=Sigma[3,2]=(rho)*model(abs(d),rv1,b1)
    Sigma[2,4]=Sigma[4,2]=(rho^2)*model(d,rv1,b1)+(1-(rho^2))*model(d,rv2,b2)
    for (z in 1:(n-i)){
      for ( x in 1:m){
        if (prop1mat[z,x]!=0){
          t11_model[i]=t11_model[i]+pmvnorm(lower=c(-Inf,-Inf,-Inf,-Inf),upper=c(q1[z,x],Inf,q1[z+i,x],Inf),mean=c(0,0,0,0),sigma=Sigma)/ prop1mat[z,x]
          t12_model[i]=t12_model[i]+pmvnorm(lower=c(-Inf,-Inf,q1[z+i,x],q2[z+i,x]),upper=c(q1[z,x],Inf,Inf,Inf),mean=c(0,0,0,0),sigma=Sigma)/ prop1mat[z,x]  
          t13_model[i]=t13_model[i]+pmvnorm(lower=c(-Inf,-Inf,q1[z+i,x],-Inf),upper=c(q1[z,x],Inf,Inf,q2[z+i,x]),mean=c(0,0,0,0),sigma=Sigma)/ prop1mat[z,x]
          t1= t1+1
        }

        if(prop2mat[z,x]!=0){
          t21_model[i]=t21_model[i]+pmvnorm(lower=c(q1[z,x],q2[z,x],-Inf,-Inf),upper=c(Inf,Inf,q1[z+i,x],Inf),mean=c(0,0,0,0),sigma=Sigma)/ prop2mat[z,x]
          t22_model[i]=t22_model[i]+pmvnorm(lower=c(q1[z,x],q2[z,x],q1[z+i,x],q2[z+i,x]),upper=c(Inf,Inf,Inf,Inf),mean=c(0,0,0,0),sigma=Sigma)/ prop2mat[z,x]
          t23_model[i]=t23_model[i]+pmvnorm(lower=c(q1[z,x],q2[z,x],q1[z+i,x],-Inf),upper=c(Inf,Inf,Inf,q2[z+i,x]),mean=c(0,0,0,0),sigma=Sigma)/ prop2mat[z,x]
          t2=t2+1
        }

        if(prop3mat[z,x]!=0){
          t31_model[i]=t31_model[i]+pmvnorm(lower=c(q1[z,x],-Inf,-Inf,-Inf),upper=c(Inf,q2[z,x],q1[z+i,x],Inf),mean=c(0,0,0,0),sigma=Sigma)/ prop3mat[z,x]
          t32_model[i]=t32_model[i]+pmvnorm(lower=c(q1[z,x],-Inf,q1[z+i,x],q2[z+i,x]),upper=c(Inf,q2[z,x],Inf,Inf),mean=c(0,0,0,0),sigma=Sigma)/ prop3mat[z,x]
          t33_model[i]=t33_model[i]+pmvnorm(lower=c(q1[z,x],-Inf,q1[z+i,x],-Inf),upper=c(Inf,q2[z,x],Inf,q2[z+i,x]),mean=c(0,0,0,0),sigma=Sigma)/ prop3mat[z,x]
          t3=t3+1
        }
      }

    }
    t11_model[i]=t11_model[i]/t1
    t12_model[i]=t12_model[i]/t1
    t13_model[i]=t13_model[i]/t1
    t21_model[i]=t21_model[i]/t2
    t22_model[i]=t22_model[i]/t2
    t23_model[i]=t23_model[i]/t2
    t31_model[i]=t31_model[i]/t3
    t32_model[i]=t32_model[i]/t3
    t33_model[i]=t33_model[i]/t3

}
d = (1:200)/10.
par(mfrow=c(3,3))
plot(d,t11exp,type="l",ylim=c(0,1))
lines(d,t11_model,lwd=2)
plot(d,t12exp,type="l",ylim=c(0,1))
lines(d,t12_model,lwd=2)
plot(d,t13exp,type="l",ylim=c(0,1))
lines(d,t13_model,lwd=2)
plot(d,t21exp,type="l",ylim=c(0,1))
lines(d,t21_model,lwd=2)
plot(d,t22exp,type="l",ylim=c(0,1))
lines(d,t22_model,lwd=2)
plot(d,t23exp,type="l",ylim=c(0,1))
lines(d,t23_model,lwd=2)
plot(d,t31exp,type="l",ylim=c(0,1))
lines(d,t31_model,lwd=2)
plot(d,t32exp,type="l",ylim=c(0,1))
lines(d,t32_model,lwd=2)
plot(d,t33exp,type="l",ylim=c(0,1))
lines(d,t33_model,lwd=2)
```
After discussion, it is more interesting to only look at the transition rates between facies.
In that case, it is not necessary to take into account the non stationary proportions

```{r}
q1g=qnorm(p1)
q2g=qnorm(1-(p2/(1-p1)))
```

```{r}
rv1=0.6
rv2=0.7
Sigma = diag(1,4)
d = 1/10
Sigma[1,2]=Sigma[2,1]= Sigma[3,4]=Sigma[4,3]=rho
Sigma[1,3]=Sigma[3,1]=model(d,rv1,b1)
Sigma[1,4]=Sigma[4,1]=(rho)*model(abs(d),rv1,b1)
Sigma[2,3]=Sigma[3,2]=(rho)*model(abs(d),rv1,b1)
Sigma[2,4]=Sigma[4,2]=(rho^2)*model(d,rv1,b1)+(1-(rho^2))*model(d,rv2,b2)
r11_model=(1-pmvnorm(lower=c(-Inf,-Inf,-Inf,-Inf),upper=c(q1g,Inf,q1g,Inf),mean=c(0,0,0,0),sigma=Sigma)/p1)
r12_model=pmvnorm(lower=c(-Inf,-Inf,q1g,q2g),upper=c(q1g,Inf,Inf,Inf),mean=c(0,0,0,0),sigma=Sigma)/(p1)
r13_model=pmvnorm(lower=c(-Inf,-Inf,q1g,-Inf),upper=c(q1g,Inf,Inf,q2g),mean=c(0,0,0,0),sigma=Sigma)/p1
r21_model=pmvnorm(lower=c(q1g,q2g,-Inf,-Inf),upper=c(Inf,Inf,q1g,Inf),mean=c(0,0,0,0),sigma=Sigma)/p2
r22_model=(1-pmvnorm(lower=c(q1g,q2g,q1g,q2g),upper=c(Inf,Inf,Inf,Inf),mean=c(0,0,0,0),sigma=Sigma)/p2)
r23_model=pmvnorm(lower=c(q1g,q2g,q1g,-Inf),upper=c(Inf,Inf,Inf,q2g),mean=c(0,0,0,0),sigma=Sigma)/p2
r31_model=pmvnorm(lower=c(q1g,-Inf,-Inf,-Inf),upper=c(Inf,q2g,q1g,Inf),mean=c(0,0,0,0),sigma=Sigma)/p3
r32_model=pmvnorm(lower=c(q1g,-Inf,q1g,q2g),upper=c(Inf,q2g,Inf,Inf),mean=c(0,0,0,0),sigma=Sigma)/p3
r33_model=(1-pmvnorm(lower=c(q1g,-Inf,q1g,-Inf),upper=c(Inf,q2g,Inf,q2g),mean=c(0,0,0,0),sigma=Sigma)/p3)
matrix(c(0,r12_model/r11_model,r13_model/r11_model,r21_model/r22_model,0,r23_model/r22_model,r31_model/r33_model,r32_model/r33_model,0),3,3,byrow=TRUE)

```
lets see what the thicknesses are
```{r}
(1/r11_model)*0.1
(1/r22_model)*0.1
(1/r33_model)*0.1
```

```{r}
r11exp=-(1-t11exp[1])/0.1
r12exp=t12exp[1]/0.1
r13exp=t13exp[1]/0.1
r21exp=t21exp[1]/0.1
r22exp=-(1-t22exp[1])/0.1
r23exp=t23exp[1]/0.1
r31exp=t31exp[1]/0.1
r32exp=t32exp[1]/0.1
r33exp=-(1-t33exp[1])/0.1
matrix(c(r11exp,r12exp,r13exp,r21exp,r22exp,r23exp,r31exp,r32exp,r33exp),3,3)
```
and mean thicknesses
```{r}
-(1/r11exp)*0.1
-(1/r22exp)*0.1
-(1/r33exp)*0.1
```

I finally think that we cannot suppose stationnarity even for the transition rates. 
Therefore I will compute them in the case of non stationarity
```{r}
rv1=5
rv2=5
b1=0
b2=0
rho=0
n=nrow(i1)
m=ncol(i1)

t11_model=t12_model=t13_model=t21_model=t22_model=t23_model=t31_model=t32_model=t33_model=0
Sigma = diag(1,4)
  t1=t2=t3=0
    d = 1/10.
    Sigma[1,2]=Sigma[2,1]= Sigma[3,4]=Sigma[4,3]=rho
    Sigma[1,3]=Sigma[3,1]=model(d,rv1,b1)
    Sigma[1,4]=Sigma[4,1]=(rho)*model(abs(d),rv1,b1)
    Sigma[2,3]=Sigma[3,2]=(rho)*model(abs(d),rv1,b1)
    Sigma[2,4]=Sigma[4,2]=(rho^2)*model(d,rv1,b1)+(1-(rho^2))*model(d,rv2,b2)
    for (z in 1:(n-1)){
      for ( x in 1:m){
        if (prop1mat[z,x]!=0){
          t11_model=t11_model+pmvnorm(lower=c(-Inf,-Inf,-Inf,-Inf),upper=c(q1[z,x],Inf,q1[z+1,x],Inf),mean=c(0,0,0,0),sigma=Sigma)/ prop1mat[z,x]
          t12_model=t12_model+pmvnorm(lower=c(-Inf,-Inf,q1[z+1,x],q2[z+1,x]),upper=c(q1[z,x],Inf,Inf,Inf),mean=c(0,0,0,0),sigma=Sigma)/ prop1mat[z,x]  
          t13_model=t13_model+pmvnorm(lower=c(-Inf,-Inf,q1[z+1,x],-Inf),upper=c(q1[z,x],Inf,Inf,q2[z+1,x]),mean=c(0,0,0,0),sigma=Sigma)/ prop1mat[z,x]
          t1= t1+1
        }

        if(prop2mat[z,x]!=0){
          t21_model=t21_model+pmvnorm(lower=c(q1[z,x],q2[z,x],-Inf,-Inf),upper=c(Inf,Inf,q1[z+1,x],Inf),mean=c(0,0,0,0),sigma=Sigma)/ prop2mat[z,x]
          t22_model=t22_model+pmvnorm(lower=c(q1[z,x],q2[z,x],q1[z+1,x],q2[z+1,x]),upper=c(Inf,Inf,Inf,Inf),mean=c(0,0,0,0),sigma=Sigma)/ prop2mat[z,x]
          t23_model=t23_model+pmvnorm(lower=c(q1[z,x],q2[z,x],q1[z+1,x],-Inf),upper=c(Inf,Inf,Inf,q2[z+1,x]),mean=c(0,0,0,0),sigma=Sigma)/ prop2mat[z,x]
          t2=t2+1
        }

        if(prop3mat[z,x]!=0){
          t31_model=t31_model+pmvnorm(lower=c(q1[z,x],-Inf,-Inf,-Inf),upper=c(Inf,q2[z,x],q1[z+1,x],Inf),mean=c(0,0,0,0),sigma=Sigma)/ prop3mat[z,x]
          t32_model=t32_model+pmvnorm(lower=c(q1[z,x],-Inf,q1[z+1,x],q2[z+1,x]),upper=c(Inf,q2[z,x],Inf,Inf),mean=c(0,0,0,0),sigma=Sigma)/ prop3mat[z,x]
          t33_model=t33_model+pmvnorm(lower=c(q1[z,x],-Inf,q1[z+1,x],-Inf),upper=c(Inf,q2[z,x],Inf,q2[z+1,x]),mean=c(0,0,0,0),sigma=Sigma)/ prop3mat[z,x]
          t3=t3+1
        }
      }

    }
    t11_model=(1-t11_model/t1)*100
    t12_model=(t12_model/t1)*100
    t13_model=(t13_model/t1)*100
    t21_model=(t21_model/t2)*100
    t22_model=(1-t22_model/t2)*100
    t23_model=(t23_model/t2)*100
    t31_model=(t31_model/t3)*100
    t32_model=(t32_model/t3)*100
    t33_model=(1-t33_model/t3)*100

matrix(c(0,t12_model/t11_model,t13_model/t11_model,t21_model/t22_model,0,t23_model/t22_model,t31_model/t33_model,t32_model/t33_model,0),3,3,byrow=TRUE)    
```

okay now we create a grid (3d) to simulate the facies 
we will see if the transiograms really matter

```{r}
grid<-array(NA,c(100,1,566))
grid[5,1,]<-env_lat[,1]
grid[15,1,]<-env_lat[,2]
grid[25,1,]<-env_lat[,3]
grid[35,1,]<-env_lat[,4]
grid[45,1,]<-env_lat[,5]
grid[55,1,]<-env_lat[,6]
grid[65,1,]<-env_lat[,7]
grid[75,1,]<-env_lat[,8]
grid[85,1,]<-env_lat[,9]
image(grid[,1,],col=c("blue","green","red"))

```

we are printing in a file 
```{r}
im<-array(NA,c(100,1,566))
im[5,1,]<-env_lat[,1]
im[6,1,]<-env_lat[,1]
im[15,1,]<-env_lat[,2]
im[16,1,]<-env_lat[,2]
im[25,1,]<-env_lat[,3]
im[26,1,]<-env_lat[,3]
im[35,1,]<-env_lat[,4]
im[36,1,]<-env_lat[,4]
im[45,1,]<-env_lat[,5]
im[46,1,]<-env_lat[,5]
im[55,1,]<-env_lat[,6]
im[56,1,]<-env_lat[,6]
im[65,1,]<-env_lat[,7]
im[66,1,]<-env_lat[,7]
im[75,1,]<-env_lat[,8]
im[76,1,]<-env_lat[,8]
im[85,1,]<-env_lat[,9]
im[86,1,]<-env_lat[,9]
image(x=(1:100)*200,y=(1:566)/10,z=im[,1,],col=c("darkslategray4","burlywood2","brown3"),xlab="Lateral distance (m)",ylab="Vertical distance (m)")
png(file="logsutah.png",width=4000,height = 2500,res=300,antialias = )
image(x=(1:100)*200,y=(1:566)/10,z=im[,1,],col=c("darkslategray4","burlywood2","brown3"),xlab="Lateral distance (m)",ylab="Vertical distance (m)")
```

we also need to put the proportions on a grid
```{r}
gridprop1<-gridprop2<-array(NA,c(100,2,566))
gridprop1[5,1,]<-prop1mat[,1]
gridprop1[15,1,]<-prop1mat[,2]
gridprop1[25,1,]<-prop1mat[,3]
gridprop1[35,1,]<-prop1mat[,4]
gridprop1[45,2,]<-prop1mat[,5]
gridprop1[55,1,]<-prop1mat[,6]
gridprop1[65,1,]<-prop1mat[,7]
gridprop1[75,1,]<-prop1mat[,8]
gridprop1[99,1,]<-prop1mat[,9]
#gridprop1[is.na(grid)]=NA
gridprop2[5,1,]<-prop2mat[,1]
gridprop2[15,1,]<-prop2mat[,2]
gridprop2[25,1,]<-prop2mat[,3]
gridprop2[35,1,]<-prop2mat[,4]
gridprop2[45,2,]<-prop2mat[,5]
gridprop2[55,1,]<-prop2mat[,6]
gridprop2[65,1,]<-prop2mat[,7]
gridprop2[75,1,]<-prop2mat[,8]
gridprop2[99,1,]<-prop2mat[,9]
#gridprop2[is.na(grid)]=NA
gridprop3=1-gridprop1-gridprop2
image(gridprop1[,1,])
legend(grconvertX(0.5, "device"), grconvertY(1, "device"), 
     c("0",".5","1"), fill = heat.colors(10)[c(1, 10, 20)], xpd = NA)
image(gridprop2[,1,])
legend(grconvertX(0.5, "device"), grconvertY(1, "device"), 
     c("0",".5","1"), fill = heat.colors(10)[c(1, 10, 20)], xpd = NA)
image(gridprop3[,1,])
legend(grconvertX(0.5, "device"), grconvertY(1, "device"), 
     c("0",".5","1"), fill = heat.colors(10)[c(1, 10, 20)], xpd = NA)
```
okay, now we need to do a kriging to interpolate these proportions
```{r}
source("functions.R")
```
we need first to untrend the global proportion of each facies to perform the kriging
```{r}
gridprop1=gridprop1-p1
gridprop2=gridprop2-p2
```

```{r}
gridprop1krig<-prop_kriging(gridprop1,500,20,20,0.1)
gridprop2krig<-prop_kriging(gridprop2,500,20,20,0.1)
#now we need to retrend the results
gridprop1krig=gridprop1krig+p1
gridprop2krig=gridprop2krig+p2
err=1-gridprop1krig-gridprop2krig
for (x in 1:n[1]){
  for(y in 1:n[2]){
    for( z in 1:n[3]){
      if (err[x,y,z]<0){
        gridprop1krig[x,y,z]=gridprop1krig[x,y,z]+err[x,y,z]
      }
    }
  }
}

image(gridprop1krig[,1,],col=heat.colors(300))
legend(grconvertX(0.5, "device"), grconvertY(1, "device"), 
     c("0",".5","1"), fill = heat.colors(300)[c(1, 200,300)], xpd = NA)
image(gridprop2krig[,1,],col=heat.colors(300))
legend(grconvertX(0.5, "device"), grconvertY(1, "device"), 
     c("0",".5","1"), fill = heat.colors(300)[c(1, 200,300)], xpd = NA)
gridprop3krig<-1-gridprop2krig-gridprop1krig
image(gridprop3krig[,1,],col=heat.colors(300))
legend(grconvertX(0.5, "device"), grconvertY(1, "device"), 
     c("0",".5","1"), fill = heat.colors(300)[c(1 , 200,300)], xpd = NA)
```
```{r}
gridprop1krig[gridprop1krig>1]
gridprop2krig[gridprop2krig>1]
gridprop1krig[gridprop1krig<0]
gridprop2krig[gridprop2krig<0]
```

```{r}
library(mvtnorm)
```
we also need to correct when proportions are higher than one
```{r}
gridprop1krig[gridprop1krig>1]=1
gridprop2krig[gridprop2krig>1]=1
gridprop1krig[gridprop1krig<0]=0
gridprop2krig[gridprop2krig<0]=0
```

Ok now we can compute the corresponding thresholds for the simulation
```{r}
n=dim(gridprop1)
q1tot=q2tot=array(NA,c(100,2,566))
Sigma1 = matrix(c(1,rho,rho,1),2,2)
for (x in 1:n[1]){
  for(y in 1:n[2]){
    for( z in 1:n[3]){
      q1tot[x,y,z]=qnorm(gridprop1krig[x,y,z])
      obj=Inf
      for(test in 1:10){ # only ten iterations for now
        q2test = qnorm(test/10)
        newobj =abs( pmvnorm(lower=c(q1tot[x,y,z],q2test),upper=c(Inf,Inf),mean=c(0,0),sigma=Sigma1) - gridprop2krig[x,y,z] ) 
        if (newobj < obj){
        q2tot[x,y,z] = q2test
        obj = newobj 
        }
      }
    }
  }
}
image(q1tot[,1,],col=heat.colors(300))
legend(grconvertX(0.5, "device"), grconvertY(1, "device"), 
     c("-Inf","0","Inf"), fill = heat.colors(300)[c(1, 150,300)], xpd = NA)
image(q2tot[,1,],col=heat.colors(300))
legend(grconvertX(0.5, "device"), grconvertY(1, "device"), 
     c("-Inf","0","Inf"), fill = heat.colors(300)[c(1, 150,300)], xpd = NA)
```
let s say now we have no correlation between the Gaussian random functions, we have thus a simplification and can directly compute q2, no approximation! 
```{r}
n=dim(gridprop1)
q1tottest=q2tottest=array(NA,c(100,2,566))
Sigma1 = matrix(c(1,rho,rho,1),2,2)
for (x in 1:n[1]){
  for(y in 1:n[2]){
    for( z in 1:n[3]){
      q1tottest[x,y,z]=qnorm(gridprop1krig[x,y,z])
      if (gridprop3krig[x,y,z]!=0) {
      q2tottest[x,y,z]=qnorm(1-(gridprop2krig[x,y,z]/(1-gridprop1krig[x,y,z])))
      }
      else{q2tottest[x,y,z]=-Inf}
    }
  }
}
image(q1tottest[,1,],col=heat.colors(300))
legend(grconvertX(0.5, "device"), grconvertY(1, "device"), 
     c("-Inf","0","Inf"), fill = heat.colors(300)[c(1, 150,300)], xpd = NA)
image(q2tottest[,1,],col=heat.colors(300))
legend(grconvertX(0.5, "device"), grconvertY(1, "device"), 
     c("-Inf","0","Inf"), fill = heat.colors(300)[c(1, 150,300)], xpd = NA)
```
we can check that the threshods on the final grid are equivalent to the one originally computed on the logs
```{r}
q1[1,1]
q1tottest[5,1,1]
q2[1,1]
q2tottest[5,1,1]
```

Once the thresholds are computed, we can do the simulation (unconditional for now)
```{r}
source("functions.R")
```

```{r}
rv1=5
rv2=5
rh=800
b1=0
b2=0
rho=0
Y1<-sim3d(rv1,rh,rh,b1,100,0.1,566,20,100,20,2)
Y2<-sim3d(rv2,rh,rh,b2,100,0.1,566,20,100,20,2)
fac<-Y1
fac[]=3
fac[Y1<q1tottest]=1
fac[Y1>q1tottest & Y2>q2tottest]=2
image(grid[,1,],col=c("darkslategray4","burlywood2","brown3"))
image(fac[,1,],col=c("darkslategray4","burlywood2","brown3"))
image(fac[,2,],col=c("darkslategray4","burlywood2","brown3"))
```
ok let's now do a conditional simulation
for the gibbs sampling we dont need the kriged proportions

```{r}
source("functions.R")
```

```{r}
env_lat[is.na(env_lat)]=Inf # with 0, the gibbs sampler will find random values
grid<-array(NA,c(100,2,566))
grid[5,1,]<-env_lat[,1]
grid[15,1,]<-env_lat[,2]
grid[25,1,]<-env_lat[,3]
grid[35,1,]<-env_lat[,4]
grid[45,2,]<-env_lat[,5]
grid[55,1,]<-env_lat[,6]
grid[65,1,]<-env_lat[,7]
grid[75,1,]<-env_lat[,8]
grid[99,1,]<-env_lat[,9]
i1grid<-grid
i1grid[grid==2]=0
i1grid[grid==3]=0
image(i1grid[,1,])
q1map<-array(NA,c(100,2,566))
q1map[5,1,]<-q1[,1]
q1map[15,1,]<-q1[,2]
q1map[25,1,]<-q1[,3]
q1map[35,1,]<-q1[,4]
q1map[45,2,]<-q1[,5]
q1map[55,1,]<-q1[,6]
q1map[65,1,]<-q1[,7]
q1map[75,1,]<-q1[,8]
q1map[99,1,]<-q1[,9]

Y1gibbs<-gibbs_sampling_map(i1grid,q1map,0.1,20,10,rv1,rh,rh,b1,3)
image(Y1gibbs[,1,])

image(i1grid[,1,])
image(Y1gibbs[,1,])
image(q1map[,1,])
```
test
```{r}
source("functions.R")
test<-gibbs_sampling_map(i1grid,q1map,0.1,20,10,rv1,rh,rh,b1,1)
image(test[,1,],col=heat.colors(300))
```

```{r}
i3grid<-grid
i3grid[grid==1]=Inf
i3grid[grid==3]=1
i3grid[grid==2]=0
q2map<-array(NA,c(100,2,566))
q2map[5,1,]<-q2tottest[5,1,]
q2map[15,1,]<-q2tottest[15,1,]
q2map[25,1,]<-q2tottest[25,1,]
q2map[35,1,]<-q2tottest[35,1,]
q2map[45,2,]<-q2tottest[45,2,]
q2map[55,1,]<-q2tottest[55,1,]
q2map[65,1,]<-q2tottest[65,1,]
q2map[75,1,]<-q2tottest[75,1,]
q2map[99,1,]<-q2tottest[99,1,]

Y2gibbs<-gibbs_sampling_map(i3grid,q2map,0.1,20,10,rv2,rh,rh,b2,3)
image(Y2gibbs[,1,])
test<-Y2gibbs
test[Y2gibbs<q2map]=1
test[Y2gibbs>q2map]=0
image(test[,1,])
image(i3grid[,1,])
image(Y2gibbs[,1,])
```

now that we have the gibbs sampling, we need to krig the difference with the unconditional simulation
je peux probablement utiliser le meme krigeage que pour les proportions

```{r}
E1=Y1gibbs-Y1
E2=Y2gibbs-Y2
E1k<-prop_kriging(E1,rh,20,20,0.1)
E2k<-prop_kriging(E2,rh,20,20,0.1)
Y1c=Y1+E1k
Y2c=Y2+E2k
facc<-Y1c
facc[]=3
facc[Y1c<q1tottest]=1
facc[Y1c>q1tottest & Y2c>q2tottest]=2
image(facc[,1,],col=c("darkslategray4","burlywood2","brown3"))
image(grid[,1,],col=c("darkslategray4","burlywood2","brown3"))
image(E1k[,1,],col=heat.colors(300))
image(E2k[,1,],col=heat.colors(300))
```

ok now we can look at the diagenesis
```{r}
diag_lat<-data.matrix(read.table("diagclastic.txt"))
diag_lat[diag_lat==0]=3
d1=d2=d3=diag_lat
d1[diag_lat!=1]=0
d2[diag_lat==2]=1
d2[diag_lat!=2]=0
d3[diag_lat==3]=1
d3[diag_lat!=3]=0
pd1=mean(d1,na.rm=TRUE)
pd2=mean(d2,na.rm=TRUE)
pd3=mean(d3,na.rm=TRUE)
c(pd1,pd2,pd3)
image(t(diag_lat),col=c("blue","green","red"))
```

load the diagenesis
```{r}

im<-array(NA,c(100,1,566))
im[5,1,]<-env_lat[,1]
im[6,1,]<-env_lat[,1]
im[8,1,]<-diag_lat[,1]+3
im[9,1,]<-diag_lat[,1]+3
im[15,1,]<-env_lat[,2]
im[16,1,]<-env_lat[,2]
im[18,1,]<-diag_lat[,2]+3
im[19,1,]<-diag_lat[,2]+3
im[25,1,]<-env_lat[,3]
im[26,1,]<-env_lat[,3]
im[28,1,]<-diag_lat[,3]+3
im[29,1,]<-diag_lat[,3]+3
im[35,1,]<-env_lat[,4]
im[36,1,]<-env_lat[,4]
im[38,1,]<-diag_lat[,4]+3
im[39,1,]<-diag_lat[,4]+3
im[45,1,]<-env_lat[,5]
im[46,1,]<-env_lat[,5]
im[48,1,]<-diag_lat[,5]+3
im[49,1,]<-diag_lat[,5]+3
im[55,1,]<-env_lat[,6]
im[56,1,]<-env_lat[,6]
im[58,1,]<-diag_lat[,6]+3
im[59,1,]<-diag_lat[,6]+3
im[65,1,]<-env_lat[,7]
im[66,1,]<-env_lat[,7]
im[68,1,]<-diag_lat[,7]+3
im[69,1,]<-diag_lat[,7]+3
im[75,1,]<-env_lat[,8]
im[76,1,]<-env_lat[,8]
im[78,1,]<-diag_lat[,8]+3
im[79,1,]<-diag_lat[,8]+3
im[85,1,]<-env_lat[,9]
im[86,1,]<-env_lat[,9]
im[88,1,]<-diag_lat[,9]+3
im[89,1,]<-diag_lat[,9]+3
image(x=(1:100)*200,y=(1:566)/10,z=im[,1,],col=c("darkslategray4","burlywood2","brown3","green","yellow","black"),xlab="Lateral distance (m)",ylab="Vertical distance (m)")
png(file="logsutah.png",width=4000,height = 2500,res=300,antialias = )
image(x=(1:100)*200,y=(1:566)/10,z=im[,1,],col=c("darkslategray4","burlywood2","brown3","green","yellow","black"),xlab="Lateral distance (m)",ylab="Vertical distance (m)")
```

simulation now with diagenesis! 
we first need to compute the relative proportions
```{r}
pd1e1=mean(i1*d1,na.rm=TRUE)/p1
pd2e1=mean(i1*d2,na.rm=TRUE)/p1
pd3e1=mean(i1*d3,na.rm=TRUE)/p1
pd1e2=mean(i2*d1,na.rm=TRUE)/p2
pd2e2=mean(i2*d2,na.rm=TRUE)/p2
pd3e2=mean(i2*d3,na.rm=TRUE)/p2
pd1e3=mean(i3*d1,na.rm=TRUE)/p3
pd2e3=mean(i3*d2,na.rm=TRUE)/p3
pd3e3=mean(i3*d3,na.rm=TRUE)/p3
matrix(c(pd1e1,pd2e1,pd3e1,pd1e2,pd2e2,pd3e2,pd1e3,pd2e3,pd3e3),3,3)
```

now we need to find the thresholds
given that d1 is only found in e2, its threshold is computed with its general proportion
but this is not the case for d2
we need first to compute the thresholds of d2 because will impact threshold of d1
```{r}
qd2e2=qnorm(1-pd2e2)
qd1e2=qnorm(1-pd2e2-pd1e2)
qd2e3=qnorm(1-pd2e3)
c(qd2e2,qd1e2,qd2e3)
```
Now I can do the simulation, with in mind that I also need to condition it! 
but it should be simpler than previously. 
I still need to rewrite the gibbs sampling for that new truncation rule
```{r}
dgrid<-array(NA,c(100,2,566))
diag_lat[is.na(diag_lat)]=Inf
dgrid[5,1,]=diag_lat[,1]
dgrid[15,1,]<-diag_lat[,2]
dgrid[25,1,]<-diag_lat[,3]
dgrid[35,1,]<-diag_lat[,4]
dgrid[45,2,]<-diag_lat[,5]
dgrid[55,1,]<-diag_lat[,6]
dgrid[65,1,]<-diag_lat[,7]
dgrid[75,1,]<-diag_lat[,8]
dgrid[99,1,]<-diag_lat[,9]
Y3gibbs<-gibbs_sampling_diag2(grid,dgrid,c(qd1e2,qd2e2,qd2e3),0.1,20,10,rv2,rh,rh,b2,3)
image(Y3gibbs[,1,])
facdg<-Y3gibbs
facdg[!is.na(facdg)]=3
facdg[ grid==2 & Y3gibbs<qd2e2 & Y3gibbs>qd1e2]=1
facdg[ grid==2 & Y3gibbs>qd2e2 ]=2
facdg[ grid==3 & Y3gibbs>qd2e3 ]=2
image(facdg[,1,],col=c("green","yellow","black"))
image(dgrid[,1,],col=c("green","yellow","black"))
```

```{r}
Y3<-sim3d(rv2,rh,rh,b2,100,0.1,566,20,100,20,2)
```
```{r}
E3=Y3gibbs-Y3
E3k<-prop_kriging(E3,rh,20,20,0.1)
Y3c=Y3+E3k
facd<-Y3c
facd[]=3
facd[ facc==2 & Y3c<qd2e2 & Y3c>qd1e2]=1
facd[ facc==2 & Y3c>qd2e2 ]=2
facd[ facc==3 & Y3c>qd2e3 ]=2
image(x=(1:100)*200,y=(1:566)/10,z=im[,1,],col=c("darkslategray4","burlywood2","brown3","green","yellow","black"),xlab="Lateral distance (m)",ylab="Vertical distance (m)")
image(facd[,1,],col=c("green","yellow","black"))
fac_comb=facc
fac_comb[facc==2 & Y3c<qd2e2 & Y3c>qd1e2]=4
fac_comb[facc==2 & Y3c>qd2e2 ]=5
fac_comb[facc==3 & Y3c>qd2e3 ]=5
image(facc[,1,],col=c("darkslategray4","burlywood2","brown3"))
image(fac_comb[,1,],col=c("darkslategray4","burlywood2","brown3","green","yellow"))
```
Now that it is working, we can make a beautiful simulation in three dimensions
```{r}
par(bg="transparent")
n=dim(gridprop1)
gridprop1<-gridprop2<-err<-array(NA,c(100,20,566))
gridprop1[5,10,]<-prop1mat[,1]
gridprop1[15,9,]<-prop1mat[,2]
gridprop1[25,10,]<-prop1mat[,3]
gridprop1[35,9,]<-prop1mat[,4]
gridprop1[45,10,]<-prop1mat[,5]
gridprop1[55,9,]<-prop1mat[,6]
gridprop1[65,10,]<-prop1mat[,7]
gridprop1[75,9,]<-prop1mat[,8]
gridprop1[99,10,]<-prop1mat[,9]
#gridprop1[is.na(grid)]=NA
gridprop2[5,10,]<-prop2mat[,1]
gridprop2[15,9,]<-prop2mat[,2]
gridprop2[25,10,]<-prop2mat[,3]
gridprop2[35,9,]<-prop2mat[,4]
gridprop2[45,10,]<-prop2mat[,5]
gridprop2[55,9,]<-prop2mat[,6]
gridprop2[65,10,]<-prop2mat[,7]
gridprop2[75,9,]<-prop2mat[,8]
gridprop2[99,10,]<-prop2mat[,9]
#gridprop2[is.na(grid)]=NA
gridprop3=1-gridprop1-gridprop2
gridprop1=gridprop1-p1
gridprop2=gridprop2-p2
gridprop1krig<-prop_kriging(gridprop1,500,20,20,0.1)
gridprop2krig<-prop_kriging(gridprop2,500,20,20,0.1)
# we are trying here to have the same proportions on every y plane (because no information on them but still want non sationarity)
for (y in 1:20){
  if (y!=10 & y!=9){
    gridprop1krig[,y,]=gridprop1krig[,10,]
    gridprop2krig[,y,]=gridprop2krig[,10,]
  }
}

#now we need to retrend the results
gridprop1krig=gridprop1krig+p1
gridprop2krig=gridprop2krig+p2
gridprop3krig=1-gridprop1krig-gridprop2krig # there is a problem  here to solve
for (x in 1:n[1]){
  for(y in 1:n[2]){
    for( z in 1:n[3]){
      err[x,y,z]=gridprop1krig[x,y,z]+gridprop2krig[x,y,z]
      if (err[x,y,z]>1){
        gridprop1krig[x,y,z]=gridprop1krig[x,y,z]+(1-err[x,y,z])
        gridprop3krig[x,y,z]=0
      }
    }
  }
}

n=dim(gridprop1)
q1tottest=q2tottest=array(NA,c(100,20,566))
for (x in 1:n[1]){
  for(y in 1:n[2]){
    for( z in 1:n[3]){
      q1tottest[x,y,z]=qnorm(gridprop1krig[x,y,z])
      if (gridprop3krig[x,y,z]>0) {
        q2tottest[x,y,z]=qnorm(1-(gridprop2krig[x,y,z]/(1-gridprop1krig[x,y,z])))
      }
      else{q2tottest[x,y,z]=-Inf}
    }
  }
}

rv1=5
rv2=5
rv3=2
rh=300
rh3=150
b1=0
b2=0
rho=0
Y1<-sim3d(rv1,rh,rh,b1,100,0.1,566,20,100,20,20)
Y2<-sim3d(rv2,rh,rh,b2,100,0.1,566,20,100,20,20)
Y3<-sim3d(rv3,rh3,rh3,b2,100,0.1,566,20,100,20,20)
fac<-Y1
fac[]=3
fac[Y1<q1tottest]=1
fac[Y1>q1tottest & Y2>q2tottest]=2
image(grid[,1,],col=c("darkslategray4","burlywood2","brown3"))
image(fac[,1,],col=c("darkslategray4","burlywood2","brown3"))
image(fac[,2,],col=c("darkslategray4","burlywood2","brown3"))
env_lat[is.na(env_lat)]=Inf # with 0, the gibbs sampler will find random values
grid<-array(NA,c(100,20,566))
grid[5,10,]<-env_lat[,1]
grid[15,9,]<-env_lat[,2]
grid[25,10,]<-env_lat[,3]
grid[35,9,]<-env_lat[,4]
grid[45,10,]<-env_lat[,5]
grid[55,9,]<-env_lat[,6]
grid[65,10,]<-env_lat[,7]
grid[75,9,]<-env_lat[,8]
grid[99,10,]<-env_lat[,9]
i1grid<-grid
i1grid[grid==2]=0
i1grid[grid==3]=0
image(i1grid[,1,])
q1map<-array(NA,c(100,20,566))
q1map[5,10,]<-q1tottest[5,10,]
q1map[15,9,]<-q1tottest[15,9,]
q1map[25,10,]<-q1tottest[25,10,]
q1map[35,9,]<-q1tottest[35,9,]
q1map[45,10,]<-q1tottest[45,10,]
q1map[55,9,]<-q1tottest[55,9,]
q1map[65,10,]<-q1tottest[65,10,]
q1map[75,9,]<-q1tottest[75,9,]
q1map[99,10,]<-q1tottest[99,10,]

Y1gibbs<-gibbs_sampling_map(i1grid,q1map,0.1,20,10,rv1,rh,rh,b1,3)
image(Y1gibbs[,10,])
image(i1grid[,10,])
image(Y1gibbs[,10,])
image(q1map[,10,])

i3grid<-grid
i3grid[grid==1]=Inf
i3grid[grid==3]=1
i3grid[grid==2]=0
q2map<-array(NA,c(100,20,566))
q2map[5,10,]<-q2tottest[5,10,]
q2map[15,9,]<-q2tottest[15,9,]
q2map[25,10,]<-q2tottest[25,10,]
q2map[35,9,]<-q2tottest[35,9,]
q2map[45,10,]<-q2tottest[45,10,]
q2map[55,9,]<-q2tottest[55,9,]
q2map[65,10,]<-q2tottest[65,10,]
q2map[75,9,]<-q2tottest[75,9,]
q2map[99,10,]<-q2tottest[99,10,]

Y2gibbs<-gibbs_sampling_map(i3grid,q2map,0.1,20,10,rv2,rh,rh,b2,3)
image(Y2gibbs[,10,])

E1=Y1gibbs-Y1
E2=Y2gibbs-Y2
E1k<-prop_kriging(E1,rh,20,20,0.1)
E2k<-prop_kriging(E2,rh,20,20,0.1)
Y1c=Y1+E1k
Y2c=Y2+E2k
facc<-Y1c
facc[]=3
facc[Y1c<q1tottest]=1
facc[Y1c>q1tottest & Y2c>q2tottest]=2
image(facc[,10,],col=c("darkslategray4","burlywood2","brown3"))
image(grid[,10,],col=c("darkslategray4","burlywood2","brown3"))
image(E1k[,10,],col=heat.colors(300))
image(E2k[,10,],col=heat.colors(300))
dgrid<-array(NA,c(100,20,566))
diag_lat[is.na(diag_lat)]=Inf
dgrid[5,10,]=diag_lat[,1]
dgrid[15,9,]<-diag_lat[,2]
dgrid[25,10,]<-diag_lat[,3]
dgrid[35,9,]<-diag_lat[,4]
dgrid[45,10,]<-diag_lat[,5]
dgrid[55,9,]<-diag_lat[,6]
dgrid[65,10,]<-diag_lat[,7]
dgrid[75,9,]<-diag_lat[,8]
dgrid[99,10,]<-diag_lat[,9]
Y3gibbs<-gibbs_sampling_diag(grid,dgrid,c(qd1e2,qd2e2,qd2e3),0.1,20,10,rv2,rh,rh,b2,3)
image(Y3gibbs[,10,])
facdg<-Y3gibbs
facdg[!is.na(facdg)]=3
facdg[ grid==2 & Y3gibbs<qd2e2 & Y3gibbs>qd1e2]=1
facdg[ grid==2 & Y3gibbs>qd2e2 ]=2
facdg[ grid==3 & Y3gibbs>qd2e3 ]=2
image(facdg[,10,],col=c("green","yellow","black"))
image(dgrid[,10,],col=c("green","yellow","black"))
E3=Y3gibbs-Y3
E3k<-prop_kriging(E3,rh3,20,20,0.1)
Y3c=Y3+E3k
facd<-Y3c
facd[]=3
facd[ facc==2 & Y3c<qd2e2 & Y3c>qd1e2]=1
facd[ facc==2 & Y3c>qd2e2 ]=2
facd[ facc==3 & Y3c>qd2e3 ]=2

image(facd[,10,],col=c("green","yellow","black"))
fac_comb=facc
fac_comb[facc==2 & Y3c<qd2e2 & Y3c>qd1e2]=4
fac_comb[facc==2 & Y3c>qd2e2 ]=5
fac_comb[facc==3 & Y3c>qd2e3 ]=5
image(facc[,10,],col=c("darkslategray4","burlywood2","brown3"))
image(fac_comb[,10,],col=c("darkslategray4","burlywood2","brown3","green","yellow"))
image(dgrid[,10,],col=c("green","yellow","black"))
```

```{r}
for ( z in 1:566){
  for ( y in 1:20){
    for ( x in 1:100){
      write(toString(c(fac_comb[x,y,z])),"utahsimu5.csv",append=TRUE)
    }
  }
}
```
we also want to export the data
```{r}
grid[grid==Inf]=NA
dgrid[dgrid==Inf]=NA
comb_grid<-grid
comb_grid[dgrid==1]=4
comb_grid[dgrid==2]=5
for ( z in 1:566){
  for ( y in 1:20){
    for ( x in 1:100){
      write(toString(c(comb_grid[x,y,z])),"utahdata.csv",append=TRUE)
    }
  }
}
```
we can also compute the resulting embedded transitions on those simulations
```{r}
i1real<-i2real<-i3real<-facc
i1real[facc!=1]=0
i2real[facc==2]=1
i2real[facc!=2]=0
i3real[facc==3]=1
i3real[facc!=3]=0
r12=embedded3d(i1real,i2real)
r13=embedded3d(i1real,i3real)
r21=embedded3d(i2real,i1real)
r23=embedded3d(i2real,i3real)
r31=embedded3d(i3real,i1real)
r32=embedded3d(i3real,i2real)
matrix(c(0,r12,r13,r21,0,r23,r31,r32,0),3,3,byrow=TRUE)
r12d=embedded2d(i1,i2)
r13d=embedded2d(i1,i3)
r21d=embedded2d(i2,i1)
r23d=embedded2d(i2,i3)
r31d=embedded2d(i3,i1)
r32d=embedded2d(i3,i2)
matrix(c(0,r12d,r13d,r21d,0,r23d,r31d,r32d,0),3,3,byrow=TRUE)
```

```{r}
real3<-matrix(c(0,r12,r13,r21,0,r23,r31,r32,0),3,3,byrow=TRUE)
```
```{r}
(real1+real2+real3)/3
```

### 2018-09-17 nonstation_functions.R

@@ -1,0 +1,309 @@
+tr_2d_vert<-function(datai,dataj,size,ncell,dz){
+  cov<-numeric(size)
+  for (l in 1:size){
+    npair = nrow(datai)-l
+    t =0
+    for ( pair in 1:npair){
+      for ( y in 1:ncol(datai)){
+        if(is.na(datai[pair,y])== FALSE & is.na(dataj[pair+l,y]) == FALSE){
+          cov[l] = cov[l]+ datai[pair,y]*dataj[pair+l,y]
+          t = t+1
+        }
+      }
+    }
+    cov[l]=cov[l]/t
+  }
+  cov = cov /mean(datai,na.rm = TRUE)# we are measuring a correlation
+  dist = (0:(size-1))/(ncell*dz)
+  plot(dist,cov,type = "p",col="black",pch=21,bg="grey",cex=2,ylim=c(0.,1),ylab = "", xlab = "", axes = FALSE)
+  axis(1,at = seq(0,3,0.5),cex.axis=1.5)
+  axis(2,cex.axis=1.5)
+  mtext("Distance", side = 1, line = 2.5, cex = 1.5)
+  #mtext("Transiogram", side = 2, line = 2.5, cex = 1.5,las = 0)
+  return(cov)
+}
+
+embedded3d<-function(datai,dataj){
+  # we assume there is no NA 
+  ndim=dim(datai)
+  embed=0
+  Tii=0
+  n=ndim[3]-1
+  prop=mean(datai[,,-(n+1)]) # the last line is not counted
+  for ( z in 1:n){
+    Tii=Tii+mean(datai[,,z]*datai[,,z+1])/n
+    embed=embed+mean(datai[,,z]*dataj[,,z+1])/n
+  }
+  Tii=(1-Tii/prop)
+  embed=embed/prop
+  return(embed/Tii) 
+}
+
+embedded2d<-function(datai,dataj){
+
+  embed=0
+  Tii=0
+  n=nrow(datai)-1
+  prop=mean(datai[-(n+1),],na.rm=TRUE) # the last line is not counted
+  count=0
+  for ( z in 1:n){
+    for (x in 1:ncol(dataj)){
+        if(is.na(datai[z,x])==FALSE & is.na(datai[z+1,x])==FALSE){
+          Tii=Tii+datai[[z,x]]*datai[[z+1,x]]
+          embed=embed+datai[[z,x]]*dataj[[z+1,x]]
+          count=count+1
[…]

### 2018-10-15 cosim_functions.R
delete useless

@@ -140,21 +140,3 @@ tr_3d_vert<-function(datai,dataj,size){
   #mtext("Transiogram", side = 2, line = 2.5, cex = 1.,las = 0)
   return(cov)
 }
-
-sim2dexp<-function(rv,rh,freq,N,dz,nz,dx,nx){
-  phase <- runif(N,0,2*pi)
-  bin <- sample(c(-1,1),N,replace=T)
-  w1 <- rcauchy(N, location = freq , scale =1/rv)
-  w2 <- rnorm(N, mean = 0 , sd = sqrt(2)/rh)
-  sim<-array(0,c(nx,nz))
-  for(i in 1:N){
-    for ( z in 1:nz){
-      for ( x in 1:nx){
-        sim[x,z] = sim[x,z] + cos(bin[i]*w1[i]*(z*dz)+w2[i]*x*dx+phase[i])
-      }
-    }
-  }
-  sim = sim *sqrt(2/N)
-  
-  return(sim)
-}

### 2018-10-15 co_sim_condi.R
commented gibbs sampling for latemar

@@ -1,6 +1,5 @@
 # conditioning for four Gaussian functions
-# the covariance matrix is going to be very big
-# probably not inversible, so that we will probably need to use exponential covariances
+# the covariance matrix is thus large
 
 negrnorm<-function(q,mean,sd){
   a=rnorm(1,mean,sd)
@@ -26,6 +25,7 @@ truncnorm<-function(qmin,qmax,mean,sd){
   return(a)
 }
 
+# covariance matrix between data locations with two variables 
 coco_cov_data<-function(data_loc,data_loc_co,dz,dhx,rv,rhx,b,rho,shift){
   # the matrix is going to be non symmetric but positive definit
   # we are here coding the general case where n can be different from n_co
@@ -379,49 +379,52 @@ dual_krig_line<-function(errorwell,rhx,dhx){
 }
 
 
+# this algorithm is based on Emery paper (2013); algorithm 7
+# adapted for four variables reprensenting four Gaussian random functions
+# although in the case studies only three Gaussian functions are used
+# we develop the algo for four Gaussian functions so that it is more generic
+# for the case studies, the third Gaussian function is chosen null
 gibbs_sampling3d<-function(grid,grid_co,q,q_co,dz,dhx,dhy,rv,rhx,rhy,b,rho,shift,it){
-  # this algorithm is based on Emery paper (2013); algorithm 7
   
-  data_values<-grid[!is.na(grid)] # getting the values
-  data_values_co<-grid_co[!is.na(grid_co)]
+  data_values<-grid[!is.na(grid)] # getting the data values of depositional facies
+  data_values_co<-grid_co[!is.na(grid_co)] # getting the data values of diagenesis
   data_loc<-which(!is.na(grid),arr.ind=TRUE) # getting the position in the grid
-  data_loc_co<-which(!is.na(grid_co),arr.ind=TRUE)
+  data_loc_co<-which(!is.na(grid_co),arr.ind=TRUE) #position can be different if heterotopic data
   n=length(data_values)
[…]

### 2018-10-15 co_sim_condi.R
commented surface kriging

@@ -300,21 +300,21 @@ cov_data_line<-function(data_loc,dhx,rhx){
   return(cov_h)
 }
 
-
+# kriging by surface because separable covariance functions
 dual_krig_surf<-function(errorwell,rhx,rhy,dhx,dhy){
   
-  # getting the positions in the grid of one horizontal line, the positions will be the same for every line
+  # getting the positions in the grid of one horizontal surface, the positions will be the same for every surface
   data_loc<-which(!is.na(errorwell[,,1]),arr.ind=TRUE) 
   toestim <-which(is.na(errorwell[,,1]),arr.ind=TRUE)
   n= nrow(data_loc)
   m = nrow(toestim)
   print(n)
   # covariance and inverse covariance matrix of a single surface
+  # it is computed once and will be used for every horizontal level
+  # which means we can invert the matrix only once
   c_data<- cov_data_surf(data_loc,dhx,dhy,rhx,rhy)
   invc<-chol2inv(chol(c_data))
   errorfield <-errorwell
-  print(c_data)
-  print(invc)
   
   # covariance vector between estimation and data of every surface
   c_estim_data<-matrix(0,m,n)

### 2018-10-15 main_latemar.Rmd
deleted some stuff

--- 2018-09-17 main.Rmd
@@
 ```{r}
-source("C:/Users/tl3315/Desktop/GitHub/AsymBiPGS/co_sim_condi.R")
-source("C:/Users/tl3315/Desktop/GitHub/AsymBiPGS/cosim_functions.R")
+source("C:/Users/tl3315/Desktop/GitHub/CyclicPGS/co_sim_condi.R")
+source("C:/Users/tl3315/Desktop/GitHub/CyclicPGS/cosim_functions.R")
 ```
@@
 ```
-
-we also compute the transiograms on the final model
-```{r}
-real1<-real2<-real3<-real4<-faciesenv
-real1[faciesenv!=1]=0
-real2[faciesenv==2]=1
-real2[faciesenv!=2]=0
-real3[faciesenv==3]=1
-real3[faciesenv!=3]=0
-real4[faciesenv==4]=1
-real4[faciesenv!=4]=0
-t11real<-tr_3d_vert(real1,real1,50)
-t12real<-tr_3d_vert(real1,real2,50)
-t13real<-tr_3d_vert(real1,real3,50)
-t14real<-tr_3d_vert(real1,real4,50)
-t21real<-tr_3d_vert(real2,real1,50)
-t22real<-tr_3d_vert(real2,real2,50)
-t23real<-tr_3d_vert(real2,real3,50)
-t24real<-tr_3d_vert(real2,real4,50)
-t31real<-tr_3d_vert(real3,real1,50)
-t32real<-tr_3d_vert(real3,real2,50)
-t33real<-tr_3d_vert(real3,real3,50)
-t34real<-tr_3d_vert(real3,real4,50)
-t41real<-tr_3d_vert(real4,real1,50)
-t42real<-tr_3d_vert(real4,real2,50)
-t43real<-tr_3d_vert(real4,real3,50)
-t44real<-tr_3d_vert(real4,real4,50)
-par(mfrow=c(4,4))
-plot(50,t11real)
-plot(length(t44real),t12real)
-plot(length(t44real),t13real)
-plot(length(t44real),t14real)
-plot(length(t44real),t21real)
-plot(length(t44real),t22real)
-plot(length(t44real),t23real)
-plot(length(t44real),t24real)
-plot(length(t44real),t31real)
-plot(length(t44real),t32real)
-plot(length(t44real),t33real)
-plot(length(t44real),t34real)
-plot(length(t44real),t41real)
-plot(length(t44real),t42real)
-plot(length(t44real),t43real)
-plot(length(t44real),t44real)
-```

### 2018-10-15 co_sim_condi.R
deleted useless stuff

@@ -1,5 +1,4 @@
-# conditioning for four Gaussian functions
-# the covariance matrix is thus large
+# Functions for conditioning four Gaussian functions
 
 negrnorm<-function(q,mean,sd){
   a=rnorm(1,mean,sd)
@@ -25,250 +24,6 @@ truncnorm<-function(qmin,qmax,mean,sd){
   return(a)
 }
 
-# covariance matrix between data locations with two variables 
-coco_cov_data<-function(data_loc,data_loc_co,dz,dhx,rv,rhx,b,rho,shift){
-  # the matrix is going to be non symmetric but positive definit
-  # we are here coding the general case where n can be different from n_co
-  n=nrow(data_loc)
-  n_co=nrow(data_loc_co)
-  dist_hx <- dist_v<- matrix(0,n,n)
-  for ( i in 1:(n-1)){
-    for (j in (i+1):n ){
-      dist_v[i,j]=-(data_loc[i,2]-data_loc[j,2])*dz
-      dist_v[j,i]=-dist_v[i,j]
-      dist_hx[i,j]=dist_hx[j,i]=abs(data_loc[i,1]-data_loc[j,1])*dhx
-    }
-  }
-  dist_hx_co <- dist_v_co<- matrix(0,n,n_co)
-  co_dist_hx <- co_dist_hy <- co_dist_v<- matrix(0,n_co,n)
-  for ( i in 1:n){
-    for (j in 1:n_co ){
-      dist_v_co[i,j]=-(data_loc[i,2]-data_loc_co[j,2])*dz
-      co_dist_v[j,i]=-dist_v_co[i,j]
-      dist_hx_co[i,j]=co_dist_hx[j,i]=abs(data_loc[i,1]-data_loc_co[j,1])*dhx
-    }
-  }
-  co_dist_hx_co  <- co_dist_v_co<- matrix(0,n_co,n_co)
-  for ( i in 1:(n_co-1)){
-    for (j in (i+1):n_co ){
-      co_dist_v_co[i,j]=-(data_loc_co[i,2]-data_loc_co[j,2])*dz
-      co_dist_v_co[j,i]=-co_dist_v_co[i,j]
-      co_dist_hx_co[i,j]=co_dist_hx_co[j,i]=abs(data_loc_co[i,1]-data_loc_co[j,1])*dhx
-    }
-  }
-  a12= rho[1]/model(shift[1],rv[1],b[1])
[…]

### 2018-10-15 cosim_functions.R
deleted useless stuff

@@ -1,34 +1,8 @@
-
+# basic simulation and computation of transiograms
 
 # Covariance function used for the Gaussian random function
 model<-function(h,range,b){return(exp(-abs(h/range)^2)*cos(b*h) )}
 model_lat<-function(h,range){return(exp(-(h/range)^2) )}
-
-# basic function to plot a transiogram
-tr_2d_vert<-function(datai,dataj,size,ncell,dz){
-  cov<-numeric(size)
-  for (l in 1:size){
-    npair = nrow(datai)-l
-    t =0
-    for ( pair in 1:npair){
-      for ( y in 1:ncol(datai)){
-        if(is.na(datai[pair,y])== FALSE & is.na(dataj[pair+l,y]) == FALSE){
-          cov[l] = cov[l]+ datai[pair,y]*dataj[pair+l-1,y]
-          t = t+1
-        }
-      }
-    }
-    cov[l]=cov[l]/t
-  }
-  cov = cov /mean(datai,na.rm = TRUE)# we are measuring a correlation
-  dist = (0:(size-1))/(ncell*dz)
-  plot(dist,cov,type = "p",col="black",pch=21,bg="grey",cex=2,ylim=c(0.,1),ylab = "", xlab = "", axes = FALSE)
-  axis(1,at = seq(0,3,0.5),cex.axis=1.5)
-  axis(2,cex.axis=1.5)
-  #mtext("Distance", side = 1, line = 2.5, cex = 1.)
-  #mtext("Transiogram", side = 2, line = 2.5, cex = 1.,las = 0)
-  return(cov)
-}
 
 embedded3d<-function(datai,dataj){
   # we assume there is no NA 
@@ -46,61 +20,8 @@ embedded3d<-function(datai,dataj){
   return(embed/Tii) 
 }
 
-embedded2d<-function(datai,dataj){
-  
-  embed=0
-  Tii=0
-  n=nrow(datai)-1
-  prop=mean(datai[-(n+1),],na.rm=TRUE) # the last line is not counted
-  count=0
-  for ( z in 1:n){
-    for (x in 1:ncol(dataj)){
-      if(is.na(datai[[z,x]])==FALSE & is.na(datai[[z+1,x]])==FALSE){
-        Tii=Tii+datai[[z,x]]*datai[[z+1,x]]
[…]

### 2018-10-15 main_bookcliff.Rmd
cleaning

@@
 
-okay, if we want to fit these transiograms, we need to implement non stationarity
+if we want to fit these transiograms, we need to implement non stationarity
 therefore, we need to compute the proportion on each horizontal 
@@
 ```
-ok we are trying to smooth the curves with moving average
+ok we are now smoothing the curves with moving average
 ```{r}
@@
 plot(1:nrow(i1),prop1filter,type = "l")
-#prop2filter<-filter(prop2,f50,sides=2)
-#prop2filter[542:566]=prop2[542:566]
-#prop2filter[1:24]=prop2[1:24]
-#plot(1:nrow(i1),prop2filter,type = "l")
+
 prop3filter<-filter(prop3,f50,sides=2)
@@
 plot(1:nrow(i1),prop2filter,type = "l")
-#prop1filter+prop2filter+prop3filter
+
 ```
@@
 this is not good because the global proportions also depend on the horizontal PC
-```{r}
-rv1=5
-rv2=5
-b1=0
-b2=0
-rho=0
-n=nrow(i1)
-# ok so the thresolds depends on the z, we have a vector
-q1=q2=numeric(n)
-Sigma1 = matrix(c(1,rho,rho,1),2,2)
-for (z in 1:n){
-  q1[z]=qnorm(prop1filter[z])
-  obj=Inf
-  for(test in 1:100){
-    q2test = qnorm(test/100)
-    newobj =abs( pmvnorm(lower=c(q1[z],q2test),upper=c(Inf,Inf),mean=c(0,0),sigma=Sigma1) - prop2filter[z] ) 
-    if (newobj < obj){
-    q2[z] = q2test
-    obj = newobj
-    }
-  }
-}
-```
+
 ```{r}
@@
 
-transiograms now only with vertical proportion curves
-```{r}
-x = (1:200)/10.
-t11_model=t12_model=t13_model=t21_model=t22_model=t23_model=t31_model=t32_model=t33_model=rep(0,200)
-Sigma = diag(1,4)
-for (i in 1:200){
-    t1=t2=t3=0
-    d = i/100.
-    Sigma[1,2]=Sigma[2,1]= Sigma[3,4]=Sigma[4,3]=rho
-    Sigma[1,3]=Sigma[3,1]=model(d,rv1,b1)
-    Sigma[1,4]=Sigma[4,1]=(rho)*model(abs(d),rv1,b1)
-    Sigma[2,3]=Sigma[3,2]=(rho)*model(abs(d),rv1,b1)
-    Sigma[2,4]=Sigma[4,2]=(rho^2)*model(d,rv1,b1)+(1-(rho^2))*model(d,rv2,b2)
-    for (z in 1:(n-i)){
-      if (prop1filter[z]!=0){
-        t11_model[i]=t11_model[i]+pmvnorm(lower=c(-Inf,-Inf,-Inf,-Inf),upper=c(q1[z],Inf,q1[z+i],Inf),mean=c(0,0,0,0),sigma=Sigma)/ prop1filter[z]
-        t12_model[i]=t12_model[i]+pmvnorm(lower=c(-Inf,-Inf,q1[z+i],q2[z+i]),upper=c(q1[z],Inf,Inf,Inf),mean=c(0,0,0,0),sigma=Sigma)/ prop1filter[z]  
-        t13_model[i]=t13_model[i]+pmvnorm(lower=c(-Inf,-Inf,q1[z+i],-Inf),upper=c(q1[z],Inf,Inf,q2[z+i]),mean=c(0,0,0,0),sigma=Sigma)/ prop1filter[z]
-        t1= t1+1
-      }
-
-      if(prop2filter[z]!=0){
-        t21_model[i]=t21_model[i]+pmvnorm(lower=c(q1[z],q2[z],-Inf,-Inf),upper=c(Inf,Inf,q1[z+i],Inf),mean=c(0,0,0,0),sigma=Sigma)/ prop2filter[z]
-        t22_model[i]=t22_model[i]+pmvnorm(lower=c(q1[z],q2[z],q1[z+i],q2[z+i]),upper=c(Inf,Inf,Inf,Inf),mean=c(0,0,0,0),sigma=Sigma)/ prop2filter[z]
-        t23_model[i]=t23_model[i]+pmvnorm(lower=c(q1[z],q2[z],q1[z+i],-Inf),upper=c(Inf,Inf,Inf,q2[z+i]),mean=c(0,0,0,0),sigma=Sigma)/ prop2filter[z]
-        t2=t2+1
-      }
-
-      if(prop3filter[z]!=0){
-        t31_model[i]=t31_model[i]+pmvnorm(lower=c(q1[z],-Inf,-Inf,-Inf),upper=c(Inf,q2[z],q1[z+i],Inf),mean=c(0,0,0,0),sigma=Sigma)/ prop3filter[z]
-        t32_model[i]=t32_model[i]+pmvnorm(lower=c(q1[z],-Inf,q1[z+i],q2[z+i]),upper=c(Inf,q2[z],Inf,Inf),mean=c(0,0,0,0),sigma=Sigma)/ prop3filter[z]
-        t33_model[i]=t33_model[i]+pmvnorm(lower=c(q1[z],-Inf,q1[z+i],-Inf),upper=c(Inf,q2[z],Inf,q2[z+i]),mean=c(0,0,0,0),sigma=Sigma)/ prop3filter[z]
-        t3=t3+1
-      }
-
-    }
-    t11_model[i]=t11_model[i]/t1
-    t12_model[i]=t12_model[i]/t1
-    t13_model[i]=t13_model[i]/t1
-    t21_model[i]=t21_model[i]/t2
-    t22_model[i]=t22_model[i]/t2
-    t23_model[i]=t23_model[i]/t2
-    t31_model[i]=t31_model[i]/t3
-    t32_model[i]=t32_model[i]/t3
-    t33_model[i]=t33_model[i]/t3
-
-}
-
-par(mfrow=c(3,3))
-plot(x,t11exp,type="l",ylim=c(0,1))
-lines(x,t11_model,lwd=2)
-plot(x,t12exp,type="l",ylim=c(0,1))
-lines(x,t12_model,lwd=2)
-plot(x,t13exp,type="l",ylim=c(0,1))
-lines(x,t13_model,lwd=2)
-plot(x,t21exp,type="l",ylim=c(0,1))
-lines(x,t21_model,lwd=2)
-plot(x,t22exp,type="l",ylim=c(0,1))
-lines(x,t22_model,lwd=2)
-plot(x,t23exp,type="l",ylim=c(0,1))
-lines(x,t23_model,lwd=2)
-plot(x,t31exp,type="l",ylim=c(0,1))
-lines(x,t31_model,lwd=2)
-plot(x,t32exp,type="l",ylim=c(0,1))
-lines(x,t32_model,lwd=2)
-plot(x,t33exp,type="l",ylim=c(0,1))
-lines(x,t33_model,lwd=2)
-```
-
-The transiograms are still not perfect, we need to also put a lateral non stationarity
-
 okay, if we want to fit these transiograms, we need to implement non stationarity
-therefore, we need to compute the proportion on each horizontal 
+therefore, we need to compute the proportion on each vertical 
 ```{r}
@@
 ```
-thresholds this one need to be the same that on the whole grid
+Now that we have the proportions on the grid
+we can compute the corresponding thresholds of the Gaussian functions according to the truncation rule
 
-```{r}
-#this one is not precise enough
-n=nrow(i1)
-m=ncol(i1)
-q1=q2=matrix(0,n,m)
-Sigma1 = matrix(c(1,rho,rho,1),2,2)
-for (z in 1:n){
-  for(x in 1:m){
-    q1[z,x]=qnorm(prop1mat[z,x])
-    obj=Inf
-    for(test in 1:10){
-      q2test = qnorm(test/10)
-      newobj =abs( pmvnorm(lower=c(q1[z,x],q2test),upper=c(Inf,Inf),mean=c(0,0),sigma=Sigma1) - prop2mat[z,x] ) 
-      if (newobj < obj){
-      q2[z,x] = q2test
-      obj = newobj
-      }
-    }
-  }
-}
-```
-we implement an analytic way to compute the thresholds
+We can compute the thresholds analytically if the Gaussian functions are not correlated to each other here
 ```{r}
@@
 ```
+Because of the non stationarity, it is more relevant to computed the transition rates between facies rather than the
+transiograms
+we can thus fit the method with the transition rates
 
-the transios now with vertical and horizontal proportion curves
-```{r}
-rv1=0.5
-rv2=0.5
-b1=0
-b2=0
-rho=0
-n=nrow(i1)
-m=ncol(i1)
-d = (1:200)/10.
-t11_model=t12_model=t13_model=t21_model=t22_model=t23_model=t31_model=t32_model=t33_model=rep(0,200)
-Sigma = diag(1,4)
-for (i in 1:200){
-    t1=t2=t3=0
-    d = i/100.
-    Sigma[1,2]=Sigma[2,1]= Sigma[3,4]=Sigma[4,3]=rho
-    Sigma[1,3]=Sigma[3,1]=model(d,rv1,b1)
-    Sigma[1,4]=Sigma[4,1]=(rho)*model(abs(d),rv1,b1)
-    Sigma[2,3]=Sigma[3,2]=(rho)*model(abs(d),rv1,b1)
-    Sigma[2,4]=Sigma[4,2]=(rho^2)*model(d,rv1,b1)+(1-(rho^2))*model(d,rv2,b2)
-    for (z in 1:(n-i)){
-      for ( x in 1:m){
-        if (prop1mat[z,x]!=0){
-          t11_model[i]=t11_model[i]+pmvnorm(lower=c(-Inf,-Inf,-Inf,-Inf),upper=c(q1[z,x],Inf,q1[z+i,x],Inf),mean=c(0,0,0,0),sigma=Sigma)/ prop1mat[z,x]
-          t12_model[i]=t12_model[i]+pmvnorm(lower=c(-Inf,-Inf,q1[z+i,x],q2[z+i,x]),upper=c(q1[z,x],Inf,Inf,Inf),mean=c(0,0,0,0),sigma=Sigma)/ prop1mat[z,x]  
-          t13_model[i]=t13_model[i]+pmvnorm(lower=c(-Inf,-Inf,q1[z+i,x],-Inf),upper=c(q1[z,x],Inf,Inf,q2[z+i,x]),mean=c(0,0,0,0),sigma=Sigma)/ prop1mat[z,x]
-          t1= t1+1
-        }
-
-        if(prop2mat[z,x]!=0){
-          t21_model[i]=t21_model[i]+pmvnorm(lower=c(q1[z,x],q2[z,x],-Inf,-Inf),upper=c(Inf,Inf,q1[z+i,x],Inf),mean=c(0,0,0,0),sigma=Sigma)/ prop2mat[z,x]
-          t22_model[i]=t22_model[i]+pmvnorm(lower=c(q1[z,x],q2[z,x],q1[z+i,x],q2[z+i,x]),upper=c(Inf,Inf,Inf,Inf),mean=c(0,0,0,0),sigma=Sigma)/ prop2mat[z,x]
-          t23_model[i]=t23_model[i]+pmvnorm(lower=c(q1[z,x],q2[z,x],q1[z+i,x],-Inf),upper=c(Inf,Inf,Inf,q2[z+i,x]),mean=c(0,0,0,0),sigma=Sigma)/ prop2mat[z,x]
-          t2=t2+1
-        }
-
-        if(prop3mat[z,x]!=0){
-          t31_model[i]=t31_model[i]+pmvnorm(lower=c(q1[z,x],-Inf,-Inf,-Inf),upper=c(Inf,q2[z,x],q1[z+i,x],Inf),mean=c(0,0,0,0),sigma=Sigma)/ prop3mat[z,x]
-          t32_model[i]=t32_model[i]+pmvnorm(lower=c(q1[z,x],-Inf,q1[z+i,x],q2[z+i,x]),upper=c(Inf,q2[z,x],Inf,Inf),mean=c(0,0,0,0),sigma=Sigma)/ prop3mat[z,x]
-          t33_model[i]=t33_model[i]+pmvnorm(lower=c(q1[z,x],-Inf,q1[z+i,x],-Inf),upper=c(Inf,q2[z,x],Inf,q2[z+i,x]),mean=c(0,0,0,0),sigma=Sigma)/ prop3mat[z,x]
-          t3=t3+1
-        }
-      }
-
-    }
-    t11_model[i]=t11_model[i]/t1
-    t12_model[i]=t12_model[i]/t1
-    t13_model[i]=t13_model[i]/t1
-    t21_model[i]=t21_model[i]/t2
-    t22_model[i]=t22_model[i]/t2
-    t23_model[i]=t23_model[i]/t2
-    t31_model[i]=t31_model[i]/t3
-    t32_model[i]=t32_model[i]/t3
-    t33_model[i]=t33_model[i]/t3
-
-}
-d = (1:200)/10.
-par(mfrow=c(3,3))
-plot(d,t11exp,type="l",ylim=c(0,1))
-lines(d,t11_model,lwd=2)
-plot(d,t12exp,type="l",ylim=c(0,1))
-lines(d,t12_model,lwd=2)
-plot(d,t13exp,type="l",ylim=c(0,1))
-lines(d,t13_model,lwd=2)
-plot(d,t21exp,type="l",ylim=c(0,1))
-lines(d,t21_model,lwd=2)
-plot(d,t22exp,type="l",ylim=c(0,1))
-lines(d,t22_model,lwd=2)
-plot(d,t23exp,type="l",ylim=c(0,1))
-lines(d,t23_model,lwd=2)
-plot(d,t31exp,type="l",ylim=c(0,1))
-lines(d,t31_model,lwd=2)
-plot(d,t32exp,type="l",ylim=c(0,1))
-lines(d,t32_model,lwd=2)
-plot(d,t33exp,type="l",ylim=c(0,1))
-lines(d,t33_model,lwd=2)
-```
-After discussion, it is more interesting to only look at the transition rates between facies.
-In that case, it is not necessary to take into account the non stationary proportions
-
+thresholds according to the truncation rule
 ```{r}
@@
 ```{r}
+rv1=5
+rv2=5
+rh=800
+b1=0
+b2=0
+rho=0
 rv1=0.6
@@
 
-I finally think that we cannot suppose stationnarity even for the transition rates. 
-Therefore I will compute them in the case of non stationarity
-```{r}
-rv1=5
-rv2=5
-b1=0
-b2=0
-rho=0
-n=nrow(i1)
-m=ncol(i1)
-
-t11_model=t12_model=t13_model=t21_model=t22_model=t23_model=t31_model=t32_model=t33_model=0
-Sigma = diag(1,4)
-  t1=t2=t3=0
-    d = 1/10.
-    Sigma[1,2]=Sigma[2,1]= Sigma[3,4]=Sigma[4,3]=rho
-    Sigma[1,3]=Sigma[3,1]=model(d,rv1,b1)
-    Sigma[1,4]=Sigma[4,1]=(rho)*model(abs(d),rv1,b1)
-    Sigma[2,3]=Sigma[3,2]=(rho)*model(abs(d),rv1,b1)
-    Sigma[2,4]=Sigma[4,2]=(rho^2)*model(d,rv1,b1)+(1-(rho^2))*model(d,rv2,b2)
-    for (z in 1:(n-1)){
-      for ( x in 1:m){
-        if (prop1mat[z,x]!=0){
-          t11_model=t11_model+pmvnorm(lower=c(-Inf,-Inf,-Inf,-Inf),upper=c(q1[z,x],Inf,q1[z+1,x],Inf),mean=c(0,0,0,0),sigma=Sigma)/ prop1mat[z,x]
-          t12_model=t12_model+pmvnorm(lower=c(-Inf,-Inf,q1[z+1,x],q2[z+1,x]),upper=c(q1[z,x],Inf,Inf,Inf),mean=c(0,0,0,0),sigma=Sigma)/ prop1mat[z,x]  
-          t13_model=t13_model+pmvnorm(lower=c(-Inf,-Inf,q1[z+1,x],-Inf),upper=c(q1[z,x],Inf,Inf,q2[z+1,x]),mean=c(0,0,0,0),sigma=Sigma)/ prop1mat[z,x]
-          t1= t1+1
-        }
-
-        if(prop2mat[z,x]!=0){
-          t21_model=t21_model+pmvnorm(lower=c(q1[z,x],q2[z,x],-Inf,-Inf),upper=c(Inf,Inf,q1[z+1,x],Inf),mean=c(0,0,0,0),sigma=Sigma)/ prop2mat[z,x]
-          t22_model=t22_model+pmvnorm(lower=c(q1[z,x],q2[z,x],q1[z+1,x],q2[z+1,x]),upper=c(Inf,Inf,Inf,Inf),mean=c(0,0,0,0),sigma=Sigma)/ prop2mat[z,x]
-          t23_model=t23_model+pmvnorm(lower=c(q1[z,x],q2[z,x],q1[z+1,x],-Inf),upper=c(Inf,Inf,Inf,q2[z+1,x]),mean=c(0,0,0,0),sigma=Sigma)/ prop2mat[z,x]
-          t2=t2+1
-        }
-
-        if(prop3mat[z,x]!=0){
-          t31_model=t31_model+pmvnorm(lower=c(q1[z,x],-Inf,-Inf,-Inf),upper=c(Inf,q2[z,x],q1[z+1,x],Inf),mean=c(0,0,0,0),sigma=Sigma)/ prop3mat[z,x]
-          t32_model=t32_model+pmvnorm(lower=c(q1[z,x],-Inf,q1[z+1,x],q2[z+1,x]),upper=c(Inf,q2[z,x],Inf,Inf),mean=c(0,0,0,0),sigma=Sigma)/ prop3mat[z,x]
-          t33_model=t33_model+pmvnorm(lower=c(q1[z,x],-Inf,q1[z+1,x],-Inf),upper=c(Inf,q2[z,x],Inf,q2[z+1,x]),mean=c(0,0,0,0),sigma=Sigma)/ prop3mat[z,x]
-          t3=t3+1
-        }
-      }
-
-    }
-    t11_model=(1-t11_model/t1)*100
-    t12_model=(t12_model/t1)*100
-    t13_model=(t13_model/t1)*100
-    t21_model=(t21_model/t2)*100
-    t22_model=(1-t22_model/t2)*100
-    t23_model=(t23_model/t2)*100
-    t31_model=(t31_model/t3)*100
-    t32_model=(t32_model/t3)*100
-    t33_model=(1-t33_model/t3)*100
-
-matrix(c(0,t12_model/t11_model,t13_model/t11_model,t21_model/t22_model,0,t23_model/t22_model,t31_model/t33_model,t32_model/t33_model,0),3,3,byrow=TRUE)    
-```
-
 okay now we create a grid (3d) to simulate the facies
-we will see if the transiograms really matter
 
@@
 
-we are printing in a file 
+we are printing this picture in a file 
 ```{r}
@@
 ```{r}
+n=dim(gridprop1)
 gridprop1krig<-prop_kriging(gridprop1,500,20,20,0.1)
@@
 ```
+test
 ```{r}
@@
 Ok now we can compute the corresponding thresholds for the simulation
-```{r}
-n=dim(gridprop1)
-q1tot=q2tot=array(NA,c(100,2,566))
-Sigma1 = matrix(c(1,rho,rho,1),2,2)
-for (x in 1:n[1]){
-  for(y in 1:n[2]){
-    for( z in 1:n[3]){
-      q1tot[x,y,z]=qnorm(gridprop1krig[x,y,z])
-      obj=Inf
-      for(test in 1:10){ # only ten iterations for now
-        q2test = qnorm(test/10)
-        newobj =abs( pmvnorm(lower=c(q1tot[x,y,z],q2test),upper=c(Inf,Inf),mean=c(0,0),sigma=Sigma1) - gridprop2krig[x,y,z] ) 
-        if (newobj < obj){
-        q2tot[x,y,z] = q2test
-        obj = newobj 
-        }
-      }
-    }
-  }
-}
-image(q1tot[,1,],col=heat.colors(300))
-legend(grconvertX(0.5, "device"), grconvertY(1, "device"), 
-     c("-Inf","0","Inf"), fill = heat.colors(300)[c(1, 150,300)], xpd = NA)
-image(q2tot[,1,],col=heat.colors(300))
-legend(grconvertX(0.5, "device"), grconvertY(1, "device"), 
-     c("-Inf","0","Inf"), fill = heat.colors(300)[c(1, 150,300)], xpd = NA)
-```
-let s say now we have no correlation between the Gaussian random functions, we have thus a simplification and can directly compute q2, no approximation! 
+
+we have no correlation between the Gaussian random functions, we have thus a simplification and can directly compute q2, with no approximation
 ```{r}
@@
 Once the thresholds are computed, we can do the simulation (unconditional for now)
-```{r}
-source("functions.R")
-```
 
@@
 for the gibbs sampling we dont need the kriged proportions
-
-```{r}
-source("functions.R")
-```
 
@@
 ```{r}
-source("functions.R")
 test<-gibbs_sampling_map(i1grid,q1map,0.1,20,10,rv1,rh,rh,b1,1)
@@
 now that we have the gibbs sampling, we need to krig the difference with the unconditional simulation
-je peux probablement utiliser le meme krigeage que pour les proportions
 
@@
 
-ok now we can look at the diagenesis
+ok now we can look at the diagenesis, we do it separately because in this example,
+the Gaussian function representing the diagenesis is not correlated to the Gaussian functions of the depositional facies
 ```{r}

### 2018-10-16 main_bookcliff.Rmd
cleaning

@@
 ```
-
+importing depositional facies
 ```{r}
@@
 
+computing transiograms on the data
 ```{r}
@@
 
-if we want to fit these transiograms, we need to implement non stationarity
+Because of the non stationarity, it is more relevant to computed the transition rates between facies rather than the
+transiograms
+we can thus fit the method with the transition rates
+
+Here are thresholds for the depositional facies according to the truncation rule
+```{r}
+q1g=qnorm(p1)
+q2g=qnorm(1-(p2/(1-p1)))
+```
+
+covariance model for the Gaussian functions
+```{r}
+model<-function(h,range,b){return(exp(-abs(h/range)^2)*cos(b*h) )}
+```
+
+Model embedded transition probabilities
+```{r}
+rv1=5
+rv2=5
+rh=800
+b1=0
+b2=0
+rho=0
+rv1=0.6
+rv2=0.7
+Sigma = diag(1,4)
+d = 1/10
+Sigma[1,2]=Sigma[2,1]= Sigma[3,4]=Sigma[4,3]=rho
+Sigma[1,3]=Sigma[3,1]=model(d,rv1,b1)
+Sigma[1,4]=Sigma[4,1]=(rho)*model(abs(d),rv1,b1)
+Sigma[2,3]=Sigma[3,2]=(rho)*model(abs(d),rv1,b1)
+Sigma[2,4]=Sigma[4,2]=(rho^2)*model(d,rv1,b1)+(1-(rho^2))*model(d,rv2,b2)
+r11_model=(1-pmvnorm(lower=c(-Inf,-Inf,-Inf,-Inf),upper=c(q1g,Inf,q1g,Inf),mean=c(0,0,0,0),sigma=Sigma)/p1)
+r12_model=pmvnorm(lower=c(-Inf,-Inf,q1g,q2g),upper=c(q1g,Inf,Inf,Inf),mean=c(0,0,0,0),sigma=Sigma)/(p1)
+r13_model=pmvnorm(lower=c(-Inf,-Inf,q1g,-Inf),upper=c(q1g,Inf,Inf,q2g),mean=c(0,0,0,0),sigma=Sigma)/p1
+r21_model=pmvnorm(lower=c(q1g,q2g,-Inf,-Inf),upper=c(Inf,Inf,q1g,Inf),mean=c(0,0,0,0),sigma=Sigma)/p2
+r22_model=(1-pmvnorm(lower=c(q1g,q2g,q1g,q2g),upper=c(Inf,Inf,Inf,Inf),mean=c(0,0,0,0),sigma=Sigma)/p2)
+r23_model=pmvnorm(lower=c(q1g,q2g,q1g,-Inf),upper=c(Inf,Inf,Inf,q2g),mean=c(0,0,0,0),sigma=Sigma)/p2
+r31_model=pmvnorm(lower=c(q1g,-Inf,-Inf,-Inf),upper=c(Inf,q2g,q1g,Inf),mean=c(0,0,0,0),sigma=Sigma)/p3
+r32_model=pmvnorm(lower=c(q1g,-Inf,q1g,q2g),upper=c(Inf,q2g,Inf,Inf),mean=c(0,0,0,0),sigma=Sigma)/p3
+r33_model=(1-pmvnorm(lower=c(q1g,-Inf,q1g,-Inf),upper=c(Inf,q2g,Inf,q2g),mean=c(0,0,0,0),sigma=Sigma)/p3)
+matrix(c(0,r12_model/r11_model,r13_model/r11_model,r21_model/r22_model,0,r23_model/r22_model,r31_model/r33_model,r32_model/r33_model,0),3,3,byrow=TRUE)
+
+```
+The resulting facies thicknesses are
+
+```{r}
+(1/r11_model)*0.1
+(1/r22_model)*0.1
+(1/r33_model)*0.1
+```
+and the experimental embedded transitions are
+
+```{r}
+r11exp=-(1-t11exp[1])/0.1
+r12exp=t12exp[1]/0.1
+r13exp=t13exp[1]/0.1
+r21exp=t21exp[1]/0.1
+r22exp=-(1-t22exp[1])/0.1
+r23exp=t23exp[1]/0.1
+r31exp=t31exp[1]/0.1
+r32exp=t32exp[1]/0.1
+r33exp=-(1-t33exp[1])/0.1
+matrix(c(r11exp,r12exp,r13exp,r21exp,r22exp,r23exp,r31exp,r32exp,r33exp),3,3)
+```
+
+and mean thicknesses
+```{r}
+-(1/r11exp)*0.1
+-(1/r22exp)*0.1
+-(1/r33exp)*0.1
+```
+Once the model is fitted, we can do the simulation,
+But we have seen that the proportions are not stationary and we need to take that into account in the simulation
+
 therefore, we need to compute the proportion on each horizontal 
@@
 
-ok now we need to compute the theoretical transiograms with the accurate proportions
-this is not good because the global proportions also depend on the horizontal PC
-
-```{r}
-model<-function(h,range,b){return(exp(-abs(h/range)^2)*cos(b*h) )}
-```
-
-okay, if we want to fit these transiograms, we need to implement non stationarity
 therefore, we need to compute the proportion on each vertical 
@@
 ```
-Now that we have the proportions on the grid
-we can compute the corresponding thresholds of the Gaussian functions according to the truncation rule
+Once the local proportions have been computed on each data point, we can interpolate those proportions in the grid
 
-We can compute the thresholds analytically if the Gaussian functions are not correlated to each other here
-```{r}
-n=nrow(i1)
-m=ncol(i1)
-q1=q2=matrix(0,n,m)
-for (z in 1:n){
-  for(x in 1:m){
-      q1[z,x]=qnorm(prop1mat[z,x])
-      if (prop3mat[z,x]!=0) {
-      q2[z,x]=qnorm(1-(prop2mat[z,x]/(1-prop1mat[z,x])))
-      }
-      else{q2[z,x]=-Inf}
-  }
-}
-```
-Because of the non stationarity, it is more relevant to computed the transition rates between facies rather than the
-transiograms
-we can thus fit the method with the transition rates
-
-thresholds according to the truncation rule
-```{r}
-q1g=qnorm(p1)
-q2g=qnorm(1-(p2/(1-p1)))
-```
-
-```{r}
-rv1=5
-rv2=5
-rh=800
-b1=0
-b2=0
-rho=0
-rv1=0.6
-rv2=0.7
-Sigma = diag(1,4)
-d = 1/10
-Sigma[1,2]=Sigma[2,1]= Sigma[3,4]=Sigma[4,3]=rho
-Sigma[1,3]=Sigma[3,1]=model(d,rv1,b1)
-Sigma[1,4]=Sigma[4,1]=(rho)*model(abs(d),rv1,b1)
-Sigma[2,3]=Sigma[3,2]=(rho)*model(abs(d),rv1,b1)
-Sigma[2,4]=Sigma[4,2]=(rho^2)*model(d,rv1,b1)+(1-(rho^2))*model(d,rv2,b2)
-r11_model=(1-pmvnorm(lower=c(-Inf,-Inf,-Inf,-Inf),upper=c(q1g,Inf,q1g,Inf),mean=c(0,0,0,0),sigma=Sigma)/p1)
-r12_model=pmvnorm(lower=c(-Inf,-Inf,q1g,q2g),upper=c(q1g,Inf,Inf,Inf),mean=c(0,0,0,0),sigma=Sigma)/(p1)
-r13_model=pmvnorm(lower=c(-Inf,-Inf,q1g,-Inf),upper=c(q1g,Inf,Inf,q2g),mean=c(0,0,0,0),sigma=Sigma)/p1
-r21_model=pmvnorm(lower=c(q1g,q2g,-Inf,-Inf),upper=c(Inf,Inf,q1g,Inf),mean=c(0,0,0,0),sigma=Sigma)/p2
-r22_model=(1-pmvnorm(lower=c(q1g,q2g,q1g,q2g),upper=c(Inf,Inf,Inf,Inf),mean=c(0,0,0,0),sigma=Sigma)/p2)
-r23_model=pmvnorm(lower=c(q1g,q2g,q1g,-Inf),upper=c(Inf,Inf,Inf,q2g),mean=c(0,0,0,0),sigma=Sigma)/p2
-r31_model=pmvnorm(lower=c(q1g,-Inf,-Inf,-Inf),upper=c(Inf,q2g,q1g,Inf),mean=c(0,0,0,0),sigma=Sigma)/p3
-r32_model=pmvnorm(lower=c(q1g,-Inf,q1g,q2g),upper=c(Inf,q2g,Inf,Inf),mean=c(0,0,0,0),sigma=Sigma)/p3
-r33_model=(1-pmvnorm(lower=c(q1g,-Inf,q1g,-Inf),upper=c(Inf,q2g,Inf,q2g),mean=c(0,0,0,0),sigma=Sigma)/p3)
-matrix(c(0,r12_model/r11_model,r13_model/r11_model,r21_model/r22_model,0,r23_model/r22_model,r31_model/r33_model,r32_model/r33_model,0),3,3,byrow=TRUE)
-
-```
-lets see what the thicknesses are
-```{r}
-(1/r11_model)*0.1
-(1/r22_model)*0.1
-(1/r33_model)*0.1
-```
-
-```{r}
-r11exp=-(1-t11exp[1])/0.1
-r12exp=t12exp[1]/0.1
-r13exp=t13exp[1]/0.1
-r21exp=t21exp[1]/0.1
-r22exp=-(1-t22exp[1])/0.1
-r23exp=t23exp[1]/0.1
-r31exp=t31exp[1]/0.1
-r32exp=t32exp[1]/0.1
-r33exp=-(1-t33exp[1])/0.1
-matrix(c(r11exp,r12exp,r13exp,r21exp,r22exp,r23exp,r31exp,r32exp,r33exp),3,3)
-```
-and mean thicknesses
-```{r}
--(1/r11exp)*0.1
--(1/r22exp)*0.1
--(1/r33exp)*0.1
-```
-
-okay now we create a grid (3d) to simulate the facies
+we create a grid (3d) to simulate the depositional facies
 
@@
 
-we also need to put the proportions on a grid
-```{r}
-gridprop1<-gridprop2<-array(NA,c(100,2,566))
-gridprop1[5,1,]<-prop1mat[,1]
-gridprop1[15,1,]<-prop1mat[,2]
-gridprop1[25,1,]<-prop1mat[,3]
-gridprop1[35,1,]<-prop1mat[,4]
-gridprop1[45,2,]<-prop1mat[,5]
-gridprop1[55,1,]<-prop1mat[,6]
-gridprop1[65,1,]<-prop1mat[,7]
-gridprop1[75,1,]<-prop1mat[,8]
-gridprop1[99,1,]<-prop1mat[,9]
-#gridprop1[is.na(grid)]=NA
-gridprop2[5,1,]<-prop2mat[,1]
-gridprop2[15,1,]<-prop2mat[,2]
-gridprop2[25,1,]<-prop2mat[,3]
-gridprop2[35,1,]<-prop2mat[,4]
-gridprop2[45,2,]<-prop2mat[,5]
-gridprop2[55,1,]<-prop2mat[,6]
-gridprop2[65,1,]<-prop2mat[,7]
-gridprop2[75,1,]<-prop2mat[,8]
-gridprop2[99,1,]<-prop2mat[,9]
-#gridprop2[is.na(grid)]=NA
-gridprop3=1-gridprop1-gridprop2
-image(gridprop1[,1,])
-legend(grconvertX(0.5, "device"), grconvertY(1, "device"), 
-     c("0",".5","1"), fill = heat.colors(10)[c(1, 10, 20)], xpd = NA)
-image(gridprop2[,1,])
-legend(grconvertX(0.5, "device"), grconvertY(1, "device"), 
-     c("0",".5","1"), fill = heat.colors(10)[c(1, 10, 20)], xpd = NA)
-image(gridprop3[,1,])
-legend(grconvertX(0.5, "device"), grconvertY(1, "device"), 
-     c("0",".5","1"), fill = heat.colors(10)[c(1, 10, 20)], xpd = NA)
-```
-okay, now we need to do a kriging to interpolate these proportions
-```{r}
-source("functions.R")
-```
-we need first to untrend the global proportion of each facies to perform the kriging
-```{r}
-gridprop1=gridprop1-p1
-gridprop2=gridprop2-p2
-```
-
-```{r}
-n=dim(gridprop1)
-gridprop1krig<-prop_kriging(gridprop1,500,20,20,0.1)
-gridprop2krig<-prop_kriging(gridprop2,500,20,20,0.1)
-#now we need to retrend the results
-gridprop1krig=gridprop1krig+p1
-gridprop2krig=gridprop2krig+p2
-err=1-gridprop1krig-gridprop2krig
-for (x in 1:n[1]){
-  for(y in 1:n[2]){
-    for( z in 1:n[3]){
-      if (err[x,y,z]<0){
-        gridprop1krig[x,y,z]=gridprop1krig[x,y,z]+err[x,y,z]
-      }
-    }
-  }
-}
-
-image(gridprop1krig[,1,],col=heat.colors(300))
-legend(grconvertX(0.5, "device"), grconvertY(1, "device"), 
-     c("0",".5","1"), fill = heat.colors(300)[c(1, 200,300)], xpd = NA)
-image(gridprop2krig[,1,],col=heat.colors(300))
-legend(grconvertX(0.5, "device"), grconvertY(1, "device"), 
-     c("0",".5","1"), fill = heat.colors(300)[c(1, 200,300)], xpd = NA)
-gridprop3krig<-1-gridprop2krig-gridprop1krig
-image(gridprop3krig[,1,],col=heat.colors(300))
-legend(grconvertX(0.5, "device"), grconvertY(1, "device"), 
-     c("0",".5","1"), fill = heat.colors(300)[c(1 , 200,300)], xpd = NA)
-```
-test
-```{r}
-gridprop1krig[gridprop1krig>1]
-gridprop2krig[gridprop2krig>1]
-gridprop1krig[gridprop1krig<0]
-gridprop2krig[gridprop2krig<0]
-```
-
-```{r}
-library(mvtnorm)
-```
-we also need to correct when proportions are higher than one
-```{r}
-gridprop1krig[gridprop1krig>1]=1
-gridprop2krig[gridprop2krig>1]=1
-gridprop1krig[gridprop1krig<0]=0
-gridprop2krig[gridprop2krig<0]=0
-```
-
-Ok now we can compute the corresponding thresholds for the simulation
-
-we have no correlation between the Gaussian random functions, we have thus a simplification and can directly compute q2, with no approximation
-```{r}
-n=dim(gridprop1)
-q1tottest=q2tottest=array(NA,c(100,2,566))
-Sigma1 = matrix(c(1,rho,rho,1),2,2)
-for (x in 1:n[1]){
-  for(y in 1:n[2]){
-    for( z in 1:n[3]){
-      q1tottest[x,y,z]=qnorm(gridprop1krig[x,y,z])
-      if (gridprop3krig[x,y,z]!=0) {
-      q2tottest[x,y,z]=qnorm(1-(gridprop2krig[x,y,z]/(1-gridprop1krig[x,y,z])))
-      }
-      else{q2tottest[x,y,z]=-Inf}
-    }
-  }
-}
-image(q1tottest[,1,],col=heat.colors(300))
-legend(grconvertX(0.5, "device"), grconvertY(1, "device"), 
-     c("-Inf","0","Inf"), fill = heat.colors(300)[c(1, 150,300)], xpd = NA)
-image(q2tottest[,1,],col=heat.colors(300))
-legend(grconvertX(0.5, "device"), grconvertY(1, "device"), 
-     c("-Inf","0","Inf"), fill = heat.colors(300)[c(1, 150,300)], xpd = NA)
-```
-we can check that the threshods on the final grid are equivalent to the one originally computed on the logs
-```{r}
-q1[1,1]
-q1tottest[5,1,1]
-q2[1,1]
-q2tottest[5,1,1]
-```
-
-Once the thresholds are computed, we can do the simulation (unconditional for now)
-
-```{r}
-rv1=5
-rv2=5
-rh=800
-b1=0
-b2=0
-rho=0
-Y1<-sim3d(rv1,rh,rh,b1,100,0.1,566,20,100,20,2)
-Y2<-sim3d(rv2,rh,rh,b2,100,0.1,566,20,100,20,2)
-fac<-Y1
-fac[]=3
-fac[Y1<q1tottest]=1
-fac[Y1>q1tottest & Y2>q2tottest]=2
-image(grid[,1,],col=c("darkslategray4","burlywood2","brown3"))
-image(fac[,1,],col=c("darkslategray4","burlywood2","brown3"))
-image(fac[,2,],col=c("darkslategray4","burlywood2","brown3"))
-```
-ok let's now do a conditional simulation
-for the gibbs sampling we dont need the kriged proportions
-
-```{r}
-env_lat[is.na(env_lat)]=Inf # with 0, the gibbs sampler will find random values
-grid<-array(NA,c(100,2,566))
-grid[5,1,]<-env_lat[,1]
-grid[15,1,]<-env_lat[,2]
-grid[25,1,]<-env_lat[,3]
-grid[35,1,]<-env_lat[,4]
-grid[45,2,]<-env_lat[,5]
-grid[55,1,]<-env_lat[,6]
-grid[65,1,]<-env_lat[,7]
-grid[75,1,]<-env_lat[,8]
-grid[99,1,]<-env_lat[,9]
-i1grid<-grid
-i1grid[grid==2]=0
-i1grid[grid==3]=0
-image(i1grid[,1,])
-q1map<-array(NA,c(100,2,566))
-q1map[5,1,]<-q1[,1]
-q1map[15,1,]<-q1[,2]
-q1map[25,1,]<-q1[,3]
-q1map[35,1,]<-q1[,4]
-q1map[45,2,]<-q1[,5]
-q1map[55,1,]<-q1[,6]
-q1map[65,1,]<-q1[,7]
-q1map[75,1,]<-q1[,8]
-q1map[99,1,]<-q1[,9]
-
-Y1gibbs<-gibbs_sampling_map(i1grid,q1map,0.1,20,10,rv1,rh,rh,b1,3)
-image(Y1gibbs[,1,])
-
-image(i1grid[,1,])
-image(Y1gibbs[,1,])
-image(q1map[,1,])
-```
-test
-```{r}
-test<-gibbs_sampling_map(i1grid,q1map,0.1,20,10,rv1,rh,rh,b1,1)
-image(test[,1,],col=heat.colors(300))
-```
-
-```{r}
-i3grid<-grid
-i3grid[grid==1]=Inf
-i3grid[grid==3]=1
-i3grid[grid==2]=0
-q2map<-array(NA,c(100,2,566))
-q2map[5,1,]<-q2tottest[5,1,]
-q2map[15,1,]<-q2tottest[15,1,]
-q2map[25,1,]<-q2tottest[25,1,]
-q2map[35,1,]<-q2tottest[35,1,]
-q2map[45,2,]<-q2tottest[45,2,]
-q2map[55,1,]<-q2tottest[55,1,]
-q2map[65,1,]<-q2tottest[65,1,]
-q2map[75,1,]<-q2tottest[75,1,]
-q2map[99,1,]<-q2tottest[99,1,]
-
-Y2gibbs<-gibbs_sampling_map(i3grid,q2map,0.1,20,10,rv2,rh,rh,b2,3)
-image(Y2gibbs[,1,])
-test<-Y2gibbs
-test[Y2gibbs<q2map]=1
-test[Y2gibbs>q2map]=0
-image(test[,1,])
-image(i3grid[,1,])
-image(Y2gibbs[,1,])
-```
-
-now that we have the gibbs sampling, we need to krig the difference with the unconditional simulation
-
-```{r}
-E1=Y1gibbs-Y1
-E2=Y2gibbs-Y2
-E1k<-prop_kriging(E1,rh,20,20,0.1)
-E2k<-prop_kriging(E2,rh,20,20,0.1)
-Y1c=Y1+E1k
-Y2c=Y2+E2k
-facc<-Y1c
-facc[]=3
-facc[Y1c<q1tottest]=1
-facc[Y1c>q1tottest & Y2c>q2tottest]=2
-image(facc[,1,],col=c("darkslategray4","burlywood2","brown3"))
-image(grid[,1,],col=c("darkslategray4","burlywood2","brown3"))
-image(E1k[,1,],col=heat.colors(300))
-image(E2k[,1,],col=heat.colors(300))
-```
-
-ok now we can look at the diagenesis, we do it separately because in this example,
-the Gaussian function representing the diagenesis is not correlated to the Gaussian functions of the depositional facies
+and the diagenesis
 ```{r}
@@
 
-load the diagenesis
+load the diagenesis data 
 ```{r}
@@
 ```
+we suppose that the diagenetic facies have a non stationarity only resuting from the non stationarity of the depositional facies
 
-simulation now with diagenesis! 
-we first need to compute the relative proportions
+we compute the relative proportions of diagenesis in depositional facies
 ```{r}
@@
 
-now we need to find the thresholds
+now we need to find the corresponding thresholds
 given that d1 is only found in e2, its threshold is computed with its general proportion
@@
 ```
-Now I can do the simulation, with in mind that I also need to condition it! 
-but it should be simpler than previously. 
-I still need to rewrite the gibbs sampling for that new truncation rule
-```{r}
-dgrid<-array(NA,c(100,2,566))
-diag_lat[is.na(diag_lat)]=Inf
-dgrid[5,1,]=diag_lat[,1]
-dgrid[15,1,]<-diag_lat[,2]
-dgrid[25,1,]<-diag_lat[,3]
-dgrid[35,1,]<-diag_lat[,4]
-dgrid[45,2,]<-diag_lat[,5]
-dgrid[55,1,]<-diag_lat[,6]
-dgrid[65,1,]<-diag_lat[,7]
-dgrid[75,1,]<-diag_lat[,8]
-dgrid[99,1,]<-diag_lat[,9]
-Y3gibbs<-gibbs_sampling_diag2(grid,dgrid,c(qd1e2,qd2e2,qd2e3),0.1,20,10,rv2,rh,rh,b2,3)
-image(Y3gibbs[,1,])
-facdg<-Y3gibbs
-facdg[!is.na(facdg)]=3
-facdg[ grid==2 & Y3gibbs<qd2e2 & Y3gibbs>qd1e2]=1
-facdg[ grid==2 & Y3gibbs>qd2e2 ]=2
-facdg[ grid==3 & Y3gibbs>qd2e3 ]=2
-image(facdg[,1,],col=c("green","yellow","black"))
-image(dgrid[,1,],col=c("green","yellow","black"))
-```
+Now I can do the simulation
+The gibbs sampling is different that in the Latemar because the truncation rule is different and adptative
 
-```{r}
-Y3<-sim3d(rv2,rh,rh,b2,100,0.1,566,20,100,20,2)
-```
-```{r}
-E3=Y3gibbs-Y3
-E3k<-prop_kriging(E3,rh,20,20,0.1)
-Y3c=Y3+E3k
-facd<-Y3c
-facd[]=3
-facd[ facc==2 & Y3c<qd2e2 & Y3c>qd1e2]=1
-facd[ facc==2 & Y3c>qd2e2 ]=2
-facd[ facc==3 & Y3c>qd2e3 ]=2
-image(x=(1:100)*200,y=(1:566)/10,z=im[,1,],col=c("darkslategray4","burlywood2","brown3","green","yellow","black"),xlab="Lateral distance (m)",ylab="Vertical distance (m)")
-image(facd[,1,],col=c("green","yellow","black"))
-fac_comb=facc
-fac_comb[facc==2 & Y3c<qd2e2 & Y3c>qd1e2]=4
-fac_comb[facc==2 & Y3c>qd2e2 ]=5
-fac_comb[facc==3 & Y3c>qd2e3 ]=5
-image(facc[,1,],col=c("darkslategray4","burlywood2","brown3"))
-image(fac_comb[,1,],col=c("darkslategray4","burlywood2","brown3","green","yellow"))
-```
-Now that it is working, we can make a beautiful simulation in three dimensions
 ```{r}
@@
 
+# now that we have the proportions, we can compute the corresponding thresholds
+# because there are no correlations between the gaussian functions, the thresholds can be computed analytically
 n=dim(gridprop1)
@@
 
+# simulation
 rv1=5

### 2018-10-16 main_bookcliff.Rmd
finished cleaning

@@
 now we need to find the corresponding thresholds
-given that d1 is only found in e2, its threshold is computed with its general proportion
-but this is not the case for d2
+given that d1 is only found in e2, its threshold is computed according to its proportion in this facies
+but this is not the case for d2 which is present in e2 and e3
 we need first to compute the thresholds of d2 because will impact threshold of d1
@@
 ```
-Now I can do the simulation
+Now the simulation is performed
 The gibbs sampling is different that in the Latemar because the truncation rule is different and adptative
@@
 n=dim(gridprop1)
+# local proportions of depositional facies
 gridprop1<-gridprop2<-err<-array(NA,c(100,20,566))
@@
 gridprop1[99,10,]<-prop1mat[,9]
-#gridprop1[is.na(grid)]=NA
+
 gridprop2[5,10,]<-prop2mat[,1]
@@
 gridprop2[99,10,]<-prop2mat[,9]
-#gridprop2[is.na(grid)]=NA
+
+# detrend the local proportions by the global proportion before the kriging
 gridprop3=1-gridprop1-gridprop2
@@
 gridprop2=gridprop2-p2
+#kriging
 gridprop1krig<-prop_kriging(gridprop1,500,20,20,0.1)
 gridprop2krig<-prop_kriging(gridprop2,500,20,20,0.1)
-# we are trying here to have the same proportions on every y plane (because no information on them but still want non sationarity)
+
+# we put the same proportions on every y plane (because no information in this direction)
 for (y in 1:20){
@@
 gridprop2krig=gridprop2krig+p2
-gridprop3krig=1-gridprop1krig-gridprop2krig # there is a problem  here to solve
+gridprop3krig=1-gridprop1krig-gridprop2krig 
 for (x in 1:n[1]){
@@
 
-# now that we have the proportions, we can compute the corresponding thresholds
+# now that we have the proportions, we can compute the corresponding thresholds defined by the truncation rule
 # because there are no correlations between the gaussian functions, the thresholds can be computed analytically
@@
 
+# the Gibbs sampling for the different Gaussian functions can be done separately
+# because there are no correlations between them
 Y1gibbs<-gibbs_sampling_map(i1grid,q1map,0.1,20,10,rv1,rh,rh,b1,3)
@@
 E2=Y2gibbs-Y2
+# kriging the error between unconditional and conditional simulation at data points
 E1k<-prop_kriging(E1,rh,20,20,0.1)
@@
 facc<-Y1c
+# truncation of the conditioned Gaussian functions
 facc[]=3
@@
 image(E2k[,10,],col=heat.colors(300))
+
+#now diagenesis, separately because Gaussian functions not correlated
 dgrid<-array(NA,c(100,20,566))
@@
 
+#final truncation
 image(facd[,10,],col=c("green","yellow","black"))

### 2018-10-16 cosim_functions.R
added 2d simulation
useful for island code

@@ -20,6 +20,23 @@ embedded3d<-function(datai,dataj){
   return(embed/Tii) 
 }
 
+sim2d<-function(rv,rh,freq,N,dz,nz,dx,nx){
+  phase <- runif(N,0,2*pi)
+  bin <- sample(c(-1,1),N,replace=T)
+  w1 <- rnorm(N, mean = freq , sd = sqrt(2)/rv)
+  w2 <- rnorm(N, mean = 0 , sd = sqrt(2)/rh)
+  sim<-array(0,c(nx,nz))
+  for(i in 1:N){
+    for ( z in 1:nz){
+      for(x in 1:nx){
+        sim[x,z] = sim[x,z] + cos(bin[i]*w1[i]*(z*dz)+w2[i]*x*dx+phase[i])
+      }
+    }
+  }
+  sim = sim *sqrt(2/N)
+  
+  return(sim)
+}
 
 # unconditional simulation of a gaussian function with Gaussian cosine covariance
 sim3d<-function(rv,rhx,rhy,freq,N,dz,nz,dx,nx,dy,ny){

### 2018-10-16 nonstation_functions.R
comments

@@ -175,6 +175,7 @@ truncnorm<-function(qmin,qmax,mean,sd){
   return(a)
 }
 
+# gibbs sampling with adaptive truncation rule
 gibbs_sampling_map<-function(grid,qmap,dz,dhx,dhy,rv,rhx,rhy,b,it){
   # this algorithm is based on Emery paper (2013); algorithm 7
   
@@ -190,7 +191,7 @@ gibbs_sampling_map<-function(grid,qmap,dz,dhx,dhy,rv,rhx,rhy,b,it){
   inv <- which(c_data <0)
   #initialization uncorrelated gaussian simulation inside the interval
   undsim = rnorm(1,0,1)
-  negsim= negrnorm(q[1],0,1) # we do this so that values do not start completely randomly
+  negsim= negrnorm(q[1],0,1)
   possim= posrnorm(q[1],0,1)
   sim<-rep(0,n)
   for ( i in 1:n){
@@ -213,7 +214,7 @@ gibbs_sampling_map<-function(grid,qmap,dz,dhx,dhy,rv,rhx,rhy,b,it){
   # gibbs sampling
   for( t in 1:it){
     for ( i in 1:n){
-      condi<-(((q-sim)/c_data[i,])+sim[i])
+      condi<-(((q-sim)/c_data[i,])+sim[i]) # the thresholds q are different at every location of the grid according to the proportions
       maxi=Inf
       mini=-Inf
       for ( j in 1:n){

### 2018-11-13 main_latemar.Rmd
updated functions path

@@
 ```{r}
-source("C:/Users/tl3315/Desktop/GitHub/CyclicPGS/co_sim_condi.R")
-source("C:/Users/tl3315/Desktop/GitHub/CyclicPGS/cosim_functions.R")
+source("co_sim_condi.R")
+source("cosim_functions.R")
 ```
